### 2021-04-19 Scripts/spatial_analisis.Rmd
Got the interpolation rolling

---
title: "Spatial Analysis"
output: html_notebook
---

```{r setup, include=FALSE}
MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps"))
```

# Load data

## Ocean adapt data

```{r dat_exploded, eval = T, echo = T}

ocean_data <- readRDS("/Volumes/Enterprise/Data/pinskylab-OceanAdapt-966adf0/data_clean/dat_exploded.rds") %>% 
  filter(spp == "Centropristis striata",
       region %in% c("Northeast US Fall" , "Northeast US Spring")) #No more seasons

```

## Maps data

```{r maps_sf, eval = F, echo = T, results = 'hide'}

us_map <- st_as_sf(map("state", plot = FALSE, fill = TRUE))

# path_world <- MyFunctions::my_path("G", extra_path = "Spatial/SAU/SAU_Shapefile")
path_world <- "~/Downloads/SAU_Shapefile"

# The File
fnam_world <- "SAUEEZ_July2015.shp"

# Load it!
World_eez_sf <- st_read(dsn = path_world,
                        layer =file_path_sans_ext(fnam_world)) %>% 
  rename(eez_name = Name) %>% 
  st_transform(crs = 4326) %>% # 4326
  # st_transform(crs = "+proj=eck4") %>% # for tbular plot
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
  filter(eez_name == "USA (East Coast)")

```

### Map of smapling points

In this case the color gradient represents wtcpue (wet tones catch per unit of effort, haul hours) from 1972 to 2019. Grey dots represent `wtcpue = 0`

```{r survey_map, eval = T, echo = T, fig.width = 12, fig.height = 8}

ggplot(us_map) +
  geom_sf() +
  geom_sf(data = World_eez_sf, aes(), fill = "white") +
  geom_point(data = subset(ocean_data, wtcpue = 0),
             aes(
               x = lon,
               y = lat
             ),
             color = "grey95",
             size = 1
  ) +
  geom_point(data = subset(ocean_data, wtcpue > 0),
             aes(
               x = lon,
               y = lat,
               color = log10(wtcpue)
             ),
             size = 1
  ) +
  scale_color_distiller(palette = "Spectral", 
                       guide_legend(title = "WCPUE per Haul (log10)")) + 
  coord_sf(xlim = c(-76, -65),ylim = c(35, 45)) +
  MyFunctions::my_ggtheme_m() +
  facet_wrap(~region)

```

# Interpolation

## SF example A

https://swilke-geoscience.net/post/spatial_interpolation/

```{r interpolation, eval = T, echo = T}

subset_data <- ocean_data %>% 
  filter(region == "Northeast US Spring",
         wtcpue > 0) %>% 
  group_by(lon,lat) %>% 
  summarise(wtcpue = sum(wtcpue,na.rm = T))

# First let's define a bounding Box to extrapolate from
bbox <- c(
  "xmin" = min(subset_data$lon),
  "ymin" = min(subset_data$lat),
  "xmax" = max(subset_data$lon),
  "ymax" = max(subset_data$lat)
)

# Expand the grid
grd_template <- expand.grid(
  lon = seq(from = bbox["xmin"], to = bbox["xmax"], by = 0.5),
  lat = seq(from = bbox["ymin"], to = bbox["ymax"], by = 0.5)
)

# ---------------- #
# Visualize the box

# ggplot() +
#   geom_point(data = grd_template, aes(x = lon, y = lat), size = 0.1) +
#   geom_point(data = subset_data,
#   mapping = aes(x = lon, y = lat, color = wtcpue), size = 3) +
#   scale_color_gradientn(colors = c("blue", "yellow", "red")) +
#   theme_bw()

# ---------------- #

# Rasterize our grid
# expects a PROJ.4 string, see https://epsg.io/25833

crs_raster_format <- "+proj=longlat +datum=WGS84 +no_defs"

grd_template_raster <- grd_template %>% 
  dplyr::mutate(Z = 0) %>% 
  raster::rasterFromXYZ( 
    crs = crs_raster_format)

# The model

# Triangular Irregular Surface
fit_tin <- interp::interp( # using {interp}
  x = subset_data$lon,           # the function actually accepts coordinate vectors
  y = subset_data$lat,
  z = subset_data$wtcpue,
  xo = grd_template$lon,     # here we already define the target grid
  yo = grd_template$lat,
  output = "points"
) %>% 
  bind_cols() %>% 
  filter(!is.na(z))

ggplot(us_map) +
  geom_sf()+
  geom_sf(data = World_eez_sf, aes(), fill = "white")+
  geom_tile( data = fit_tin,
             aes(
               x = x,
               y = y,
               fill =z,
               colour = z
             )
  ) +
  geom_point(data = subset(subset_data, wtcpue > 0),
             aes(
               x = lon,
               y = lat
             ),
             alpha = 0.2
  ) +
  scale_color_distiller(palette = "Spectral", 
                        guide_legend(title = "WCPUE per Haul")) + 
  scale_fill_distiller(palette = "Spectral", 
                       guide_legend(title = "WCPUE per Haul")) +
  coord_sf(xlim = c(-76, -65),ylim = c(35, 45)) +
  MyFunctions::my_ggtheme_m()

```

### 2021-04-19 Allocation_tool/server.R
included a basin flow

@@ -7,20 +7,137 @@
 #    http://shiny.rstudio.com/
 #
 
-library(shiny)
+MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","DT"))
+
+us_map <- st_as_sf(map("state", plot = FALSE, fill = TRUE))
+
 
 # Define server logic required to draw a histogram
 shinyServer(function(input, output) {
-
-    output$distPlot <- renderPlot({
-
-        # generate bins based on input$bins from ui.R
-        x    <- faithful[, 2]
-        bins <- seq(min(x), max(x), length.out = input$bins + 1)
-
-        # draw the histogram with the specified number of bins
-        hist(x, breaks = bins, col = 'darkgray', border = 'white')
-
+    
+    datasetInput <- reactive({
+        
+        data <- readRDS("/Volumes/Enterprise/Data/pinskylab-OceanAdapt-966adf0/data_clean/dat_exploded.rds") %>% 
+            filter(spp %in% c ("Centropristis striata","Gadus morhua"),
+                   region %in% c("Northeast US Fall" , "Northeast US Spring")) #No more seasons
+        
     })
-
+    
+    # Main plot
+    output$distPlot <- renderPlot({
+        
+        # Set the filters
+        species <- input$SppSelection
+        # species <- c("Centropristis striata","gadus morhua")
+        # survey <- c("Northeast US Fall" , "Northeast US Spring")
+        survey <- input$SurveySelection
+        # years <- input$YearSelection
+        
+        # Set the plot data
+        plot_data <- data %>%
+            filter(spp %in% species,
+                   region %in% survey)#,
+        # year %in% years)
+        
+        # Density map
+        if(input$PlotStyle == 2){
+            
+            # Set manual breaks for bins
+            bins <- seq(1970,2020,10)
+            
+            map_data <- plot_data %>%
+                group_by(spp,year,lat,lon,depth) %>%
+                summarise_if(is_numeric,mean,na.rm=T) %>%
+                mutate(
+                    year = as.numeric(year),
+                    period = cut(year, breaks = bins)
+                ) %>%
+                group_by(period,lat,lon) %>%
+                summarise_if(is.numeric,mean,na.rm=T) %>%
+                filter(wtcpue>0)
+            
+            
+            ggplot(us_map) +
+                geom_sf() +
+                stat_density_2d(data = map_data, geom = "polygon",
+                                aes(x = lon, y = lat, fill = ..level..)) +
+                geom_point(data = map_data,
[…]

### 2021-04-19 Allocation_tool/ui.R

@@ -7,7 +7,13 @@
 #    http://shiny.rstudio.com/
 #
 
-library(shiny)
+# Load libraries and data
+MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny"))
+
+spp_survey <- read.csv("./data/spp_region.csv") %>% 
+    filter(spp %in% c ("Centropristis striata","Gadus morhua"),
+           region %in% c("Northeast US Fall" , "Northeast US Spring")) #No more seasons
+    
 
 # Define UI for application that draws a histogram
 shinyUI(fluidPage(
@@ -21,14 +27,14 @@ shinyUI(fluidPage(
             # Select which Gender(s) to plot
             checkboxGroupInput(inputId = "SurveySelection",
                                label = "Select Survey(s)",
-                               choices = c("Fall" = "M", "Summer" = "F"),
-                               selected = "Fall"),
+                               choices = unique(spp_survey$region)#,
+                               # selected = "Fall"
+                               ),
             # Select Species
             selectInput(inputId = "SppSelection",
                         label = "Select Species",
-                        # choices = levels(Species),
-                        choices = c("Black Sea Bass","Y. Flounder","Spp"),
-                        selected = "Balck Sea Bass",
+                        choices = unique(spp_survey$spp),
+                        # selected = "Balck Sea Bass",
                         width = "220px"
             ),
             # Set Time Range
@@ -40,27 +46,29 @@ shinyUI(fluidPage(
             # Choose the years you want to plot
             sliderInput(inputId = "YearSelection",
                         label = "Select Year Range",
-                        min = 1971,
-                        max = 2015,
+                        min = 1972,
+                        max = 2019,
                         step = 1,
                         sep = "",
                         animate = FALSE,
-                        value = c(1971,2015),
+                        value = c(1972,2019),
                         width = "220px"),
         # Select which plot you want to create
         checkboxGroupInput(inputId = "PlotStyle",
-                           label = "Select Result(s)",
-                           choices = c("Allocation Area" = "M", 
-                                       "Survey Point" = "F", 
-                                       "Distribution Map" = "F",
-                                       "Distribution Point" = "g",
-                                       "States' Table" = "ST"),
-                           selected = "ST")
+                           label = "Select Result",
+                           choices = c("Survey Point" = 1, 
+                                       "Distribution Map" = 2,
+                                       "Allocation Area" = 3),
[…]

### 2021-04-19 Scripts/ocean_adapt_exploration.Rmd
some exploration

---
title: "Ocean adapt exploration script"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps"))
```

# Ocean adapta data

```{r basic_exploratin, eval = F, echo = F}

head(by_species)
names(by_species)
unique(by_species$spp)
unique(by_species$region)
max(by_species$year)
min(by_species$year)

```

## By species data exploration

- for each region, year, species combination, the mean location and biomass, shows species averages.

```{r by_species_data, eval = T, echo = T}

by_species <- read_csv(here::here("data_clean/by_species.csv"))

head(by_species)

by_species %>% 
  filter(spp == "Centropristis striata",
         region %in% c("Northeast US Fall" , "Northeast US Spring")
         )

```

```{r plot_by_species, eval = T, echo = T, message = F, warning = F}

suppressWarnings(
  by_species %>% 
    filter(spp == "Centropristis striata",
           region %in% c("Northeast US Fall" , "Northeast US Spring")) %>% 
    group_by(spp,year,lat,lon,depth) %>%
    summarise_if(is_numeric,mean) %>%
    ggplot() +
    geom_point(
      aes(
        x = lon,
        y = lat,
        fill = as.numeric(year),
        col = as.numeric(year)
      )
    )
)
```

## By species data exploration

- for every region and year, all of the species for that region, including zeros if they were not present.

```{r dat_exploded, eval = T, echo = T}

dat_exploded <- readRDS("/Volumes/Enterprise/Data/pinskylab-OceanAdapt-966adf0/data_clean/dat_exploded.rds") %>% 
  filter(spp == "Centropristis striata",
         region %in% c("Northeast US Fall" , "Northeast US Spring")) #No more seasons

head(dat_exploded)

```

O.K. so now we have a `wtcpue` column here. Lets now get some data wrangling going and exploration figures

### Survey plots

```{r plot_data, eval = T, echo = T, fig.width = 12, fig.height = 8}

plot_data <- dat_exploded %>% 
  group_by(spp,year,lat,lon,depth) %>%
  summarise_if(is_numeric,mean,na.rm=T) %>%
  mutate(
    year = as.numeric(year)
  )

```

#### Histogram of data points

```{r histogram, eval = T, echo = T}

plot_data %>% 
  filter(wtcpue < 10,
         wtcpue >0) %>% #remove THAT one outlier
  mutate(depth = depth*-1) %>% 
  gather("variable","value",depth:wtcpue) %>% 
  # View(.)
    ggplot() +
    geom_histogram(
      aes(
        x = value,
      ),
      binwidth = 1
    ) +
  facet_wrap(~variable,
             ncol = 1,
             scales = "free_x")

```

#### Timeline of depth and wtcpue

```{r timeline, eval = T, echo = T}

plot_data %>% 
  # filter(wtcpue < 200) %>% #remove THAT one outlier
  mutate(depth = depth*-1) %>%
  gather("variable","value",depth:wtcpue) %>% 
  mutate(lat_round = round(lat)) %>% 
  group_by(variable,year,lat_round) %>% 
  summarise_at(vars(value),sum) %>% 
  # View(.)
    ggplot() +
    geom_line(
      aes(
        x = year,
        y = value,
        col = as.factor(lat_round)
      )
    ) +
  facet_wrap(~variable,
             ncol = 1,
             scales = "free_y") +
  MyFunctions::my_ggtheme_p()

```

#### Boxplot of data

```{r boxplot, eval = T, echo = T}

plot_data %>% 
  # filter(wtcpue < 200) %>% #remove THAT one outlier
  mutate(depth = depth*-1) %>%
  gather("variable","value",depth:wtcpue) %>% 
  mutate(lat_round = round(lat)) %>% 
    ggplot() +
    geom_boxplot(
      aes(
        x = as.factor(lat_round),
        y = value
        # fill = as.factor(year)
      )
    ) +
  facet_wrap(~variable,
             # ncol = 2,
             scales = "free")

```

```{r time_line_facet, eval = T, echo = T}

# Set manual breaks for bins
bins <- seq(1970,2020,10)

plot_data %>% 
  # filter(wtcpue < 200) %>% #remove THAT one outlier
  mutate(depth = depth*-1) %>%
  gather("variable","value",depth:wtcpue) %>% 
  mutate(lat_round = round(lat),
         period = cut(year, breaks = bins)) %>% 
  group_by(variable,year,period,lat_round) %>% 
  summarise_at(vars(value),sum,na.rm=T) %>% 
  # View(.)
    ggplot() +
    geom_line(
      aes(
        x = year,
        y = value#,
        # col = ,
        # fill = as.factor(year)
      )
    ) +
  facet_wrap(~variable+lat_round,
             # ncol = 2,
             scales = "free_y")

gc()
```

### Survey maps

```{r maps_sf, eval = F, echo = T, results = 'hide'}

us_map <- st_as_sf(map("state", plot = FALSE, fill = TRUE))

path_world <- MyFunctions::my_path("G", extra_path = "Spatial/SAU/SAU_Shapefile")
path_world <- "~/Downloads/SAU_Shapefile"

# The File
fnam_world <- "SAUEEZ_July2015.shp"

# Load it!
World_eez_sf <- st_read(dsn = path_world,
                        layer =file_path_sans_ext(fnam_world)) %>% 
  rename(eez_name = Name) %>% 
  st_transform(crs = 4326) %>% # 4326
  # st_transform(crs = "+proj=eck4") %>% # for tbular plot
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
  filter(eez_name == "USA (East Coast)")

```

```{r map_data, eval = T, echo = T, fig.width = 12, fig.height = 8}

# Set manual breaks for bins
bins <- seq(1970,2020,5)

map_data <- dat_exploded %>% 
  group_by(spp,year,lat,lon,depth) %>%
  summarise_if(is_numeric,mean,na.rm=T) %>%
  mutate(
    year = as.numeric(year),
    period = cut(year, breaks = bins)
  ) %>% 
  group_by(period,lat,lon) %>% 
  summarise_if(is.numeric,mean,na.rm=T) %>% 
  filter(wtcpue>0)

```

#### Map of smapling points

In this case the color gradiant represents year from 1972 to 2019

```{r survey_map, eval = T, echo = T, fig.width = 12, fig.height = 8}

ggplot(us_map) +
  geom_sf() +
  geom_sf(data = World_eez_sf, aes(), fill = "white") +
  geom_point(data = map_data,
             aes(
               x = lon,
               y = lat,
               color = year
             ),
             size = 1
  ) +
  scale_color_distiller(palette = "Spectral", 
                       guide_legend(title = "Probability \ndensity")) + 
  coord_sf(xlim = c(-76, -65),ylim = c(35, 45)) +
  MyFunctions::my_ggtheme_m()

```

### Density map

This is a simple 2d kenell analysis using `ggplot2::stat_density_2d()` of the sampling points

Looks to me that the stock might not be shifting _per se_ but expanding its northern range

```{r density_map, eval = T, echo = T, fig.width = 12, fig.height = 8}

# Expansion of the stock
ggplot(us_map) +
  geom_sf() +
  geom_sf(data = World_eez_sf, aes(), fill = "white") +
  stat_density_2d(data = map_data, geom = "polygon", 
                  aes(x = lon, y = lat, fill = ..level..)) + 
  geom_point(data = map_data,
             aes(
               x = lon,
               y = lat
             ),
             size = 0.1
  ) +
  facet_wrap(~period,
             nrow = 2) +
  scale_fill_distiller(palette = "Spectral", 
                       guide_legend(title = "Probability \ndensity")) + 
  # viridis::scale_fill_viridis() +
  # viridis::scale_colour_viridis() +
  coord_sf(xlim = c(-76, -65),ylim = c(35, 45)) +
  MyFunctions::my_ggtheme_m()

```

### CPUE (wt CPUE) data

```{r biomass_time_map, eval = T, echo = T, fig.width = 12, fig.height = 8}

ggplot(us_map) +
  geom_sf() +
  geom_sf(data = World_eez_sf, aes(), fill = "white") +
  geom_point(data = subset(map_data, wtcpue < 100),
             aes(
               x = lon,
               y = lat,
               color = wtcpue
             ),

  ) +
  # facet_wrap(~period,
  #            nrow = 2) +
  scale_color_distiller(palette = "Spectral", 
                       guide_legend(title = "CPUE")) + 
  # viridis::scale_fill_viridis() +
  # viridis::scale_colour_viridis() +
  coord_sf(xlim = c(-76, -65),ylim = c(35, 45)) +
  MyFunctions::my_ggtheme_m()

```

# ERDDAP

This is the data extracted directly from NOAA in has four available surveys (OceanAdapt only two)

- Northeast Fisheries Science Center (NEFSC) Fall Bottom Trawl Survey	
- Northeast Fisheries Science Center (NEFSC) Spring Bottom Trawl Survey	
- Northeast Fisheries Science Center (NEFSC) Summer Bottom Trawl Survey	
- Northeast Fisheries Science Center (NEFSC) Winter Bottom Trawl Survey

- Black seabass code is 141

### 2021-04-19 Allocation_tool/server.R
Included the interpolation in the app

@@ -12,14 +12,30 @@ MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","map
 us_map <- st_as_sf(map("state", plot = FALSE, fill = TRUE))
 
 
+# First let's define a bounding Box to extrapolate from
+    bbox <- c(
+        "xmin" = -76,
+        "ymin" = 35,
+        "xmax" = -65,
+        "ymax" = 45
+    )
+
+# Expand the grid
+grd_template <- expand.grid(
+    lon = seq(from = bbox["xmin"], to = bbox["xmax"], by = 0.5),
+    lat = seq(from = bbox["ymin"], to = bbox["ymax"], by = 0.5)
+)
+
 # Define server logic required to draw a histogram
 shinyServer(function(input, output) {
     
     datasetInput <- reactive({
         
         data <- readRDS("/Volumes/Enterprise/Data/pinskylab-OceanAdapt-966adf0/data_clean/dat_exploded.rds") %>% 
-            filter(spp %in% c ("Centropristis striata","Gadus morhua"),
-                   region %in% c("Northeast US Fall" , "Northeast US Spring")) #No more seasons
+            filter(
+                # spp %in% c ("Centropristis striata","Gadus morhua"),
+                   region %in% c("Northeast US Fall" , "Northeast US Spring")
+                   ) #No more seasons
         
     })
     
@@ -28,83 +44,100 @@ shinyServer(function(input, output) {
         
         # Set the filters
         species <- input$SppSelection
-        # species <- c("Centropristis striata","gadus morhua")
-        # survey <- c("Northeast US Fall" , "Northeast US Spring")
         survey <- input$SurveySelection
         # years <- input$YearSelection
         
         # Set the plot data
-        plot_data <- data %>%
+        plot_data <- datasetInput() %>%
             filter(spp %in% species,
                    region %in% survey)#,
         # year %in% years)
         
         # Density map
-        if(input$PlotStyle == 2){
-            
-            # Set manual breaks for bins
-            bins <- seq(1970,2020,10)
-            
-            map_data <- plot_data %>%
-                group_by(spp,year,lat,lon,depth) %>%
-                summarise_if(is_numeric,mean,na.rm=T) %>%
-                mutate(
-                    year = as.numeric(year),
-                    period = cut(year, breaks = bins)
-                ) %>%
-                group_by(period,lat,lon) %>%
-                summarise_if(is.numeric,mean,na.rm=T) %>%
-                filter(wtcpue>0)
-            
[…]

### 2021-04-19 Allocation_tool/ui.R

@@ -11,7 +11,8 @@
 MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny"))
 
 spp_survey <- read.csv("./data/spp_region.csv") %>% 
-    filter(spp %in% c ("Centropristis striata","Gadus morhua"),
+    filter(
+        # spp %in% c ("Centropristis striata","Gadus morhua"),
            region %in% c("Northeast US Fall" , "Northeast US Spring")) #No more seasons
     
 

### 2021-04-26 Allocation_tool/server.R
included extrapolation method in plot title

@@ -41,7 +41,6 @@ shinyServer(function(input, output) {
     
     # Main plot
     output$distPlot <- renderPlot({
-        
         # Set the filters
         species <- input$SppSelection
         survey <- input$SurveySelection
@@ -79,6 +78,7 @@ shinyServer(function(input, output) {
                 coord_sf(xlim = c(-76, -65),ylim = c(35, 45)) +
                 MyFunctions::my_ggtheme_m() +
                 facet_wrap(~region)
+                
             
         }else{
             
@@ -111,6 +111,7 @@ shinyServer(function(input, output) {
                     filter(!is.na(z))
                 
                 # The actual map
+                
                 ggplot(us_map) +
                     geom_sf()+
                     geom_tile( data = fit_tin,
@@ -134,9 +135,9 @@ shinyServer(function(input, output) {
                                          guide_legend(title = "WCPUE per Haul")) +
                     coord_sf(xlim = c(-76, -65),ylim = c(35, 45)) +
                     
-                    MyFunctions::my_ggtheme_m()
+                    MyFunctions::my_ggtheme_m() +
+                    ggtitle("Distribution estimated by using Triangular Irregular Surface method")
                 
-
             }
         }
         

### 2021-04-26 Allocation_tool/ui.R
Inlcuded project intro

@@ -18,10 +18,48 @@ spp_survey <- read.csv("./data/spp_region.csv") %>%
 
 # Define UI for application that draws a histogram
 shinyUI(fluidPage(
-
+    tabPanel("Home",
+             fluidRow(
+                 column(
+                     12,
+                     align = "center",
+                     h1("Managing across boundaries: preventing interjurisdictional conflicts arising from shifting fish stocks"),
+                 ),
+                 br(),
+                 column(
+                     10,
+                     align = "justified",
+                     offset = 2,
+                     p(h3("The project")),
+                     p(
+                         "To develop and test a scientific tool for evaluating policy options for managing fish stocks that are shifting across management boundaries, and to assess the socio-economic benefits and tradeoffs of these options for two important fisheries in the U.S. Mid-Atlantic."
+                     )
+                 ),
+                 column(
+                     10,
+                     align = "justified",
+                     offset = 2,
+                     p(strong(h4("PROJECT PARTNERS"))),
+                     p("Arielle Levine, San Diego State University (Prospective Grantee)"),
+                     p("Rod Fujita, Environmental Defense Fund (Project Director)"),
+                     p("Katie Longo, Marine Stewardship Council"),
+                     p("Olaf Jensen, University of Wisconsin, Madison"),
+                     p("Lisa Wainger, University of Maryland Center for Environmental Science"),
+                     p("Ellen Bolen, Virginia Marine Resources Commission"),
+                     p("Scott Crosson, NOAA"),
+                     p("Juliano Palacios-Abrantes, University of Wisconsin, Madison")
+                 )
+             ) # close fluid row
+    ), # tabPanel close
     # Application title
-    titlePanel("Stock allocation formula"),
-
+    tabPanel("Stock allocation formula",
+             br(),
+             br(),
+             column(
+                 12,
+                 align = "justified",
+                 h3("Stock allocation formula"),
+             ),
     # Sidebar with a slider input for number of bins
     sidebarLayout(
         sidebarPanel(
@@ -35,7 +73,7 @@ shinyUI(fluidPage(
             selectInput(inputId = "SppSelection",
                         label = "Select Species",
                         choices = unique(spp_survey$spp),
-                        # selected = "Balck Sea Bass",
+                        selected = "Centropristis striata",
                         width = "220px"
             ),
             # Set Time Range
@@ -71,5 +109,6 @@ shinyUI(fluidPage(
             p(h4(strong("Allocation Table"))),
             dataTableOutput("Allocation_tbl")
         )
+    )
     )
 ))

### 2021-04-26 Scripts/spatial_analisis.Rmd
exploring border extrapolation

@@
 
-us_map <- st_as_sf(map("state", plot = FALSE, fill = TRUE))
+us_map <- st_as_sf(map("state", plot = FALSE, fill = TRUE)) %>% 
+  filter(ID %in% c("maine", "new hampshire", "massachusets", "connecticut", "rhode island", "new york", "new jersey", "delaware", "maryland", "virginia", "north carolina"))
 
@@
   filter(eez_name == "USA (East Coast)")
+
+# US state waters
+# https://www.fisheries.noaa.gov/inport/item/39963
+
+path_world <- MyFunctions::my_path("D", extra_path = "Spatial/USMaritimeLimitsAndBoundariesSHP")
+path_world <- "~/Desktop/GAFBorders"
+
+# The File
+fnam_world <- "Statistical_Areas_2010_withNames.shp"
+
+# Load it!
+us_sf <- st_read(dsn = path_world,
+                        layer =file_path_sans_ext(fnam_world)) %>% 
+  st_transform(crs = 4326) %>% # 4326
+  janitor::clean_names() %>% 
+  # st_transform(crs = "+proj=eck4") %>% # for tbular plot
+  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) #%>% 
+  # filter(region == "Atlantic Coast and Gulf of Mexico")
+  # filter(name %in% c("Maine", "Vermont", "New Hampshire", "Massachusets", "Connecticut", "rhode island", "new york", "new jersey", "delaware", "maryland", "virginia", "north carolina", "south carolina", "georgia", "florida", "pennsylvania"))
+
+us_sf$full_name
+
+ggplot(us_sf) +
+  geom_sf(aes(fill = nafodiv)) +
+  geom_sf(data =  us_map,aes()) +
+  coord_sf(xlim = c(-76, -65),ylim = c(35, 45))
+
+us_map %>% 
+  ggplot() +
+  geom_sf(aes(fill = ID)) +
+  # geom_sf(data =  us_map,aes()) +
+  coord_sf(xlim = c(-76, -65),ylim = c(35, 45))
+
+st_intersects(us_map)
+
+```
+
+### Exploring spatial regions
+
+```{r}
 

### 2021-05-03 Allocation_tool/ui.R
Splitted tool in two pages and removed warning messages

@@ -8,107 +8,125 @@
 #
 
 # Load libraries and data
-MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny"))
+MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","png"))
 
 spp_survey <- read.csv("./data/spp_region.csv") %>% 
     filter(
         # spp %in% c ("Centropristis striata","Gadus morhua"),
-           region %in% c("Northeast US Fall" , "Northeast US Spring")) #No more seasons
-    
+        region %in% c("Northeast US Fall" , "Northeast US Spring")) #No more seasons
+
+
+
 
 # Define UI for application that draws a histogram
-shinyUI(fluidPage(
-    tabPanel("Home",
-             fluidRow(
-                 column(
-                     12,
-                     align = "center",
-                     h1("Managing across boundaries: preventing interjurisdictional conflicts arising from shifting fish stocks"),
-                 ),
-                 br(),
-                 column(
-                     10,
-                     align = "justified",
-                     offset = 2,
-                     p(h3("The project")),
-                     p(
-                         "To develop and test a scientific tool for evaluating policy options for managing fish stocks that are shifting across management boundaries, and to assess the socio-economic benefits and tradeoffs of these options for two important fisheries in the U.S. Mid-Atlantic."
-                     )
-                 ),
-                 column(
-                     10,
-                     align = "justified",
-                     offset = 2,
-                     p(strong(h4("PROJECT PARTNERS"))),
-                     p("Arielle Levine, San Diego State University (Prospective Grantee)"),
-                     p("Rod Fujita, Environmental Defense Fund (Project Director)"),
-                     p("Katie Longo, Marine Stewardship Council"),
-                     p("Olaf Jensen, University of Wisconsin, Madison"),
-                     p("Lisa Wainger, University of Maryland Center for Environmental Science"),
-                     p("Ellen Bolen, Virginia Marine Resources Commission"),
-                     p("Scott Crosson, NOAA"),
-                     p("Juliano Palacios-Abrantes, University of Wisconsin, Madison")
-                 )
-             ) # close fluid row
-    ), # tabPanel close
-    # Application title
-    tabPanel("Stock allocation formula",
-             br(),
-             br(),
-             column(
-                 12,
-                 align = "justified",
-                 h3("Stock allocation formula"),
-             ),
-    # Sidebar with a slider input for number of bins
-    sidebarLayout(
-        sidebarPanel(
[…]

### 2021-05-03 Allocation_tool/ui.R
updated UI

@@ -25,108 +25,129 @@ shinyUI(
                    ".shiny-output-error { visibility: hidden; }",
                    ".shiny-output-error:before { visibility: hidden; }"
         ),
-    navbarPage(id = "MMM_Nav_Bar",
-               # Page title
-               "Across Boundaries",
-               tabPanel("About",
-                        fluidRow(
-                            column(
-                                12,
-                                align = "center",
-                                h1("Managing across boundaries: preventing interjurisdictional conflicts arising from shifting fish stocks"),
-                            ),
-                            br(),
-                            column(
-                                10,
-                                align = "justified",
-                                p(h3("The project")),
-                                p(
-                                    "The objective of this tool is to evaluate policy options for managing fish stocks that are shifting across management boundaries, and to assess the socio-economic benefits and tradeoffs of these options for two important fisheries in the U.S. Mid-Atlantic."
-                                )
-                            ),
-                            column(
-                                6,
-                                align = "justified",
-                                p(h3("Project Partners")),
-                                p("Arielle Levine, San Diego State University"),
-                                p("Rod Fujita, Environmental Defense Fund"),
-                                p("Katie Longo, Marine Stewardship Council"),
-                                p("Olaf Jensen, University of Wisconsin, Madison"),
-                                p("Ellen Bolen, Virginia Marine Resources Commission"),
-                                p("Scott Crosson, NOAA"),
-                                p("Chris Dumas, University of North Carolina Wilmington"),
-                                p("Juliano Palacios-Abrantes, University of Wisconsin, Madison")
-                            ),
-                            column(
-                                4,
-                                img(src= 'logos.png',
-                                    height = 300,
-                                    width = 500),
-                            )
-                        ) # close fluid row
-               ), # tabPanel close
-               # Application title
-               tabPanel("Stock allocation formula",
-                        fluidRow(
-                        br(),
-                        br(),
-                        column(
-                            12,
-                            align = "justified",
-                            h3("Stock allocation formula"),
-                        ),
-                        # Sidebar with a slider input for number of bins
-                        sidebarLayout(
-                            sidebarPanel(
-                                # Select which Gender(s) to plot
-                                checkboxGroupInput(inputId = "SurveySelection",
-                                                   label = "Select Survey(s)",
-                                                   choices = unique(spp_survey$region)#,
-                                                   # selected = "Fall"
+        navbarPage(id = "MMM_Nav_Bar",
+                   # Page title
+                   "Across Boundaries",
+                   tabPanel("About",
[…]

### 2021-05-03 Allocation_tool/ui.R
Included a theme and some instructions in the tool

@@ -8,7 +8,7 @@
 #
 
 # Load libraries and data
-MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","png"))
+MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny"))
 
 spp_survey <- read.csv("./data/spp_region.csv") %>% 
     filter(
@@ -20,12 +20,15 @@ spp_survey <- read.csv("./data/spp_region.csv") %>%
 
 # Define UI for application that draws a histogram
 shinyUI(
-    fluidPage( # remove shiny "red" warning messages on GUI
+    fluidPage( 
+        # remove shiny "red" warning messages on GUI
         tags$style(type="text/css",
                    ".shiny-output-error { visibility: hidden; }",
                    ".shiny-output-error:before { visibility: hidden; }"
         ),
         navbarPage(id = "MMM_Nav_Bar",
+                   # Set a theme for the tool
+                   theme = shinythemes::shinytheme("spacelab"),
                    # Page title
                    "Across Boundaries",
                    tabPanel("About",
@@ -89,12 +92,27 @@ shinyUI(
                    # Application title
                    tabPanel("Stock allocation formula",
                             fluidRow(
+                                column(
+                                    12,
+                                    align = "justified",
+                                    h1("Instructions"),
+                                    p("Wellcome to our interactive tool. In here you will be able to visualize how marine species have been
+                                      shifting, or not, along the United States East coast since 1971 to date. Please go to the Control panel
+                                      section, where you can choose the species, the survey, the time period, the allocation equation and the
+                                      type of result"),
+                                    h2("Outputs"),
+                                    p("There are currently 3 output options to choose from; Survey Point, this will return the raw survey points
+                                      from the NCSF dataset; Distribution Map, this will return a distribution map of the stock based on a 
+                                      Triangular Irregular Surface method; and Allocation Area that will produce the proportion of the stock's
+                                      distribution that each state had from the years selected. In all cases the tool will show the first and last 
+                                      5 years of data"),
+                                ),
                                 br(),
                                 br(),
                                 column(
                                     12,
                                     align = "justified",
-                                    h3("Stock allocation formula"),
+                                    h1("Control panel"),
                                 ),
                                 # Sidebar with a slider input for number of bins
                                 sidebarLayout(
@@ -142,6 +160,7 @@ shinyUI(
                                     mainPanel(
[…]

### 2021-05-03 Allocation_tool/ui.R
Changes on visualization (Renata)

@@ -85,30 +85,18 @@ shinyUI(
                                 column(
                                     12,
                                     align = "center",
-                                    h1("This project is part of the Leanfest"),
+                                    h5("This is a project funded by The Lenfest Ocean Program"),
+                                    p("Know more about the Lenfest program", a(img(src= 'logo_lenfest.jpeg',
+                                                                                   height = 30,
+                                                                                   width = 50),
+                                                                               href="https://www.lenfestocean.org/en/about-us")
+                                    )
                                 ),
                             ) # close fluid row
                    ), # tabPanel close
                    # Application title
                    tabPanel("Stock allocation formula",
                             fluidRow(
-                                column(
-                                    12,
-                                    align = "justified",
-                                    h1("Instructions"),
-                                    p("Wellcome to our interactive tool. In here you will be able to visualize how marine species have been
-                                      shifting, or not, along the United States East coast since 1971 to date. Please go to the Control panel
-                                      section, where you can choose the species, the survey, the time period, the allocation equation and the
-                                      type of result"),
-                                    h2("Outputs"),
-                                    p("There are currently 3 output options to choose from; Survey Point, this will return the raw survey points
-                                      from the NCSF dataset; Distribution Map, this will return a distribution map of the stock based on a 
-                                      Triangular Irregular Surface method; and Allocation Area that will produce the proportion of the stock's
-                                      distribution that each state had from the years selected. In all cases the tool will show the first and last 
-                                      5 years of data"),
-                                ),
-                                br(),
-                                br(),
                                 column(
                                     12,
                                     align = "justified",
@@ -120,8 +108,8 @@ shinyUI(
                                         # Select which Gender(s) to plot
                                         checkboxGroupInput(inputId = "SurveySelection",
                                                            label = "Select Survey(s)",
-                                                           choices = unique(spp_survey$region)#,
-                                                           # selected = "Fall"
+                                                           choices = unique(spp_survey$region),
+                                                           selected = "Fall"
                                         ),
                                         # Select Species
                                         selectInput(inputId = "SppSelection",
@@ -164,8 +152,33 @@ shinyUI(
                                         p(h4(strong("Allocation Table"))),
                                         dataTableOutput("Allocation_tbl")
                                     )
+                                ),
+                                br(),
+                                br(),
+                                # ----------- #
+                                # Instructions
+                                # ----------- #
+                                column(
+                                    5,
+                                    align = "justified",
+                                    h3("Instructions"),
[…]

### 2021-05-03 Allocation_tool/server.R
Inlcuded year filter and reduced grid to 0.1

@@ -7,23 +7,23 @@
 #    http://shiny.rstudio.com/
 #
 
-MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","DT"))
+MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","DT","plotly"))
 
 us_map <- st_as_sf(map("state", plot = FALSE, fill = TRUE))
 
 
 # First let's define a bounding Box to extrapolate from
-    bbox <- c(
-        "xmin" = -76,
-        "ymin" = 35,
-        "xmax" = -65,
-        "ymax" = 45
-    )
+bbox <- c(
+    "xmin" = -76,
+    "ymin" = 35,
+    "xmax" = -65,
+    "ymax" = 45
+)
 
 # Expand the grid
 grd_template <- expand.grid(
-    lon = seq(from = bbox["xmin"], to = bbox["xmax"], by = 0.5),
-    lat = seq(from = bbox["ymin"], to = bbox["ymax"], by = 0.5)
+    lon = seq(from = bbox["xmin"], to = bbox["xmax"], by = 0.1),
+    lat = seq(from = bbox["ymin"], to = bbox["ymax"], by = 0.1)
 )
 
 # Define server logic required to draw a histogram
@@ -34,27 +34,134 @@ shinyServer(function(input, output) {
         data <- readRDS("/Volumes/Enterprise/Data/pinskylab-OceanAdapt-966adf0/data_clean/dat_exploded.rds") %>% 
             filter(
                 # spp %in% c ("Centropristis striata","Gadus morhua"),
-                   region %in% c("Northeast US Fall" , "Northeast US Spring")
-                   ) #No more seasons
+                region %in% c("Northeast US Fall" , "Northeast US Spring")
+            ) #No more seasons
         
     })
+    
+    # Main plot
+    # output$distPlot <- renderPlotly({
+    #     # Set the filters
+    #     species <- input$SppSelection
+    #     survey <- input$SurveySelection
+    #     # years <- input$YearSelection
+    #     
+    #     # Set the plot data
+    #     plot_data <- datasetInput() %>%
+    #         filter(spp %in% species,
+    #                region %in% survey)#,
+    #     # year %in% years)
+    #     
+    #     # Density map
+    #     if(input$PlotStyle == 1){
+    #         
+    #         ggplotly(
+    #             ggplot(us_map) +
+    #                 geom_sf() +
[…]

### 2021-05-03 Scripts/spatial_analisis.Rmd
exploring buffer

--- 2021-04-19 Scripts/spatial_analisis.Rmd
@@
 
-us_map <- st_as_sf(map("state", plot = FALSE, fill = TRUE))
+States <- c("maine", "new hampshire", "massachusets", "connecticut", "rhode island", "new york", "new jersey", "delaware", "maryland", "virginia", "north carolina")
+
+# US State Map (land)
+
+land_sf <- st_as_sf(map("state", plot = FALSE, fill = TRUE)) %>% 
+  filter(ID %in% States)
+
+# ggplot(us_map) +
+  # geom_sf()
+
+# US EEZ map
 
@@
 # Load it!
-World_eez_sf <- st_read(dsn = path_world,
+eez_sf <- st_read(dsn = path_world,
                         layer =file_path_sans_ext(fnam_world)) %>% 
@@
   filter(eez_name == "USA (East Coast)")
+
+# ggplot(World_eez_sf) +
+  # geom_sf()
+
+# ggplot() +
+#   geom_sf(data = World_eez_sf, aes(), color = "red") +
+#   geom_sf(data = us_map, aes(), color = "blue")
+
+# US state waters
+# https://catalog.data.gov/dataset/federal-and-state-waters
+
+# us_state_w <- rgdal::readOGR(dsn = "~/Downloads/FederalAndStateWaters/FederalAndStateWaters.gdb")
+state_sf <-  st_read("~/Downloads/FederalAndStateWaters/FederalAndStateWaters.gdb") %>% 
+  janitor::clean_names() %>% 
+  mutate(jurisdicti = str_to_lower(jurisdicti)) %>% 
+  filter(jurisdicti %in% States)
+
+# plot <- state_sf %>%
+  # st_simplify(preserveTopology = TRUE, dTolerance = 10000) %>%
+  # ggplot()  +
+  # geom_sf(aes(col = Jurisdicti))
+
+# ggsave("plot.png",plot)
+
+```
+
+### Exploring spatial regions (a.k.a  buffers)
+
+```{r}
+
+## Test with st_buffer
+
+test <- state_sf %>% 
+  filter(jurisdicti == "maine") %>% 
+  select(jurisdicti,Shape)
+
+ggplot(test) +
+  geom_sf()
+
+pbuf = st_buffer(test, 100)
+
+p <- ggplot() +
+  geom_sf(data = test, aes(), color = "blue") +
+  geom_sf(data = pbuf, aes(), color = "red")
+
+ggsave("testplot.png",p)
+
+### Test with library(ggforce)
+# install.packages("ggforce")
+library(ggforce)
+
+ test <- state_sf %>% 
+  filter(jurisdicti == "maine") %>% 
+  select(jurisdicti,Shape)
 

### 2021-05-05 Allocation_tool/ui.R
Included an "info" tab

@@ -94,8 +94,39 @@ shinyUI(
                                 ),
                             ) # close fluid row
                    ), # tabPanel close
-                   # Application title
-                   tabPanel("Stock allocation formula",
+                   # ----------------------- #
+                   # General info
+                   # ----------------------- #
+                   navbarMenu("Information",
+                              tabPanel("Transboundary stocks",
+                                       column(
+                                           10,
+                                           align = "justified",
+                                           p(h3("Project background")),
+                                           p(
+                                               "Climate change is driving shifts in fish stock distributions that will affect resource availability across
+                                    different jurisdictions around the world. Elinor Ostrom’s fundamental principles of common pool
+                                    resource governance include a requirement for clear boundaries over resource units. 
+                                    However, when stock ranges shift, governance systems and boundaries are no longer aligned. 
+                                    This misalignment has already created conflicts around access and the re-distribution of benefits 
+                                    flowing from the stocks. This is a global challenge that is likely to increase as the effects of 
+                                    climate change intensify in the coming years. 
+                                    
+                                    Specific problems that arise from the movement of stocks across jurisdictions include: 
+                                    overfishing; conflicts over access; unfairness to stakeholders who have borne the costs of resource 
+                                    stewardship but cannot capture the benefits due to stock movement; and high costs and conflicts associated 
+                                    with re-negotiating allocation, which is typically the most contentious aspect of fishery management."
+                                           )
+                                           )
+                                       ),
+                              tabPanel("Climate change"),
+                              tabPanel("Dynamic management")
+                            
+                   ), # close information tab
+                   # ----------------------- #
+                   # Stock allocation formula
+                   # ----------------------- #
+                   tabPanel("Quota allocation",
                             fluidRow(
                                 column(
                                     12,

### 2021-05-05 Allocation_tool/scripts/climate_change.Rmd
Included a mardonw with climate change text

---
output:
  bookdown::html_document2: 
    toc: yes
header-includes:
    - \usepackage[utf8]{inputenc}
    - \usepackage{wrapfig}
    - \usepackage{lipsum}
---

# Climate change and its effect on marine species

By 2017, greenhouse gas emissions from human activities are estimated to have warmed the Earth's surface by $1 \pm 0.2^ oC$ above pre-industrial levels causing changes in ocean conditions [@IPCC:2018ws]. The ocean has absorbed 93% of heat produced from greenhouse gas emissions since 1970 [@Rheim:2013fv; @IPCC:2019tn]. As a consequence, global sea surface temperature (SST) has increased by 0.63$^o$C relative to 1850-1900 [@IPCC:2019tn]. Also, an assessment by the Intergovernmental Panel on Climate Change (IPCC) has concluded that marine heatwaves have become more frequent [@Frolicher:2018dc], and ice sheets and glaciers have lost mass at an average rate of 220 $\pm$ 30 Gt $yr^{–1}$ between 2006 and 2015 [@IPCC:2019tn]. The ocean has also sequestered about 30% of the carbon dioxide ($CO_{2}$) emissions from the atmosphere since the late 1980's, causing a pH decrease of 0.1 unit that corresponds to a 26% increase in acidity [@Ross:2011kd; @IPCC:2019tn]. Moreover, increasing stratification of oceanic waters, changes in ventilation and biogeochemistry have led to a 0.5 to 3.3% loss of oxygen content in the upper layer (1000 m) of the open ocean between 1970 and 2010. During the same period, oxygen minimum zones have expanded by 3 to 8% in volume [@IPCC:2019tn].

![Past and future changes in sea surface temperature, surface ocean pH and oxygen content (100-600 m depth). Adapted from IPCC (2019)](../www/ipcc.png)

There are substantial regional variations in the $CO_{2}$-induced changes in ocean properties. For example, the Southern Ocean accounted for 35 to 43% of the total heat gain in the upper 2000 m layer of the global ocean between 1970 and 2017, and 25% of the global oxygen decline between 1970 and 1992 [@IPCC:2019tn]. Large reductions in oxygen have also been recorded for the north Pacific [@IPCC:2019tn]. In terms of pH, the largest declines between 1991 and 2011 were in the Indian Ocean (--0.027 units decade$^{ – 1}$), eastern Equatorial Pacific (--0.026 units decade$^{–1}$) and the South Pacific subtropical oceans (--0.022 units decade$^{–1}$) [@IPCC:2019tn].

Ocean properties are expected to continue to change in the $21^{st}$ century, although the intensity of these changes depends on the decisions' society will take in the future in relation to carbon mitigation [@Gattuso:2015jz; @IPCC:2019tn]. The IPCC assessed the future climate using scenarios of greenhouse gas concentration in the atmosphere. These scenarios, known as Representative Concentration Pathways (RCPs), range from a "strong climate mitigation" (RCP 2.6) scenario to a "no mitigation" scenario where society has no effective greenhouse gases mitigation policies (RCP 8.5). Under RCP 2.6, radiative forcing increases 2.6 $W/m^2$ by 2100 relative to pre-industrial conditions while RCP 8.5 leads to a radiative forcing of 8.5 $W/m^2$ [@vanVuuren:2011cs]. Under RCP 2.6, SST is projected to increase by 1.6$^o$C (CI[^1]: 1.1 - 2.0$^o$C) by 2031 - 2050 relative to 1850-1900, maintaining this trend (1.6$^o$C; CI: 0.9 - 2.4$^o$C) towards the end of the $21^{st}$ century. In contrast, following RCP 8.5 would result in an increase of 2$^o$C (CI: 1.5 - 2.4$^o$C) by 2031 - 2050 reaching 4.3$^oC$ (CI: 3.2 - 5.4$^o$C) by the end of the $21^{st}$ century relative to the same time period [@IPCC:2019tn; @Riahi:2011dk]. In addition, the IPCC considers two intermediate scenarios, RCPs 4.5 and 6.0. While RCP 4.5 leads to a radiative forcing of 4.5 $W/m^2$ by 2100 relative to pre-industrial conditions and RCP 6.0 leads to 6.0 $W/m^2$ [@Thomson:2011iy; @Masui:2011gr]. <!-- , RCP 1.5 leads to a much lower radiative forcing, 1.9 $W/m^2$. The RCP 1.5 is a scenario that align most closely to aspired carbon mitigation level under the Paris Agreement of the United Nations Framework Convention on Climate Change [@IPCC:2019tn; @IPCC:2014bz].  --> Here, I focus on RCP 2.6 and RCP 8.5 to capture the lower and upper range of climate change impacts on shared fish stocks and fisheries.

[^1]: In this case, the confidence interval used by the IPCC lies between the 17--83% probability range.

The ocean is projected to become warmer, less oxygenated and with lower pH in the $21^{st}$ century relative to the present day (e.g., 1986-2005) under all RCPs [@IPCC:2019tn]. Specifically, by 2050, global mean SST is expected to increase by 0.65$^o$C (CI: 0.33 to 0.96$^o$C) under RCP 2.6 and 0.95$^o$C (CI: 0.60 to 1.29$^o$C) under RCP 8.5. The largest SST warming will be in the North Pacific, the tropical East Pacific, and in parts of the Arctic [@Gattuso:2015jz]. At the same time, surface pH will be reduced by -0.072 (CI: --0.072 to --0.072) units under RCP 2.6 and 0.108 (CI: --0.106 to --0.110) units under RCP 8.5, with the Arctic experiencing the largest decrease [@IPCC:2019tn; @Gattuso:2015jz]. Dissolved oxygen within the first 600 m will also be reduced by -0.9% (CI: -0,3 to -1.5) under RCP 2.6 and -1.4% (CI: --1.0 to --1.8) under RCP 8.5 [@IPCC:2019tn]. The subsurface layer of mid-latitude regions is prone to see the largest changes in dissolved oxygen [@Gattuso:2015jz]. By the end of the $21^{st}$ century under RCP 8.5, ocean surface will be 3.2$^o$C warmer, --0.4 pH units lower, and have 3.9% less dissolved oxygen relative to the pre-industrial level. In contrast, under RCP 2.6, ocean surface will be 1.2$^o$C warmer, pH will be --0.14 units lower and oxygen will be about 1% less than the pre-industrial level [@IPCC:2019tn; @Gattuso:2015jz].

In responses to the change in ocean properties, marine species are altering their productivity, distribution, and phenology [@Scheffers:2016gz]. The type and magnitude of the responses will vary depending on the oceanic region, taxonomic group and life history and ecological characteristics of the organisms [@Poloczanska:2016kk; @Gattuso:2015jz; @Scheffers:2016gz]. Changes in maximum sustainable yield (MSY) of 235 populations of 162 species have been related to increasing water temperature. Between 1930 and 2010, MSY decreased by 4.1% (1.4 million tons) with some ecoregions (e.g., East Asia) experiencing losses of up to 35% [@Free:2019jq]. Future projections suggest that by the end of the $21^{st}$ century, 41 and 91% of global fish stocks will see a decline in MSY relative to 2012 under RCP 2.5 and 8.5 respectively [@Gaines:2018sg]. Moreover, shifting distributions has been the most widely documented response of marine species to ocean warming [@Poloczanska:2016kk; @Gattuso:2015jz]. Marine species, from phytoplankton to top predators have shifted their distribution ranges, mostly poleward, by an average of 72.0 $\pm$ 13.5 km per decade [@Poloczanska:2016kk]. These shifts are consistent with projections from species distribution models and are expected to continue in the $21^{st}$ century, even under a low emission scenario (RCP 2.6) [@Cheung:2010dt; @Barange:2014kr; @GarciaMolinos:2015fk]. Warming and less oxygenated waters have also been related to changes in size of marine fishes [@Oke:2020hi; @Forster:2012cq; @Audzijonyte:2020hy]. Overall, fish body size is expected to decrease under a warming ocean [@Cheung:2012fo; @Pauly:2017hpa; @Pauly:2018hq] with variations between regions and species [@Audzijonyte:2020hy].

Shifts in exploited marine species abundance, distribution and phenology will consequently impact the economics of fisheries [@Lam:2016dy; @Sumaila:2019ew; @Sumaila:2019gh] and food security [@Bell:2017hm; @Golden:2016gd] of communities that depend on them. It was estimated that in 2010, global fish landings were about 100 million tonnes (most of it destined to direct human consumption) generating about USD 150 billion [@Tai2017]. Estimates under RCP 8.5 suggest that global catches and revenue from fisheries could drop by 8 and 10%, respectively by 2050 with large regional differences [@Lam:2016dy]. For example, under RCP 8.5, the Exclusive Economic Zone (EEZ) of many tropical countries are expected to see \>50% reductions in both catch and revenue [@Lam:2016dy]. This is the case of many Pacific Islands nations like the Philippines where fish represents a high proportion of animal-sourced food [@Asch:2018ca; @FAO:2018KK; @Bell:2017hm]. On the contrary, high latitude EEZs such as the Russian in the north and the Chilean in the south could see increases of up to 30% [@Lam:2016dy]. Similarly, societal vulnerability to climate change impacts on fisheries will not be the same across coastal communities. For example, indigenous fishing communities that rely on marine resources for food security and wellbeing are particularly vulnerable to climate change due to reduced access to resources [@Weatherdon:2016ws; @CisnerosMontemayor:2016gq]. Reducing greenhouse gas emissions to limit warming to a 1.5$^o$C increase by the end of the $21^{st}$ century (RCP 2.6) could increase fisheries catch potential by up to 30% [@Cheung:2016tt]. This would result in a USD 4.6 billion annual revenue increase benefiting 75% of coastal nations from which \~90% represent developing countries [@Sumaila:2019ew].

<!-- ## Transboundary fisheries management under climate change -->

<!-- Current transboundary fisheries management might not be adapted to cope with shifts in species distributions under climate change [@Pinsky:2018cb, Chapter 4]. When a fish stock shifts from one EEZ to another due to climate change, fisheries in the states that lose the resource may opt to maximize the exploitation of the fish stock. In contrast, the states that benefits from an increasing share of the fish stock may have more incentive to conserve it because of its increasing stake on the state's fisheries resources [@Diekert:2017fa]. As climate change continues to drive shifts in biogeography of exploited species, fish stocks are expected to expand into EEZs they did not occupy before. In some cases, abundance will decrease in the lower latitudinal range of the species potentially exacerbating conflicts over stock's ownership and quota allocation [@Pinsky:2018cb; @Oremus:2020id]. Despite historical and projected changes in species distributions, today, many treaties concerning on the management of shared stocks are not well equipped to respond to stock shifts [@CullisSuzuki:2010fi; @Pinsky:2018cb; @Sumby:2021gw, Chapter 4]. Specifically, some basic fisheries management strategies, such as quota allocations, are based on historical catch proportions, or stock's historical distribution, and could become outdated as stocks shift to cope with a changing ocean [@Pinsky:2014by; @Beaugrand:2011fd, Chapter 4]. Lack of or insufficient adaptation of management of shared stocks to changing ocean conditions and stocks distributions will impact their effectiveness in ensuring the sustainability and benefits from the fisheries [@Sumaila:2020tp]. -->

<!-- Both the magnitude and pattern of range shifts are important to characterize the risk and impacts of shifting shared stocks on transboundary fisheries management [@Pinsky:2012kq; @Link:2010ei]. The distribution of a fish stock can change in multiple ways. For example, the stock range can shift from one EEZ to another while approximately maintaining its total range size. Also, the distribution of the stock can contract from or expand into a neighboring EEZ, resulting in a decrease or increase in range size, respectively (Figure \@ref(fig:ShiftsFigure)). The magnitude and characteristics of range shifts of shared stocks will have different consequences to their management [@Link:2010ei]. Historically, such shifts have caused conflict between neighboring nations and compromised the sustainability of diverse shared stocks. Prominent examples include the 1980's conflict over Pacific salmon between the United States (US) and Canada [@Miller:2004fpa; @Song:2017va]. -->

<!-- In addition to the magnitude and pattern of range shifts, it is important to understand the time frame at when the shifts and their impacts on fisheries will become apparent [@Pinsky:2014by; @Hawkins:2012hc]. The IPCC Special Report on the Ocean and Cryosphere in a Changing Climate used the concept of "time of emergence" (ToE) to discuss the challenge of changing ocean conditions, marine ecosystems and their challenges to ocean governance [@IPCC:2019tn]. As defined by the IPCC (adopted from Hawkins and Sutton, 2012), ToE is the moment in time when an anthropogenic change signal (e.g., future trend) rises above the background noise of natural variability (e.g., historical variation) [@IPCC:2019tn]. The premise behind ToE is that we can only be confident that a significant change has been detected when the signal of anthropogenic climate change is larger than the background of natural climate variability [@Hawkins:2012hc]. The concept of ToE has been extensively used to determine the time by which diverse oceanic variables (e.g., temperature, oxygen, $CO_2$) have raised above natural variability (e.g., emerged) in the global ocean [@Rodgers:2015jq; @Keller:2014jv; @Frolicher:2016dg; @Hawkins:2012hc; @Mahlstein:2011fy]. However, this concept has not been widely used on studies related to climate change and fisheries, until a recent study investigating the impacts of marine heatwaves in selected fisheries of the northeast Pacific [@Cheung:2020ja]. The concept ToE is useful to elucidate the impacts of climate change on transboundary fisheries and the consequences for their governance. For example, in the US, the arrival of the jumbo squid *Dosidicus gigas* to Washington state in 2009 created a new fishery under a *de facto* open access regime due to a lack of existing regulation. The time it took policy to be implemented was too long, and the fishery was over-exploited [@Pinsky:2014by]. Moreover, since 2007 when Atlantic mackerel (*Scomber scombrus*) extended its distribution to Iceland's EEZ, the European Union (EU) and Norway, and Iceland have been in dispute over fishing rights and quota allocation [@Spijkers:2017ij]. -->

### 2021-05-05 Allocation_tool/ui.R
included a "info" tab

@@ -93,35 +93,79 @@ shinyUI(
                                     )
                                 ),
                             ) # close fluid row
-                   ), # tabPanel close
+                   ), # tabPanel About close
                    # ----------------------- #
                    # General info
                    # ----------------------- #
                    navbarMenu("Information",
-                              tabPanel("Transboundary stocks",
+                              tabPanel("Shared stocks",
+                                       column(10,
+                                              align = "justified",
+                                              p(h3("Shared fisheries management")),
+                                              p(
+                                                  "From 1973 to 1982, members of the United Nations (UN) held a series of meetings to discuss 
+                                               regulations regarding the high seas, a region of international common property, at that time, 
+                                               consisting of waters beyond 12 nautical miles (22.22 km) from shore [@Munro:2004ug].
+                                               Among the main outcomes of these meetings was the establishment of the UN Convention on the Law of the Sea (UNCLOS).
+                                               Under UNCLOS coastal states were allowed to claim special rights over the exploration and
+                                               exploitation of marine resources up to 200 nautical miles (370 km) from their coasts.
+                                               Area within which such special rights were claimed delineate today the states' Exclusive Economic Zone (EEZ) [@UnitedNations2018].
+                                               
+                                               The inception of the concept of shared stocks in fisheries management called for the establishment of new fisheries governance 
+                                               approaches and organizations. Many straddling and highly migratory stocks are managed by Regional Fisheries Management Organizations 
+                                               (RFMOs) [@MonllorHurtado:2017cm; @Song:2017va; @CullisSuzuki:2010fi]. At the EEZ level, transboundary stocks can be jointly managed 
+                                               by neighbouring countries under bi-lateral agreements or unilaterally without legal-binding agreements with other countries."
+                                              ),
+                                              p(h3("Classification of shared stocks")),
+                                              p(
+                                                  "Generally speaking, shared fish stocks are those populations that move between different jurisdictions in the course of their life.
+                                               The Food and Agricultural Organization (FAO) recognizes four types of shared stocks:"
+                                              ),
+                                              p(
+                                                  "(i) transboundary stocks are those that are shared between neighboring coastal nations e.g., Pacific halibut
+                                               (*Hippoglossus stenolepis*) shared between Canada and the United States"
+                                              ),
+                                              p(
+                                                  "(ii) straddling stocks are those that occur in two or more adjacent national jurisdictions and the high seas e.g.,
[…]

### 2021-05-05 Allocation_tool/scripts/about.Rmd
Included about mrkd.

# Project background

Climate change is driving shifts in fish stock distributions that will affect resource availability across different jurisdictions around the world. Elinor Ostrom’s fundamental principles of common pool resource governance include a requirement for clear boundaries over resource units. However, when stock ranges shift, governance systems and boundaries are no longer aligned. This misalignment has already created conflicts around access and the re-distribution of benefits flowing from the stocks. This is a global challenge that is likely to increase as the effects of climate change intensify in the coming years. Specific problems that arise from the movement of stocks across jurisdictions include: overfishing; conflicts over access; unfairness to stakeholders who have borne the costs of resource stewardship but cannot capture the benefits due to stock movement; and high costs and conflicts associated with re-negotiating allocation, which is typically the most contentious aspect of fishery management.

# Objective and research questions

The objective of this tool is to evaluate policy options for managing fish stocks that are shifting across management boundaries, and to assess the socio-economic benefits and tradeoffs of these options for two important fisheries in the U.S. Mid-Atlantic.

1. Would  adaptive allocation  have reduced fuel use and carbon emissions, had it been applied when black sea bass and summer flounder stocks started to shift?

2. Would adaptive allocation have a positive economic impact on these fisheries, had it been applied when black sea bass and summer flounder stocks started to shift?

3.	How can conflicts around allocation be reduced in the context of shifting stocks?

4.	Where else in the U.S.  could this type of solution be applied to alleviate the challenges that arise when stocks shift?

# Partners

- [Arielle Levine, San Diego State University](https://geography.sdsu.edu/people/bios/levine)

- [Rod Fujita, Environmental Defense Fund](https://www.edf.org/people/rod-m-fujita)

- [Katie Longo, Marine Stewardship Council](https://www.researchgate.net/profile/Catherine-Longo)

- [Olaf Jensen, University of Wisconsin, Madison](https://limnology.wisc.edu/staff/jensen-olaf/)

- [Scott Crosson, NOAA](https://www.fisheries.noaa.gov/contact/scott-crosson-phd)

- [Chris Dumas, University of North Carolina Wilmington](https://csbapp.uncw.edu/data/fs/vita.aspx?id=8307)

- [Juliano Palacios-Abrantes, University of Wisconsin, Madison](https://limnology.wisc.edu/staff/palacios-abrantes-juliano/)

![](../www/logo_all2.png)

### 2021-05-05 Allocation_tool/ui.R

@@ -40,47 +40,53 @@ shinyUI(
                                 ),
                                 br(),
                                 column(
-                                    10,
+                                    8,
+                                    offset = 2,
                                     align = "justified",
-                                    p(h3("Project background")),
-                                    p(
-                                        "Climate change is driving shifts in fish stock distributions that will affect resource availability across
-                                    different jurisdictions around the world. Elinor Ostrom’s fundamental principles of common pool
-                                    resource governance include a requirement for clear boundaries over resource units. 
-                                    However, when stock ranges shift, governance systems and boundaries are no longer aligned. 
-                                    This misalignment has already created conflicts around access and the re-distribution of benefits 
-                                    flowing from the stocks. This is a global challenge that is likely to increase as the effects of 
-                                    climate change intensify in the coming years. 
-                                    
-                                    Specific problems that arise from the movement of stocks across jurisdictions include: 
-                                    overfishing; conflicts over access; unfairness to stakeholders who have borne the costs of resource 
-                                    stewardship but cannot capture the benefits due to stock movement; and high costs and conflicts associated 
-                                    with re-negotiating allocation, which is typically the most contentious aspect of fishery management."
-                                    ),
-                                    p(h3("Objective")),
-                                    p("The objective of this tool is to evaluate policy options for managing
-                                    fish stocks that are shifting across management boundaries, and to assess 
-                                    the socio-economic benefits and tradeoffs of these options for two important 
-                                    fisheries in the U.S. Mid-Atlantic."
-                                    )
+                                includeMarkdown("./scripts/about.Rmd")
                                 ),
-                                column(
-                                    6,
-                                    p(h3("Partners")),
-                                    p(a("Arielle Levine, San Diego State University",href = "https://geography.sdsu.edu/people/bios/levine")),
-                                    p(a("Rod Fujita, Environmental Defense Fund", href = "https://www.edf.org/people/rod-m-fujita")),
-                                    p(a("Katie Longo, Marine Stewardship Council", href = "https://www.researchgate.net/profile/Catherine-Longo")),
-                                    p(a("Olaf Jensen, University of Wisconsin, Madison", href = "https://limnology.wisc.edu/staff/jensen-olaf/")),
-                                    p(a("Scott Crosson, NOAA", href = "https://www.fisheries.noaa.gov/contact/scott-crosson-phd")),
[…]

### 2021-05-05 Allocation_tool/ui.R
Fixed margins

@@ -33,8 +33,7 @@ shinyUI(
                    "Across Boundaries",
                    tabPanel("About",
                             fluidRow(
-                                column(
-                                    12,
+                                column(12,
                                     align = "center",
                                     h1("Managing across boundaries: preventing interjurisdictional conflicts arising from shifting fish stocks"),
                                 ),
@@ -45,51 +44,9 @@ shinyUI(
                                     align = "justified",
                                 includeMarkdown("./scripts/about.Rmd")
                                 ),
-                                # column(
-                                #     10,
-                                #     align = "justified",
-                                #     p(h3("Project background")),
-                                #     p(
-                                #         "Climate change is driving shifts in fish stock distributions that will affect resource availability across
-                                #     different jurisdictions around the world. Elinor Ostrom’s fundamental principles of common pool
-                                #     resource governance include a requirement for clear boundaries over resource units. 
-                                #     However, when stock ranges shift, governance systems and boundaries are no longer aligned. 
-                                #     This misalignment has already created conflicts around access and the re-distribution of benefits 
-                                #     flowing from the stocks. This is a global challenge that is likely to increase as the effects of 
-                                #     climate change intensify in the coming years. 
-                                #     
-                                #     Specific problems that arise from the movement of stocks across jurisdictions include: 
-                                #     overfishing; conflicts over access; unfairness to stakeholders who have borne the costs of resource 
-                                #     stewardship but cannot capture the benefits due to stock movement; and high costs and conflicts associated 
-                                #     with re-negotiating allocation, which is typically the most contentious aspect of fishery management."
-                                #     ),
-                                #     p(h3("Objective")),
-                                #     p("The objective of this tool is to evaluate policy options for managing
-                                #     fish stocks that are shifting across management boundaries, and to assess 
-                                #     the socio-economic benefits and tradeoffs of these options for two important 
-                                #     fisheries in the U.S. Mid-Atlantic."
-                                #     )
-                                # ),
-                                # column(
-                                #     6,
-                                #     p(h3("Partners")),
-                                #     p(a("Arielle Levine, San Diego State University",href = "https://geography.sdsu.edu/people/bios/levine")),
-                                #     p(a("Rod Fujita, Environmental Defense Fund", href = "https://www.edf.org/people/rod-m-fujita")),
[…]

### 2021-05-05 Allocation_tool/server.R
Working on sanity

@@ -7,7 +7,12 @@
 #    http://shiny.rstudio.com/
 #
 
-MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","DT","plotly"))
+# ---------------------------- #
+# Setup
+# ---------------------------- #
+
+# Get functions and shapefiles
+MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","DT"))
 
 us_map <- st_as_sf(map("state", plot = FALSE, fill = TRUE))
 
@@ -22,13 +27,19 @@ bbox <- c(
 
 # Expand the grid
 grd_template <- expand.grid(
-    lon = seq(from = bbox["xmin"], to = bbox["xmax"], by = 0.1),
-    lat = seq(from = bbox["ymin"], to = bbox["ymax"], by = 0.1)
+    lon = seq(from = bbox["xmin"], to = bbox["xmax"], by = 0.3),
+    lat = seq(from = bbox["ymin"], to = bbox["ymax"], by = 0.3)
 )
 
-# Define server logic required to draw a histogram
+
+# ---------------------------- #
+# Tool start ####
+# ---------------------------- #
 shinyServer(function(input, output) {
     
+    # ---------------------------- #
+    # Biological Survey Data ####
+    # ---------------------------- #
     datasetInput <- reactive({
         
         data <- readRDS("/Volumes/Enterprise/Data/pinskylab-OceanAdapt-966adf0/data_clean/dat_exploded.rds") %>% 
@@ -39,222 +50,191 @@ shinyServer(function(input, output) {
         
     })
     
-    # Main plot
-    # output$distPlot <- renderPlotly({
-    #     # Set the filters
-    #     species <- input$SppSelection
-    #     survey <- input$SurveySelection
-    #     # years <- input$YearSelection
-    #     
-    #     # Set the plot data
-    #     plot_data <- datasetInput() %>%
-    #         filter(spp %in% species,
-    #                region %in% survey)#,
-    #     # year %in% years)
-    #     
-    #     # Density map
-    #     if(input$PlotStyle == 1){
-    #         
-    #         ggplotly(
-    #             ggplot(us_map) +
-    #                 geom_sf() +
-    #                 geom_point(data = subset(plot_data, wtcpue = 0),
-    #                            aes(
-    #                                x = lon,
-    #                                y = lat
-    #                            ),
-    #                            color = "grey95",
[…]

### 2021-05-05 Allocation_tool/ui.R

@@ -31,6 +31,9 @@ shinyUI(
                    theme = shinythemes::shinytheme("spacelab"),
                    # Page title
                    "Across Boundaries",
+                   # ---------------------------- #
+                   # About tab ######
+                   # ---------------------------- #
                    tabPanel("About",
                             fluidRow(
                                 column(12,
@@ -58,7 +61,7 @@ shinyUI(
                             ) # close fluid row
                    ), # tabPanel About close
                    # ----------------------- #
-                   # General info
+                   # General info ####
                    # ----------------------- #
                    navbarMenu("Information",
                               tabPanel("Shared stocks",
@@ -139,7 +142,7 @@ shinyUI(
                               
                    ), # close information tab
                    # ----------------------- #
-                   # Stock allocation formula
+                   # Tool UI ####
                    # ----------------------- #
                    tabPanel("Quota allocation",
                             fluidRow(
@@ -155,7 +158,7 @@ shinyUI(
                                         checkboxGroupInput(inputId = "SurveySelection",
                                                            label = "Select Survey(s)",
                                                            choices = unique(spp_survey$region),
-                                                           selected = "Fall"
+                                                           selected = unique(spp_survey$region)[1]
                                         ),
                                         # Select Species
                                         selectInput(inputId = "SppSelection",
@@ -183,24 +186,26 @@ shinyUI(
                                         # Select which plot you want to create
                                         checkboxGroupInput(inputId = "PlotStyle",
                                                            label = "Select Result",
-                                                           choices = c("Survey Point" = 1, 
-                                                                       "Distribution Map" = 2,
-                                                                       "Allocation Area" = 3),
+                                                           choices = c(
+                                                               "Latitudinal Shift" = 1,
+                                                               "Survey Point" = 2, 
+                                                               "Distribution Map" = 3,
+                                                               "Allocation Area" = 4
+                                                               ),
                                                            selected = 1
                                         )
                                     ),
                                     
                                     # Show a plot of the generated distribution
                                     mainPanel(
-                                        p(h4(strong("Result plot"))),
-                                        plotOutput("distPlot"),
+                                        plotOutput("distPlot")
                                         # plotlyOutput("distPlot"),
-                                        p(h4(strong("Allocation Table"))),
-                                        dataTableOutput("Allocation_tbl")
                                     )
                                 ),
                                 br(),
                                 br(),
+                                p(h3(strong("Quota allocation table"))),
+                                dataTableOutput("Allocation_tbl"),
[…]

### 2021-05-25 Allocation_tool/ui.R
Include about as a rmd

@@ -45,7 +45,7 @@ shinyUI(
                                     8,
                                     offset = 2,
                                     align = "justified",
-                                includeMarkdown("./scripts/about.Rmd")
+                                includeMarkdown("./scripts/about.Rmd") # Call the About info
                                 ),
                                 br(),
                                 column(

### 2021-05-25 Scripts/spatial_analisis.Rmd
Got the buffer

@@
   # st_transform(crs = "+proj=eck4") %>% # for tbular plot
-  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
+  st_simplify(preserveTopology = TRUE, dTolerance = 10000) %>% #0.1
   filter(eez_name == "USA (East Coast)")
 
-# ggplot(World_eez_sf) +
-  # geom_sf()
+# ggplot(eez_sf) +
+# geom_sf(aes(),fill =NA)
 
@@
   mutate(jurisdicti = str_to_lower(jurisdicti)) %>% 
-  filter(jurisdicti %in% States)
+  filter(jurisdicti %in% States) %>% 
+  st_transform(crs = 4326) # for matching projections
 
@@
 
-## Test with st_buffer
+# Buffer state waters
 
-test <- state_sf %>% 
-  filter(jurisdicti == "maine") %>% 
-  select(jurisdicti,Shape)
+state_bf = st_buffer(state_sf, 405000)
 
-ggplot(test) +
+# ------------------------------ #
+# Testing and visualizing the buffer 
+# ------------------------------ #
+
+# p <- ggplot() +
+#   geom_sf(data = eez_sf, aes(), fill = NA) +
+#   geom_sf(data = state_bf, aes(color = jurisdicti), fill = NA) +
+#   geom_sf(data = state_sf, aes(color = jurisdicti), fill = NA)
+#
+
+# ggsave("testplotb.png",p)
+
+# ------------------------------ #
+
+#Join eez shapefile wih buffer
+
+state_bf_ezz <- st_join(state_bf,eez_sf,join = st_contains)
+
+pp <- ggplot(state_bf_ezz) +
   geom_sf()
 
-pbuf = st_buffer(test, 100)
-
-p <- ggplot() +
-  geom_sf(data = test, aes(), color = "blue") +
-  geom_sf(data = pbuf, aes(), color = "red")
-
 ggsave("testplot.png",p)
-
-### Test with library(ggforce)
-# install.packages("ggforce")
-library(ggforce)
-
- test <- state_sf %>% 
-  filter(jurisdicti == "maine") %>% 
-  select(jurisdicti,Shape)
 

### 2021-06-01 Scripts/spatial_analisis.Rmd
Got a matching grid!

@@
 
-```{r dat_exploded, eval = T, echo = T}
+- Using only "Northeast US Fall and Spring surveys for now
+
+```{r dat_exploded, eval = T, echo = F}
 
@@
 
-```{r maps_sf, eval = F, echo = T, results = 'hide'}
+```{r maps_sf, eval = T, echo = T, results = 'hide'}
 
@@
   st_transform(crs = 4326) %>% # 4326
-  # st_transform(crs = "+proj=eck4") %>% # for tbular plot
-  st_simplify(preserveTopology = TRUE, dTolerance = 10000) %>% #0.1
+  st_simplify(preserveTopology = TRUE, dTolerance = 10000) %>% #0.1 for paper
   filter(eez_name == "USA (East Coast)")
@@
   filter(jurisdicti %in% States) %>% 
-  st_transform(crs = 4326) # for matching projections
-
-# plot <- state_sf %>%
-  # st_simplify(preserveTopology = TRUE, dTolerance = 10000) %>%
-  # ggplot()  +
-  # geom_sf(aes(col = Jurisdicti))
-
-# ggsave("plot.png",plot)
+  rename(state = jurisdicti)
+  # st_transform(crs = 4326)  # for matching projections
+  # st_simplify(preserveTopology = TRUE, dTolerance = 0.1)
 
@@
 
-### Exploring spatial regions (a.k.a  buffers)
+### 1. Expand Spatial regions (a.k.a  buffers)
 
-```{r}
+A buffer of *410000* m (410 KM / 221) overshoots the EEZ a bit, but is eventually cropped
+
+```{r buffer, eval = T, echo = T}
 
 # Buffer state waters
-
-state_bf = st_buffer(state_sf, 405000)
+state_bf = st_buffer(state_sf, 410000) %>% 
+  st_transform(4326) %>% # to match shape
+  st_set_crs(4326)
 
@@
 
-# p <- ggplot() +
-#   geom_sf(data = eez_sf, aes(), fill = NA) +
-#   geom_sf(data = state_bf, aes(color = jurisdicti), fill = NA) +
-#   geom_sf(data = state_sf, aes(color = jurisdicti), fill = NA)
+state_bf_plot <- ggplot() +
+  geom_sf(data = eez_sf, aes(), fill = NA) +
+  geom_sf(data = state_bf, aes(color = state), fill = NA)
 #
 
-# ggsave("testplotb.png",p)
+# ggsave("../Results/Partial/state_waters_buffer.png",state_bf_plot)
 
@@
 
-#Join eez shapefile wih buffer
+state_bf_plot
 
-state_bf_ezz <- st_join(state_bf,eez_sf,join = st_contains)
+```
 
-pp <- ggplot(state_bf_ezz) +
-  geom_sf()
+### 2. Expand grid within buffer
 
-ggsave("testplot.png",p)
+Here we expand a grid within the buffer so we can estimate the catch within
+
+```{r grid_indexing, eval = T, echo = T, message = F, warning = F}
+
+# Create grid of the region
+bbox <- c(st_bbox(state_bf))
+
+# Expand the grid
+ne_grid <- expand.grid(
+    lon = seq(from = bbox["xmin"], to = bbox["xmax"], by = 0.3),
+    lat = seq(from = bbox["ymin"], to = bbox["ymax"], by = 0.3)
+) %>% 
+  rowid_to_column("index")
+
+# ----------- #
+# [TEST] Plot all layers
+# ----------- #
+
+# Looks good
+state_sf %>%
+  st_transform(4326) %>% # to match shape
+  st_set_crs(4326) %>%
+  st_simplify(preserveTopology = TRUE, dTolerance = 10000) %>%
+  ggplot() +
+  geom_sf(aes(color = state))+
+  # geom_sf(data = eez_sf, aes(),fill =NA) +
+  # ggplot()+
+  geom_tile(data = ne_grid,
+            aes(
+              x = lon,
+              y = lat
+            ),
+            alpha = 0.2
+  )
+
+```
+
+#### 2.1 Merge grid and buffers
+
+Here we converted the grid to `sf`, merged with the buffered states and filter out everything outside the states polygon
+
+```{r grid_buf_merge, eval = T, echo = T, message = F, warning = F, fig.width = 10}
+
+# ---------------- #
+# Convert grid to sf
+# ---------------- #
+grid_sf <- st_as_sf(ne_grid,
+             coords = c("lon", "lat"),
+             crs = 4326) %>% 
+  st_join(state_bf) %>% 
+  filter(!is.na(state))
+
+# Create data frame for future computations
+# Note, will be used in next chunk
+grid_bf_dt <- as.data.frame(grid_sf) %>%
+    select(index,state)
+    # group_by(state) %>% 
+    # summarise(length(index))
+
+# ---------------- #
+# [TEST] 
+# Visualization of grid
+# ---------------- #
+
+gridExtra::grid.arrange(
+  # Overall (overlapping) position
+  ggplot(grid_sf) +
+    geom_sf(aes(color = state)) +
+    geom_sf(data = eez_sf, aes(),fill =NA) + 
+    theme(legend.position = ""),
+  # Showing each state separatley
+  ggplot() +
+    geom_sf(data = grid_sf, aes(color = state),size = 0.1) +
+    facet_wrap(~state) +
+    theme(legend.position = "top"),
+  nrow = 1)
+
+```
+
+### 3. Crop buffers to EEZ
+
+```{r buff_to_eez, eval = T, echo = T, message = F, warning = F}
+
+# I don't know how to undo st_simplify so need to re-load the shapefile
+eez_sf <- st_read(dsn = path_world,
+                        layer =file_path_sans_ext(fnam_world)) %>% 
+  rename(eez_name = Name) %>% 
+  st_transform(crs = 4326) %>% # 4326
+  filter(eez_name == "USA (East Coast)")
+
+# Get the overlapping segments
+grid_eez_sf <- st_intersection(grid_sf,eez_sf)
+
+# Get final df with index
+grid_eez_df <- as.data.frame(grid_eez_sf) %>%
+  select(state,index)
+
+# Plot to make sure makes sense (Picasso syle)
+grid_eez_sf %>% 
+  st_simplify(preserveTopology = TRUE, dTolerance = 10000) %>% #0.1 for paper
+  ggplot() +
+  geom_sf(aes(color = state))
 

### 2021-06-01 Scripts/spatial_analisis.Rmd
Looks like... its... done?

@@
 title: "Spatial Analysis"
-output: html_notebook
+# output: html_notebook
+output: html_document
 ---
@@
 ```{r setup, include=FALSE}
-MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps"))
+MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","viridis"))
+library(MyFunctions)
 ```
@@
   filter(jurisdicti %in% States) %>% 
-  rename(state = jurisdicti)
+  rename(state = jurisdicti) %>% 
   # st_transform(crs = 4326)  # for matching projections
-  # st_simplify(preserveTopology = TRUE, dTolerance = 0.1)
+  st_simplify(preserveTopology = TRUE, dTolerance = 10000) #0.1 for paper
+
+grid_sf <-  st_read("/Volumes/Enterprise/Data/AcrossBoundaries/Data/Spatial/grid_sf/grid_eez_sf.shp")
 
 ```
+
+## Create basis sf
+
+In this first step we first combine the North East EEZ shapefile (SAU) with the state waters sf provided by [NOAA](link) and girded the area following these steps:
+
+- 1. Expand state waters using a buffer
+
+- 2. Grid that buffer on a 0.3 ressolution
+
+- 3. Crop the buffer to the EEZ
 
@@
 
+# write_sf(grid_eez_sf, "../Results/Partial/grid_eez_sf.shp")
+
 # Get final df with index
@@
 
+# write_csv(grid_eez_df, "../Results/Partial/grid_eez_df.csv")
+
 # Plot to make sure makes sense (Picasso syle)
-grid_eez_sf %>% 
-  st_simplify(preserveTopology = TRUE, dTolerance = 10000) %>% #0.1 for paper
-  ggplot() +
-  geom_sf(aes(color = state))
+# grid_eez_sf %>%
+#   st_simplify(preserveTopology = TRUE, dTolerance = 10000) %>% #0.1 for paper
+#   ggplot() +
+#   geom_sf(aes(color = state))
 
@@
 
-### Map of smapling points
+## Map of smapling points
 
@@
 
-```{r survey_map, eval = T, echo = T, fig.width = 12, fig.height = 8}
+```{r survey_map, eval = F, echo = T, fig.width = 12, fig.height = 8}
 
-ggplot(us_map) +
+ggplot(land_sf) +
   geom_sf() +
-  geom_sf(data = World_eez_sf, aes(), fill = "white") +
+  geom_sf(data = eez_sf, aes(), fill = "white") +
   geom_point(data = subset(ocean_data, wtcpue = 0),
@@
 
-## SF example A
+Here we [interpolate](https://swilke-geoscience.net/post/spatial_interpolation/) the survey data within the grid. We
 
-https://swilke-geoscience.net/post/spatial_interpolation/
+## Prepare data
 
-```{r interpolation, eval = T, echo = T}
+- We removed cases where `wtcpue < 0`
 
+```{r prepare_data, eval = T, echo = T}
+
+# Subset data
 subset_data <- ocean_data %>% 
-  filter(region == "Northeast US Spring",
-         wtcpue > 0) %>% 
-  group_by(lon,lat) %>% 
-  summarise(wtcpue = sum(wtcpue,na.rm = T))
+  filter(
+    region == "Northeast US Spring",
+    wtcpue > 0)
 
-# First let's define a bounding Box to extrapolate from
-bbox <- c(
-  "xmin" = min(subset_data$lon),
-  "ymin" = min(subset_data$lat),
-  "xmax" = max(subset_data$lon),
-  "ymax" = max(subset_data$lat)
-)
+# Get grid
+grd_template <- data.frame(index = grid_sf$index,
+                       state = grid_sf$state,
+                       st_coordinates(grid_sf))
 
-# Expand the grid
-grd_template <- expand.grid(
-  lon = seq(from = bbox["xmin"], to = bbox["xmax"], by = 0.5),
-  lat = seq(from = bbox["ymin"], to = bbox["ymax"], by = 0.5)
-)
+```
 
-# ---------------- #
-# Visualize the box
+## Fun. interpol
 
-# ggplot() +
-#   geom_point(data = grd_template, aes(x = lon, y = lat), size = 0.1) +
-#   geom_point(data = subset_data,
-#   mapping = aes(x = lon, y = lat, color = wtcpue), size = 3) +
-#   scale_color_gradientn(colors = c("blue", "yellow", "red")) +
-#   theme_bw()
+This is the main function used to interpolate the data per year. It follows a Triangular Irregular Surface method using the `interp::interp()` function.
 
-# ---------------- #
+```{r interpol_function, eval = T, echo = T}
 
-# Rasterize our grid
-# expects a PROJ.4 string, see https://epsg.io/25833
+tis <- function(input_data,yr){
 
-crs_raster_format <- "+proj=longlat +datum=WGS84 +no_defs"
+  # print(paste(yr))
 
-grd_template_raster <- grd_template %>% 
-  dplyr::mutate(Z = 0) %>% 
-  raster::rasterFromXYZ( 
-    crs = crs_raster_format)
+  data <- input_data %>% 
+    filter(year == yr)
 
-# The model
-
+  if(nrow(data) == 0){
+    return(tibble())
+  }else{
     # Triangular Irregular Surface
     fit_tin <- interp::interp( # using {interp}
-  x = subset_data$lon,           # the function actually accepts coordinate vectors
-  y = subset_data$lat,
-  z = subset_data$wtcpue,
-  xo = grd_template$lon,     # here we already define the target grid
-  yo = grd_template$lat,
+      x = data$lon,           # the function actually accepts coordinate vectors
+      y = data$lat,
+      z = data$wtcpue,
+      xo = grd_template$X,     # here we already define the target grid
+      yo = grd_template$Y,
       output = "points"
@@
       bind_cols() %>% 
-  filter(!is.na(z))
+      bind_cols(grd_template) %>%
+      mutate(year = yr) %>% 
+      select(index, state, year, lon=x, lat=y, value = z)
 
-ggplot(us_map) +
-  geom_sf()+
-  geom_sf(data = World_eez_sf, aes(), fill = "white")+
-  geom_tile( data = fit_tin,
+    return(fit_tin)
+  }
+}
+
+```
+
+## Control pannel
+
+```{r contro_pannel, eval = T, echo = T}
+
+# Run interpolation for all years
+years <- seq(1973,2019,1)
+
+historic_tif <- bind_rows(
+  lapply(years,tis,input_data = subset_data)
+)
+
+write_csv(historic_tif,
+          paste0(my_path("R",),"interpolated_data.csv"))
+
+```
+
+# Results
+
+```{r load_data}
+
+# Periods
+periods <-tibble(
+  period = c(rep("a early",12),
+             rep("b mid",12),
+             rep("c late",12),
+             rep("d now",12)
+             ),
+  year = c(seq(1972,1984,1),
+            seq(1985,1997,1),
+            seq(1998,2011,1),
+            seq(2012,2019,1)
+            )
+  )
+
+```
+
+## Points
+
+```{r area_plot, eval = T, echo = T}
+
+ data_grid <- historic_tif %>% 
+  # left_join(periods) %>% 
+  # group_by(state,lat,lon,period) %>% 
+  group_by(state,lat,lon) %>% 
+  summarise(mean = mean(value,na.rm= T), .groups = "drop") %>% 
+  rename(ID = state)
+
+ggplot(data_grid) +
+  geom_tile(
     aes(
-               x = x,
-               y = y,
-               fill =z,
-               colour = z
+      x = lon,
+      y = lat,
+      fill = mean,
+      col = mean
     )
   ) +
-  geom_point(data = subset(subset_data, wtcpue > 0),
-             aes(
-               x = lon,
-               y = lat
-             ),
-             alpha = 0.2
-  ) +
-  scale_color_distiller(palette = "Spectral", 
-                        guide_legend(title = "WCPUE per Haul")) + 
-  scale_fill_distiller(palette = "Spectral", 
-                       guide_legend(title = "WCPUE per Haul")) +
-  coord_sf(xlim = c(-76, -65),ylim = c(35, 45)) +
-  MyFunctions::my_ggtheme_m()
+  facet_wrap(~ ID) +
+  scale_fill_viridis("Mean Proportion", alpha = 0.8) +
+  scale_color_viridis("Mean Proportion", alpha = 0.8)
 
 ```
+
+## Map
+
+```{r area_plot, eval = T, echo = T}
+
+total_fited <- historic_tif %>% 
+  group_by(year) %>% 
+  summarise(total_value = sum(value,na.rm=T))
+
+state_fit <- historic_tif %>% 
+  group_by(state,year) %>% 
+  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
+  left_join(total_fited,
+            by = "year") %>%
+  mutate(percentage = state_value/total_value*100) %>% 
+  left_join(periods) %>% 
+  group_by(ID = state,period) %>% 
+  summarise(mean_per = round(mean(percentage)))
+
+# check percentages
+# state_fit %>% 
+#   group_by(period) %>% 
+#   summarise(sum(mean_per))
+
+land_sf %>% 
+  left_join(state_fit,
+            by = "ID") %>% 
+  ggplot() +
+  geom_sf(aes(fill = mean_per)) +
+  viridis::scale_fill_viridis("Mean Proportion", alpha = 0.8) +
+  facet_wrap(~period, nrow = 1) +
+  my_ggtheme_m()
+
+```
+
+## Area plot
+
+This graph shows the proportion of each State over time
+
+```{r area_plot, eval = T, echo = T}
+
+total_fited <- historic_tif %>% 
+  group_by(year) %>% 
+  summarise(total_value = sum(value,na.rm=T))
+
+# group by state
+state_fit <- historic_tif %>% 
+  group_by(state,year) %>% 
+  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
+  left_join(total_fited,
+            by = "year") %>%
+  mutate(percentage = state_value/total_value*100)
+
+p <- ggplot(state_fit) +
+  geom_area(
+    aes(
+      x = year,
+      y = round(percentage),
+      fill = state
+    )
+  ) +
+  viridis::scale_fill_viridis(discrete = T, alpha = 0.8) +
+  MyFunctions::my_ggtheme_p()
+
+plotly::ggplotly(p)
+
+```

### 2021-06-08 Scripts/spatial_analisis.Rmd
End to end analysis done  for black seabass

@@
 title: "Spatial Analysis"
-# output: html_notebook
-output: html_document
+output: 
+ # html_document
+  html_notebook:
+  fig_width: 6
+  fig_height: 4
+  toc: false
+  toc_depth: 3
+  code_folding: hide
+  toc_float:
+    collapsed: false
 ---
@@
 ```{r setup, include=FALSE}
-MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","viridis"))
 library(MyFunctions)
+MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","viridis","wesanderson","knitr","kableExtra","plotly"))
 ```
@@
 
-## Ocean adapt data
+## Maps data
 
-- Using only "Northeast US Fall and Spring surveys for now
+We use three different shapefiles for the continental U.S.
+land mass, the State waters of maine, new hampshire, massachusets, connecticut, rhode island, new york, new jersey, delaware, maryland, virginia, north carolina and the North East EEZ.
 
-```{r dat_exploded, eval = T, echo = F}
+1.- **Land shapefile;** covers the US land territory for visualization. Data provided from the `map` package.
 
-ocean_data <- readRDS("/Volumes/Enterprise/Data/pinskylab-OceanAdapt-966adf0/data_clean/dat_exploded.rds") %>% 
-  filter(spp == "Centropristis striata",
-       region %in% c("Northeast US Fall" , "Northeast US Spring")) #No more seasons
+2.- **State waters;** covers the state waters of the NE US states. Data from [data.gov](https://catalog.data.gov/dataset/federal-and-state-waters).
 
-```
+*License: No license information was provided.
+If this work was prepared by an officer or employee of the United States government as part of that person's official duties it is considered a U.S.
+Government Work.*
 
-## Maps data
+3.- **EEZ shapefile;** Used the *Sea Around Us* shapefle updated to June 2016.
 
@@
 
-States <- c("maine", "new hampshire", "massachusets", "connecticut", "rhode island", "new york", "new jersey", "delaware", "maryland", "virginia", "north carolina")
+States <- c("maine", "new hampshire", "massachusetts", "connecticut", "rhode island", "new york", "new jersey", "delaware", "maryland", "virginia", "north carolina","pennsylvania")
 
@@
 
+unique(land_sf$ID)
+
 ```
 
-## Create basis sf
+## Spatial component
 
-In this first step we first combine the North East EEZ shapefile (SAU) with the state waters sf provided by [NOAA](link) and girded the area following these steps:
+### Create base shapefile for computation
+
+As a first step we need to divide the NE US EEZ among the different states.
+For that we expanded state waters up to the 200 nautical miles to then estimate the percentage that each expanded-state-waters occupied.
+Note that in all cases these areas overlapped and percentages accounted for it.
+We did this by following these steps:
 
@@
 
-- 2. Grid that buffer on a 0.3 ressolution
+- 2. Grid that buffer on a 0.3 resolution
 
@@
 
-### 1. Expand Spatial regions (a.k.a  buffers)
+#### 1. Expand Spatial regions (a.k.a  buffers)
 
-A buffer of *410000* m (410 KM / 221) overshoots the EEZ a bit, but is eventually cropped
+We set a buffer of *410000* m (410 km, ~ 221 nm) that overshoots the EEZ a bit, but is eventually cropped
 
@@
 
-### 2. Expand grid within buffer
+#### 2. Expand grid within buffer
 
-Here we expand a grid within the buffer so we can estimate the catch within
+Here we expand a grid within the buffer so we can estimate the proportion of each state
 
@@
 
-#### 2.1 Merge grid and buffers
+##### 2.1 Merge grid and buffers
 
-Here we converted the grid to `sf`, merged with the buffered states and filter out everything outside the states polygon
+Once we have a gridded area, we converted the grid to a `sf` so we can merge it with the buffered states and finally filter out everything outside the states polygon
 
@@
   ggplot(grid_sf) +
-    geom_sf(aes(color = state)) +
+    geom_sf(aes(color = state), alpha = 0.3) +
     geom_sf(data = eez_sf, aes(),fill =NA) + 
@@
   ggplot() +
-    geom_sf(data = grid_sf, aes(color = state),size = 0.1) +
+    geom_sf(data = grid_sf, aes(color = state),size = 0.1, alpha = 0.3) +
     facet_wrap(~state) +
@@
 
-### 3. Crop buffers to EEZ
+#### 3. Crop buffers to EEZ
 
-```{r buff_to_eez, eval = T, echo = T, message = F, warning = F}
+Finally, we crop the grided buffers to within the EEZ to capture the actual water space.
+
+*Note:* This step takes quite a while because of the size of the EEZ shapefile. No, you cannot use `st_simplify()` here
+
+```{r buff_to_eez, eval =T, echo = T, message = F, warning = F}
 
@@
 
-# write_sf(grid_eez_sf, "../Results/Partial/grid_eez_sf.shp")
+# write_sf(grid_eez_sf, paste0(my_path("D", "Spatial"),"grid_eez_sf.shp"))
 
@@
 grid_eez_df <- as.data.frame(grid_eez_sf) %>%
-  select(state,index)
+  select(state,index) %>% 
+  left_join(ne_grid, 
+            by = "index")
 
-# write_csv(grid_eez_df, "../Results/Partial/grid_eez_df.csv")
+# write_csv(grid_eez_df, paste0(my_path("R", "Partial"),"grid_eez_df.csv"))
 
 # Plot to make sure makes sense (Picasso syle)
-# grid_eez_sf %>%
-#   st_simplify(preserveTopology = TRUE, dTolerance = 10000) %>% #0.1 for paper
-#   ggplot() +
-#   geom_sf(aes(color = state))
+grid_eez_sf %>%
+  st_simplify(preserveTopology = TRUE, dTolerance = 10000) %>% #0.1 for paper
+  ggplot() +
+  geom_sf(aes(color = state), alpha = 0.3)
 
@@
 
-## Map of smapling points
+## Interpolation rutine
 
-In this case the color gradient represents wtcpue (wet tones catch per unit of effort, haul hours) from 1972 to 2019. Grey dots represent `wtcpue = 0`
+Here we [interpolate](https://swilke-geoscience.net/post/spatial_interpolation/) the survey data within the previously created grid.
 
-```{r survey_map, eval = F, echo = T, fig.width = 12, fig.height = 8}
+- We removed cases where `wtcpue < 0`
 
-ggplot(land_sf) +
-  geom_sf() +
-  geom_sf(data = eez_sf, aes(), fill = "white") +
-  geom_point(data = subset(ocean_data, wtcpue = 0),
+### Function for interpolation
+
+This is the main function used to interpolate the data per year. It follows a Triangular Irregular Surface method using the `interp::interp()` function.
+
+```{r interpol_function, eval = T, echo = T}
+
+tis <- function(input_data, grid, yr, taxa, reg){
+
+  # print(paste(yr))
+
+  data <- input_data %>% 
+    filter(year == yr,
+           spp == taxa,
+           region == reg
+    ) %>% 
+    filter(wtcpue > 0)
+
+    if(nrow(data) == 0){
+      return(tibble())
+    }else{
+
+      # Triangular Irregular Surface
+      fit_tin <- interp::interp( # using {interp}
+        x = data$lon,           # the function actually accepts coordinate vectors
+        y = data$lat,
+        z = data$wtcpue,
+        xo = grid$lon,     # here we already define the target grid
+        yo = grid$lat,
+        output = "points"
+      ) %>% 
+        bind_cols() %>% 
+        bind_cols(grid) %>%
+        mutate(year = yr,
+               region = reg,
+               spp = taxa) %>% 
+        select(index, state, year, region, spp, lon=x, lat=y, value = z)
+
+    }
+
+    return(fit_tin)
+  }
+
+```
+
+### Ocean adapt data
+
+- Using only the Northeast US Fall and Spring bottom trawl survey data for now
+
+```{r dat_exploded, eval = T, echo = F}
+
+ocean_data <- readRDS("/Volumes/Enterprise/Data/pinskylab-OceanAdapt-966adf0/data_clean/dat_exploded.rds") #%>% 
+  # filter(spp == "Centropristis striata",
+       # region %in% c("Northeast US Fall" , "Northeast US Spring")) #No more seasons
+
+subset_data <- ocean_data %>% 
+  filter(spp == "Centropristis striata",
+       region %in% c("Northeast US Fall" , "Northeast US Spring")
+       )
+
+ggplot() +
+  geom_point(data = subset(subset_data, wtcpue = 0.0),
              aes(
@@
              ),
-             color = "grey95",
-             size = 1
+             color = "grey95"
   ) +
-  geom_point(data = subset(ocean_data, wtcpue > 0),
+  geom_point(data = subset(subset_data, wtcpue > 0),
              aes(
@@
 
-# Interpolation
+### Control Pannel
 
-Here we [interpolate](https://swilke-geoscience.net/post/spatial_interpolation/) the survey data within the grid. We
-
-## Prepare data
-
-- We removed cases where `wtcpue < 0`
-
-```{r prepare_data, eval = T, echo = T}
-
-# Subset data
-subset_data <- ocean_data %>% 
-  filter(
-    region == "Northeast US Spring",
-    wtcpue > 0)
-
-# Get grid
-grd_template <- data.frame(index = grid_sf$index,
-                       state = grid_sf$state,
-                       st_coordinates(grid_sf))
-
-```
-
-## Fun. interpol
-
-This is the main function used to interpolate the data per year. It follows a Triangular Irregular Surface method using the `interp::interp()` function.
-
-```{r interpol_function, eval = T, echo = T}
-
-tis <- function(input_data,yr){
-
-  # print(paste(yr))
-
-  data <- input_data %>% 
-    filter(year == yr)
-
-  if(nrow(data) == 0){
-    return(tibble())
-  }else{
-    # Triangular Irregular Surface
-    fit_tin <- interp::interp( # using {interp}
-      x = data$lon,           # the function actually accepts coordinate vectors
-      y = data$lat,
-      z = data$wtcpue,
-      xo = grd_template$X,     # here we already define the target grid
-      yo = grd_template$Y,
-      output = "points"
-    ) %>% 
-      bind_cols() %>% 
-      bind_cols(grd_template) %>%
-      mutate(year = yr) %>% 
-      select(index, state, year, lon=x, lat=y, value = z)
-
-    return(fit_tin)
-  }
-}
-
-```
-
-## Control pannel
+Load required data. Note that some of it has been previously created
 
 ```{r contro_pannel, eval = T, echo = T}
+
+# Load grid df
+grid_eez_df <- my_path("D","Spatial","grid_eez_df.csv", read = T)
 
@@
 
-historic_tif <- bind_rows(
-  lapply(years,tis,input_data = subset_data)
+# taxa
+spp <- "Centropristis striata"
+
+# regions
+regions <- c("Northeast US Fall" , "Northeast US Spring")
+
+```
+
+### Run routine
+
+```{r run_routine, eval = T, echo = T}
+
+# Run for a single region
+# historic_tif <- bind_rows(
+  # lapply(years,tis,input_data = ocean_data, grid = grid, taxa = "Centropristis striata", reg = regions[2])
+# )
+
+# Simple for-loop for running both regions (seasons)
+for(r in 1:2){
+
+  partial_df <- bind_rows(
+    lapply(years,tis,input_data = ocean_data, grid = grid, taxa = spp, reg = regions[r])
   )
 
-write_csv(historic_tif,
-          paste0(my_path("R",),"interpolated_data.csv"))
+  if(r == 1){
+    historic_tif <- partial_df
+  }else{
+    historic_tif <- bind_rows(historic_tif,partial_df)
+  }
+
+}
+
+# Save data for future plotting
+# write_csv(historic_tif,
+          # paste0(my_path("R","Partial"),"interpolated_data.csv"))
+
+# Show data in notebook
+head(historic_tif,10) %>% 
+   kable(
+    format = "html",
+    caption = "Extrapolated data") %>% 
+  kableExtra::kable_minimal() %>% 
+  kableExtra::kable_styling() %>%
+  kableExtra:: scroll_box(width = "100%", height = "300px")
 
@@
 ```{r load_data}
+
+# Load interpolated data
+historic_tif <- my_path("R","Partial","interpolated_data.csv",read = T)
 
@@
 
+# State pallet
+
+state_pallet <- c(wes_palette(n = 5, name = "Darjeeling1"),
+                               wes_palette(n = 5, name = "Darjeeling2"),
+                               wes_palette(n = 3, name = "Royal1")
+                  )
+
 ```
@@
 
-```{r area_plot, eval = T, echo = T}
+```{r area_map_state, eval = T, echo = T, fig.width=10, fig.height=12}
 
@@
   # group_by(state,lat,lon,period) %>% 
-  group_by(state,lat,lon) %>% 
+  group_by(state,lat,lon,region) %>% 
   summarise(mean = mean(value,na.rm= T), .groups = "drop") %>% 
@@
   ) +
-  facet_wrap(~ ID) +
+  facet_wrap(~ ID  +  region,
+             ncol = 4) +
   scale_fill_viridis("Mean Proportion", alpha = 0.8) +
@@
 
-```{r area_plot, eval = T, echo = T}
+```{r area_map, eval = T, echo = T, fig.width = 10}
 
 total_fited <- historic_tif %>% 
-  group_by(year) %>% 
+  group_by(year,region) %>% 
   summarise(total_value = sum(value,na.rm=T))
@@
 state_fit <- historic_tif %>% 
-  group_by(state,year) %>% 
+  group_by(state,year,region) %>% 
   summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
   left_join(total_fited,
-            by = "year") %>%
+            by = c("year","region")) %>%
   mutate(percentage = state_value/total_value*100) %>% 
   left_join(periods) %>% 
-  group_by(ID = state,period) %>% 
+  group_by(ID = state,period,region) %>% 
   summarise(mean_per = round(mean(percentage)))
@@
   viridis::scale_fill_viridis("Mean Proportion", alpha = 0.8) +
-  facet_wrap(~period, nrow = 1) +
+  facet_wrap(~region + period, nrow = 2) +
   my_ggtheme_m()
@@
 
-```{r area_plot, eval = T, echo = T}
+```{r area_plot, eval = T, echo = T, fig.height = 10, fig.width = 10}
 
 total_fited <- historic_tif %>% 
-  group_by(year) %>% 
+  group_by(year,region) %>% 
   summarise(total_value = sum(value,na.rm=T))
@@
 state_fit <- historic_tif %>% 
-  group_by(state,year) %>% 
+  group_by(state,year,region) %>% 
   summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
   left_join(total_fited,
-            by = "year") %>%
-  mutate(percentage = state_value/total_value*100)
+            by = c("year","region")) %>%
+  mutate(percentage = state_value/total_value*100) %>% 
+  group_by(state,region)
 
@@
   ) +
-  viridis::scale_fill_viridis(discrete = T, alpha = 0.8) +
-  MyFunctions::my_ggtheme_p()
+  ylab("Percentage (%)") +
+  # viridis::scale_fill_viridis(discrete = T, alpha = 0.8) +
+  scale_fill_manual(values = state_pallet) +
+  MyFunctions::my_ggtheme_p() +
+  facet_wrap(~region, ncol = 1)
 
-plotly::ggplotly(p)
+ggplotly(p,
+         dynamicTicks = TRUE) %>% 
+  layout(hovermode = "x") %>% 
+  # add_trace() %>% 
+  rangeslider()
 
 ```
+## Area plot (running)
+
+This graph shows the proportion of each State smoothed over a 10 years running mean. It helps seeing the trends better (I Think...)
+
+```{r area_lm_plot, eval = T, echo = T, fig.height = 10, fig.width = 10}
+
+# group by state
+state_fit <- historic_tif %>% 
+  group_by(state,year,region) %>% 
+  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
+  left_join(total_fited,
+            by = c("year","region")) %>%
+  mutate(percentage = state_value/total_value*100) %>% 
+  group_by(state,region) %>% 
+  mutate(RMean = zoo::rollmean(x = percentage, 
+                            10,
+                            fill = NA,
+                            na.rm=T)
+    )
+
+# Plot me
+p <- ggplot(state_fit) +
+  geom_area(
+    aes(
+      x = year,
+      y = round(RMean),
+      fill = state
+    )
+  ) +
+  ylab("10 yrs running average (%)") +
+  # viridis::scale_fill_viridis(discrete = T, alpha = 0.8) +
+  scale_fill_manual(values = state_pallet) +
+  MyFunctions::my_ggtheme_p() +
+  facet_wrap(~region, ncol = 1)
+
+suppressWarnings(
+ggplotly(p,
+         dynamicTicks = TRUE) %>% 
+  layout(hovermode = "x") %>% 
+  # add_trace() %>% 
+  rangeslider()
+)
+
+```

### 2021-06-08 Allocation_tool/server.R
included true area plot and tif data

@@ -12,23 +12,13 @@
 # ---------------------------- #
 
 # Get functions and shapefiles
-MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","DT"))
+MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","DT","plotly","wesanderson"))
 
 us_map <- st_as_sf(map("state", plot = FALSE, fill = TRUE))
 
-
-# First let's define a bounding Box to extrapolate from
-bbox <- c(
-    "xmin" = -76,
-    "ymin" = 35,
-    "xmax" = -65,
-    "ymax" = 45
-)
-
-# Expand the grid
-grd_template <- expand.grid(
-    lon = seq(from = bbox["xmin"], to = bbox["xmax"], by = 0.3),
-    lat = seq(from = bbox["ymin"], to = bbox["ymax"], by = 0.3)
+state_pallet <- c(wes_palette(n = 5, name = "Darjeeling1"),
+                  wes_palette(n = 5, name = "Darjeeling2"),
+                  wes_palette(n = 3, name = "Royal1")
 )
 
 
@@ -40,7 +30,7 @@ shinyServer(function(input, output) {
     # ---------------------------- #
     # Biological Survey Data ####
     # ---------------------------- #
-    datasetInput <- reactive({
+    raw_data <- reactive({
         
         data <- readRDS("/Volumes/Enterprise/Data/pinskylab-OceanAdapt-966adf0/data_clean/dat_exploded.rds") %>% 
             filter(
@@ -52,16 +42,35 @@ shinyServer(function(input, output) {
     
     
     # ---------------------------- #
+    # Extrapolated data
+    # Triangular Irregular Surface  
+    # ---------------------------- #
+    tif_data <- reactive({
+        
+        data <- MyFunctions::my_path("R","Partial","interpolated_data.csv",read = T)
+
+    })
+    
+    
+    
+    # ---------------------------- #
     # Main plot ####
     # ---------------------------- #
     output$distPlot <- renderPlot({
         # Set the filters
-        species <-  input$SppSelection #"Gadus morhua"
+        species <- input$SppSelection #"Gadus morhua"
         survey <- input$SurveySelection #"Northeast US Fall"
         years <- seq(input$YearSelection[1],input$YearSelection[2],1) #seq(1971,2019,1)
         
         # Set the plot data
-        plot_data <- datasetInput() %>%
[…]

### 2021-06-08 Allocation_tool/ui.R

@@ -8,7 +8,7 @@
 #
 
 # Load libraries and data
-MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny"))
+MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","plotly"))
 
 spp_survey <- read.csv("./data/spp_region.csv") %>% 
     filter(
@@ -191,21 +191,21 @@ shinyUI(
                                                                "Survey Point" = 2, 
                                                                "Distribution Map" = 3,
                                                                "Allocation Area" = 4
-                                                               ),
-                                                           selected = 1
+                                                               )#,
+                                                           # selected = 1
                                         )
                                     ),
                                     
                                     # Show a plot of the generated distribution
                                     mainPanel(
-                                        plotOutput("distPlot")
-                                        # plotlyOutput("distPlot"),
+                                        plotlyOutput("distPlot"),
+                                        plotlyOutput("areaPlot")
                                     )
                                 ),
                                 br(),
                                 br(),
                                 p(h3(strong("Quota allocation table"))),
-                                dataTableOutput("Allocation_tbl"),
+                                # dataTableOutput("Allocation_tbl"),
                                 # ----------- #
                                 # Instructions
                                 # ----------- #

### 2021-06-08 Allocation_tool/server.R
included area plottly

@@ -282,11 +282,12 @@ shinyServer(function(input, output) {
             ylab("Percentage (%)") +
             scale_fill_manual(values = state_pallet) +
             MyFunctions::my_ggtheme_p() +
-            facet_wrap(~region, ncol = 1)
+            theme(legend.position = "top") #+
+            # facet_wrap(~region, ncol = 1)
         
         ggplotly(p,
                  dynamicTicks = TRUE,
-                 height = 1000) %>% 
+                 height = 500) %>% 
             layout(hovermode = "x") %>% 
             # add_trace() %>% 
             rangeslider()

### 2021-06-08 Allocation_tool/ui.R

@@ -195,11 +195,16 @@ shinyUI(
                                                            # selected = 1
                                         )
                                     ),
-                                    
                                     # Show a plot of the generated distribution
                                     mainPanel(
-                                        plotlyOutput("distPlot"),
-                                        plotlyOutput("areaPlot")
+                                        conditionalPanel(
+                                            condition = "input.PlotStyle != 4",
+                                        plotOutput("distPlot")
+                                        ),
+                                        conditionalPanel(
+                                            condition = "input.PlotStyle == 4",
+                                            plotlyOutput("areaPlot")
+                                        )
                                     )
                                 ),
                                 br(),

### 2021-06-08 Allocation_tool/server.R
Inlcuded allocation table

@@ -12,6 +12,7 @@
 # ---------------------------- #
 
 # Get functions and shapefiles
+library(MyFunctions)
 MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","DT","plotly","wesanderson"))
 
 us_map <- st_as_sf(map("state", plot = FALSE, fill = TRUE))
@@ -249,13 +250,13 @@ shinyServer(function(input, output) {
         
         if(input$PlotStyle == 4){
             # Set the filters
-            # species <- input$SppSelection #"Gadus morhua"
+            species <- input$SppSelection #"Gadus morhua"
             survey <- input$SurveySelection #"Northeast US Fall"
             years <- seq(input$YearSelection[1],input$YearSelection[2],1) #seq(1971,2019,1)
          
         
         total_fited <- tif_data() %>% 
-                filter(#spp %in% species,
+                filter(spp %in% species,
                        region %in% survey,
                        year %in% years
                        ) %>% 
@@ -287,7 +288,7 @@ shinyServer(function(input, output) {
         
         ggplotly(p,
                  dynamicTicks = TRUE,
-                 height = 500) %>% 
+                 height = 600) %>% 
             layout(hovermode = "x") %>% 
             # add_trace() %>% 
             rangeslider()
@@ -298,41 +299,51 @@ shinyServer(function(input, output) {
     # ---------------------------- #
     # Allocation Table ####
     # ---------------------------- #
-    # output$Allocation_tbl <- renderDataTable({
+    output$Allocation_tbl <- renderDataTable({
         
-        # species <- input$SppSelection
-        # survey <- input$SurveySelection
-        # years <- input$YearSelection
-        
+        if(input$PlotStyle == 4){
+
+        species <- input$SppSelection
+        survey <- input$SurveySelection
+        years <- input$YearSelection
+
         # Set the plot data
-        # total_fited <- tif_data() %>% 
-            # filter(spp %in% species,
-            #        region %in% survey,
-            #        year %in% years)
-        # group_by(year,region) %>% 
-        #     summarise(total_value = sum(value,na.rm=T))
-        # 
+        total_fited <- tif_data() %>%
+        filter(#spp %in% species,
+               region %in% survey,
+               #year %in% years
+        ) %>% 
+        group_by(year,region) %>%
+            summarise(total_value = sum(value,na.rm=T))
+
         # group by state
-        # state_fit <- tif_data() %>% 
-        #     group_by(state,year,region) %>% 
[…]

### 2021-06-08 Allocation_tool/ui.R

@@ -191,12 +191,13 @@ shinyUI(
                                                                "Survey Point" = 2, 
                                                                "Distribution Map" = 3,
                                                                "Allocation Area" = 4
-                                                               )#,
-                                                           # selected = 1
+                                                               ),
+                                                           selected = 1
                                         )
                                     ),
                                     # Show a plot of the generated distribution
                                     mainPanel(
+                                        # Cndition between plot and plotly
                                         conditionalPanel(
                                             condition = "input.PlotStyle != 4",
                                         plotOutput("distPlot")
@@ -209,8 +210,11 @@ shinyUI(
                                 ),
                                 br(),
                                 br(),
-                                p(h3(strong("Quota allocation table"))),
-                                # dataTableOutput("Allocation_tbl"),
+                                conditionalPanel(
+                                    condition = "input.PlotStyle == 4",
+                                    p(h3(strong("Quota allocation table"))),
+                                    dataTableOutput("Allocation_tbl")
+                                ),
                                 # ----------- #
                                 # Instructions
                                 # ----------- #

### 2021-06-09 Scripts/spatial_analisis.Rmd
created function to run and save tis

@@
 
+  # --------------- #
+  # Testing
   # print(paste(yr))
+  # yr = 1976
+  # --------------- #
 
+  # Filter data
   data <- input_data %>% 
@@
     ) %>% 
+    # Average duplicated hauls in the same spot
+    group_by(region,year,spp,lat,lon) %>%
+    summarise_at(vars(wtcpue),
+                 mean,na.rm = T) %>%
     filter(wtcpue > 0)
 
-    if(nrow(data) == 0){
-      return(tibble())
+  # Only interpolate cases where there is more than 3 rows
+  # Marked by the function 
+    if(nrow(data) <= 3){
+      fit_tin <- tibble()
     }else{
@@
     return(fit_tin)
+}
+
+# Test me
+# Needs variables in Control panel
+# Test no data: "Alosa aestivalis", reg = "Northeast US Fall", yr = 1974 
+tis(input_data = ocean_data, grid = grid_eez_df, taxa = spp[1], reg = "Northeast US Fall", yr = 1974)
+
+```
+
+### Run function
+
+```{r interpol_run_fun, eval = T, echo = T}
+
+run_tis <- function(input_data, grid, years, taxa, reg){
+
+  # Run tis for species and surveys
+  for(r in 1:2){
+
+    partial_df <- bind_rows(
+      lapply(years,tis,input_data = ocean_data, grid = grid_eez_df, taxa = taxa, reg = regions[r])
+    )
+
+    if(r == 1){
+      historic_tif <- partial_df
+    }else{
+      historic_tif <- bind_rows(historic_tif,partial_df)
+    }
+
+  }
+
+  # ----------------------- #
+  # Save dataset per species
+  # ----------------------- #
+
+  # Set file name
+  name <- paste0("tif_",str_replace(taxa," ","_"),".csv")
+
+  # Set path name
+  save_path <- my_path("R","Partial/Interpolation")
+
+  # Set complete path
+  save_name <- paste0(save_path,name)
+
+  # Create folder if it does not exist
+  if(file.exists(save_path) == F){
+    dir.create(save_path)
+  }
+
+  #  Save file
+  write_csv(historic_tif,save_name)
+
 }
@@
 
-# taxa
-spp <- "Centropristis striata"
-
 # regions
 regions <- c("Northeast US Fall" , "Northeast US Spring")
+
+# taxa
+# spp <- "Centropristis striata"
+
+spp <- ocean_data %>% 
+  filter(region %in% regions,
+         spp != "NA") %>% 
+  pull(spp) %>% 
+  unique()
 
@@
 
-# Simple for-loop for running both regions (seasons)
-for(r in 1:2){
+# # Simple for-loop for running both regions (seasons)
+# for(r in 1:2){
+#   
+#   partial_df <- bind_rows(
+#     lapply(years,tis,input_data = ocean_data, grid = grid, taxa = spp, reg = regions[r])
+#   )
+#   
+#   if(r == 1){
+#     historic_tif <- partial_df
+#   }else{
+#     historic_tif <- bind_rows(historic_tif,partial_df)
+#   }
+#   
+# }
 
-  partial_df <- bind_rows(
-    lapply(years,tis,input_data = ocean_data, grid = grid, taxa = spp, reg = regions[r])
-  )
+# Run for one species
+    run_tis(input_data = ocean_data, grid = grid_eez_df, taxa = "Centropristis striata", years = years, reg = regions)
 
-  if(r == 1){
-    historic_tif <- partial_df
-  }else{
-    historic_tif <- bind_rows(historic_tif,partial_df)
-  }
-
-}
+# Run for multiple species
+    run_tis(input_data = ocean_data, grid = grid_eez_df, taxa = spp[1], years = years, reg = regions)
 

### 2021-06-09 Scripts/spatial_analisis.Rmd
run interpolation for all species

@@
   # Testing
-  # print(paste(yr))
-  # yr = 1976
+  print(paste(yr))
+  yr = 1976
   # --------------- #
@@
 # Test no data: "Alosa aestivalis", reg = "Northeast US Fall", yr = 1974 
-tis(input_data = ocean_data, grid = grid_eez_df, taxa = spp[1], reg = "Northeast US Fall", yr = 1974)
+tis(input_data = ocean_data, grid = grid_eez_df, taxa = "Illex illecebrosus", reg = "Northeast US Fall", yr = 1973)
+
+lapply(years,tis,input_data = ocean_data, grid = grid_eez_df, taxa = "Illex illecebrosus", reg = regions[2])
 
@@
 
+  return_msg <- paste("Interpolation done for", taxa)
+
+  return(return_msg)
+
 }
+
+# Test me
+    # run_tis(input_data = ocean_data, grid = grid_eez_df, taxa = "Centropristis striata", years = years, reg = regions)
 
@@
 
-# taxa
-# spp <- "Centropristis striata"
-
+# species list
 spp <- ocean_data %>% 
@@
   unique()
+
+# Double check runs
+
+spp_runs <- tibble(taxa = (list.files(my_path("R","Partial/Interpolation")))) %>%
+  mutate(
+    taxa = str_remove(taxa, "tif_"),
+    taxa = str_remove(taxa, ".csv"),
+    taxa = str_replace(taxa, "_", " ")
+  )
+
+# Missing runs
+spp <- tibble(taxa=spp) %>% 
+  anti_join(spp_runs) %>% 
+  pull(taxa)
 
@@
 
-# Run for a single region
-# historic_tif <- bind_rows(
-  # lapply(years,tis,input_data = ocean_data, grid = grid, taxa = "Centropristis striata", reg = regions[2])
+# single species run
+# run_tis(input_data = ocean_data,
+#         grid = grid_eez_df,
+#         years = years,
+#         reg = regions,
+#         taxa = "Illex illecebrosus"
 # )
 
-# # Simple for-loop for running both regions (seasons)
-# for(r in 1:2){
-#   
-#   partial_df <- bind_rows(
-#     lapply(years,tis,input_data = ocean_data, grid = grid, taxa = spp, reg = regions[r])
-#   )
-#   
-#   if(r == 1){
-#     historic_tif <- partial_df
-#   }else{
-#     historic_tif <- bind_rows(historic_tif,partial_df)
-#   }
-#   
-# }
-
-# Run for one species
-    run_tis(input_data = ocean_data, grid = grid_eez_df, taxa = "Centropristis striata", years = years, reg = regions)
-
-# Run for multiple species
-    run_tis(input_data = ocean_data, grid = grid_eez_df, taxa = spp[1], years = years, reg = regions)
-
-# Save data for future plotting
-# write_csv(historic_tif,
-          # paste0(my_path("R","Partial"),"interpolated_data.csv"))
-
-# Show data in notebook
-head(historic_tif,10) %>% 
-   kable(
-    format = "html",
-    caption = "Extrapolated data") %>% 
-  kableExtra::kable_minimal() %>% 
-  kableExtra::kable_styling() %>%
-  kableExtra:: scroll_box(width = "100%", height = "300px")
+# Run them all in parallel
+parallel::mclapply(spp,
+                   run_tis, 
+                   input_data = ocean_data,
+                   grid = grid_eez_df,
+                   years = years,
+                   reg = regions
+)
 

### 2021-06-09 Scripts/spatial_analisis.Rmd
run analysis for bsb

@@
   # Testing
-  print(paste(yr))
-  yr = 1976
+  # print(paste(yr))
+  # yr = 1976
   # --------------- #
@@
 # Test no data: "Alosa aestivalis", reg = "Northeast US Fall", yr = 1974 
-tis(input_data = ocean_data, grid = grid_eez_df, taxa = "Illex illecebrosus", reg = "Northeast US Fall", yr = 1973)
+# tis(input_data = ocean_data, grid = grid_eez_df, taxa = "Illex illecebrosus", reg = "Northeast US Fall", yr = 1973)
 
-lapply(years,tis,input_data = ocean_data, grid = grid_eez_df, taxa = "Illex illecebrosus", reg = regions[2])
+# lapply(years,tis,input_data = ocean_data, grid = grid_eez_df, taxa = "Illex illecebrosus", reg = regions[2])
 
@@
 # Load interpolated data
-historic_tif <- my_path("R","Partial","interpolated_data.csv",read = T)
+# "Centropristis striata"
+# 
+historic_tif <- my_path("R","Partial/Interpolation","tif_Centropristis_striata.csv", read = T)
+
+# Spatial data
+
+States <- c("maine", "new hampshire", "massachusetts", "connecticut", "rhode island", "new york", "new jersey", "delaware", "maryland", "virginia", "north carolina","pennsylvania")
+
+# US State Map (land)
+
+land_sf <- st_as_sf(map("state", plot = FALSE, fill = TRUE)) %>% 
+  filter(ID %in% States)
 
@@
 
+# print for notebook
+head(historic_tif)
 ```
@@
   group_by(year,region) %>% 
-  summarise(total_value = sum(value,na.rm=T))
+  summarise(total_value = sum(value,na.rm=T),.groups = "drop")
 
@@
   group_by(ID = state,period,region) %>% 
-  summarise(mean_per = round(mean(percentage)))
+  summarise(mean_per = round(mean(percentage)),.groups = "drop")
 
@@
             by = c("year","region")) %>%
-  mutate(percentage = state_value/total_value*100) %>% 
-  group_by(state,region)
+  mutate(percentage = state_value/total_value*100)
 
@@
 state_fit <- historic_tif %>% 
-  group_by(state,year,region) %>% 
+  group_by(state,year,region,.groups = "drop") %>% 
   summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 

### 2021-06-09 Allocation_tool/server.R
Yes, is faster!

@@ -33,11 +33,15 @@ shinyServer(function(input, output) {
     # ---------------------------- #
     raw_data <- reactive({
         
-        data <- readRDS("/Volumes/Enterprise/Data/pinskylab-OceanAdapt-966adf0/data_clean/dat_exploded.rds") %>% 
-            filter(
-                # spp %in% c ("Centropristis striata","Gadus morhua"),
-                region %in% c("Northeast US Fall" , "Northeast US Spring")
-            ) #No more seasons
+        name <- paste0("obs_",str_replace(input$SppSelection," ","_"),".csv")
+        
+        data <- my_path("D","Spp/Observation",name = name, read = T)
+        
+        # data <- readRDS("/Volumes/Enterprise/Data/pinskylab-OceanAdapt-966adf0/data_clean/dat_exploded.rds") %>%
+        #     filter(
+        #         # spp %in% c ("Centropristis striata","Gadus morhua"),
+        #         region %in% c("Northeast US Fall" , "Northeast US Spring")
+        #     ) #No more seasons
         
     })
     
@@ -48,7 +52,9 @@ shinyServer(function(input, output) {
     # ---------------------------- #
     tif_data <- reactive({
         
-        data <- MyFunctions::my_path("R","Partial","interpolated_data.csv",read = T)
+        name <- paste0("tif_",str_replace(input$SppSelection," ","_"),".csv")
+        
+        data <- my_path("R","Partial/Interpolation",name = name, read = T)
 
     })
     
@@ -85,7 +91,7 @@ shinyServer(function(input, output) {
             avr_lat <- plot_data %>% 
                 filter(wtcpue > 0) %>% 
                 group_by(year,spp) %>%
-                summarise(mean_lat = mean(lat,na.rm = T)) %>% 
+                summarise(mean_lat = mean(lat,na.rm = T), .groups = "drop") %>% 
                 group_by(spp) %>%
                 mutate(Rmean = zoo::rollmean(x = mean_lat,
                                              5,
@@ -261,7 +267,7 @@ shinyServer(function(input, output) {
                        year %in% years
                        ) %>% 
             group_by(year,region) %>% 
-            summarise(total_value = sum(value,na.rm=T))
+            summarise(total_value = sum(value,na.rm=T), .groups = "drop")
         
         # group by state
         state_fit <- tif_data() %>% 
@@ -314,7 +320,7 @@ shinyServer(function(input, output) {
                #year %in% years
         ) %>% 
[…]

### 2021-06-09 Scripts/spatial_analisis.Rmd
spread ocean data into taxa files for faster computarion on app

@@
 
-```{r dat_exploded, eval = T, echo = F}
+```{r dat_exploded, eval = T, echo = F, fig.width = 9}
 
@@
        # region %in% c("Northeast US Fall" , "Northeast US Spring")) #No more seasons
+
+spp_data <- function(spp){
+
+  name_save <- paste0(my_path("D","Spp/Observation"),"obs_",str_replace(spp[1], " ", "_"),".csv")
+
+ocean_data %>% 
+  filter(spp == spp,
+       region %in% c("Northeast US Fall" , "Northeast US Spring")
+       ) %>% 
+  write_csv(., name_save)
+
+}
+
+spp_list <- ocean_data %>% 
+  filter(region %in% regions,
+         spp != "NA") %>% 
+  pull(spp) %>% 
+  unique()
+
+lapply(spp_list, spp_data)
 

### 2021-06-15 Scripts/spatial_analisis.Rmd
trtying to get the style right

@@
   html_notebook:
+    css: _config.yml
   fig_width: 6

### 2021-06-15 Scripts/spatial_analisis.Rmd
included name

--- 2021-06-09 Scripts/spatial_analisis.Rmd
@@
 title: "Spatial Analysis"
+author: "Juliano Palacios Abrantes"
 output: 

### 2021-06-15 Scripts/spatial_analisis.Rmd

--- 2021-06-09 Scripts/spatial_analisis.Rmd
@@
 title: "Spatial Analysis"
+author: "Juliano Palacios Abrantes"
 output:
- # html_document
   html_notebook:
@@
     fig_height: 4
-  toc: false
+    code_folding: hide
+    toc: yes
     toc_depth: 3
-  code_folding: hide
     toc_float:
       collapsed: false
+    theme: darkly
 ---

### 2021-06-15 Scripts/spatial_analisis.Rmd
better explained index

@@
 
-# Load data
+# Methods
 
-## Maps data
+## Spatial data preparation
+
+### Load data
+
+#### Maps data
 
@@
 
-## Spatial component
-
 ### Create base shapefile for computation
@@
   geom_sf(data = eez_sf, aes(), fill = NA) +
-  geom_sf(data = state_bf, aes(color = state), fill = NA)
+  geom_sf(data = state_bf, aes(color = state), fill = NA) +
+  scale_color_manual(values = state_pallet)
 #
@@
 
-Here we expand a grid within the buffer so we can estimate the proportion of each state
+Here we expand a grid within the buffer so we can estimate the proportion of each state.
+
+*Note:* Dark grey shaded area is the grid
 
@@
             alpha = 0.2
-  )
+  ) +
+  scale_color_manual(values = state_pallet)
 
@@
     geom_sf(data = eez_sf, aes(),fill =NA) + 
+    scale_color_manual(values = state_pallet) +
     theme(legend.position = ""),
@@
   ggplot() +
-    geom_sf(data = grid_sf, aes(color = state),size = 0.1, alpha = 0.3) +
+    geom_sf(data = grid_sf, aes(color = state),size = 0.1, alpha = 0.5) +
     facet_wrap(~state) +
-    theme(legend.position = "top"),
+    theme(legend.position = "top") +
+    scale_color_manual(values = state_pallet),
   nrow = 1)
@@
 
-## Interpolation rutine
+### Interpolation rutine
 
-Here we [interpolate](https://swilke-geoscience.net/post/spatial_interpolation/) the survey data within the previously created grid.
+In this step we [interpolate](https://swilke-geoscience.net/post/spatial_interpolation/) the survey data within the previously created grid following a Triangular Irregular Surface method.
 
@@
 
-### Function for interpolation
+#### Functions needed
 
-This is the main function used to interpolate the data per year. It follows a Triangular Irregular Surface method using the `interp::interp()` function.
+We need to create a couple of functions to run the whole process
+
+##### Interpolation main fx (tis).
+
+This is the main function used to interpolate the data per year. It follows a Triangular Irregular Surface method using the `interp::interp()` function. If you want to see the function clic on `code`
 
@@
 
-### Run function
+##### Run function
+
+This is a sub-function that runs the `tis()` function by taxa and region. It saves the output as a .csv file for each species.
 
@@
 
-### Ocean adapt data
+#### Survey data
+
+The interpolation was done with NOAA Northeast Fisheries Science Center Spring and Fall Bottom Trawl Surveys [data](https://www.fisheries.noaa.gov/region/new-england-mid-atlantic#science) provided by [Ocean adapt](https://oceanadapt.rutgers.edu/).
+Data was accessed trough the [Github](https://github.com/pinskylab/OceanAdapt).
+
+*In primary publications using data from the database, please cite Pinsky et al.
+2013.
+Marine taxa track local climate velocities.
+Science 341: 1239-1242 doi: 10.1126/science.1239352, as well as the original data sources.*
 
 - Using only the Northeast US Fall and Spring bottom trawl survey data for now
+
+##### Splitting up data
+
+- No part on spatial analysis. Can be ignored.
+
+This is just a sub-step to split up the data into single species files. This makes the app faster as it only needs to load species specific data, rather than all the data at de begining.
 
@@
 
-### Control Pannel
+#### Control Pannel
 
-Load required data. Note that some of it has been previously created
+This is where we load the required data and prepare to run the interpolation function. Note that some of the data here has been previously created
 
@@
 
-### Run routine
+#### Run routine
+
+Here we just run the routine for each of the species present in the Northeast US Fall and Spring surveys between 1973 and 2019.
+
+- Note there are 43 identified taxa
+- Some taxa do not have presence data in some years
 
@@
 
-```{r load_data}
+This section shows preliminary results for Black sea bass (*Centropristis striata*).
+
+```{r load_data, eval = T, echo = T}
 
@@
 
-## Points
+## Average proportion
+
+This map shows the average proportion of the extrapolated value from the whole study period within each State's water.
+
+*Note:* Grey tiles represent `NAs`
 
@@
   scale_color_viridis("Mean Proportion", alpha = 0.8)
-
 ```
 
-## Map
+## Proportion Change
+
+Here we show the average proportion of the interpolation by State and time period. Time periods were arbitrary defined as;
+
+- Early; 1972 to 1984
+- Mid; 1985 to 1997
+- Late; 1998 to 2011
+- Now; 2012 to 2019
+
+*Notes:* To panel represents Fall survey and bottom panel Spring. This computation considers the Overlapping of state waters.
 
@@
   mutate(percentage = state_value/total_value*100) %>% 
-  left_join(periods) %>% 
+  left_join(periods,
+            by = "year") %>% 
   group_by(ID = state,period,region) %>% 
@@
 
-This graph shows the proportion of each State over time
+This graph shows the proportion of the interpolation value each State has over time.
+
+*Note:* This plot is interactive. For ease comparison between States you can;
+
+- *One* click on any State to *remove* it from the plot 
+- *Two* clicks on any State to *isolate it* from the plot (other states can then be added by just clicking on them).
+- The bottom panel allows you to reduce the time frame
 
@@
   layout(hovermode = "x") %>%
-  # add_trace() %>% 
   rangeslider()
@@
 ```
-## Area plot (running)
 
-This graph shows the proportion of each State smoothed over a 10 years running mean. It helps seeing the trends better (I Think...)
+## Area plot (running mean)
+
+This graph shows the proportion of each State smoothed over a *10 years running mean**. It allows to better see increasing and decreasing trends.
+
+*Note:* This plot is also interactive and thus, follows the same options of the previous one.
 

### 2021-06-15 Scripts/spatial_analisis.Rmd
Final updates to inddex

@@
   ggplot() +
-  geom_sf(aes(color = state), alpha = 0.3)
+  geom_sf(aes(color = state), alpha = 0.3) +
+  scale_color_manual(values = state_pallet)
 

### 2021-06-22 Scripts/Abstract.Rmd
included IMBER abstract

---
title: "Managing across boundaries: shifts in stock distribution challenges United States' north Atlantic fisheries management"
author: "Crosson Scott, Dumas Chris, Fujita Rod, Jensen Olaf, Levine Arielle, Longo Katie, Palacios-Abrantes Juliano"
output: word_document
---

# Abstract 
(Currently 202/250-300 words)

Climate change is driving shifts in fish stock distributions that will affect resource availability across different jurisdictions around the world. Elinor Ostrom’s fundamental principles of common pool resource governance include a requirement for clear boundaries over resource units. However, when stock ranges shift, governance systems and boundaries are no longer aligned. This misalignment has already created conflicts around access and the re-distribution of benefits flowing from the stocks. Here, we look at the historical shift in the distribution of managed stocks across the North East Atlantic coast of the United States of America. We estimate the yearly abundance proportion that each State had from 1971 to 2019 and compare that to the current quota allocation policy. We found that, for many species, the stock proportion has shifted since the establishment of the allocations policy, creating a misalignment between the quota allocation and the stock's biomass distribution. Our findings have direct impact of on the management of stocks that cross jurisdictions highlighting the need for allocation strategies that can cope with such biomass changes. Moreover, the implementation of such strategies are challenged by the complexity of the Northeast Atlantic social-ecological system that expands multiple stakeholders and where changes can result in winner and looser States. Strategies that account for changes in stock distribution are key to maintain the sustainability of the stock but should consider strategies to address the potential re-distribution of benefits.

# Instructions

- Deadline to submit: 30 June
- Your abstract must be uploaded as a Word file with 11 point Arial font.
- Title
- Author(s) (last name, first name). If there is more than one author, underline the name of the presenter.
- The abstract should be between 250-300 words

### 2021-06-28 Scripts/spatial_analisis.Rmd
Removed Pennsylvania from the analysis

@@
 output:
+  # html_document
   html_notebook:
@@
 
-States <- c("maine", "new hampshire", "massachusetts", "connecticut", "rhode island", "new york", "new jersey", "delaware", "maryland", "virginia", "north carolina","pennsylvania")
+States <- c("maine", "new hampshire", "massachusetts", "connecticut", "rhode island", "new york", "new jersey", "delaware", "maryland", "virginia", "north carolina")
 
@@
 grid_sf <-  st_read("/Volumes/Enterprise/Data/AcrossBoundaries/Data/Spatial/grid_sf/grid_eez_sf.shp")
+
+# Create specific state pallet from our friend Wes Andersson
+state_pallet <- c(wes_palette(n = 5, name = "Darjeeling1"),
+                               wes_palette(n = 5, name = "Darjeeling2"),
+                               wes_palette(n = 3, name = "Royal1")
+                  )
 
@@
   ) +
-  scale_color_manual(values = state_pallet)
+  scale_color_manual(values = state_pallet) +
+  theme_bw()
 
@@
 # Get the overlapping segments 
+# NOTE: Takes some gooooood time
 grid_eez_sf <- st_intersection(grid_sf,eez_sf)
 
-# write_sf(grid_eez_sf, paste0(my_path("D", "Spatial"),"grid_eez_sf.shp"))
+write_sf(grid_eez_sf, paste0(my_path("D", "Spatial"),"grid_eez_sf.shp"))
 
@@
 # write_csv(grid_eez_df, paste0(my_path("R", "Partial"),"grid_eez_df.csv"))
+
+# Remove Pennsylvania from sf
+grid_eez_df <-  st_read("/Volumes/Enterprise/Data/AcrossBoundaries/Data/Spatial/grid_sf/grid_eez_sf.shp") %>% 
+  filter(state != "pennsylvania")
+
+# Make sure no Penn.
+unique(grid_eez_df$state)
+
+# over write sf
+write_sf(grid_eez_df, paste0(my_path("D", "Spatial"),"grid_eez_sf.shp"))
+
+#Make sure of things
+
+grid_eez_sf <-  st_read("/Volumes/Enterprise/Data/AcrossBoundaries/Data/Spatial/grid_sf/grid_eez_sf.shp")
+
+unique(grid_eez_sf$state)
+
+# DONE!
 

### 2021-06-28 Scripts/spatial_analisis.Rmd
Keep the zeros!

@@
     summarise_at(vars(wtcpue),
-                 mean,na.rm = T) %>%
-    filter(wtcpue > 0)
+                 mean,na.rm = T)
 

### 2021-06-28 Scripts/spatial_analisis.Rmd
grid eez df for pens.

@@
 # Remove Pennsylvania from sf
-grid_eez_df <-  st_read("/Volumes/Enterprise/Data/AcrossBoundaries/Data/Spatial/grid_sf/grid_eez_sf.shp") %>% 
+grid_eez_sf <-  st_read("/Volumes/Enterprise/Data/AcrossBoundaries/Data/Spatial/grid_sf/grid_eez_sf.shp") %>% 
   filter(state != "pennsylvania")
@@
 # Make sure no Penn.
-unique(grid_eez_df$state)
+unique(grid_eez_sf$state)
 
 # over write sf
-write_sf(grid_eez_df, paste0(my_path("D", "Spatial"),"grid_eez_sf.shp"))
+write_sf(grid_eez_sf, paste0(my_path("D", "Spatial"),"grid_eez_sf.shp"))
 
@@
 unique(grid_eez_sf$state)
+
+# Now save it as a DF too
+
+grid_eez_df <- as.data.frame(grid_eez_sf) %>%
+  select(state,index) %>% 
+  left_join(ne_grid, 
+            by = "index")
+
+write_csv(grid_eez_df, paste0(my_path("R", "Partial"),"grid_eez_df.csv"))
 

### 2021-06-28 Scripts/spatial_analisis.Rmd
moved the pen. analysis to its own chunk

@@
 
-write_sf(grid_eez_sf, paste0(my_path("D", "Spatial"),"grid_eez_sf.shp"))
+# write_sf(grid_eez_sf, paste0(my_path("D", "Spatial"),"grid_eez_sf.shp"))
 
@@
 # write_csv(grid_eez_df, paste0(my_path("R", "Partial"),"grid_eez_df.csv"))
+
+# Plot to make sure makes sense (Picasso syle)
+grid_eez_sf %>%
+  st_simplify(preserveTopology = TRUE, dTolerance = 10000) %>% #0.1 for paper
+  ggplot() +
+  geom_sf(aes(color = state), alpha = 0.3) +
+  scale_color_manual(values = state_pallet)
+
+```
+
+```{r remove_pen, eval = F, echo = F}
+
+####____________________________________________### 
+# Solving for Issue #8 Pennsylvania has NO coast
+####____________________________________________###
 
@@
 
-grid_eez_sf <-  st_read("/Volumes/Enterprise/Data/AcrossBoundaries/Data/Spatial/grid_sf/grid_eez_sf.shp")
+# grid_eez_sf <-  st_read("/Volumes/Enterprise/Data/AcrossBoundaries/Data/Spatial/grid_sf/grid_eez_sf.shp")
 
-unique(grid_eez_sf$state)
+# unique(grid_eez_sf$state)
 
@@
 
-grid_eez_df <- as.data.frame(grid_eez_sf) %>%
-  select(state,index) %>% 
-  left_join(ne_grid, 
-            by = "index")
+# grid_eez_df <- as.data.frame(grid_eez_sf) %>%
+  # select(state,index) %>%
+  # left_join(ne_grid,
+            # by = "index")
 
-write_csv(grid_eez_df, paste0(my_path("R", "Partial"),"grid_eez_df.csv"))
-
-# DONE!
-
-# Plot to make sure makes sense (Picasso syle)
-grid_eez_sf %>%
-  st_simplify(preserveTopology = TRUE, dTolerance = 10000) %>% #0.1 for paper
-  ggplot() +
-  geom_sf(aes(color = state), alpha = 0.3) +
-  scale_color_manual(values = state_pallet)
-
+# write_csv(grid_eez_df, paste0(my_path("R", "Partial"),"grid_eez_df.csv"))
 ```

### 2021-06-29 Scripts/spatial_analisis.Rmd
Area plot and map created for paper

@@
 output:
-  # html_document
-  html_notebook:
+  html_document
+  # html_notebook:
     fig_width: 6
@@
 library(MyFunctions)
-MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","viridis","wesanderson","knitr","kableExtra","plotly"))
+MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","viridis","wesanderson","knitr","kableExtra","plotly","ggrepel","ggsflabel"))
 ```
@@
 land_sf <- st_as_sf(map("state", plot = FALSE, fill = TRUE)) %>% 
-  filter(ID %in% States)
+  filter(ID %in% States) %>%
 
@@
 
-This is just a sub-step to split up the data into single species files. This makes the app faster as it only needs to load species specific data, rather than all the data at de begining.
+This is just a sub-step to split up the data into single species files. This makes the app faster as it only needs to load species specific data, rather than all the data at de beginning.
 
-```{r dat_exploded, eval = T, echo = F, fig.width = 9}
+```{r dat_exploded, eval = F, echo = F, fig.width = 9}
 
@@
 # Run them all in parallel
-parallel::mclapply(spp,
+lapply(spp,
                    run_tis, 
@@
 # 
-historic_tif <- my_path("R","Partial/Interpolation","tif_Centropristis_striata.csv", read = T)
+historic_tif <- my_path("R","Partial/Interpolation","tif_Centropristis_striata.csv", read = T) %>% 
+  mutate(state = str_to_sentence(state))
 
@@
 land_sf <- st_as_sf(map("state", plot = FALSE, fill = TRUE)) %>% 
-  filter(ID %in% States)
+  filter(ID %in% States) %>% 
+  mutate(abrev = c("CO","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VI"),
+         state = str_to_sentence(ID)
+         )
 
@@
 periods <-tibble(
-  period = c(rep("a early",12),
-             rep("b mid",12),
-             rep("c late",12),
-             rep("d now",12)
+  order = c(rep("a",12),
+            rep("b",12),
+            rep("c",12),
+            rep("d",11)
   ),
-  year = c(seq(1972,1984,1),
-            seq(1985,1997,1),
-            seq(1998,2011,1),
-            seq(2012,2019,1)
+  label = c(rep("1973-1984",12),
+            rep("1985-1996",12),
+            rep("1997-2008",12),
+            rep("2009-2019",11)
+  ),
+  year = c(seq(1973,1984,1),
+           seq(1985,1996,1),
+           seq(1997,2008,1),
+           seq(2009,2019,1)
   )
 )
+
+state_lat <- historic_tif %>%
+  group_by(state) %>% 
+  summarise(
+    order = mean(lat)
+  ) %>% 
+  mutate(abrev = c("CO","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VI")
+  ) %>% 
+  arrange(desc(order)) %>% 
+  mutate(order= letters[1:11])
 
@@
                                wes_palette(n = 5, name = "Darjeeling2"),
-                               wes_palette(n = 3, name = "Royal1")
+                               # wes_palette(n = 2, name = "GrandBudapest1")
+                  "#FD6467"
                   )
@@
 
-*Note:* Grey tiles represent `NAs`
+*Note:* This is intended to be a supplemental figure
 
@@
 
-ggplot(data_grid) +
+ggplot(data = subset(data_grid, !is.na(mean))) +
   geom_tile(
@@
   ) +
+  geom_sf(data = land_sf, aes()) +
   facet_wrap(~ ID  +  region,
              ncol = 4) +
+  labs(x = "Longitude", y = "Latitude") +
   scale_fill_viridis("Mean Proportion", alpha = 0.8) +
-  scale_color_viridis("Mean Proportion", alpha = 0.8)
+  scale_color_viridis("Mean Proportion", alpha = 0.8) +
+  my_ggtheme_p()
 ```
@@
 
-- Early; 1972 to 1984
+- Early; 1973 to 1984
 - Mid; 1985 to 1997
@@
 
-*Notes:* To panel represents Fall survey and bottom panel Spring. This computation considers the Overlapping of state waters.
+*Notes:* Panel represents the **Spring.** survey. This computation considers the Overlapping of state waters.
 
-```{r area_map, eval = T, echo = T, fig.width = 10}
+```{r paper_figure_area_map, eval = F, echo = F, results='hide'}
 
@@
             by = "year") %>% 
-  group_by(ID = state,period,region) %>% 
-  summarise(mean_per = round(mean(percentage)),.groups = "drop")
+  group_by(state,order,label,region) %>% 
+  summarise(mean_per = round(mean(percentage)),.groups = "drop") %>% 
+  #Only show results for spring
+  filter(str_detect(region,"Spring"))
 
@@
   left_join(state_fit,
-            by = "ID") %>% 
+            by = "state") %>% 
   ggplot() +
   geom_sf(aes(fill = mean_per)) +
-  viridis::scale_fill_viridis("Mean Proportion", alpha = 0.8) +
-  facet_wrap(~region + period, nrow = 2) +
-  my_ggtheme_m()
+  viridis::scale_fill_viridis("Average proportion per State", alpha = 0.8) +
+  facet_wrap(~ label, nrow = 1) +
+  geom_sf_label_repel(data = land_sf, aes(label= abrev), 
+                      size = 2,
+                      box.padding = 0.10,
+                      hjust = 1) +
+  labs(x = "Latitude", 
+       y = "Longitude") +
+  my_ggtheme_p(facet_tx_s = 16,
+               leg_pos = "bottom") +
+  theme(legend.key.width = unit(4,"line")) +
+  ggsave(filename = "proportion_chg.jpg",
+         plot = ggplot2::last_plot(),
+         path = my_path("R","Figures"),
+         width = 12,
+         height = 5
+         )
+
+```
+
+```{r area_map, eval = T, echo = T, fig.width = 10, fig.height=6}
+
+total_fited <- historic_tif %>% 
+  group_by(year,region) %>% 
+  summarise(total_value = sum(value,na.rm=T),.groups = "drop")
+
+state_fit <- historic_tif %>% 
+  group_by(state,year,region) %>% 
+  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
+  left_join(total_fited,
+            by = c("year","region")) %>%
+  mutate(percentage = state_value/total_value*100) %>% 
+  left_join(periods,
+            by = "year") %>% 
+  group_by(state,order,label,region) %>% 
+  summarise(mean_per = round(mean(percentage)),.groups = "drop")
+
+# check percentages
+# state_fit %>% 
+#   group_by(period) %>% 
+#   summarise(sum(mean_per))
+
+p <- land_sf %>% 
+  left_join(state_fit,
+            by = "state") %>% 
+  ggplot() +
+  # geom_sf(aes(fill = mean_per)) +
+  geom_sf(aes(fill = mean_per, text = paste(state, mean_per,"% of proportion"))) +
+  viridis::scale_fill_viridis("Average proportion per State", alpha = 0.8) +
+  facet_wrap(~ region + label, 
+             nrow = 2) +
+  labs(x = "Latitude", 
+       y = "Longitude") +
+  my_ggtheme_p(facet_tx_s = 12,
+               leg_pos = "bottom") +
+  theme(legend.key.width = unit(1,"line"))
+
+ggplotly(p,
+         tooltip = "text",
+         dynamicTicks = FALSE) %>% 
+    style(hoverlabel = list(bgcolor = "white"), hoveron = "fill")
 
@@
 
+# Plot me
 p <- ggplot(state_fit) +
@@
 
-```{r area_lm_plot, eval = T, echo = T, fig.height = 10, fig.width = 10}
+```{r paper_plot_area_ave, eval = F, echo = F, results='hide'}
+
+# group by state
+state_fit <- historic_tif %>% 
+  group_by(state,year,region) %>% 
+  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
+  left_join(total_fited,
+            by = c("year","region")) %>%
+  mutate(percentage = state_value/total_value*100) %>% 
+  group_by(state,region) %>% 
+  mutate(RMean = zoo::rollmean(x = percentage, 
+                            10,
+                            fill = NA,
+                            na.rm=T)
+    ) %>% 
+  #Only show results for spring
+  filter(str_detect(region,"Spring"),
+         !is.na(RMean) # Remove NAs from rollmean
+         ) %>%  
+  left_join(state_lat)
+
+# Plot me
+ggplot(state_fit) +
+  geom_area(
+    aes(
+      x = year,
+      y = round(RMean),
+      fill = order
+      # fill = state
+    )
+  ) +
+  ylab("Propotion (10 yrs running average)") +
+  # viridis::scale_fill_viridis(discrete = T, alpha = 0.8) +
+  scale_fill_manual(
+    "State",
+    values = state_pallet,
+    labels = state_fit %>% arrange(order) %>%  pull(state) %>% unique()
+  ) +
+  my_ggtheme_p(leg_pos = "right") +
+  theme(legend.key.width = unit(1,"line")) + 
+  ggsave(filename = "area_plot_avg.jpg",
+         plot = ggplot2::last_plot(),
+         path = my_path("R","Figures"),
+         width = 8,
+         height = 6
+  )
+
+```
+
+```{r area_plot, eval = T, echo = T, fig.height = 10, fig.width = 10}
 
@@
                             na.rm=T)
-    )
+    ) %>%  
+  left_join(state_lat)
 
@@
       fill = state
+      # fill = order
     )
@@
   ylab("10 yrs running average (%)") +
-  # viridis::scale_fill_viridis(discrete = T, alpha = 0.8) +
-  scale_fill_manual(values = state_pallet) +
+  scale_fill_manual(
+    "State",
+    values = state_pallet,
+    # labels = state_fit %>% arrange(order) %>%  pull(state) %>% unique()
+  ) +
   MyFunctions::my_ggtheme_p() +

### 2021-06-29 Scripts/spatial_analisis.Rmd
created figure of buffers for manuscript

@@
   filter(ID %in% States) %>% 
+  mutate(abrev = c("CO","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VI"))
 
@@
   scale_color_manual(values = state_pallet)
+
+```
+
+```{r cropped_plot_paper}
+
+plot_data <-grid_eez_sf %>% 
+    mutate(state = str_to_sentence(state)) %>% 
+    left_join(state_lat)
+
+p <- gridExtra::grid.arrange(
+  # Overall (overlapping) position
+  ggplot(plot_data) +
+    geom_sf(data = eez_sf, aes(), fill = "white") + 
+    geom_sf(aes(color = order, fill = order), alpha = 0.3) +
+    geom_sf(data = land_sf, aes()) +
+    geom_sf_label_repel(data = land_sf, aes(label= abrev), 
+                      size = 2,
+                      box.padding = 0.10,
+                      hjust = 1) +
+    scale_color_manual(values = state_pallet) +
+    scale_fill_manual(values = state_pallet) +
+    my_ggtheme_p(leg_pos = "",
+                 ax_tx_s = 12) +
+    coord_sf(ylim = c(30,48)) +
+    scale_y_continuous(breaks = c(30,35,40,45))+
+    labs(x = "", y = ""),
+  # Showing each state separately
+
+    ggplot(plot_data) +
+    geom_sf(data = land_sf, aes(), fill = "grey80") +
+    geom_sf( aes(color = order),size = 0.1, alpha = 0.8) +
+    facet_wrap(~ state) +
+    theme(legend.position = "top") +
+    scale_color_manual(values = state_pallet,
+                       labels = plot_data %>% arrange(order) %>%  pull(state) %>% unique()) +
+    my_ggtheme_p(leg_pos = "",
+                 ax_tx_s = 6,
+                 axx_tx_ang = 45,
+                 hjust = 1
+                 ),
+  nrow = 1,
+  bottom = "Longitude",
+  left = "Latitude")
+
+  ggsave(filename = "buffer_figure.jpg",
+         plot = p,
+         path = my_path("R","Figures"),
+         width = 10,
+         height = 5
+         )
 
@@
 States <- c("maine", "new hampshire", "massachusetts", "connecticut", "rhode island", "new york", "new jersey", "delaware", "maryland", "virginia", "north carolina")
+
+# Managed species by Mid-Atlantic Council Management Plans, and State waters
+# https://www.fisheries.noaa.gov/new-england-mid-atlantic/commercial-fishing/new-england-mid-atlantic-fishery-management-plans
+
+Species <- c(
+  "Scomber scombrus",
+  "Doryteuthis (Amerigo) pealeii", #longfin squid
+  "Peprilus triacanthus", # butterfish
+  "Illex illecebrosus", #shortfin squid
+  "Paralichthys dentatus", #summer flounder
+  "Stenotomus chrysops", #Scoop"
+  "Centropristis striata", # black sea bass
+  "Pomatomus saltatrix", # Bluefish
+  "Lopholatilus chamaeleonticeps", #golden tilefish
+  "Caulolatilus microps", #blueline tilefish
+  "Clupea harengus" # Atlantic herring (Jointly in State and Federal Waters)
+
+  )
 

### 2021-06-29 Scripts/spatial_analisis.Rmd
all species analysis

@@
 
+# Species data
+
 # Load interpolated data
@@
 # 
-historic_tif <- my_path("R","Partial/Interpolation","tif_Centropristis_striata.csv", read = T) %>% 
-  mutate(state = str_to_sentence(state))
-
-# Spatial data
-
-States <- c("maine", "new hampshire", "massachusetts", "connecticut", "rhode island", "new york", "new jersey", "delaware", "maryland", "virginia", "north carolina")
+# historic_tif <- my_path("R","Partial/Interpolation","tif_Centropristis_striata.csv", read = T) %>% 
+#   mutate(state = str_to_sentence(state))
+
+# Multiple species
 
@@
   "Scomber scombrus",
-  "Doryteuthis (Amerigo) pealeii", #longfin squid
+  "Doryteuthis (Amerigo) pealeii", #longfin squid WE DONT HAVE IT
   "Peprilus triacanthus", # butterfish
@@
   "Clupea harengus" # Atlantic herring (Jointly in State and Federal Waters)
-
-  )
+  )
+
+spp_paths <- list.files(my_path("R",extra_path = "Partial/Interpolation"))
+
+# Some gibiris for names
+taxon_list <- gsub("_"," ",spp_paths)
+taxon_list <- gsub("tif ","",taxon_list)
+taxon_list <- gsub(".csv","",taxon_list)
+
+taxon_list <- taxon_list[taxon_list %in% Species]
+
+# Now set a list of files to read
+taxon_read <- paste0("tif_",taxon_list,".csv")
+taxon_read <- gsub(" ","_",taxon_read)
+
+taxon_read <- spp_paths[spp_paths %in% taxon_read]
+
+taxon_read <- paste0(my_path("R",extra_path = "Partial/Interpolation"),taxon_read)
+
+# Load all sp in one table
+historic_spp <- bind_rows(lapply(taxon_read, fread)) %>% 
+  mutate(state = str_to_sentence(state))
+
+# Spatial data
+
+States <- c("maine", "new hampshire", "massachusetts", "connecticut", "rhode island", "new york", "new jersey", "delaware", "maryland", "virginia", "north carolina")
 
@@
 
-state_lat <- historic_tif %>%
+state_lat <- historic_spp %>%
   group_by(state) %>% 
@@
 # print for notebook
-head(historic_tif)
+head(historic_spp)
 ```
@@
 
- data_grid <- historic_tif %>% 
-  # left_join(periods) %>% 
-  # group_by(state,lat,lon,period) %>% 
+ data_grid <- historic_spp %>% 
   group_by(state,lat,lon,region) %>% 
-  summarise(mean = mean(value,na.rm= T), .groups = "drop") %>% 
-  rename(ID = state)
+  summarise(sum = sum(value,na.rm= T), .groups = "drop") %>% # sum of all species
+  group_by(state,lat,lon,region) %>% 
+  summarise(mean = mean(sum,na.rm= T), .groups = "drop") # average of all years
 
@@
   geom_sf(data = land_sf, aes()) +
-  facet_wrap(~ ID  +  region,
+  facet_wrap(~ state  +  region,
              ncol = 4) +
@@
 
-*Notes:* Panel represents the **Spring.** survey. This computation considers the Overlapping of state waters.
+*Notes:* Figure represents the **Spring** survey. This computation considers the Overlapping of state waters.
+
+### Proportional change per species
 
@@
 
-total_fited <- historic_tif %>% 
+total_fited <- historic_spp %>% 
+  group_by(year,region,spp) %>% 
+  summarise(total_value = sum(value,na.rm=T),.groups = "drop")
+
+state_fit <- historic_spp %>% 
+  group_by(state,year,region,spp) %>% 
+  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
+  left_join(total_fited,
+            by = c("year","region","spp")) %>%
+  mutate(percentage = state_value/total_value*100) %>% 
+  left_join(periods,
+            by = "year") %>% 
+  group_by(state,order,label,region,spp) %>% 
+  summarise(mean_per = round(mean(percentage)),.groups = "drop") %>% 
+  #Only show results for spring
+  filter(str_detect(region,"Spring")) %>% 
+  mutate(spp = gsub(" ","\n",spp))
+
+# The plot
+land_sf %>% 
+  left_join(state_fit,
+            by = "state") %>% 
+  ggplot() +
+  geom_sf(aes(fill = mean_per)) +
+  viridis::scale_fill_viridis("Average proportion per State", alpha = 0.8) +
+  facet_grid(spp ~ label) +
+  labs(x = "Longitude", 
+       y = "Latitude") +
+  my_ggtheme_p(facet_tx_s = 20,
+               leg_pos = "bottom",
+               axx_tx_ang = 45,
+               ax_tx_s = 12,
+               ax_tl_s = 18,
+               hjust = 1) +
+  theme(legend.key.width = unit(4,"line")) +
+  ggsave(filename = "proportion_chg_spp.jpg",
+         plot = ggplot2::last_plot(),
+         path = my_path("R","Figures"),
+         width = 14,
+         height = 17
+         )
+
+```
+
+### Aggregated Proportional change
+
+```{r area_map_aggregated, eval = T, echo = T, fig.width = 10, fig.height=6}
+
+total_fited <- historic_spp %>% 
   group_by(year,region) %>% 
@@
 
-state_fit <- historic_tif %>% 
+state_fit <- historic_spp %>% 
   group_by(state,year,region) %>% 
@@
   summarise(mean_per = round(mean(percentage)),.groups = "drop") %>% 
-  #Only show results for spring
   filter(str_detect(region,"Spring"))
-
-# check percentages
-# state_fit %>% 
-#   group_by(period) %>% 
-#   summarise(sum(mean_per))
 
@@
   facet_wrap(~ label, nrow = 1) +
-  geom_sf_label_repel(data = land_sf, aes(label= abrev), 
-                      size = 2,
-                      box.padding = 0.10,
-                      hjust = 1) +
-  labs(x = "Latitude", 
-       y = "Longitude") +
+  labs(x = "Longitude", 
+       y = "Latitude") +
   my_ggtheme_p(facet_tx_s = 16,
-               leg_pos = "bottom") +
-  theme(legend.key.width = unit(4,"line")) +
-  ggsave(filename = "proportion_chg.jpg",
+               leg_pos = "bottom",
+               leg_tl_s = 14,
+               ax_tx_s = 10,
+               ax_tl_s = 14) +
+  theme(legend.key.width = unit(2,"line")) +
+  ggsave(filename = "proportion_chg_agg.jpg",
          plot = ggplot2::last_plot(),
          path = my_path("R","Figures"),
-         width = 12,
+         width = 9,
          height = 5
@@
 
-```{r area_map, eval = T, echo = T, fig.width = 10, fig.height=6}
-
-total_fited <- historic_tif %>% 
+```{r area_map_aggregated, eval = T, echo = T, fig.width = 10, fig.height=6}
+
+total_fited <- historic_spp %>% 
   group_by(year,region) %>% 
@@
 
+total_fited <- historic_spp %>% 
+  group_by(year,region) %>% 
+  summarise(total_value = sum(value,na.rm=T),.groups = "drop")
+
 # group by state
-state_fit <- historic_tif %>% 
+state_fit <- historic_spp %>% 
   group_by(state,year,region) %>% 
@@
   theme(legend.key.width = unit(1,"line")) + 
-  ggsave(filename = "area_plot_avg.jpg",
+  ggsave(filename = "area_plot_avg_agg.jpg",
          plot = ggplot2::last_plot(),

### 2021-06-29 Scripts/spatial_analisis.Rmd
misc
Area plot for multi spp

@@
 
-### Proportional change per species
+### Per species maps
 
@@
 
+### Dynamic aggregated plot
+
 ```{r area_plot, eval = T, echo = T, fig.height = 10, fig.width = 10}
 
-total_fited <- historic_tif %>% 
+total_fited <- historic_spp %>% 
   group_by(year,region) %>% 
@@
 # group by state
-state_fit <- historic_tif %>% 
+state_fit <- historic_spp %>% 
   group_by(state,year,region) %>% 
@@
 
+### Dynamic aggregated plot
+
 *Note:* This plot is also interactive and thus, follows the same options of the previous one.
+
+```{r area_plot, eval = T, echo = T, fig.height = 10, fig.width = 10}
+
+# group by state
+state_fit <- historic_tif %>% 
+  group_by(state,year,region,.groups = "drop") %>% 
+  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
+  left_join(total_fited,
+            by = c("year","region")) %>%
+  mutate(percentage = state_value/total_value*100) %>% 
+  group_by(state,region) %>% 
+  mutate(RMean = zoo::rollmean(x = percentage, 
+                            10,
+                            fill = NA,
+                            na.rm=T)
+    ) %>%  
+  left_join(state_lat)
+
+# Plot me
+p <- ggplot(state_fit) +
+  geom_area(
+    aes(
+      x = year,
+      y = round(RMean),
+      fill = state
+      # fill = order
+    )
+  ) +
+  ylab("10 yrs running average (%)") +
+  scale_fill_manual(
+    "State",
+    values = state_pallet,
+    # labels = state_fit %>% arrange(order) %>%  pull(state) %>% unique()
+  ) +
+  MyFunctions::my_ggtheme_p() +
+  facet_wrap(~region, ncol = 1)
+
+suppressWarnings(
+ggplotly(p,
+         dynamicTicks = TRUE) %>% 
+  layout(hovermode = "x") %>% 
+  # add_trace() %>% 
+  rangeslider()
+)
+
+```
+
+### Aggregated Proportional change
 
@@
 
-```{r area_plot, eval = T, echo = T, fig.height = 10, fig.width = 10}
+### Per Species Proportional change
+
+```{r paper_plot_area_ave, eval = F, echo = F, results='hide'}
+
+total_fited <- historic_spp %>% 
+  group_by(year,region,spp) %>% 
+  summarise(total_value = sum(value,na.rm=T),.groups = "drop")
 
 # group by state
-state_fit <- historic_tif %>% 
-  group_by(state,year,region,.groups = "drop") %>% 
+state_fit <- historic_spp %>% 
+  group_by(state,year,region,spp) %>% 
   summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
   left_join(total_fited,
-            by = c("year","region")) %>%
+            by = c("year","region","spp")) %>%
   mutate(percentage = state_value/total_value*100) %>% 
-  group_by(state,region) %>% 
+  group_by(state,region,spp) %>% 
   mutate(RMean = zoo::rollmean(x = percentage, 
@@
     ) %>% 
+  #Only show results for spring
+  filter(str_detect(region,"Spring"),
+         !is.na(RMean) # Remove NAs from rollmean
+         ) %>%  
   left_join(state_lat)
@@
 # Plot me
-p <- ggplot(state_fit) +
+ggplot(state_fit) +
   geom_area(
@@
       y = round(RMean),
-      fill = state
-      # fill = order
+      fill = order
+      # fill = state
     )
   ) +
-  ylab("10 yrs running average (%)") +
+  ylab("Propotion (10 yrs running average)") +
+  # viridis::scale_fill_viridis(discrete = T, alpha = 0.8) +
   scale_fill_manual(
@@
     values = state_pallet,
-    # labels = state_fit %>% arrange(order) %>%  pull(state) %>% unique()
+    labels = state_fit %>% arrange(order) %>%  pull(state) %>% unique()
   ) +
-  MyFunctions::my_ggtheme_p() +
-  facet_wrap(~region, ncol = 1)
-
-suppressWarnings(
-ggplotly(p,
-         dynamicTicks = TRUE) %>% 
-  layout(hovermode = "x") %>% 
-  # add_trace() %>% 
-  rangeslider()
-)
-
-```
+  my_ggtheme_p(leg_pos = "right") +
+  theme(legend.key.width = unit(1,"line")) + 
+  facet_wrap(~spp, ncol = 1, strip.position = "right") +
+  ggsave(filename = "area_plot_avg_spp.jpg",
+         plot = ggplot2::last_plot(),
+         path = my_path("R","Figures"),
+         width = 10,
+         height = 12
+  )
+
+```

### 2021-06-30 Scripts/spatial_analisis.Rmd
qupta vs distribution allocation by year

@@
 
-This section shows preliminary results for Black sea bass (*Centropristis striata*).
+Results are now for eight species managed under Mid-Atlantic Council Management Plans according to [NOAA](https://www.fisheries.noaa.gov/new-england-mid-atlantic/commercial-fishing/new-england-mid-atlantic-fishery-management-plans).
+
+*Scomber scombrus*, *Peprilus triacanthus* (butterfish), *Illex illecebrosus* (shortfin squid), *Paralichthys dentatus* (summer flounder), *Stenotomus chrysops* (Scoop), *Centropristis striata* (black sea bass), *Pomatomus saltatrix* (Bluefish), *Lopholatilus chamaeleonticeps* (Golden tilefish), *Caulolatilus microps* (blueline tilefish) and *Clupea harengus*
 
@@
   "Paralichthys dentatus", #summer flounder
-  "Stenotomus chrysops", #Scoop"
+  "Stenotomus chrysops", #Scup"
   "Centropristis striata", # black sea bass
@@
 
+unique(historic_spp$spp)
+
 # Spatial data
-
 States <- c("maine", "new hampshire", "massachusetts", "connecticut", "rhode island", "new york", "new jersey", "delaware", "maryland", "virginia", "north carolina")
@@
 # US State Map (land)
-
 land_sf <- st_as_sf(map("state", plot = FALSE, fill = TRUE)) %>% 
@@
   ) %>% 
-  mutate(abrev = c("CO","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VI")
+  mutate(abrev = c("CT","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VA")
   ) %>% 
@@
 ```
+
+## Historic quota Vs distributions
+
+This section of the results explores the differences between the historic distribution of te stock and the historic quota allocation.
+We collected the proportion of the total quota that each State gets for each species.
+
+Right now the analysis only covers black sea bass, summer flounder and scup. But we can go speceis by species to see which ones have their quota allocated by state to include them in the analysis.
+
+- [Black Sea Bass; *Centropristis striata*](https://www.mafmc.org/newsfeed/2021/asmfc-and-mafmc-approve-bsb-commercial-allocation-changes)
+
+**Note:** We are using the new allocations based on the stock's most recent biomass distribution*
+
+- [Summer flounder](http://www.asmfc.org/uploads/file/5f9af82a2019SummerFlounderFMP_Review.pdf)
+
+- [Scup](http://www.asmfc.org/uploads/file/5f99d0112019_Scup_FMP_Review_approved.pdf) Summer period
+
+For State-level managed species see the [Atlantic States Marine Fisheries Comission](http://www.asmfc.org/fisheries-management/program-overview) website and go species-by-species.
+
+```{r state_quota_tbl,eval= T, echo = T}
+
+quota_allocation <- state_lat %>% 
+  mutate(
+    "Centropristis striata" = c(
+      0.0040, #ME
+      0.0040, #NH
+      0.1564, #MA
+      0.1323, #RI
+      0.0367, #CT
+      0.0857, #NY
+      0.2010, #NJ
+      0.0411, #DE
+      0.0888, #MD
+      0.1614, #VA
+      0.0888 #NC
+    ),
+    "Paralichthys dentatus" = c(
+      0.0004756, #ME 
+      0.0000046, #NH 
+      0.0682046, #MA 
+      0.1568298, #RI 
+      0.0225708, #CT 
+      0.0764699, #NY 
+      0.1672499, #NJ 
+      0.0001779, #DE 
+      0.0203910, #MD
+      0.2131676, #VA
+      0.2744584 #NC
+    ),
+    "Stenotomus chrysops" = c(
+      0.0012101, #ME
+      0.0000000, #HN
+      0.2158729, #MA
+      0.5619456, #RI
+      0.0315399, #CT
+      0.1582466, #NY
+      0.0291667, #NJ
+      0.0000000, #DE
+      0.0001190, #MD
+      0.0016502, #VA
+      0.0002490 #NC
+    )
+  ) %>% 
+  gather("spp","quota",4:6)
+
+# Double check they all add to 1...
+quota_allocation %>% 
+  group_by(spp) %>% 
+  summarise_at(vars(quota),sum)
+
+quota_allocation %>% 
+  arrange(order) %>% 
+  select(-order) %>% 
+  spread(spp,quota) %>% 
+  kable()
+```
+
+### Prepare data
+
+```{r}
+
+total_fited <- historic_spp %>% 
+  group_by(year,region,spp) %>% 
+  summarise(total_value = sum(value,na.rm=T),.groups = "drop")
+
+# group by state
+state_fit <- historic_spp %>% 
+  group_by(state,year,region,spp) %>% 
+  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
+  left_join(total_fited,
+            by = c("year","region","spp")) %>%
+  mutate(percentage = state_value/total_value*100) %>% 
+  #Only show results for spring
+  filter(str_detect(region,"Spring"))
+
+quota_df <- quota_allocation %>% 
+  gather("spp","quota",4:6) %>% 
+  left_join(historic_spp) %>% 
+  group_by(state,abrev,year,region,spp,quota) %>% 
+  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
+  left_join(total_fited,
+            by = c("year","region","spp")) %>%
+  mutate(Distribution = state_value/total_value*100,
+         Historic = quota*100) %>% 
+  group_by(state,quota,spp) %>% 
+  mutate(RMean = zoo::rollmean(x = Distribution, 
+                            10,
+                            fill = NA,
+                            na.rm=T)
+    ) %>% 
+  #Only show results for spring
+  filter(str_detect(region,"Spring"),
+         !is.na(RMean) # Remove NAs from rollmean
+         ) %>%  
+  left_join(state_lat) %>% 
+  filter(
+    # spp =="Centropristis striata"
+    spp %in% quota_allocation$spp
+  )
+
+```
+
+### Difference line plot
+
+This version shows the difference between the Historic quota allocation and the distribution proportion of the stock:
+
+- diff < 0 = the distribution proportion is *larger* than the allocated quota
+- diff > 0 = the distribution proportion is *smaller* than the allocated quota
+
+```{r}
+# Option one
+
+quota_df %>%
+  mutate(diff = Historic- Distribution,
+         diff_rmean = RMean- Distribution) %>% 
+  gather("type","value",diff:diff_rmean) %>% 
+  # View()
+  ggplot() +
+  geom_line(
+    aes(
+      x = year,
+      y = value,
+      color = order
+    )
+  ) +
+  scale_color_manual("State",
+    values = state_pallet,
+    labels = quota_df %>% arrange(order) %>%  pull(state) %>% unique()
+    ) +
+  facet_wrap(~type, nrow = 2, scales = "free")
+
+```
+### Linetype plot
+
+Here, we plot the distributional quota (solid lines) with each State's allocation with dashed (----) lines
+
+```{r}
+# Option one
+
+quota_df %>% 
+  gather("level","quota",Distribution:RMean) %>% 
+  filter(
+    spp =="Centropristis striata"
+  ) %>% 
+  # mutate(diff = quota_per- percentage) %>% 
+  # View()
+  ggplot() +
+  geom_line(
+    aes(
+      x = year,
+      y = quota,
+      color = order
+    )
+  ) +
+  labs(x = "Year",y = "Quota (%)") +
+  scale_fill_manual("State",
+    values = state_pallet,
+    labels = quota_df %>% arrange(order) %>%  pull(state) %>% unique()
+    ) +
+  scale_color_manual("State",
+    values = state_pallet,
+    labels = quota_df %>% arrange(order) %>%  pull(state) %>% unique()
+    ) +
+  scale_linetype("Quota") +
+  facet_wrap(~level)
+
+```
+### Efficiency index
+
+The idea here is create and *efficiency index* (Danger!) that computes the alignment between the distribution and the actual allocation. The index is simply;
+
+$$ei = \frac{HistoricQuota}{DistributionProportion}$$ 
+So, in cases qhere *ei* = 1, the quota is aligned with the distribution; when *ei* > 1 then the historic quota is more than the stock's State's distribution, contrarily, *ei* < 1 means that the historic quota is less than what the State currently has.
+
+```{r}
+# Option one
+
+quota_df %>% 
+  filter(
+    spp =="Centropristis striata"
+  ) %>% 
+  mutate(index = Historic/Distribution,
+         index_rmean = Historic/RMean) %>%
+  gather("level","index",index:index_rmean) %>%
+  filter(index < 5) %>% 
+  # View()
+  ggplot() +
+  geom_line(
+    aes(
+      x = year,
+      y = index,
+      color = state
+    ),
+  ) +
+  labs(x = "Year",y = "Efficiency index") +
+  scale_fill_manual("State",
+    values = state_pallet,
+    labels = quota_df %>% arrange(order) %>%  pull(state) %>% unique()
+    ) +
+  scale_color_manual("State",
+    values = state_pallet,
+    labels = quota_df %>% arrange(order) %>%  pull(state) %>% unique()
+    ) +
+  facet_wrap(~level, ncol = 1, scales = "free")
+
+```

### 2021-06-30 Scripts/Abstract.Rmd
submitted abstract to IMBER

@@
 ---
-title: "Managing across boundaries: shifts in stock distribution challenges United States' north Atlantic fisheries management"
-author: "Crosson Scott, Dumas Chris, Fujita Rod, Jensen Olaf, Levine Arielle, Longo Katie, Palacios-Abrantes Juliano"
+title: "Managing across boundaries: Shifts in stock distribution challenges United States’ northeastern Atlantic fisheries management"
+author: "Palacios-Abrantes Juliano, Crosson Scott, Dumas Chris, Fujita Rod, Jensen Olaf, Levine Arielle, Longo Catherine"
 output: word_document
@@
 # Abstract
-(Currently 202/250-300 words)
+<!-- (Currently 202/250-300 words) -->
 
 Climate change is driving shifts in fish stock distributions that will affect resource availability across different jurisdictions around the world.
-Elinor Ostrom’s fundamental principles of common pool resource governance include a requirement for clear boundaries over resource units.
+Effective resource governance includes a requirement for clear boundaries over resource units.
 However, when stock ranges shift, governance systems and boundaries are no longer aligned.
-This misalignment has already created conflicts around access and the re-distribution of benefits flowing from the stocks.
+This misalignment has already created conflicts around access and the redistribution of benefits flowing from the stocks, e.g., on how to revise catch allocations across jurisdictions and/or recreational and industrial sectors.
+New allocation rules, for example using current species distributions to update relative quotas assigned, compensation schemes and gradual transition times, are difficult to evaluate when they may have controversial outcomes.
+Looking retrospectively at the effect one might have seen when implementing different rules in the past, helps explore their performance applied to real data, while still being only hypothetical.
 Here, we look at the historical shift in the distribution of managed stocks across the North East Atlantic coast of the United States of America.
-We estimate the yearly abundance proportion that each State had from 1971 to 2019 and compare that to the current quota allocation policy.
-We found that, for many species, the stock proportion has shifted since the establishment of the allocations policy, creating a misalignment between the quota allocation and the stock's biomass distribution.
-Our findings have direct impact of on the management of stocks that cross jurisdictions highlighting the need for allocation strategies that can cope with such biomass changes.
-Moreover, the implementation of such strategies are challenged by the complexity of the Northeast Atlantic social-ecological system that expands multiple stakeholders and where changes can result in winner and looser States.
-Strategies that account for changes in stock distribution are key to maintain the sustainability of the stock but should consider strategies to address the potential re-distribution of benefits.
+We estimate the yearly abundance proportion near each State from 1971 to 2019 and compare that to the current quota allocation policy.
+While this is ongoing work, we believe our findings could directly inform regulatory reform in the US where alternative approaches for managing stocks that cross State jurisdictions are being considered.
+Strategies that account for changes in stock distributions are key to managing them sustainability but, to be successful, will have to be designed so as to also address the consequences of potential re-distributions of benefits and how these are perceived by stakeholders.
 
-# Instructions
+<!-- # Instructions -->
 
-- Deadline to submit: 30 June
-- Your abstract must be uploaded as a Word file with 11 point Arial font.
-- Title
-- Author(s) (last name, first name). If there is more than one author, underline the name of the presenter.
-- The abstract should be between 250-300 words
+<!-- - Workshop title Workshop 3: Ocean governance and climate adaption: comparing responses, charting future courses -->
+<!-- - Workshop link https://imber.info/imbizo6-workshop-3/ -->
+<!-- - Deadline to submit: 30 June -->
+<!-- - Your abstract must be uploaded as a Word file with 11 point Arial font. -->
+<!-- - Title -->
+<!-- - Author(s) (last name, first name). If there is more than one author, underline the name of the presenter. -->
+<!-- - The abstract should be between 250-300 words -->
+
+<!-- ## Workshop objectives  -->
+
+<!-- The overall objective of this workshop is to share case study experiences on how ocean climate adaptation is faring at regional, national and local levels in order to draw out buoyant governance practices and lessons learned.
+These lessons can be based on learning from success, but also include learning from failure.
+Key multilevel governance questions will be explored in the case studies.
+Examples of the types of questions that may be addressed at the three different levels are listed below.
+These are not exhaustive and alternative questions for exploration are welcomed.
+-->

### 2021-06-30 Scripts/spatial_analisis.Rmd
updated notebook

@@
 output:
-  html_document
-  # html_notebook:
+  # html_document
+  html_notebook:
     fig_width: 6
@@
 
-```{r area_map_aggregated, eval = T, echo = T, fig.width = 10, fig.height=6}
+```{r area_map_aggregated_formans, eval = T, echo = T, fig.width = 10, fig.height=6}
 
@@
 
-```{r area_plot, eval = T, echo = T, fig.height = 10, fig.width = 10}
+```{r dynamic_area_plot, eval = T, echo = T, fig.height = 10, fig.width = 10}
 
@@
 # group by state
-state_fit <- historic_tif %>% 
+state_fit <- historic_spp %>% 
   group_by(state,year,region,.groups = "drop") %>% 
@@
 
-```{r paper_plot_area_ave, eval = F, echo = F, results='hide'}
+```{r plot_area_ave_agg, eval = F, echo = F, results='hide'}
 
@@
 
-```{r paper_plot_area_ave, eval = F, echo = F, results='hide'}
+```{r paper_plot_area_ave_spp, eval = F, echo = F, results='hide'}
 
@@
 quota_df <- quota_allocation %>% 
-  gather("spp","quota",4:6) %>% 
   left_join(historic_spp) %>% 
@@
 
+head(quota_df) %>% 
+  kable()
 ```
@@
     ) +
-  facet_wrap(~type, nrow = 2, scales = "free")
+  facet_grid(type~spp, 
+             scales = "free")
 
@@
   gather("level","quota",Distribution:RMean) %>% 
-  filter(
-    spp =="Centropristis striata"
-  ) %>% 
   # mutate(diff = quota_per- percentage) %>% 
@@
   scale_linetype("Quota") +
-  facet_wrap(~level)
+  facet_grid(spp ~ level)
 
@@
 
+**Note:** There are some crazzy outliers that have been removed, for now...
+
 ```{r}
@@
 quota_df %>% 
-  filter(
-    spp =="Centropristis striata"
-  ) %>% 
-  mutate(index = Historic/Distribution,
-         index_rmean = Historic/RMean) %>%
+  # filter(
+  #   spp =="Centropristis striata"
+  # ) %>% 
+  mutate(index = Distribution/Historic,
+         index_rmean = RMean/Historic) %>%
   gather("level","index",index:index_rmean) %>%
-  filter(index < 5) %>% 
+  filter(index < 5) %>% # there are some craaaazy outliers
   # View()
@@
     ) +
-  facet_wrap(~level, ncol = 1, scales = "free")
-
-```
+  facet_grid(level~spp,
+             scales = "free")
+
+```
+### Efficiency index
+
+```{r}
+
+s
+
+```

### 2021-07-08 Scripts/spatial_analisis.Rmd
ughhhh... Big Sur and updates...

@@
 library(MyFunctions)
-MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","viridis","wesanderson","knitr","kableExtra","plotly","ggrepel","ggsflabel"))
+MyFunctions::my_lib(c("ggmap","sf","st","tidyverse","tools","readr","data.table","maps","viridis","wesanderson","knitr","kableExtra","plotly","ggrepel","ggsflabel","janitor","interp","rnaturalearth"))
 ```
@@
 
-# path_world <- MyFunctions::my_path("G", extra_path = "Spatial/SAU/SAU_Shapefile")
-path_world <- "~/Downloads/SAU_Shapefile"
+# path_world <- my_path("G", extra_path = "Spatial/SAU/SAU_Shapefile")
+path_world <- "~/OneDrive - UW-Madison/Spatial_data/World_EEZ_v11_20191118/"
 
 # The File
-fnam_world <- "SAUEEZ_July2015.shp"
+fnam_world <- "eez_boundaries_v11.shp"
 
 # Load it!
+
 eez_sf <- st_read(dsn = path_world,
                         layer =file_path_sans_ext(fnam_world)) %>%
-  rename(eez_name = Name) %>% 
-  st_transform(crs = 4326) %>% # 4326
-  st_simplify(preserveTopology = TRUE, dTolerance = 10000) %>% #0.1 for paper
-  filter(eez_name == "USA (East Coast)")
+  # rename(eez_name = Name) %>%
+  # st_transform(crs = 4326) %>% # 4326
+  filter(TERRITORY1 == "United States",
+         LENGTH_KM == 2734) #%>%
+  # filter(str_detect(EEZ1, "United States")) %>%
+  # st_simplify(preserveTopology = TRUE, dTolerance = 0.1) #0.1 for paper
 
 # ggplot(eez_sf) +
-# geom_sf(aes(),fill =NA)
+  # geom_sf()
 
@@
 # us_state_w <- rgdal::readOGR(dsn = "~/Downloads/FederalAndStateWaters/FederalAndStateWaters.gdb")
-state_sf <-  st_read("~/Downloads/FederalAndStateWaters/FederalAndStateWaters.gdb") %>%
+state_sf <-  st_read("~/OneDrive - UW-Madison/Spatial_Data/USFedAndStateW/FederalAndStateWaters.gdb") %>%
   janitor::clean_names() %>% 
@@
 
+ggplot() +
+  geom_sf(data = eez_sf, aes()) +
+  geom_sf(data = state_sf, aes(color = state), fill = NA) +
+  scale_color_manual(values = state_pallet)+
+  theme_dark()
+
 ```
@@
 state_bf_plot <- ggplot() +
+  geom_sf(data = state_sf, aes(color = state), fill = NA) +
   geom_sf(data = eez_sf, aes(), fill = NA) +
   geom_sf(data = state_bf, aes(color = state), fill = NA) +
-  scale_color_manual(values = state_pallet)
+  scale_color_manual(values = state_pallet)+
+  theme_dark()
 #
@@
   st_set_crs(4326) %>%
-  st_simplify(preserveTopology = TRUE, dTolerance = 10000) %>%
+  # st_simplify(preserveTopology = TRUE, dTolerance = 10000) %>%
   ggplot() +
@@
   scale_color_manual(values = state_pallet) +
-  theme_bw()
+  theme_bw()+
+  theme_dark()
 
@@
   ggplot(grid_sf) +
+    geom_sf(data = state_sf, aes(), fill = NA) +
     geom_sf(aes(color = state), alpha = 0.3) +
@@
     scale_color_manual(values = state_pallet) +
+    theme_dark() +
     theme(legend.position = ""),
@@
     facet_wrap(~state) +
+    theme_dark() +
     theme(legend.position = "top") +
@@
 # I don't know how to undo st_simplify so need to re-load the shapefile
-eez_sf <- st_read(dsn = path_world,
-                        layer =file_path_sans_ext(fnam_world)) %>% 
+
+eez_sf <- st_read(my_path("G", extra_path = "Spatial/SAU/SAU_Shapefile", name = "SAUEEZ_July2015.shp")) %>% 
   rename(eez_name = Name) %>% 
@@
   filter(eez_name == "USA (East Coast)")
+
+eez_sf <- st_read("/Volumes/Enterprise/Data/Spatial/World_EEZ_v11_20191118/eez_v11.shp") %>%
+  # rename(eez_name = Name) %>%
+  # st_transform(crs = 4326) %>% # 4326
+  filter(TERRITORY1 == "United States") %>% 
+  st_crop(xmin = -85, xmax = -60, ymin = 30, ymax = 50)
+
+# ggplot(eez_sf) +
+#   geom_sf()
 
@@
 
-# Plot to make sure makes sense (Picasso syle)
+# Plot to make sure makes sense
 grid_eez_sf %>%
-  st_simplify(preserveTopology = TRUE, dTolerance = 10000) %>% #0.1 for paper
   ggplot() +
   geom_sf(aes(color = state), alpha = 0.3) +
-  scale_color_manual(values = state_pallet)
-
-```
-
-```{r cropped_plot_paper}
+  scale_color_manual(values = state_pallet) +
+  geom_sf(data = eez_sf,aes(), fill = NA) +
+  theme_dark()
+
+```
+
+##### 3.1 Paper figure; buffer plot
+
+```{r cropped_plot_paper, eval = F, echo = T}
 
@@
 ```
+
+![Buffer figure for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/buffer_figure.jpg)
 
@@
 
-s
-
-```
+```

### 2021-07-08 Scripts/spatial_analisis.Rmd
re-plotted for only scop, flounder and bsb

@@
 Species <- c(
-  "Scomber scombrus",
-  "Doryteuthis (Amerigo) pealeii", #longfin squid WE DONT HAVE IT
-  "Peprilus triacanthus", # butterfish
-  "Illex illecebrosus", #shortfin squid
+  # "Scomber scombrus",
+  # "Doryteuthis (Amerigo) pealeii", #longfin squid WE DONT HAVE IT
+  # "Peprilus triacanthus", # butterfish
+  # "Illex illecebrosus", #shortfin squid
   "Paralichthys dentatus", #summer flounder
   "Stenotomus chrysops", #Scup"
-  "Centropristis striata", # black sea bass
-  "Pomatomus saltatrix", # Bluefish
-  "Lopholatilus chamaeleonticeps", #golden tilefish
-  "Caulolatilus microps", #blueline tilefish
-  "Clupea harengus" # Atlantic herring (Jointly in State and Federal Waters)
+  "Centropristis striata"#, # black sea bass
+  # "Pomatomus saltatrix", # Bluefish
+  # "Lopholatilus chamaeleonticeps", #golden tilefish
+  # "Caulolatilus microps", #blueline tilefish
+  # "Clupea harengus" # Atlantic herring (Jointly in State and Federal Waters)
   )
@@
 
-This map shows the average proportion of the extrapolated value from the whole study period within each State's water.
+This map shows the aggregated extrapolated value from all three species per State average across the whole study period within each State's water.
 
@@
   labs(x = "Longitude", y = "Latitude") +
-  scale_fill_viridis("Mean Proportion", alpha = 0.8) +
-  scale_color_viridis("Mean Proportion", alpha = 0.8) +
-  my_ggtheme_p()
+  scale_fill_viridis("Mean Interpolation", alpha = 0.8) +
+  scale_color_viridis("Mean Interpolation", alpha = 0.8) +
+  theme_bw()
 ```
@@
 
-### Per species maps
+### Paper figure; Per species maps
 
@@
 # The plot
-land_sf %>% 
+map_plot <- land_sf %>% 
   left_join(state_fit,
@@
                hjust = 1) +
-  theme(legend.key.width = unit(4,"line")) +
+  theme(legend.key.width = unit(4,"line"))
+
   ggsave(filename = "proportion_chg_spp.jpg",
-         plot = ggplot2::last_plot(),
+         plot = map_plot,
          path = my_path("R","Figures"),
          width = 14,
-         height = 17
-         )
-
-```
+         height = 14
+         )
+
+```
+
+![Proportion change per species map for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/proportion_chg_spp.jpg)
 

### 2021-07-08 Scripts/spatial_analisis.Rmd
First try to represent offset

@@
 
+### Dynamic figure: Aggregated Proportional change per survey
+
+```{r area_map_aggregated, eval = T, echo = T, fig.width = 10, fig.height=6}
+
+total_fited <- historic_spp %>% 
+  group_by(year,region) %>% 
+  summarise(total_value = sum(value,na.rm=T),.groups = "drop")
+
+state_fit <- historic_spp %>% 
+  group_by(state,year,region) %>% 
+  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
+  left_join(total_fited,
+            by = c("year","region")) %>%
+  mutate(percentage = state_value/total_value*100) %>% 
+  left_join(periods,
+            by = "year") %>% 
+  group_by(state,order,label,region) %>% 
+  summarise(mean_per = round(mean(percentage)),.groups = "drop")
+
+# check percentages
+# state_fit %>% 
+#   group_by(period) %>% 
+#   summarise(sum(mean_per))
+
+p <- land_sf %>% 
+  left_join(state_fit,
+            by = "state") %>% 
+  ggplot() +
+  # geom_sf(aes(fill = mean_per)) +
+  geom_sf(aes(fill = mean_per, text = paste(state, mean_per,"% of proportion"))) +
+  viridis::scale_fill_viridis("Average proportion per State", alpha = 0.8) +
+  facet_wrap(~ region + label, 
+             nrow = 2) +
+  labs(x = "Latitude", 
+       y = "Longitude") +
+  my_ggtheme_p(facet_tx_s = 12,
+               leg_pos = "bottom") +
+  theme(legend.key.width = unit(1,"line")) +
+  theme_dark()
+
+ggplotly(p,
+         tooltip = "text",
+         dynamicTicks = FALSE) %>% 
+    style(hoverlabel = list(bgcolor = "white"), hoveron = "fill")
+
+```
+
 ### Paper figure; Per species maps
 
-```{r paper_figure_area_map, eval = F, echo = F, results='hide'}
+```{r paper_figure_area_map, eval = F, echo = T, results='hide'}
 
@@
 
-### Aggregated Proportional change
+### Paper figure: Aggregated Proportional change
 
@@
 
-land_sf %>% 
+agg_map <- land_sf %>% 
   left_join(state_fit,
@@
                ax_tl_s = 14) +
-  theme(legend.key.width = unit(2,"line")) +
+  theme(legend.key.width = unit(2,"line"))
+
   ggsave(filename = "proportion_chg_agg.jpg",
-         plot = ggplot2::last_plot(),
+         plot = agg_map,
          path = my_path("R","Figures"),
@@
 
-```{r area_map_aggregated, eval = T, echo = T, fig.width = 10, fig.height=6}
-
-total_fited <- historic_spp %>% 
-  group_by(year,region) %>% 
-  summarise(total_value = sum(value,na.rm=T),.groups = "drop")
-
-state_fit <- historic_spp %>% 
-  group_by(state,year,region) %>% 
-  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
-  left_join(total_fited,
-            by = c("year","region")) %>%
-  mutate(percentage = state_value/total_value*100) %>% 
-  left_join(periods,
-            by = "year") %>% 
-  group_by(state,order,label,region) %>% 
-  summarise(mean_per = round(mean(percentage)),.groups = "drop")
-
-# check percentages
-# state_fit %>% 
-#   group_by(period) %>% 
-#   summarise(sum(mean_per))
-
-p <- land_sf %>% 
-  left_join(state_fit,
-            by = "state") %>% 
-  ggplot() +
-  # geom_sf(aes(fill = mean_per)) +
-  geom_sf(aes(fill = mean_per, text = paste(state, mean_per,"% of proportion"))) +
-  viridis::scale_fill_viridis("Average proportion per State", alpha = 0.8) +
-  facet_wrap(~ region + label, 
-             nrow = 2) +
-  labs(x = "Latitude", 
-       y = "Longitude") +
-  my_ggtheme_p(facet_tx_s = 12,
-               leg_pos = "bottom") +
-  theme(legend.key.width = unit(1,"line"))
-
-ggplotly(p,
-         tooltip = "text",
-         dynamicTicks = FALSE) %>% 
-    style(hoverlabel = list(bgcolor = "white"), hoveron = "fill")
-
-```
+![Proportion change aggregated all species map for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/proportion_chg_agg.jpg)
 
@@
   MyFunctions::my_ggtheme_p() +
-  facet_wrap(~region, ncol = 1)
+  facet_wrap(~region, ncol = 1) +
+  theme_dark()
 
@@
 # Plot me
-ggplot(state_fit) +
+agg_area <- ggplot(state_fit) +
   geom_area(
@@
   my_ggtheme_p(leg_pos = "right") +
-  theme(legend.key.width = unit(1,"line")) + 
+  theme(legend.key.width = unit(1,"line"))
+
   ggsave(filename = "area_plot_avg_agg.jpg",
-         plot = ggplot2::last_plot(),
+         plot = agg_area,
          path = my_path("R","Figures"),
@@
 
-### Per Species Proportional change
+![Proportion change aggregated all species map for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/area_plot_avg_agg.jpg)
+
+### Paper figure: Per Species Proportional change
 
@@
 # Plot me
-ggplot(state_fit) +
+ssp_area <- ggplot(state_fit) +
   geom_area(
@@
   ) +
-  my_ggtheme_p(leg_pos = "right") +
+  my_ggtheme_p(leg_pos = "bottom") +
   theme(legend.key.width = unit(1,"line")) + 
-  facet_wrap(~spp, ncol = 1, strip.position = "right") +
+  facet_wrap(~spp, ncol = 1, strip.position = "right")
+
   ggsave(filename = "area_plot_avg_spp.jpg",
-         plot = ggplot2::last_plot(),
+         plot = ssp_area,
          path = my_path("R","Figures"),
@@
 ```
+![Proportion change aggregated all species map for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/area_plot_avg_spp.jpg)
 
@@
 
-### Prepare data
+### Get data ready
 
@@
 
-### Difference line plot
+### Exploring different ways to show the results
+
+#### Difference line plot
 
@@
   facet_grid(type~spp, 
-             scales = "free")
-
-```
-### Linetype plot
+             scales = "free") +
+  theme_dark()
+
+```
+#### Linetype plot
 
@@
   scale_linetype("Quota") +
-  facet_grid(spp ~ level)
-
-```
-### Efficiency index
+  facet_grid(spp ~ level)+
+  theme_dark()
+
+```
+#### Efficiency index
 
@@
 $$ei = \frac{HistoricQuota}{DistributionProportion}$$ 
-So, in cases qhere *ei* = 1, the quota is aligned with the distribution; when *ei* > 1 then the historic quota is more than the stock's State's distribution, contrarily, *ei* < 1 means that the historic quota is less than what the State currently has.
-
-**Note:** There are some crazzy outliers that have been removed, for now...
+So, in cases where *ei* = 1, the quota is aligned with the distribution; when *ei* > 1 then the historic quota is more than the stock's State's distribution, contrarily, *ei* < 1 means that the historic quota is less than what the State currently has.
+
+**Note:** 
+- There are some crazzy outliers that have been removed, for now... 
+- Bottom plot representing index as a Rmean
+
+##### As a normal year to year
 
@@
 
-quota_df %>% 
+eff_index <- quota_df %>% 
   # filter(
@@
   gather("level","index",index:index_rmean) %>%
-  filter(index < 5) %>% # there are some craaaazy outliers
+  filter(index < 5) # there are some craaaazy outliers
   # View()
-  ggplot() +
+
+ggplot(eff_index) +
   geom_line(
@@
   facet_grid(level~spp,
-             scales = "free")
-
-```
-### Efficiency index
-
-```{r}
-
-```
+             scales = "free")+
+  theme_dark()
+
+```

### 2021-07-13 Allocation_tool/server.R
Included running mean for allocation area

@@ -13,7 +13,7 @@
 
 # Get functions and shapefiles
 library(MyFunctions)
-MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","DT","plotly","wesanderson"))
+MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","DT","plotly","wesanderson","zoo"))
 
 us_map <- st_as_sf(map("state", plot = FALSE, fill = TRUE))
 
@@ -259,6 +259,7 @@ shinyServer(function(input, output) {
             species <- input$SppSelection #"Gadus morhua"
             survey <- input$SurveySelection #"Northeast US Fall"
             years <- seq(input$YearSelection[1],input$YearSelection[2],1) #seq(1971,2019,1)
+            # rmena_value <- ifelse(input$Rmean == 0,)
          
         
         total_fited <- tif_data() %>% 
@@ -276,13 +277,18 @@ shinyServer(function(input, output) {
             left_join(total_fited,
                       by = c("year","region")) %>%
             mutate(percentage = state_value/total_value*100) %>% 
-            group_by(state,region)
+            group_by(state,region) %>% 
+            mutate(RMean = zoo::rollmean(x = percentage,
+                                         input$Rmean,
+                                         fill = NA,
+                                         na.rm=T)
+            )
         
         p <- ggplot(state_fit) +
             geom_area(
                 aes(
                     x = year,
-                    y = round(percentage),
+                    y = round(RMean),
                     fill = state
                 )
             ) +

### 2021-07-13 Allocation_tool/ui.R

@@ -193,11 +193,17 @@ shinyUI(
                                                                "Allocation Area" = 4
                                                                ),
                                                            selected = 1
-                                        )
-                                    ),
+                                        ),
+                                    #Set RMean
+                                    sliderInput(inputId = "Rmean",
+                                                label = "Running average for allocation area",
+                                                min = 1,
+                                                max = 20,
+                                                value = 1)
+                                    ), # Close side panel
                                     # Show a plot of the generated distribution
                                     mainPanel(
-                                        # Cndition between plot and plotly
+                                        # Condition between plot and plotly
                                         conditionalPanel(
                                             condition = "input.PlotStyle != 4",
                                         plotOutput("distPlot")

### 2021-07-13 Allocation_tool/server.R
Formatted table to look pretty :)

@@ -13,7 +13,7 @@
 
 # Get functions and shapefiles
 library(MyFunctions)
-MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","DT","plotly","wesanderson","zoo"))
+MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","DT","plotly","wesanderson","zoo","formattable"))
 
 us_map <- st_as_sf(map("state", plot = FALSE, fill = TRUE))
 
@@ -55,7 +55,7 @@ shinyServer(function(input, output) {
         name <- paste0("tif_",str_replace(input$SppSelection," ","_"),".csv")
         
         data <- my_path("R","Partial/Interpolation",name = name, read = T)
-
+        
     })
     
     
@@ -260,102 +260,108 @@ shinyServer(function(input, output) {
             survey <- input$SurveySelection #"Northeast US Fall"
             years <- seq(input$YearSelection[1],input$YearSelection[2],1) #seq(1971,2019,1)
             # rmena_value <- ifelse(input$Rmean == 0,)
-         
-        
-        total_fited <- tif_data() %>% 
+            
+            
+            total_fited <- tif_data() %>% 
                 filter(spp %in% species,
                        region %in% survey,
                        year %in% years
-                       ) %>% 
-            group_by(year,region) %>% 
-            summarise(total_value = sum(value,na.rm=T), .groups = "drop")
-        
-        # group by state
-        state_fit <- tif_data() %>% 
-            group_by(state,year,region) %>% 
-            summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
-            left_join(total_fited,
-                      by = c("year","region")) %>%
-            mutate(percentage = state_value/total_value*100) %>% 
-            group_by(state,region) %>% 
-            mutate(RMean = zoo::rollmean(x = percentage,
-                                         input$Rmean,
-                                         fill = NA,
-                                         na.rm=T)
-            )
-        
-        p <- ggplot(state_fit) +
-            geom_area(
-                aes(
-                    x = year,
-                    y = round(RMean),
-                    fill = state
+                ) %>% 
+                group_by(year,region) %>% 
+                summarise(total_value = sum(value,na.rm=T), .groups = "drop")
+            
+            # group by state
+            state_fit <- tif_data() %>% 
+                group_by(state,year,region) %>% 
[…]

### 2021-07-13 Allocation_tool/ui.R

@@ -8,7 +8,7 @@
 #
 
 # Load libraries and data
-MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","plotly"))
+MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","plotly","formattable"))
 
 spp_survey <- read.csv("./data/spp_region.csv") %>% 
     filter(
@@ -218,8 +218,8 @@ shinyUI(
                                 br(),
                                 conditionalPanel(
                                     condition = "input.PlotStyle == 4",
-                                    p(h3(strong("Quota allocation table"))),
-                                    dataTableOutput("Allocation_tbl")
+                                    p(h3(strong("Proportion distribution across states"))),
+                                    formattableOutput("Allocation_tbl")
                                 ),
                                 # ----------- #
                                 # Instructions

### 2021-07-13 Allocation_tool/server.R
Included map of average proportional change

@@ -202,50 +202,77 @@ shinyServer(function(input, output) {
                         
                         MyFunctions::my_ggtheme_m() +
                         ggtitle("Distribution estimated by using Triangular Irregular Surface method")
-                    
-                }#else{
-                #     
-                #     # ---------------------------- #
-                #     # Area plot ######
-                #     # ---------------------------- #
-                #     if(input$PlotStyle == 4){
-                #         
-                #         area_data <- plot_data %>% 
-                #             mutate(grp = round(lat)) %>% 
-                #             group_by(grp,year) %>% 
-                #             summarise(tot = sum(wtcpue,na.rm=T))
-                #         
-                #         
-                #         year_tot <- area_data %>% 
-                #             group_by(year) %>% 
-                #             summarise(tot_year = sum(tot,na.rm=T))
-                #         
-                #         area_data_p <- area_data %>% 
-                #             left_join(year_tot) %>% 
-                #             mutate(per = tot/tot_year)
-                #         
-                #         
-                #         ggplot(area_data_p) +
-                #             geom_area(
-                #                 aes(
-                #                     x = as.numeric(year),
-                #                     y = per*100,
-                #                     fill = as.factor(grp)
-                #                 )
-                #             ) +
-                #             xlab("Year") +
-                #             ylab("Distribution Percentage (%)") +
-                #             MyFunctions::my_ggtheme_p() +
-                #             viridis::scale_fill_viridis(discrete = T,
-                #                                         direction = -1,
-                #                                         guide_legend(title = "State")
-                #             )
-                #     }
-                # }
                 
+                }else{
+
+                    # ---------------------------- #
+                    # Distribution proportion map ######
+                    # ---------------------------- #
+                    if(input$PlotStyle == 5){
+                        
+                        periods <-tibble(
+                            order = c(rep("a",12),
+                                      rep("b",12),
+                                      rep("c",12),
+                                      rep("d",11)
+                            ),
+                            label = c(rep("1973-1984",12),
+                                      rep("1985-1996",12),
+                                      rep("1997-2008",12),
+                                      rep("2009-2019",11)
+                            ),
+                            year = c(seq(1973,1984,1),
+                                     seq(1985,1996,1),
+                                     seq(1997,2008,1),
+                                     seq(2009,2019,1)
+                            )
+                        )
+                       
+                        total_fited <- tif_data() %>% 
[…]

### 2021-07-13 Allocation_tool/ui.R

@@ -187,10 +187,11 @@ shinyUI(
                                         checkboxGroupInput(inputId = "PlotStyle",
                                                            label = "Select Result",
                                                            choices = c(
-                                                               "Latitudinal Shift" = 1,
-                                                               "Survey Point" = 2, 
-                                                               "Distribution Map" = 3,
-                                                               "Allocation Area" = 4
+                                                               "Latitudinal Shift (P)" = 1,
+                                                               "Survey Points (P)" = 2, 
+                                                               "Distribution (M)" = 3,
+                                                               "Proportion change (M)" = 5,
+                                                               "Allocation Area (P)" = 4
                                                                ),
                                                            selected = 1
                                         ),

### 2021-07-13 Allocation_tool/server.R
Included change proportion version with plotly

@@ -331,7 +331,80 @@ shinyServer(function(input, output) {
                 layout(hovermode = "x") %>% 
                 # add_trace() %>% 
                 rangeslider()
+        }else{
+            # ---------------------------- #
+            # Distribution proportion map ######
+            # ---------------------------- #
+            if(input$PlotStyle == 6){
+                
+                periods <-tibble(
+                    order = c(rep("a",12),
+                              rep("b",12),
+                              rep("c",12),
+                              rep("d",11)
+                    ),
+                    label = c(rep("1973-1984",12),
+                              rep("1985-1996",12),
+                              rep("1997-2008",12),
+                              rep("2009-2019",11)
+                    ),
+                    year = c(seq(1973,1984,1),
+                             seq(1985,1996,1),
+                             seq(1997,2008,1),
+                             seq(2009,2019,1)
+                    )
+                )
+                
+                total_fited <- tif_data() %>% 
+                    group_by(year,region,spp) %>% 
+                    summarise(total_value = sum(value,na.rm=T),.groups = "drop")
+                
+                
+                state_fit <- tif_data() %>% 
+                    group_by(state,year,region,spp) %>% 
+                    summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
+                    left_join(total_fited,
+                              by = c("year","region","spp")) %>%
+                    mutate(percentage = state_value/total_value*100) %>% 
+                    left_join(periods,
+                              by = "year") %>% 
+                    group_by(state,order,label,region,spp) %>% 
+                    summarise(mean_per = round(mean(percentage)),.groups = "drop") %>% 
+                    #Only show results for spring
+                    filter(str_detect(region,"Spring")) %>% 
+                    mutate(spp = gsub(" ","\n",spp))
+                
+                # The plot
+                p <- us_map %>% 
+                    filter(ID %in% c("maine", "new hampshire", "massachusetts", "connecticut", 
+                                     "rhode island", "new york", "new jersey", "delaware", "maryland",
+                                     "virginia", "north carolina")) %>% 
+                    rename(state = ID) %>% 
+                    left_join(state_fit,
+                              by = "state") %>% 
+                    ggplot() +
+                    geom_sf(aes(fill = mean_per,
+                                text = paste(state, mean_per,"% of proportion")
+                                )) +
+                    viridis::scale_fill_viridis("Average proportion\nper State", alpha = 0.8) +
[…]

### 2021-07-13 Allocation_tool/ui.R

@@ -191,6 +191,7 @@ shinyUI(
                                                                "Survey Points (P)" = 2, 
                                                                "Distribution (M)" = 3,
                                                                "Proportion change (M)" = 5,
+                                                               "Proportion change (Mp)" = 6,
                                                                "Allocation Area (P)" = 4
                                                                ),
                                                            selected = 1
@@ -210,7 +211,7 @@ shinyUI(
                                         plotOutput("distPlot")
                                         ),
                                         conditionalPanel(
-                                            condition = "input.PlotStyle == 4",
+                                            condition = "input.PlotStyle %in% c(4,6)",
                                             plotlyOutput("areaPlot")
                                         )
                                     )

### 2021-07-14 Scripts/manuscript_acrossboundaries.Rmd
Manuscript draft

---
title: "Challenges on quantifying fish range shifts across management boundaries"
subtitle: "*target journal* PlosOne"
output: word_document
---

<!-- # Journals -->
<!-- Ecography, ecology oriented -->
<!-- -	Conservation biology, -->
<!-- -	Fisheries journals; Fisheries -->

<!-- # Extra Ideas… -->

<!-- - Expanding from US to international -->
<!-- - Fishing communities and processing plans are fixed in time and space (e.g., Salmon in Canada, Peruvian anchoveta) -->

# Introduction

Fish range shifts have been occurring rapidly.

When harvested species shift across management boundaries, there can be a growing disconnect between the management jurisdictions in which fish are found and the management jurisdictions which hold harvest rights.

While the problem is increasingly well known, quantifying it is difficult for two reasons: (1) management jurisdiction in the ocean is often ill-defined, especially at the subnational level or beyond exclusive economic zones, and (2) quantifying fish distributions in relation to these boundaries is difficult, even where fishery-independent surveys exist, because of seasonal and interannual variation.

Here we examine both of these challenges using fish distributions relative to states in the Northeast U.S. as an example.

# Results
-	Two boundaries methods
-	Two surveys

### 2021-07-28 Scripts/spatial_analisis.Rmd
Updated maps and port shapefile fom GFW

@@
 library(MyFunctions)
-MyFunctions::my_lib(c("ggmap","sf","st","tidyverse","tools","readr","data.table","maps","viridis","wesanderson","knitr","kableExtra","plotly","ggrepel","ggsflabel","janitor","interp","rnaturalearth"))
+MyFunctions::my_lib(c("ggmap","sf","st","tidyverse","tools","readr","data.table","maps","viridis","wesanderson","knitr","kableExtra","plotly","ggrepel","ggsflabel","janitor","interp","rnaturalearth","readxl"))
+
+# Fix new updats of sf package
+sf::sf_use_s2(use_s2 = FALSE)
+
+# Create specific state pallet from our friend Wes Andersson
+state_pallet <- c(wes_palette(n = 5, name = "Darjeeling1"),
+                               wes_palette(n = 5, name = "Darjeeling2"),
+                               wes_palette(n = 3, name = "Royal1")
+                  )
+
 ```
@@
 land mass, the State waters of maine, new hampshire, massachusets, connecticut, rhode island, new york, new jersey, delaware, maryland, virginia, north carolina and the North East EEZ.
-
-1.- **Land shapefile;** covers the US land territory for visualization. Data provided from the `map` package.
-
-2.- **State waters;** covers the state waters of the NE US states. Data from [data.gov](https://catalog.data.gov/dataset/federal-and-state-waters).
+Moreover, we use the NOAA dataset of landings per port.
+
+##### 1.- Land shapefile
+
+Covers the US land territory for visualization. Data provided from the `map` package.
+
+```{r land_sf, eval = T, echo = T, results = 'hide'}
+
+States <- c("maine", "new hampshire", "massachusetts", "connecticut", "rhode island", "new york", "new jersey", "delaware", "maryland", "virginia", "north carolina")
+
+# -------------- #
+# US State Map (land)
+# -------------- #
+
+land_sf <- st_as_sf(map("state", plot = FALSE, fill = TRUE)) %>% 
+  filter(ID %in% States) %>% 
+  mutate(abrev = c("CO","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VI"),
+         state = str_to_sentence(ID)
+         )
+
+# Visual exploration (o.k! )
+ggplot(land_sf) +
+  geom_sf(aes(fill = state)) +
+  scale_fill_manual(values = state_pallet) +
+  theme_dark()
+
+```
+
+#####  2.- EEZ shapefile
+
+Used the *Sea Around Us* shapefle updated to June 2016.
+
+```{r eez_sf, eval = T, echo = T}
+
+# US EEZ map
+path_world <- my_path("G", extra_path = "Spatial/SAU/SAU_Shapefile", name = "SAUEEZ_July2015.shp")
+
+# Load it!
+eez_sf <- st_read(path_world) %>%
+  rename(eez_name = Name) %>%
+  st_transform(crs = 4326) %>% # 4326
+  filter(eez_name == "USA (East Coast)") %>%
+  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) #0.1 for paper
+
+# Visual exploration (o.k! )
+ggplot(eez_sf) +
+  geom_sf() +
+  theme_dark()
+
+```
+
+#####  3.-  State waters
+
+Covers the state waters of the NE US states. Data from [data.gov](https://catalog.data.gov/dataset/federal-and-state-waters).
 
@@
 
-3.- **EEZ shapefile;** Used the *Sea Around Us* shapefle updated to June 2016.
-
-```{r maps_sf, eval = T, echo = T, results = 'hide'}
-
-States <- c("maine", "new hampshire", "massachusetts", "connecticut", "rhode island", "new york", "new jersey", "delaware", "maryland", "virginia", "north carolina")
-
-# US State Map (land)
-
-land_sf <- st_as_sf(map("state", plot = FALSE, fill = TRUE)) %>% 
-  filter(ID %in% States) %>% 
-  mutate(abrev = c("CO","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VI"))
-
-# ggplot(us_map) +
-  # geom_sf()
-
-# US EEZ map
-
-# path_world <- my_path("G", extra_path = "Spatial/SAU/SAU_Shapefile")
-path_world <- "~/OneDrive - UW-Madison/Spatial_data/World_EEZ_v11_20191118/"
-
-# The File
-fnam_world <- "eez_boundaries_v11.shp"
-
-# Load it!
-
-eez_sf <- st_read(dsn = path_world,
-                        layer =file_path_sans_ext(fnam_world)) %>%
-  # rename(eez_name = Name) %>%
-  # st_transform(crs = 4326) %>% # 4326
-  filter(TERRITORY1 == "United States",
-         LENGTH_KM == 2734) #%>%
-  # filter(str_detect(EEZ1, "United States")) %>%
-  # st_simplify(preserveTopology = TRUE, dTolerance = 0.1) #0.1 for paper
-
-# ggplot(eez_sf) +
-  # geom_sf()
-
-# ggplot() +
-#   geom_sf(data = World_eez_sf, aes(), color = "red") +
-#   geom_sf(data = us_map, aes(), color = "blue")
-
-# US state waters
-# https://catalog.data.gov/dataset/federal-and-state-waters
-
-# us_state_w <- rgdal::readOGR(dsn = "~/Downloads/FederalAndStateWaters/FederalAndStateWaters.gdb")
+```{r state_sf, eval = T, echo = T}
+
+# us_state_file <- my_path("G", extra_path = "Spatial/USFedAndStateW/FederalAndStateWaters.gdb")
+
 state_sf <-  st_read("~/OneDrive - UW-Madison/Spatial_Data/USFedAndStateW/FederalAndStateWaters.gdb") %>%
@@
   filter(jurisdicti %in% States) %>% 
-  rename(state = jurisdicti) %>% 
-  # st_transform(crs = 4326)  # for matching projections
+  mutate(state = str_to_sentence(jurisdicti)) %>% 
+  st_transform(crs = 4326) %>%   # for matching projections
   st_simplify(preserveTopology = TRUE, dTolerance = 10000) #0.1 for paper
 
-grid_sf <-  st_read("/Volumes/Enterprise/Data/AcrossBoundaries/Data/Spatial/grid_sf/grid_eez_sf.shp")
-
-# Create specific state pallet from our friend Wes Andersson
-state_pallet <- c(wes_palette(n = 5, name = "Darjeeling1"),
-                               wes_palette(n = 5, name = "Darjeeling2"),
-                               wes_palette(n = 3, name = "Royal1")
-                  )
-
-unique(land_sf$ID)
-
+# Visual exploration (o.k! )
+ggplot(state_sf) +
+  geom_sf(aes(fill = state)) +
+  scale_fill_manual(values = state_pallet) +
+  theme_dark()
+
+```
+
+##### 5.- Fishing ports
+
+We used [Global Fishing Watch](https://globalfishingwatch.org/datasets-and-code-anchorages/)'s database on 
+Anchorages, Ports and Voyages.
+
+*The Global Fishing Watch anchorages dataset is a global database of anchorage locations where vessels congregate.
+The dataset contains over 160,000 individual anchorage locations, which are further grouped into nearly 32,000 ports when applicable.*
+
+```{r ports_sf, eval = T, echo = T}
+
+# ports_data <- my_path("D","NOAA", name = "SSmith_2015-2021 Landings_JUN 2021.xlsx", read = T) %>% 
+#   slice(-50) %>% # remove uneccessary row
+#
+
+gfw_data <- my_path("D","Spatial",name = "gfw_portdata.csv", read = T) %>% 
+  filter(iso3 == "USA")
+
+# Visualize data (o.k!)
+# ggplot(gfw_data) +
+#   geom_point(
+#     aes(
+#     x = lon,
+#     y = lat
+#   )
+#   )
+
+# Convert data to sf for mergig
+wpi_sf <- st_as_sf(wpi_data,
+             coords = c("longitude", "latitude"),
+             crs = 4326)
+
+# Merge data with state waters to,locate ports 
+port_sf <- st_join(wpi_sf,state_sf) %>% 
+  filter(!is.na(jurisdicti)) # remove points outside stat waters
+
+ggplot(port_sf)  +
+  geom_sf(aes(color = jurisdicti)) +
+  scale_color_manual(values = state_pallet) +
+  theme_dark()
+
+```
+
+This is how all the shapefiles look like together
+
+```{r all_sf, eval = T, echo = T}
+# Visual exploration of all together (o.k! )
 ggplot() +
   geom_sf(data = eez_sf, aes()) +
+  geom_sf(data = land_sf, aes(fill = state), alpha = 0.3) +
   geom_sf(data = state_sf, aes(color = state), fill = NA) +
+  geom_sf(data = port_sf, aes(color = state)) +
+  scale_color_manual(values = state_pallet) +
+  scale_fill_manual(values = state_pallet) +
+  theme_dark()
+
+```
+
+### Create base shapefile for computation
+
+As a first step we need to divide the NE US EEZ among the different states.
+For that, we expanded a buffer-polygon to the 200 nautical miles to then estimate the percentage that each expanded polygon occupied.
+For the initial buffer point we used two approaches; state waters and US ports.
+Note that in all cases these areas overlapped and percentages accounted for it.
+We did this by following these steps:
+
+- 1. Expand state waters / US ports using a buffer
+
+- 2. Grid that buffer on a 0.3 resolution
+
+- 3. Crop the buffer to the EEZ
+
+#### 1. Expand Spatial regions (a.k.a  buffers)
+
+##### 1.1 State Waters
+
+We set a buffer of *410000* m (410 km, ~ 221 nm) that overshoots the EEZ a bit, but is eventually cropped
+
+```{r buffer, eval = T, echo = T}
+
+# Buffer state waters
+state_bf = st_buffer(state_sf, 410000) %>% 
+  st_transform(4326) %>% # to match shape
+  st_set_crs(4326)
+
+# ------------------------------ #
+# Testing and visualizing the buffer 
+# ------------------------------ #
+
+state_bf_plot <- ggplot() +
+  geom_sf(data = state_sf, aes(color = state), fill = NA) +
+  geom_sf(data = eez_sf, aes(), fill = NA) +
+  geom_sf(data = state_bf, aes(color = state), fill = NA) +
   scale_color_manual(values = state_pallet)+
   theme_dark()
-
-```
-
-### Create base shapefile for computation
-
-As a first step we need to divide the NE US EEZ among the different states.
-For that we expanded state waters up to the 200 nautical miles to then estimate the percentage that each expanded-state-waters occupied.
-Note that in all cases these areas overlapped and percentages accounted for it.
-We did this by following these steps:
-
-- 1. Expand state waters using a buffer
-
-- 2. Grid that buffer on a 0.3 resolution
-
-- 3. Crop the buffer to the EEZ
-
-#### 1. Expand Spatial regions (a.k.a  buffers)
+#
+
+# ggsave("../Results/Partial/state_waters_buffer.png",state_bf_plot)
+
+# ------------------------------ #
+
+state_bf_plot
+
+```
+
+##### 1.1 US. Ports
 
@@
 ```
+
+# Recycling code
+## Sarah's data
+
+```{r}
+
+# This dataset includes all landings from 2015-July 2021. It includes the species landed, the port, and the Hull ID and vessel name for black sea bass and summer flounder.
+
+# *License, from Sarah Smith: This is confidential data, so please do not share this file with others.
+You may need to contact NOAA directly just to request permission.
+My contact has been Alison Ferguson (Alison.Ferguson@noaa.gov) in their data department.*
+
+### SRAH LANDING DATA
+# read_excel_allsheets <- function(filename, tibble = TRUE) {
+#     # I prefer straight data.frames
+#     # but if you like tidyverse tibbles (the default with read_excel)
+#     # then just pass tibble = TRUE
+#     sheets <- readxl::excel_sheets(filename)[2:8]
+#     x <- lapply(sheets, function(X) readxl::read_excel(filename, sheet = X))
+#     if(!tibble) x <- lapply(x, as.data.frame)
+#     names(x) <- sheets
+#     x
+# }
+# # Get data path
+# ports_path <- my_path("D","NOAA", name = "SSmith_2015-2021 Landings_JUN 2021.xlsx")
+# 
+# ports_data <- bind_rows(read_excel_allsheets(ports_path)) %>% 
+#   clean_names() %>% 
+#   mutate_if(is.character,
+#               ~ str_to_lower(.))
+
+```

### 2021-07-28 Scripts/spatial_analisis.Rmd
got port buffers

@@
 
-# ports_data <- my_path("D","NOAA", name = "SSmith_2015-2021 Landings_JUN 2021.xlsx", read = T) %>% 
-#   slice(-50) %>% # remove uneccessary row
-#
-
+# Get Global Fishig Watch data
 gfw_data <- my_path("D","Spatial",name = "gfw_portdata.csv", read = T) %>% 
@@
 # Buffer state waters
-state_bf = st_buffer(state_sf, 410000) %>% 
+state_bf = st_buffer(state_sf, 4) %>% 
   st_transform(4326) %>% # to match shape
@@
 
-We set a buffer of *410000* m (410 km, ~ 221 nm) that overshoots the EEZ a bit, but is eventually cropped
+We set a buffer of *4* deg (410 km, ~ 221 nm) that overshoots the EEZ a bit, but is eventually cropped
 
@@
 # Buffer state waters
-state_bf = st_buffer(state_sf, 410000) %>% 
+ports_bf = st_buffer(port_sf, 4) %>% 
   st_transform(4326) %>% # to match shape
@@
 
-state_bf_plot <- ggplot() +
-  geom_sf(data = state_sf, aes(color = state), fill = NA) +
-  geom_sf(data = eez_sf, aes(), fill = NA) +
-  geom_sf(data = state_bf, aes(color = state), fill = NA) +
+ggplot() +
+  geom_sf(data = eez_sf, aes(),fill = NA) +
+  geom_sf(data = ports_bf, aes(color = state), fill = NA) +
   scale_color_manual(values = state_pallet)+
   theme_dark()
-#
-
-# ggsave("../Results/Partial/state_waters_buffer.png",state_bf_plot)
-
-# ------------------------------ #
-
-state_bf_plot
 
@@
 
-*Note:* Dark grey shaded area is the grid
+*Note:* Dark grey shaded area is the grid and is the same for both approaches
 
@@
   scale_color_manual(values = state_pallet) +
-  theme_bw()+
+  theme_bw() +
   theme_dark()
@@
 
-Once we have a gridded area, we converted the grid to a `sf` so we can merge it with the buffered states and finally filter out everything outside the states polygon
+Once we have a gridded area, we converted the grid to a `sf` so we can merge it with the buffered statesand ports and finally filter out everything outside the states polygon
+
+###### 2.1.1 State Waters
 

### 2021-08-02 Scripts/spatial_analisis.Rmd
Included port analysis

@@
   filter(ID %in% States) %>% 
-  mutate(abrev = c("CO","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VI"),
+  mutate(abrev = c("CT","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VA"),
          state = str_to_sentence(ID)
@@
 
-##### 5.- Fishing ports
+##### 4.- Fishing ports
 
@@
 # Convert data to sf for mergig
-wpi_sf <- st_as_sf(wpi_data,
-             coords = c("longitude", "latitude"),
+gfw_sf <- st_as_sf(gfw_data,
+             coords = c("lon", "lat"),
              crs = 4326)
@@
 # Merge data with state waters to,locate ports 
-port_sf <- st_join(wpi_sf,state_sf) %>% 
+port_sf <- st_join(gfw_sf,state_sf) %>% 
   filter(!is.na(jurisdicti)) # remove points outside stat waters
@@
 ggplot(port_sf)  +
+  geom_sf(aes(color = distance_from_shore_m)) +
+  theme_dark()
+
+```
+So...Looks like some ports are "far from shore" which I don't really know what it means. For now, I am only selecting those ports that ar 0 meter from shore.
+
+```{r ports_inshore, eval = T, echo = F}
+
+# Get numner of ports per state
+ports_n_data <- port_sf %>% 
+  as.data.frame() %>% 
+    filter(distance_from_shore_m == 0) %>% 
+    group_by(state) %>% 
+    summarise(n_ports = n())
+
+# plot it
+gridExtra::grid.arrange(
+  port_sf %>% 
+    filter(distance_from_shore_m == 0) %>% 
+    ggplot()  +
     geom_sf(aes(color = jurisdicti)) +
     scale_color_manual(values = state_pallet) +
-  theme_dark()
-
-```
+    theme_dark() +
+    theme(legend.position = ""),
+  tableGrob(ports_n_data),
+  ncol = 2
+)
+
+```
+
+There are still too many ports in each state (?). Specially New Jersey! One approach is to use NOAA's landing-per-port data to filter out...
+
+###### 4.1 NOAA's data
+
+This dataset includes all landings from 2015-July 2021. It includes the species landed, the port, and the Hull ID and vessel name for black sea bass and summer flounder.
+
+*License, from Sarah Smith: This is confidential data, so please do not share this file with others.
+You may need to contact NOAA directly just to request permission.
+My contact has been Alison Ferguson (Alison.Ferguson@noaa.gov) in their data department.*
+
+```{r}
+
+### SRAH LANDING DATA
+read_excel_allsheets <- function(filename, tibble = TRUE) {
+    # I prefer straight data.frames
+    # but if you like tidyverse tibbles (the default with read_excel)
+    # then just pass tibble = TRUE
+    sheets <- readxl::excel_sheets(filename)[2:8]
+    x <- lapply(sheets, function(X) readxl::read_excel(filename, sheet = X))
+    if(!tibble) x <- lapply(x, as.data.frame)
+    names(x) <- sheets
+    x
+}
+# Get data path
+ports_path <- my_path("D","NOAA", name = "SSmith_2015-2021 Landings_JUN 2021.xlsx")
+
+# 
+ports_data <- bind_rows(read_excel_allsheets(ports_path)) %>%
+  clean_names() %>%
+  mutate_if(is.character,
+              ~ str_to_lower(.)) %>% 
+  mutate(landing_port = str_remove(landing_port,"[:blank:]\\(state\\)"))
+
+noaa_ports <- unique(ports_data$landing_port)
+
+noaa_port <- port_sf %>% 
+  filter(distance_from_shore_m == 0) %>% 
+  mutate(label = str_to_lower(label)) %>% 
+  filter(label %in% noaa_ports)
+
+# Get number of ports per state
+noaa_ports_n_data <- noaa_port %>% 
+  as.data.frame() %>% 
+    group_by(state) %>% 
+    summarise(noaa_ports = n())
+
+# Get number of ports in the NOAA database
+
+n_ports_data <- ports_data %>% 
+  group_by(landing_state) %>% 
+  summarise(noaa_ports = length(unique(landing_port))) %>% 
+  mutate(abrev = str_to_upper(landing_state)) %>% 
+  left_join(land_sf) %>% 
+  select(state,noaa_ports) %>% 
+  filter(!is.na(state)) %>% 
+  left_join(noaa_ports_n_data)
+
+# plot it
+gridExtra::grid.arrange(
+  port_sf %>% 
+    mutate(label = str_to_lower(label)) %>% 
+    filter(distance_from_shore_m == 0,
+           label %in% noaa_ports
+           ) %>% 
+    ggplot()  +
+    geom_sf(aes(color = jurisdicti)) +
+    scale_color_manual(values = state_pallet) +
+    theme_dark(),
+    # theme(legend.position = ""),
+  tableGrob(n_ports_data),
+  ncol = 2
+)
+
+```
+
+This approach removes a lot of ports to the point that Delaware is completely port-less
+
+###### 4.2 World Port Index
+
+In this approach we only use the ports categorized within the [WPI](https://msi.nga.mil/NGAPortal/MSI.portal?_nfpb=true&_pageLabel=msi_portal_page_62&pubCode=0015) and with `distance_from_shore_m == 0`  and `at_dock == TRUE`.
+
+- `at_dock` == Anchorages within a 450 meter buffer around a combined land shape file are considered at dock.
+
+```{r wpi_approach, eval = T, echo = F}
+
+gridExtra::grid.arrange(
+  port_sf %>% 
+    filter(distance_from_shore_m == 0,
+           label_source %in% c("WPI_ports"),
+           at_dock == TRUE) %>% 
+    ggplot()  +
+    geom_sf(aes(color = jurisdicti)) +
+    scale_color_manual(values = state_pallet) +
+    theme_dark(),
+  port_sf %>% 
+    as.data.frame() %>% 
+    filter(distance_from_shore_m == 0,
+           label_source %in% c("WPI_ports"),
+           at_dock == TRUE) %>% 
+    group_by(state) %>% 
+    summarise(n_ports = n()) %>% 
+    tableGrob(),
+  ncol = 2
+)
+
+```
+
+This approach might be better suited. It also has teh advantage that we are using the WPI.
 
@@
 ```{r all_sf, eval = T, echo = T}
+
+port_sf <- port_sf %>% 
+    filter(distance_from_shore_m == 0,
+           label_source %in% c("WPI_ports"),
+           at_dock == TRUE)
+
 # Visual exploration of all together (o.k! )
@@
   scale_fill_manual(values = state_pallet) +
-  theme_dark()
+  theme_dark() +
+  coord_sf(ylim = c(33,48))
 
@@
 
-```{r buffer, eval = T, echo = T}
+```{r sw_buffer, eval = T, echo = T}
 
@@
 
-We set a buffer of *4* deg (410 km, ~ 221 nm) that overshoots the EEZ a bit, but is eventually cropped
-
-```{r buffer, eval = T, echo = T}
+We set a buffer of *5* deg (510 km, ~ 221 nm) that overshoots the EEZ a bit, but is eventually cropped
+
+```{r fp_buffer, eval = T, echo = T}
 
 # Buffer state waters
-ports_bf = st_buffer(port_sf, 4) %>% 
+port_bf = st_buffer(port_sf, 5) %>% # port
   st_transform(4326) %>% # to match shape
@@
   geom_sf(data = eez_sf, aes(),fill = NA) +
-  geom_sf(data = ports_bf, aes(color = state), fill = NA) +
+  geom_sf(data = port_bf, aes(color = state), fill = NA) +
   scale_color_manual(values = state_pallet)+
@@
 
-Once we have a gridded area, we converted the grid to a `sf` so we can merge it with the buffered statesand ports and finally filter out everything outside the states polygon
+Once we have a gridded area, we converted the grid to a `sf` so we can merge it with the buffered states and ports and finally filter out everything outside the states polygon
 
@@
 
-```{r grid_buf_merge, eval = T, echo = T, message = F, warning = F, fig.width = 10}
+```{r grid_sw_buf_merge, eval = T, echo = T, message = F, warning = F, fig.width = 10}
 
@@
 # ---------------- #
-grid_sf <- st_as_sf(ne_grid,
+grid_sw_sf <- st_as_sf(ne_grid,
              coords = c("lon", "lat"),
@@
 # Note, will be used in next chunk
-grid_bf_dt <- as.data.frame(grid_sf) %>%
+grid_sw_bf_dt <- as.data.frame(grid_sw_sf) %>%
     select(index,state)
@@
   # Overall (overlapping) position
-  ggplot(grid_sf) +
+  ggplot(grid_sw_sf) +
     geom_sf(data = state_sf, aes(), fill = NA) +
@@
   ggplot() +
-    geom_sf(data = grid_sf, aes(color = state),size = 0.1, alpha = 0.5) +
+    geom_sf(data = grid_sw_sf, aes(color = state),size = 0.1, alpha = 0.5) +
     facet_wrap(~state) +
@@
 
+###### 2.1.1 Fishing Ports
+
+```{r grid_fp_buf_merge, eval = T, echo = T, message = F, warning = F, fig.width = 10}
+
+# ---------------- #
+# Convert grid to sf
+# ---------------- #
+grid_fp_sf <- st_as_sf(ne_grid,
+             coords = c("lon", "lat"),
+             crs = 4326) %>% 
+  st_join(port_bf) %>% # join to port sf
+  filter(!is.na(state)) %>% 
+  distinct(index,state, .keep_all = TRUE) #removes like 400K overlapping rows
+
+# Create data frame for future computations
+# Note, will be used in next chunk
+grid_fp_bf_dt <- as.data.frame(grid_fp_sf) %>%
+    select(index,state)
+
+# ---------------- #
+# [TEST] 
+# Visualization of grid
+# ---------------- #
+
+gridExtra::grid.arrange(
+  # Overall (overlapping) position
+  ggplot(grid_fp_sf) +
+    geom_sf(data = port_sf, aes(), fill = NA) +
+    geom_sf(aes(color = state), alpha = 0.3) +
+    geom_sf(data = eez_sf, aes(),fill =NA) + 
+    scale_color_manual(values = state_pallet) +
+    theme_dark() +
+    theme(legend.position = ""),
+  # Showing each state separately
+  ggplot() +
+    geom_sf(data = grid_fp_sf, aes(color = state),size = 0.1, alpha = 0.5) +
+    facet_wrap(~state) +
+    theme_dark() +
+    theme(legend.position = "top") +
+    scale_color_manual(values = state_pallet),
+  nrow = 1)
+
+```
+
 #### 3. Crop buffers to EEZ
@@
 
-```{r buff_to_eez, eval =T, echo = T, message = F, warning = F}
+#### 3.1 State Waters
+
+```{r buff_sw_to_eez, eval =T, echo = T, message = F, warning = F}
 
@@
 
-eez_sf <- st_read("/Volumes/Enterprise/Data/Spatial/World_EEZ_v11_20191118/eez_v11.shp") %>%
-  # rename(eez_name = Name) %>%
-  # st_transform(crs = 4326) %>% # 4326
-  filter(TERRITORY1 == "United States") %>% 
-  st_crop(xmin = -85, xmax = -60, ymin = 30, ymax = 50)
-
-# ggplot(eez_sf) +
-#   geom_sf()
-
 # Get the overlapping segments 
-# NOTE: Takes some gooooood time
-grid_eez_sf <- st_intersection(grid_sf,eez_sf)
-
+# NOTE: Takes some gooooood time (~20 min)
+Sys.time()
+grid_eez_sf_sw <- st_intersection(grid_sw_sf,eez_sf)
+Sys.time()
 # write_sf(grid_eez_sf, paste0(my_path("D", "Spatial"),"grid_eez_sf.shp"))
@@
 # Get final df with index
-grid_eez_df <- as.data.frame(grid_eez_sf) %>%
+grid_eez_sw_df <- as.data.frame(grid_eez_sf_sw) %>%
   select(state,index) %>%
@@
 # Plot to make sure makes sense
-grid_eez_sf %>%
+
+eez_sf <- eez_sf %>% 
+  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) #0.1 for paper
+
+grid_eez_sf_sw %>%
   ggplot() +
@@
   geom_sf(data = eez_sf,aes(), fill = NA) +
+  theme_dark()
+
+```
+
+#### 3.2 Fishing Ports
+
+```{r buff_fp_to_eez, eval =T, echo = T, message = F, warning = F}
+
+# Get the overlapping segments 
+# NOTE: Takes some gooooood time (~20 min)
+Sys.time()
+grid_eez_fp_sw <- st_intersection(grid_fp_sf,eez_sf)
+Sys.time()
+# write_sf(grid_eez_sf, paste0(my_path("D", "Spatial"),"grid_eez_sf.shp"))
+
+# Get final df with index
+grid_eez_fp_df <- as.data.frame(grid_eez_fp_sw) %>%
+  select(state,index) %>%
+  left_join(ne_grid,
+            by = "index")
+
+# write_csv(grid_eez_df, paste0(my_path("R", "Partial"),"grid_eez_df.csv"))
+
+# Plot to make sure makes sense
+grid_eez_fp_sw %>%
+  ggplot() +
+  geom_sf(aes(color = state), alpha = 0.3) +
+  scale_color_manual(values = state_pallet) +
+  geom_sf(data = eez_sf,aes(), fill = NA) +
+  theme_dark()
+
+```
+
+#### 3.3 Differences at cropede level
+
+By looking at the plots we do not see that the number of grid cells that each state has is slightly different depending on the approach.
+This comes to light when we count the number of gridcells that each state gets in each approach.
+We see that the state waters one is substantially higher.
+
+We can visualize the difference of the cropped area for each state next.
+Again, the fishing port approach results in less area for all states, but such area is not proportional among states.
+For example, Delaware looses roughly 35% of fishing grounds with this approach
+
+```{r state_bf_diff_tbl, eval = T, echo = T}
+
+grid_eez_sw_df %>% 
+  mutate(approach = "state_waters") %>% 
+  bind_rows(grid_eez_fp_df) %>%
+  mutate(approach = ifelse(is.na(approach),"fishing_port",approach)) %>% 
+  group_by(state,approach) %>% 
+  summarise(n_grid = n()) %>% 
+  spread(approach,n_grid) %>% 
+  mutate(difference =state_waters-fishing_port,
+         percentage_sw = round((difference/state_waters)*100)
+         )
+
+```
+
+And here is the map visualization of the cropped difference
+
+```{r state_bf_diff_map, eval = T, echo = T}
+
+grid_eez_sw_df %>% 
+  mutate(approach = "state_waters") %>% 
+  bind_rows(grid_eez_fp_df) %>%
+  mutate(approach = ifelse(is.na(approach),"fishing_port",approach)) %>% 
+  ggplot() +
+  geom_tile(
+    aes(
+      x = lon,
+      y = lat,
+      color = approach,
+      fill = approach
+    )
+  ) +
+  facet_wrap(~state) +
+  scale_color_brewer(palette = "Set2") +
+  scale_fill_brewer(palette = "Set2") +
   theme_dark()
@@
 ```
-
-# Recycling code
-## Sarah's data
-
-```{r}
-
-# This dataset includes all landings from 2015-July 2021. It includes the species landed, the port, and the Hull ID and vessel name for black sea bass and summer flounder.
-
-# *License, from Sarah Smith: This is confidential data, so please do not share this file with others.
-You may need to contact NOAA directly just to request permission.
-My contact has been Alison Ferguson (Alison.Ferguson@noaa.gov) in their data department.*
-
-### SRAH LANDING DATA
-# read_excel_allsheets <- function(filename, tibble = TRUE) {
-#     # I prefer straight data.frames
-#     # but if you like tidyverse tibbles (the default with read_excel)
-#     # then just pass tibble = TRUE
-#     sheets <- readxl::excel_sheets(filename)[2:8]
-#     x <- lapply(sheets, function(X) readxl::read_excel(filename, sheet = X))
-#     if(!tibble) x <- lapply(x, as.data.frame)
-#     names(x) <- sheets
-#     x
-# }
-# # Get data path
-# ports_path <- my_path("D","NOAA", name = "SSmith_2015-2021 Landings_JUN 2021.xlsx")
-# 
-# ports_data <- bind_rows(read_excel_allsheets(ports_path)) %>% 
-#   clean_names() %>% 
-#   mutate_if(is.character,
-#               ~ str_to_lower(.))
-
-```

### 2021-08-05 Scripts/spatial_analisis.Rmd
Created spatial polygon of ports data

@@
 output:
-  # html_document
-  html_notebook:
+  html_document:
+  # html_notebook:
     fig_width: 6
@@
 
-# Fix new updats of sf package
+# Fix new updates of sf package
 sf::sf_use_s2(use_s2 = FALSE)
@@
 
-# Get numner of ports per state
+# Get number of ports per state
 ports_n_data <- port_sf %>% 
@@
 Sys.time()
-grid_eez_fp_sw <- st_intersection(grid_fp_sf,eez_sf)
+grid_eez_sf_fp <- st_intersection(grid_fp_sf,eez_sf)
 Sys.time()
-# write_sf(grid_eez_sf, paste0(my_path("D", "Spatial"),"grid_eez_sf.shp"))
+
+# write_sf(grid_eez_sf_fp, paste0(my_path("D", "Spatial/grid_eez_fp_sf"),"grid_eez_fp.shp"))
 
 # Get final df with index
-grid_eez_fp_df <- as.data.frame(grid_eez_fp_sw) %>%
+grid_eez_fp_df <- as.data.frame(grid_eez_sf_fp) %>%
   select(state,index) %>%
@@
 
-# write_csv(grid_eez_df, paste0(my_path("R", "Partial"),"grid_eez_df.csv"))
+write_csv(grid_eez_fp_df, paste0(my_path("R", "Partial"),"grid_eez_fp_df.csv"))
 
 # Plot to make sure makes sense
-grid_eez_fp_sw %>%
+grid_eez_sf_fp %>%
   ggplot() +
@@
 
-#### 3.3 Differences at cropede level
+#### 3.3 Differences at croped level
 
@@
 
-```{r state_bf_diff_tbl, eval = T, echo = T}
+```{r state_bf_diff_ntbl, eval = T, echo = T}
 
@@
 
-##### 3.1 Paper figure; buffer plot
+#### 3.4 Paper plot; Buffer plot
 
@@
 
-plot_data <-grid_eez_sf %>% 
-    mutate(state = str_to_sentence(state)) %>% 
-    left_join(state_lat)
-
-p <- gridExtra::grid.arrange(
+#### Data needed ####
+
+# Get state order from North to south
+state_order <- my_path("R","Partial/", name = "grid_eez_fp_df.csv",read = T) %>%
+  group_by(state) %>% 
+  summarise(
+    order = mean(lat)
+  ) %>% 
+  mutate(abrev = c("CT","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VA")
+  ) %>% 
+  arrange(desc(order)) %>% 
+  mutate(order= c("b","a",letters[3:11])) # weirdly maine goes below
+
+# Load grid of state waters
+grid_eez_sw_sf <- st_read(my_path("D","Spatial/grid_eez_sw_sf", name = "grid_eez_sf.shp")) %>% 
+  select(index,state,geometry) %>% 
+  mutate(method = "state_waters",
+         state = str_to_sentence(state)) %>% 
+  left_join(state_order)
+
+grid_eez_sw_sf$group <- factor(grid_eez_sw_sf$abrev,      # Reordering group factor levels
+                               levels = state_order$abrev)
+
+# Load grid of fishing ports
+grid_eez_fp_sf <- st_read(my_path("D","Spatial/grid_eez_fp_sf", name = "grid_eez_fp.shp")) %>% 
+  select(index,state = jursdct,geometry) %>% 
+  mutate(method = "fishing_port",
+         state = str_to_sentence(state))%>% 
+  left_join(state_order)
+
+grid_eez_fp_sf$group <- factor(grid_eez_fp_sf$abrev,      # Reordering group factor levels
+                               levels = state_order$abrev)
+
+# Plotting 
+# Make sure st_simplify() is run for eez sf
+
+# State waters plot
+
+p_sw <- gridExtra::grid.arrange(
   # Overall (overlapping) position
-  ggplot(plot_data) +
+  ggplot(grid_eez_sw_sf) +
     geom_sf(data = eez_sf, aes(), fill = "white") + 
-    geom_sf(aes(color = order, fill = order), alpha = 0.3) +
+    geom_sf(aes(color =abrev , fill = abrev), alpha = 0.3) +
     geom_sf(data = land_sf, aes()) +
-    geom_sf_label_repel(data = land_sf, aes(label= abrev), 
-                      size = 2,
+    ggsflabel::geom_sf_label_repel(data = land_sf, aes(label= abrev), 
+                                   size = 4,
                                    box.padding = 0.10,
@@
     my_ggtheme_p(leg_pos = "",
-                 ax_tx_s = 12) +
+                 ax_tx_s = 13) +
     coord_sf(ylim = c(30,48)) +
     scale_y_continuous(breaks = c(30,35,40,45))+
-    labs(x = "", y = ""),
+    labs(x = "", y = "", title = "A) State waters extrapolation") +
+    theme(plot.title = element_text(size = 20)),
   # Showing each state separately
-
-    ggplot(plot_data) +
+  ggplot(grid_eez_sw_sf) +
     geom_sf(data = land_sf, aes(), fill = "grey80") +
-    geom_sf( aes(color = order),size = 0.1, alpha = 0.8) +
-    facet_wrap(~ state) +
+    geom_sf(aes(color = abrev),size = 0.1, alpha = 0.3) +
+    facet_wrap(~ group) +
     theme(legend.position = "top") +
     scale_color_manual(values = state_pallet,
-                       labels = plot_data %>% arrange(order) %>%  pull(state) %>% unique()) +
+                       # labels = unique(grid_eez_sw_sf$group)) +
+                       labels = grid_eez_sw_sf %>% arrange(order) %>%  pull(state) %>% unique()) +
+    ggtitle("") +
     my_ggtheme_p(leg_pos = "",
-                 ax_tx_s = 6,
+                 ax_tx_s = 11,
                  axx_tx_ang = 45,
@@
     ),
-  nrow = 1,
+  nrow = 1)
+
+##### ------------- ####
+# Fishing Ports plot
+##### ------------- ####
+
+p_fp <- gridExtra::grid.arrange(
+  # Overall (overlapping) position
+  ggplot(grid_eez_fp_sf) +
+    geom_sf(data = eez_sf, aes(), fill = "white") + 
+    geom_sf(aes(color = abrev, fill = abrev), alpha = 0.3) +
+    geom_sf(data = land_sf, aes()) +
+    ggsflabel::geom_sf_label_repel(data = land_sf, aes(label= abrev), 
+                                   size = 4,
+                                   box.padding = 0.10,
+                                   hjust = 1) +
+    scale_color_manual(values = state_pallet) +
+    scale_fill_manual(values = state_pallet) +
+    my_ggtheme_p(leg_pos = "",
+                 ax_tx_s = 13) +
+    coord_sf(ylim = c(30,48)) +
+    scale_y_continuous(breaks = c(30,35,40,45)) +
+    labs(x = "", y = "", title = "B) Fishing ports extrapolation") +
+    theme(plot.title = element_text(size = 20)),
+  # Showing each state separately
+  ggplot(grid_eez_fp_sf) +
+    geom_sf(data = land_sf, aes(), fill = "grey80") +
+    geom_sf(aes(color = abrev),size = 0.1, alpha = 0.3) +
+    facet_wrap(~ group) +
+    theme(legend.position = "top") +
+    scale_color_manual(values = state_pallet,
+                       # labels = unique(grid_eez_fp_sf$group)) +
+                       labels = grid_eez_fp_sf %>% arrange(order) %>%  pull(state) %>% unique()) +
+    ggtitle("") +
+    my_ggtheme_p(leg_pos = "",
+                 ax_tx_s = 11,
+                 axx_tx_ang = 45,
+                 hjust = 1
+    ),
+  nrow = 1)
+
+combined_plot <- gridExtra::grid.arrange(p_sw,p_fp,
                                          bottom = "Longitude",
@@
 
-  ggsave(filename = "buffer_figure.jpg",
-         plot = p,
+ggsave(filename = "buffer_figure_b.jpg",
+       plot = combined_plot,
        path = my_path("R","Figures"),
-         width = 10,
-         height = 5
-         )
-
-```
-
-![Buffer figure for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/buffer_figure.jpg)
+       width = 11,
+       height = 11
+)
+
+```
+
+![Buffer figure for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/buffer_figure_b.jpg)
 
@@
 # Load all sp in one table
-historic_spp <- bind_rows(lapply(taxon_read, fread)) %>% 
+historic_spp_sw <- bind_rows(lapply(taxon_read, fread)) %>% 
   mutate(state = str_to_sentence(state))

### 2021-08-05 Scripts/spatial_analisis.Rmd
tweeked function to include extrapolation method

@@
 
-run_tis <- function(input_data, grid, years, taxa, reg){
+run_tis <- function(input_data, grid, years, taxa, reg, method){
 
@@
     partial_df <- bind_rows(
-      lapply(years,tis,input_data = ocean_data, grid = grid_eez_df, taxa = taxa, reg = regions[r])
+      lapply(years,tis,input_data = input_data, grid = grid, taxa = taxa, reg = reg[r])
     )
@@
 
+  complement <- paste0("Partial/Interpolation/",method)
+
   # Set path name
-  save_path <- my_path("R","Partial/Interpolation")
+  save_path <- my_path("R",complement)
 
@@
 # Test me
-    # run_tis(input_data = ocean_data, grid = grid_eez_df, taxa = "Centropristis striata", years = years, reg = regions)
+    # run_tis(input_data = ocean_data, grid = grid_eez_fp_df, taxa = "Centropristis striata", years = seq(1970,1980), reg = regions, method = "testa")
 

### 2021-08-09 Scripts/spatial_analisis.Rmd
updated website for presentation

@@
 output:
-  html_document:
-  # html_notebook:
+  # html_document:
+  html_notebook:
     fig_width: 6
@@
     toc: yes
-    toc_depth: 3
+    toc_depth: 6
     toc_float:
@@
 # Load grid df
-grid_eez_df <- my_path("D","Spatial","grid_eez_df.csv", read = T)
+# For fishing ports
+grid_eez_fp_df <- my_path("D","Spatial/grid_eez_fp_sf","grid_eez_fp_df.csv", read = T)
+
+# For state waters
+# grid_eez_sw_df <- my_path("D","Spatial/grid_eez_fp_sf","grid_eez_fp_df.csv", read = T)
 
@@
 
-spp_runs <- tibble(taxa = (list.files(my_path("R","Partial/Interpolation")))) %>%
+spp_runs <- tibble(taxa = (list.files(my_path("R","Partial/Interpolation/fp")))) %>%
   mutate(
@@
 
-# single species run
+# # single species run
 # run_tis(input_data = ocean_data,
-#         grid = grid_eez_df,
+#         grid = grid_eez_fp_df,
 #         years = years,
 #         reg = regions,
-#         taxa = "Illex illecebrosus"
+#         taxa = "Illex illecebrosus",
+#         method = "fp"
 # )
@@
        input_data = ocean_data,
-                   grid = grid_eez_df,
+       grid = grid_eez_fp_df,
        years = years,
-                   reg = regions
+       reg = regions,
+       method = "fp"
 )

### 2021-08-13 Allocation_tool/server.R
updated path

@@ -54,7 +54,7 @@ shinyServer(function(input, output) {
         
         name <- paste0("tif_",str_replace(input$SppSelection," ","_"),".csv")
         
-        data <- my_path("R","Partial/Interpolation",name = name, read = T)
+        data <- my_path("R","Partial/Interpolation/sw",name = name, read = T)
         
     })
     

### 2021-08-13 Scripts/manuscript_acrossboundaries.Rmd
included results

@@
 
+# Methods
+
+We expanded the grid following two methods (Fig. 1).
+
+![Figure 1.
+Spatial regions within the United States' North East Exclusive Economic Zone.
+A) Spatial buffers from each State's waters.
+B) Spatial buffers from the main fishing ports.
+States are aligned by average latitude from north to south.
+ME = Maine; NH, New Hampshire; MA, Massachusetts; RI, Rhode Island; CT, Connecticut; NY, New York; NY, New Jersey; DE, Delaware; MD, Maryland; VA Virginia; North Carolina.](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F1_buffer_figure.jpg)
+
 # Results
--	Two boundaries methods
--	Two surveys
+
+![Figure 2.
+Change in the proportion of species distribution per State in recent years (2002 - 2014) relative to the reference years (1990-2001) following the fishing ports (top) and State waters (middle) approach.
+Bottom pannel showing the percentage difference between both approaches.
+](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F2_proportion_chg_diff.jpg)
+
+![Figure 3.
+Aggregated distribution proportion per state of Paralichthys dentatus, Stenotomus chrysops and Centropristis striata over time.
+Each color represent a State ordered latitudinal.
+Grey box represents the base-period used for the fisheries quota allocation ](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F3_area_plot_avg_agg_sptl.jpg)
+
+![Figure 4.
+Proportion of the distribution of Paralichthys dentatus, Stenotomus chrysops and Centropristis striata over time.
+Each color represent a State ordered latitudinal.
+Grey box represents the base-period used for the fisheries quota allocation ](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F4_area_plot_avg_spp_sptl.jpg)

### 2021-08-13 Scripts/spatial_analisis.Rmd
Results for both approaches

@@
 output:
-  # html_document:
-  html_notebook:
+  html_document:
+  # html_notebook:
     fig_width: 6
@@
 # Get state order from North to south
-state_order <- my_path("R","Partial/", name = "grid_eez_fp_df.csv",read = T) %>%
+state_order <- my_path("D","Spatial/grid_eez_fp_sf", name = "grid_eez_fp_df.csv",read = T) %>%
   group_by(state) %>% 
@@
   arrange(desc(order)) %>% 
-  mutate(order= c("b","a",letters[3:11])) # weirdly maine goes below
+  mutate(order= c("b","a",letters[3:11])) %>% # weirdly maine goes below
+  arrange(order)
 
@@
 
+grid_eez_fp_sf <- arrange(grid_eez_fp_sf,group)
 # Plotting 
@@
     geom_sf(data = eez_sf, aes(), fill = "white") + 
-    geom_sf(aes(color =abrev , fill = abrev), alpha = 0.3) +
+    geom_sf(aes(color =group , fill = group), alpha = 0.3) +
     geom_sf(data = land_sf, aes()) +
@@
     scale_y_continuous(breaks = c(30,35,40,45))+
-    labs(x = "", y = "", title = "A) State waters extrapolation") +
+    labs(x = "", y = "", title = "A) State waters approach") +
     theme(plot.title = element_text(size = 20)),
@@
     geom_sf(data = land_sf, aes(), fill = "grey80") +
-    geom_sf(aes(color = abrev),size = 0.1, alpha = 0.3) +
+    geom_sf(aes(color = group),size = 0.1, alpha = 0.3) +
     facet_wrap(~ group) +
@@
     geom_sf(data = eez_sf, aes(), fill = "white") + 
-    geom_sf(aes(color = abrev, fill = abrev), alpha = 0.3) +
+    geom_sf(aes(color = group, fill = abrev), alpha = 0.3) +
     geom_sf(data = land_sf, aes()) +
@@
     scale_y_continuous(breaks = c(30,35,40,45)) +
-    labs(x = "", y = "", title = "B) Fishing ports extrapolation") +
+    labs(x = "", y = "", title = "B) Fishing ports approach") +
     theme(plot.title = element_text(size = 20)),
@@
 
-ggsave(filename = "buffer_figure_b.jpg",
+ggsave(filename = "buffer_figure.jpg",
        plot = combined_plot,
@@
 # # single species run
-# run_tis(input_data = ocean_data,
-#         grid = grid_eez_fp_df,
-#         years = years,
-#         reg = regions,
-#         taxa = "Illex illecebrosus",
-#         method = "fp"
-# )
+run_tis(input_data = ocean_data,
+        grid = grid_eez_fp_df,
+        years = years,
+        reg = regions,
+        taxa = "Stenotomus chrysops",
+        method = "fp"
+)
 
@@
 Results are now for eight species managed under Mid-Atlantic Council Management Plans according to [NOAA](https://www.fisheries.noaa.gov/new-england-mid-atlantic/commercial-fishing/new-england-mid-atlantic-fishery-management-plans).
+
+State allocations of the commercial black sea bass coastwide quota were originally implemented in 2003 as part of Amendment 13, loosely based on historical landings from 1980- 2001.
 
@@
 
-spp_paths <- list.files(my_path("R",extra_path = "Partial/Interpolation"))
+spp_paths <- list.files(my_path("R",extra_path = "Partial/Interpolation/sw"))
 
@@
 
-taxon_read <- paste0(my_path("R",extra_path = "Partial/Interpolation"),taxon_read)
+#### Load sw interpolation
+
+taxon_sw <- my_path("R",extra_path = "Partial/Interpolation/sw", name = taxon_read)
+
+taxon_fp <- my_path("R",extra_path = "Partial/Interpolation/fp", name = taxon_read)
 
 # Load all sp in one table
-historic_spp_sw <- bind_rows(lapply(taxon_read, fread)) %>% 
-  mutate(state = str_to_sentence(state))
+historic_spp <- bind_rows(lapply(taxon_sw, fread)) %>% 
+  mutate(spatial = "sw") %>% 
+  bind_rows(
+    bind_rows(lapply(taxon_fp, fread))
+  ) %>% 
+  mutate(state = str_to_sentence(state),
+         spatial = ifelse(is.na(spatial),"fp",spatial))
 
 unique(historic_spp$spp)
+unique(historic_spp$spatial)
 
@@
 data_grid <- historic_spp %>% 
-  group_by(state,lat,lon,region) %>% 
+  group_by(state,lat,lon,region,spatial) %>% 
   summarise(sum = sum(value,na.rm= T), .groups = "drop") %>% # sum of all species
-  group_by(state,lat,lon,region) %>% 
+  group_by(state,lat,lon,region,spatial) %>% 
   summarise(mean = mean(sum,na.rm= T), .groups = "drop") # average of all years
@@
   geom_sf(data = land_sf, aes()) +
-  facet_wrap(~ state  +  region,
-             ncol = 4) +
+  facet_wrap(~ state  +  region + spatial) +
   labs(x = "Longitude", y = "Latitude") +
@@
 total_fited <- historic_spp %>% 
-  group_by(year,region) %>% 
+  group_by(year,region,spatial) %>% 
   summarise(total_value = sum(value,na.rm=T),.groups = "drop")
@@
 state_fit <- historic_spp %>% 
-  group_by(state,year,region) %>% 
+  group_by(state,year,region,spatial) %>% 
   summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
   left_join(total_fited,
-            by = c("year","region")) %>%
+            by = c("year","region","spatial")) %>%
   mutate(percentage = state_value/total_value*100) %>% 
@@
             by = "year") %>% 
-  group_by(state,order,label,region) %>% 
+  group_by(state,order,label,region,spatial) %>% 
   summarise(mean_per = round(mean(percentage)),.groups = "drop")
@@
   viridis::scale_fill_viridis("Average proportion per State", alpha = 0.8) +
-  facet_wrap(~ region + label, 
+  facet_wrap(~ region + label +spatial, 
              nrow = 2) +
@@
 total_fited <- historic_spp %>% 
-  group_by(year,region,spp) %>% 
+  group_by(year,region,spp,spatial) %>% 
   summarise(total_value = sum(value,na.rm=T),.groups = "drop")
@@
 state_fit <- historic_spp %>% 
-  group_by(state,year,region,spp) %>% 
+  group_by(state,year,region,spp,spatial) %>% 
   summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
   left_join(total_fited,
-            by = c("year","region","spp")) %>%
-  mutate(percentage = state_value/total_value*100) %>% 
-  left_join(periods,
-            by = "year") %>% 
-  group_by(state,order,label,region,spp) %>% 
+            by = c("year","region","spp","spatial")) %>%
+  mutate(percentage = state_value/total_value*100,
+         label = ifelse(year >= 1980 & year <= 2001,"Reference",
+                         ifelse(year > 2001,"Today",NA)
+                         )
+         ) %>% 
+  # left_join(periods,
+  #           by = "year") %>% 
+  group_by(state,label,region,spp,spatial) %>% 
   summarise(mean_per = round(mean(percentage)),.groups = "drop") %>% 
   #Only show results for spring
-  filter(str_detect(region,"Spring")) %>% 
-  mutate(spp = gsub(" ","\n",spp))
+  filter(str_detect(region,"Spring"),
+         !is.na(label)) %>% 
+  spread(spatial,mean_per) %>% 
+  mutate(difference = (fp-sw)/((fp+sw)/2)*100,
+         difference = ifelse(difference > 100,100,
+                             ifelse(difference < -100,-100,difference)
+         )
+  ) %>% 
+  gather("spatial","mean_per",fp:difference) %>% 
+  mutate(spp = gsub(" ","\n",spp),
+         spatial = ifelse(spatial == "fp","Fishing ports",
+                          ifelse(spatial == "sw","State Waters","Difference")
+         )
+  )
 
@@
             by = "state") %>% 
+  filter(spatial != "Difference") %>% 
   ggplot() +
@@
   viridis::scale_fill_viridis("Average proportion per State", alpha = 0.8) +
-  facet_grid(spp ~ label) +
-  labs(x = "Longitude", 
-       y = "Latitude") +
+  facet_grid(spatial~ spp+label) +
+  labs(x = "", 
+       y = "") +
   my_ggtheme_p(facet_tx_s = 20,
@@
 
-  ggsave(filename = "proportion_chg_spp.jpg",
-         plot = map_plot,
+diff_plot <- land_sf %>% 
+  left_join(state_fit,
+            by = "state") %>% 
+  filter(spatial == "Difference") %>% 
+  ggplot() +
+  geom_sf(aes(fill = mean_per)) +
+  viridis::scale_fill_viridis("Percentage difference", alpha = 0.8) +
+  facet_grid(spatial~ spp+label) +
+  labs(x = "", 
+       y = "") +
+  my_ggtheme_p(facet_tx_s = 20,
+               leg_pos = "bottom",
+               axx_tx_ang = 45,
+               ax_tx_s = 12,
+               ax_tl_s = 18,
+               hjust = 1) +
+  theme(legend.key.width = unit(4,"line"),
+        strip.background = element_blank(),
+        strip.text.x = element_blank()
+        )
+
+# Cowplot option
+p <- ggdraw() +
+  # Revenue circular
+  draw_plot(map_plot, x = 0, y = 0.2, width = 1, height = 0.8) +
+  # Catch circular
+  draw_plot(diff_plot, x = 0, y = 0, width = 1, height = 0.4) +
+  draw_plot_label(label = c("Latitude", "Longitude"), 
+                  size = 18,
+                  angle = c(90,0),
+                  x = c(0,0.45), 
+                  y = c(0.45,0.15)
+  )
+
+save_plot(
   path = my_path("R","Figures"),
-         width = 14,
-         height = 14
-         )
-
-```
-
-![Proportion change per species map for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/proportion_chg_spp.jpg)
-
-### Paper figure: Aggregated Proportional change
-
-```{r area_map_aggregated_formans, eval = T, echo = T, fig.width = 10, fig.height=6}
+  "proportion_chg_spp_spatial.jpg",
+  p,
+  base_height = 14,
+  base_width = 14
+)
+
+```
+
+### Proportion change realtive to past
+
+```{r paper_figure_area_map, eval = F, echo = T, results='hide'}
 
 total_fited <- historic_spp %>%
-  group_by(year,region) %>% 
+  group_by(year,region,spp,spatial) %>%
   summarise(total_value = sum(value,na.rm=T),.groups = "drop")
 
-state_fit <- historic_spp %>% 
-  group_by(state,year,region) %>% 
+state_change <-historic_spp %>% 
+  group_by(state,year,region,spp,spatial) %>% 
   summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
   left_join(total_fited,
-            by = c("year","region")) %>%
-  mutate(percentage = state_value/total_value*100) %>% 
-  left_join(periods,
-            by = "year") %>% 
-  group_by(state,order,label,region) %>% 
+            by = c("year","region","spp","spatial")) %>%
+  mutate(percentage = state_value/total_value*100,
+         label = ifelse(year >= 1980 & year <= 2001,"Reference",
+                         ifelse(year > 2001,"Today",NA)
+                         )
+         ) %>% 
+  # left_join(periods,
+            # by = "year") %>% 
+  group_by(state,label,region,spp,spatial) %>% 
   summarise(mean_per = round(mean(percentage)),.groups = "drop") %>% 
-  filter(str_detect(region,"Spring"))
-
-agg_map <- land_sf %>% 
+  #Only show results for spring
+  filter(str_detect(region,"Spring"),
+         !is.na(label)
+         ) %>% 
+  select(-region) %>% 
+  spread(label,mean_per) %>% 
+  mutate(change = (Today-Reference)/(Today)*100,
+         change = ifelse(change > 100,100,
+                         ifelse(change < -100,-100,change)
+         )
+  ) %>%
+  select(-4,-5) %>% 
+  spread(spatial,change) %>% 
+  mutate(difference = (fp-sw)/((fp+sw)/2)*100,
+         difference = ifelse(difference > 100,100,
+                             ifelse(difference < -100,-100,difference)
+         )
+  ) %>% 
+  gather("spatial","mean_per",fp:difference) %>% 
+  mutate(
+         spatial = ifelse(spatial == "fp","Fishing ports",
+                          ifelse(spatial == "sw","State Waters","Difference")
+         )
+  )
+
+# The plot
+prop_chng_map <- land_sf %>% 
+  left_join(state_change,
+            by = "state") %>% 
+  filter(spatial != "Difference") %>% 
+  ggplot() +
+  geom_sf(aes(fill = mean_per)) +
+  viridis::scale_fill_viridis("Change in proportion today\n relative to 1973-1984\n(%)", alpha = 0.8,
+                              limits = c(-100,100),
+                              breaks = seq(-100,100,25),
+                              labels = c(seq(-100,75,25),">100")
+                              ) +
+  facet_grid(spatial~ spp) +
+  labs(x = "", 
+       y = "") +
+  my_ggtheme_p(facet_tx_s = 20,
+               leg_pos = "bottom",
+               axx_tx_ang = 45,
+               ax_tx_s = 12,
+               ax_tl_s = 18,
+               hjust = 1) +
+  theme(legend.key.width = unit(4,"line"),
+        legend.title.align=0.5)
+
+ggsave(filename = "temp_proportion_chng.jpg",
+         plot = prop_chng_map,
+         path = my_path("R","Figures"),
+         width = 10,
+         height = 10
+  )
+
+#### Option with differences
+
+prop_chng_map_diff <- land_sf %>% 
+  left_join(state_change,
+            by = "state") %>% 
+  filter(spatial == "Difference") %>% 
+  ggplot() +
+  geom_sf(aes(fill = mean_per)) +
+  viridis::scale_fill_viridis("Change in proportion\n relative to 1980-2001 (%)", 
+                              alpha = 0.8,
+                              # option = "C"
+                              limits = c(-100,100),
+                              breaks = seq(-100,100,25),
+                              labels = c(seq(-100,75,25),">100")
+                              ) +
+  facet_grid(spatial~ spp) +
+  labs(x = "", 
+       y = "") +
+  my_ggtheme_p(facet_tx_s = 20,
+               leg_pos = "bottom",
+               axx_tx_ang = 45,
+               ax_tx_s = 12,
+               ax_tl_s = 18,
+               hjust = 1) +
+  theme(legend.key.width = unit(4,"line"),
+        legend.title.align=0.5,
+        strip.background = element_blank(),
+        strip.text.x = element_blank())
+
+# Cowplot option
+p <- ggdraw() +
+  # Revenue circular
+  draw_plot(prop_chng_map, x = 0, y = 0.25, width = 1, height = 0.65) +
+  # Catch circular
+  draw_plot(prop_chng_map_diff, x = 0.101, y = 0, width = 0.798, height = 0.4) +
+  draw_plot_label(label = c("Latitude", "Longitude"), 
+                  size = 16,
+                  angle = c(90,0),
+                  x = c(0.1,0.45), 
+                  y = c(0.45,0.11)
+  )
+
+save_plot(
+  path = my_path("R","Figures"),
+  "proportion_chg_diff.jpg",
+  p,
+  base_height = 14,
+  base_width = 14
+)
+
+```
+
+![Proportion change per species map for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/temp_proportion_chng.jpg)
+
+### Paper figure: Aggregated Proportional change
+
+```{r area_map_aggregated_formans, eval = T, echo = T, fig.width = 10, fig.height=6}
+
+total_fited <- historic_spp %>% 
+  group_by(year,region,spatial) %>% 
+  summarise(total_value = sum(value,na.rm=T),.groups = "drop")
+
+state_fit <- historic_spp %>% 
+  group_by(state,year,region,spatial) %>% 
+  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
+  left_join(total_fited,
+            by = c("year","region","spatial")) %>%
+  mutate(percentage = state_value/total_value*100, 
+  # left_join(periods,
+            # by = "year") %>% 
+  label = ifelse(year >= 1980 & year <= 2001,"Reference",
+                         ifelse(year > 2001,"Today",NA)
+                         )
+         ) %>% 
+  group_by(state,label,region,spatial) %>% 
+  summarise(mean_per = round(mean(percentage)),.groups = "drop") %>% 
+  filter(str_detect(region,"Spring"),
+         !is.na(label)
+         ) %>% 
+  spread(spatial,mean_per) %>% 
+  mutate(difference = (fp-sw)/((fp+sw)/2)*100,
+         difference = ifelse(difference > 100,100,
+                             ifelse(difference < -100,-100,difference)
+         )
+  ) %>% 
+  gather("spatial","mean_per",fp:difference) %>% 
+  mutate(
+         spatial = ifelse(spatial == "fp","Fishing ports",
+                          ifelse(spatial == "sw","State Waters","Difference")
+         )
+  )
+
+# Spatial map
+agg_sppatial_map <- land_sf %>% 
   left_join(state_fit,
             by = "state") %>% 
+  filter(spatial != "Difference") %>% 
   ggplot() +
   geom_sf(aes(fill = mean_per)) +
-  viridis::scale_fill_viridis("Average proportion per State", alpha = 0.8) +
-  facet_wrap(~ label, nrow = 1) +
-  labs(x = "Longitude", 
-       y = "Latitude") +
+  viridis::scale_fill_viridis("Distribution\nProportion", alpha = 0.8) +
+  facet_grid(spatial~ label) +
+  labs(x = "", 
+       y = "") +
   my_ggtheme_p(facet_tx_s = 16,
-               leg_pos = "bottom",
+               leg_pos = "right",
                leg_tl_s = 14,
@@
                ax_tl_s = 14) +
-  theme(legend.key.width = unit(2,"line"))
-
-  ggsave(filename = "proportion_chg_agg.jpg",
-         plot = agg_map,
+theme(legend.title.align=0.5)
+
+# Difference map
+agg_diff_map <- land_sf %>% 
+  left_join(state_fit,
+            by = "state") %>% 
+  filter(spatial == "Difference") %>% 
+  ggplot() +
+  geom_sf(aes(fill = mean_per)) +
+  viridis::scale_fill_viridis("Percentage\nDifference",option = "C", alpha = 0.8) +
+  facet_grid(spatial~ label) +
+  labs(x = "", 
+       y = "") +
+  my_ggtheme_p(facet_tx_s = 16,
+               leg_pos = "right",
+               leg_tl_s = 14,
+               ax_tx_s = 10,
+               ax_tl_s = 14)+
+  theme(
+        strip.background = element_blank(),
+        strip.text.x = element_blank(),
+        legend.title.align=0.5
+        )
+
+# Cowplot option
+p <- ggdraw() +
+  # Revenue circular
+  draw_plot(agg_sppatial_map, x = 0, y = 0.35, width = 1, height = 0.65) +
+  # Catch circular
+  draw_plot(agg_diff_map, x = 0.093, y = 0.05, width = 0.814, height = 0.4) +
+  draw_plot_label(label = c("Latitude", "Longitude"), 
+                  size = 10,
+                  angle = c(90,0),
+                  x = c(0,0.35), 
+                  y = c(0.45,0.11)
+  )
+
+save_plot(
   path = my_path("R","Figures"),
-         width = 9,
-         height = 5
+  "proportion_chg_agg.jpg",
+  p,
+  base_height = 8,
+  base_width = 8
 )
@@
 state_fit <- historic_spp %>% 
-  group_by(state,year,region) %>% 
+  group_by(state,year,region,spatial) %>% 
   summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
   left_join(total_fited,
-            by = c("year","region")) %>%
+            by = c("year","region","spatial")) %>%
   mutate(percentage = state_value/total_value*100) %>% 
-  group_by(state,region) %>% 
+  group_by(state,region,spatial) %>% 
   mutate(RMean = zoo::rollmean(x = percentage, 
@@
          ) %>%  
-  left_join(state_lat)
+  left_join(state_lat) %>% 
+  mutate(
+         spatial = ifelse(spatial == "fp","Fishing ports",
+                          ifelse(spatial == "sw","State Waters","Difference")
+         )
+  )
 
@@
   ) +
+  annotate(geom= "rect",
+           xmin = 1980, xmax = 2001, 
+           ymin = 0, ymax = 100,
+            fill = "gray90",
+           colour = NA,
+           alpha = 0.5) +
   ylab("Propotion (10 yrs running average)") +
@@
   scale_fill_manual(
-    "State",
+    "State\n(Latitudinal order)",
     values = state_pallet,
@@
   ) +
-  my_ggtheme_p(leg_pos = "right") +
-  theme(legend.key.width = unit(1,"line"))
-
-  ggsave(filename = "area_plot_avg_agg.jpg",
+  scale_x_continuous(breaks = seq(1979,2015,9),limits = c(1979,2015))+
+  xlab("Year") +
+  my_ggtheme_p(leg_pos = "right", hjust = 1,ax_tx_s = 10,leg_tx_s = 10, leg_tl_s = 12,ax_tl_s = 12) +
+  theme(legend.key.width = unit(1,"line"),
+        legend.title.align=0.5) +
+  facet_wrap(~spatial)
+
+    ggsave(filename = "area_plot_avg_agg_sptl.jpg",
          plot = agg_area,
@@
 
-![Proportion change aggregated all species map for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/area_plot_avg_agg.jpg)
+![Proportion change aggregated all species map for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/area_plot_avg_agg_sptl.jpg)
 
@@
 state_fit <- historic_spp %>% 
-  group_by(state,year,region,spp) %>% 
+  group_by(state,year,region,spp,spatial) %>% 
   summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
   left_join(total_fited,
-            by = c("year","region","spp")) %>%
+            by = c("year","region","spp","spatial")) %>%
   mutate(percentage = state_value/total_value*100) %>% 
-  group_by(state,region,spp) %>% 
+  group_by(state,region,spp,spatial) %>% 
   mutate(RMean = zoo::rollmean(x = percentage, 
@@
   ) +
-  my_ggtheme_p(leg_pos = "bottom") +
-  theme(legend.key.width = unit(1,"line")) + 
-  facet_wrap(~spp, ncol = 1, strip.position = "right")
-
-  ggsave(filename = "area_plot_avg_spp.jpg",
+  facet_grid(spp~spatial) +
+  scale_x_continuous(breaks = seq(1979,2015,9),limits = c(1979,2015))+
+  xlab("Year") +
+  my_ggtheme_p(leg_pos = "right", hjust = 0.9,ax_tx_s = 14,leg_tx_s = 16, leg_tl_s = 18,ax_tl_s = 18,facet_tx_s = 16) +
+  theme(legend.key.width = unit(1,"line"),
+        legend.title.align=0.5)
+
+  ggsave(filename = "area_plot_avg_spp_sptl.jpg",
          plot = ssp_area,
          path = my_path("R","Figures"),
-         width = 10,
-         height = 12
-  )
-
-```
-![Proportion change aggregated all species map for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/area_plot_avg_spp.jpg)
+         width = 12,
+         height = 10
+  )
+
+```
+![Proportion change aggregated all species map for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/area_plot_avg_spp_sptl.jpg)
 

### 2021-08-19 Scripts/spatial_analisis.Rmd
Fixed grid for matching extrapolation

@@
 
-# us_state_file <- my_path("G", extra_path = "Spatial/USFedAndStateW/FederalAndStateWaters.gdb")
-
-state_sf <-  st_read("~/OneDrive - UW-Madison/Spatial_Data/USFedAndStateW/FederalAndStateWaters.gdb") %>%
+state_sf <-  st_read("~/OneDrive - UW-Madison/FederalAndStateWaters/FederalAndStateWaters.gdb") %>%
   janitor::clean_names() %>% 
@@
 # Buffer state waters
-port_bf = st_buffer(port_sf, 5) %>% # port
+port_bf <- st_buffer(port_sf, 5) %>% # port
   st_transform(4326) %>% # to match shape
@@
   theme_dark()
+
+```
+
+##### 2.1 Create grid for interpolation
+
+```{r inter_grid, eval = T, echo = T}
+
+# Crop grid to EEz
+inter_grid_sf <- st_as_sf(ne_grid,
+             coords = c("lon", "lat"),
+             crs = 4326) %>% 
+  st_intersection(eez_sf)
+
+inter_grid_df <- as.data.frame(inter_grid_sf) %>% 
+  select(index) %>% 
+  left_join(ne_grid)
+
+write_csv(inter_grid_df, paste0(my_path("D", "Spatial"),"inter_grid_df.csv"))
+
+ggplot(inter_grid_sf) +
+  geom_sf()
 
@@
 Sys.time()
-grid_eez_sf_sw <- st_intersection(grid_sw_sf,eez_sf)
+grid_eez_sw_sf <- st_intersection(grid_sw_sf,eez_sf)
 Sys.time()
-# write_sf(grid_eez_sf, paste0(my_path("D", "Spatial"),"grid_eez_sf.shp"))
+
+write_sf(grid_eez_sw_sf, paste0(my_path("D", "Spatial/grid_eez_sw_sf"),"grid_eez_sw_sf.shp"))
 
@@
 
-# write_csv(grid_eez_df, paste0(my_path("R", "Partial"),"grid_eez_df.csv"))
+write_csv(grid_eez_sw_df, paste0(my_path("D", "Spatial/grid_eez_sw_sf","grid_eez_sw_df.csv")))
 
@@
 
-# write_sf(grid_eez_sf_fp, paste0(my_path("D", "Spatial/grid_eez_fp_sf"),"grid_eez_fp.shp"))
+write_sf(grid_eez_sf_fp, paste0(my_path("D", "Spatial/grid_eez_fp_sf"),"grid_eez_fp.shp"))
 
@@
 
-write_csv(grid_eez_fp_df, paste0(my_path("R", "Partial"),"grid_eez_fp_df.csv"))
+write_csv(grid_eez_fp_df, paste0(my_path("D", "Spatial/grid_eez_fp_sf"),"grid_eez_fp_df.csv"))
 
@@
       y = lat,
-      color = approach,
       fill = approach
-    )
+    ),
+    alpha = 0.5
   ) +
@@
 # Get state order from North to south
-state_order <- my_path("D","Spatial/grid_eez_fp_sf", name = "grid_eez_fp_df.csv",read = T) %>%
+state_order <- my_path("D","Spatial/grid_eez_sw_sf", name = "grid_eez_sw_df.csv",read = T) %>%
   group_by(state) %>% 
@@
 # Load grid of state waters
-grid_eez_sw_sf <- st_read(my_path("D","Spatial/grid_eez_sw_sf", name = "grid_eez_sf.shp")) %>% 
+grid_eez_sw_sf <- grid_eez_sw_sf %>% 
+  # st_read(my_path("D","Spatial/grid_eez_sw_sf", name = "grid_eez_sw_sf.shp")) %>%
   select(index,state,geometry) %>% 
@@
 # Load grid of fishing ports
-grid_eez_fp_sf <- st_read(my_path("D","Spatial/grid_eez_fp_sf", name = "grid_eez_fp.shp")) %>% 
-  select(index,state = jursdct,geometry) %>% 
+grid_eez_fp_sf <- grid_eez_sf_fp %>% 
+  # st_read(my_path("D","Spatial/grid_eez_fp_sf", name = "grid_eez_fp.shp")) %>% 
+  select(index,state,geometry) %>% 
   mutate(method = "fishing_port",
@@
 
-ggsave(filename = "buffer_figure.jpg",
+ggsave(filename = "buffer_figureb.jpg",
        plot = combined_plot,
@@
 In this step we [interpolate](https://swilke-geoscience.net/post/spatial_interpolation/) the survey data within the previously created grid following a Triangular Irregular Surface method.
-
-- We removed cases where `wtcpue < 0`
 
@@
 # For fishing ports
-grid_eez_fp_df <- my_path("D","Spatial/grid_eez_fp_sf","grid_eez_fp_df.csv", read = T)
-
-# For state waters
-# grid_eez_sw_df <- my_path("D","Spatial/grid_eez_fp_sf","grid_eez_fp_df.csv", read = T)
+inter_grid <- my_path("D","Spatial","grid_eez_fp_df.csv", read = T)
 
@@
 # Run them all in parallel
-lapply(spp,
+lapply(species,
        run_tis, 
@@
 
+### Previouslly created grids
+
+grids <- my_path("D", "Spatial/grid_eez_fp_sf", name = "grid_eez_fp_df.csv", read = T) %>% 
+  mutate(
+    spatial = "fp"
+  ) %>% 
+  bind_rows(
+    my_path("D", "Spatial/grid_eez_sw_sf", name = "grid_eez_sw_df.csv", read = T)
+  ) %>% 
+  mutate(
+    spatial = ifelse(is.na(spatial),"sw",spatial)
+  ) %>% 
+  spread(spatial,index)
+
 # Species data
-
-# Load interpolated data
-# "Centropristis striata"
-# 
-# historic_tif <- my_path("R","Partial/Interpolation","tif_Centropristis_striata.csv", read = T) %>% 
-#   mutate(state = str_to_sentence(state))
-
-# Multiple species
 
@@
 Species <- c(
-  # "Scomber scombrus",
-  # "Doryteuthis (Amerigo) pealeii", #longfin squid WE DONT HAVE IT
-  # "Peprilus triacanthus", # butterfish
-  # "Illex illecebrosus", #shortfin squid
   "Paralichthys dentatus", #summer flounder
@@
   "Centropristis striata"#, # black sea bass
-  # "Pomatomus saltatrix", # Bluefish
-  # "Lopholatilus chamaeleonticeps", #golden tilefish
-  # "Caulolatilus microps", #blueline tilefish
-  # "Clupea harengus" # Atlantic herring (Jointly in State and Federal Waters)
   )
@@
 
-taxon_fp <- my_path("R",extra_path = "Partial/Interpolation/fp", name = taxon_read)
-
 # Load all sp in one table
 historic_spp <- bind_rows(lapply(taxon_sw, fread)) %>% 
-  mutate(spatial = "sw") %>% 
-  bind_rows(
-    bind_rows(lapply(taxon_fp, fread))
-  ) %>% 
-  mutate(state = str_to_sentence(state),
-         spatial = ifelse(is.na(spatial),"fp",spatial))
+  mutate(state = str_to_sentence(state)) %>% 
+  # dplyr::select(-lon,-lat) %>% 
+  full_join(grids,
+            by = c("index","state")
+            )
+
+historic_spp %>% 
+  filter(is.na(spatial)) %>% 
+  filter(year == 1973,
+         region == "Northeast US Fall") %>% 
+  ggplot() +
+    geom_tile(
+      aes(
+        x = lon.x,
+        y = lat.x,
+        fill = index
+      )
+    ) +
+  facet_grid(spp~state) + 
+  geom_sf(data = land_sf,aes()) +
+  geom_sf(data = eez_sf, aes(), fill =NA)
 
@@
 unique(historic_spp$spatial)
+unique(historic_spp$region)
 
@@
   path = my_path("R","Figures"),
-  "proportion_chg_spp_spatial.jpg",
+  "proportion_chg_spp_spatialN.jpg",
   p,
@@
 
-state_fit <- historic_spp %>% 
+state_change <- historic_spp %>% 
   group_by(state,year,region,spatial) %>% 
@@
   mutate(percentage = state_value/total_value*100,
+         label = ifelse(year >= 1980 & year <= 2001,"reference",
+                         ifelse(year > 2001,"today",NA)
+                         )
+         ) %>% 
   # left_join(periods,
             # by = "year") %>% 
-  label = ifelse(year >= 1980 & year <= 2001,"Reference",
-                         ifelse(year > 2001,"Today",NA)
-                         )
-         ) %>% 
   group_by(state,label,region,spatial) %>% 
   summarise(mean_per = round(mean(percentage)),.groups = "drop") %>% 
-  filter(str_detect(region,"Spring"),
+  #Only show results for spring
+  filter(#str_detect(region,"Spring"),
          !is.na(label)
          ) %>% 
-  spread(spatial,mean_per) %>% 
-  mutate(difference = (fp-sw)/((fp+sw)/2)*100,
-         difference = ifelse(difference > 100,100,
-                             ifelse(difference < -100,-100,difference)
-         )
-  ) %>% 
-  gather("spatial","mean_per",fp:difference) %>% 
+  # select(-region) %>% 
+  # Estimate percentage change
+  spread(label,mean_per) %>% 
+  mutate(change = (today-reference)/(today)*100,
+         change = ifelse(change > 100,100,
+                         ifelse(change < -100,-100,change)
+         )
+  ) %>%
+  select(-reference,-today)
+
+  # Estimate spatial differences in percentage change
+season_diff <- state_change %>% 
+  spread(spatial,change) %>% 
+  mutate(difference_season = (fp-sw)/((fp+sw)/2)*100,
+         difference_season = ifelse(difference_season > 100,100,
+                                  ifelse(difference_season < -100,-100,difference_season)
+         )
+  ) %>% 
+  select(state, category = region, diff = difference_season)
+
+# Estimate regional differences in percentage change
+spatial_diff <- state_change %>% 
+  spread(region,change) %>%  
+  mutate(difference_spat = (`Northeast US Fall`-`Northeast US Spring`)/((`Northeast US Fall`+`Northeast US Spring`)/2)*100,
+         difference_spat = ifelse(difference_spat > 100,100,
+                                 ifelse(difference_spat < -100,-100,difference_spat)
+         )
+  ) %>% 
+  select(state,category = spatial,diff = difference_spat)
+
+differences <- season_diff %>% 
+  bind_rows(spatial_diff) %>% 
   mutate(
-         spatial = ifelse(spatial == "fp","Fishing ports",
-                          ifelse(spatial == "sw","State Waters","Difference")
-         )
-  )
-
-# Spatial map
-agg_sppatial_map <- land_sf %>% 
-  left_join(state_fit,
+    label = ifelse(category == "fp","Fishing ports",
+                          ifelse(category == "sw","State Waters",category)
+         )
+  )
+
+# The main plot
+prop_chng_map <- land_sf %>% 
+  left_join(state_change,
             by = "state") %>% 
-  filter(spatial != "Difference") %>% 
+  # filter(spatial != "Difference" & cat != "difference_reg") %>% 
   ggplot() +
-  geom_sf(aes(fill = mean_per)) +
-  viridis::scale_fill_viridis("Distribution\nProportion", alpha = 0.8) +
-  facet_grid(spatial~ label) +
+  geom_sf(aes(fill = change)) +
+  viridis::scale_fill_viridis("Change in proportion today\n relative to 1973-1984\n(%)", alpha = 0.8,
+                              limits = c(-100,100),
+                              breaks = seq(-100,100,25),
+                              labels = c(seq(-100,75,25),">100")
+                              ) +
+  facet_grid(spatial~ region) +
   labs(x = "", 
        y = "") +
-  my_ggtheme_p(facet_tx_s = 16,
-               leg_pos = "right",
-               leg_tl_s = 14,
-               ax_tx_s = 10,
-               ax_tl_s = 14) +
-theme(legend.title.align=0.5)
-
-# Difference map
-agg_diff_map <- land_sf %>% 
-  left_join(state_fit,
+  my_ggtheme_p(facet_tx_s = 20,
+               leg_pos = "bottom",
+               axx_tx_ang = 45,
+               ax_tx_s = 12,
+               ax_tl_s = 18,
+               hjust = 1) +
+  theme(legend.key.width = unit(4,"line"),
+        legend.title.align=0.5,
+        strip.text.y = element_blank(),
+        strip.background = element_blank(),
+        )
+
+ggsave(filename = "proportion_chng_agg.jpg",
+         plot = prop_chng_map,
+         path = my_path("R","Figures"),
+         width = 10,
+         height = 10
+  )
+
+#### Option with differences
+
+# Season differencce
+
+spat_diff <- land_sf %>% 
+  left_join(differences,
             by = "state") %>% 
-  filter(spatial == "Difference") %>% 
+  filter(!category %in% c("fp","sw")) %>% 
   ggplot() +
-  geom_sf(aes(fill = mean_per)) +
-  viridis::scale_fill_viridis("Percentage\nDifference",option = "C", alpha = 0.8) +
-  facet_grid(spatial~ label) +
+  geom_sf(aes(fill = diff)) +
+  viridis::scale_fill_viridis("Differences", 
+                              alpha = 0.8,
+                              option = "C",
+                              limits = c(-100,100),
+                              breaks = seq(-100,100,25),
+                              labels = c(seq(-100,75,25),">100")
+                              ) +
+  facet_wrap(~ label,
+             ncol = 2) +
   labs(x = "", 
        y = "") +
-  my_ggtheme_p(facet_tx_s = 16,
-               leg_pos = "right",
-               leg_tl_s = 14,
-               ax_tx_s = 10,
-               ax_tl_s = 14)+
-  theme(
+  my_ggtheme_p(facet_tx_s = 20,
+               leg_pos = "bottom",
+               axx_tx_ang = 45,
+               ax_tx_s = 12,
+               ax_tl_s = 18,
+               hjust = 1) +
+  theme(legend.key.width = unit(4,"line"),
+        legend.title.align=0.5,
         strip.background = element_blank(),
-        strip.text.x = element_blank(),
-        legend.title.align=0.5
-        )
-
-# Cowplot option
-p <- ggdraw() +
-  # Revenue circular
-  draw_plot(agg_sppatial_map, x = 0, y = 0.35, width = 1, height = 0.65) +
-  # Catch circular
-  draw_plot(agg_diff_map, x = 0.093, y = 0.05, width = 0.814, height = 0.4) +
-  draw_plot_label(label = c("Latitude", "Longitude"), 
-                  size = 10,
-                  angle = c(90,0),
-                  x = c(0,0.35), 
-                  y = c(0.45,0.11)
-  )
-
-save_plot(
+        strip.text.x = element_blank())
+
+ggsave(filename = "spat_diff.jpg",
+         plot = spat_diff,
          path = my_path("R","Figures"),
-  "proportion_chg_agg.jpg",
-  p,
-  base_height = 8,
-  base_width = 8
+         width = 8,
+         height = 6
+  )
+
+# seasonal
+seas_diff <- land_sf %>% 
+  left_join(differences,
+            by = "state") %>% 
+  filter(category %in% c("fp","sw")) %>% 
+  ggplot() +
+  geom_sf(aes(fill = diff)) +
+  viridis::scale_fill_viridis("Differences", 
+                              alpha = 0.8,
+                              option = "C",
+                              limits = c(-100,100),
+                              breaks = seq(-100,100,25),
+                              labels = c(seq(-100,75,25),">100")
+                              ) +
+  facet_wrap(~ label,
+             ncol = 1,
+             strip.position="right") +
+  labs(x = "", 
+       y = "") +
+  my_ggtheme_p(facet_tx_s = 20,
+               leg_pos = "",
+               axx_tx_ang = 45,
+               ax_tx_s = 12,
+               ax_tl_s = 18,
+               hjust = 1) +
+  theme(strip.background = element_blank(),
+        # strip.text.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.line.y = element_blank()
+        )
+
+ggsave(filename = "seas_diff.jpg",
+         plot = seas_diff,
+         path = my_path("R","Figures"),
+         width = 8,
+         height = 6
   )

### 2021-08-26 Scripts/spatial_analisis.Rmd
fixed figure 2 and estimated means

@@
                spp = taxa) %>% 
-        select(index, state, year, region, spp, lon=x, lat=y, value = z)
+        select(index, 
+               # state,
+               year, region, spp, lon=x, lat=y, value = z)
 
@@
 
-run_tis <- function(input_data, grid, years, taxa, reg, method){
+run_tis <- function(input_data, grid, years, taxa, reg){
 
@@
 
-  complement <- paste0("Partial/Interpolation/",method)
+  complement <- paste0("Partial/Interpolation/")
 
@@
 # For fishing ports
-inter_grid <- my_path("D","Spatial","grid_eez_fp_df.csv", read = T)
+inter_grid <- my_path("D","Spatial","inter_grid_df.csv", read = T)
 
@@
 # Run them all in parallel
-lapply(species,
+lapply(Species,
        run_tis, 
        input_data = ocean_data,
-       grid = grid_eez_fp_df,
+       grid = inter_grid,
        years = years,
-       reg = regions,
-       method = "fp"
+       reg = regions
 )
@@
 
-spp_paths <- list.files(my_path("R",extra_path = "Partial/Interpolation/sw"))
+spp_paths <- list.files(my_path("R",extra_path = "Partial/Interpolation/"))
 
@@
 
-taxon_sw <- my_path("R",extra_path = "Partial/Interpolation/sw", name = taxon_read)
+taxon_sw <- my_path("R",extra_path = "Partial/Interpolation/", name = taxon_read)
 
@@
 historic_spp <- bind_rows(lapply(taxon_sw, fread)) %>% 
-  mutate(state = str_to_sentence(state)) %>% 
-  # dplyr::select(-lon,-lat) %>% 
-  full_join(grids,
-            by = c("index","state")
-            )
-
-historic_spp %>% 
-  filter(is.na(spatial)) %>% 
-  filter(year == 1973,
-         region == "Northeast US Fall") %>% 
-  ggplot() +
-    geom_tile(
-      aes(
-        x = lon.x,
-        y = lat.x,
-        fill = index
-      )
-    ) +
-  facet_grid(spp~state) + 
-  geom_sf(data = land_sf,aes()) +
-  geom_sf(data = eez_sf, aes(), fill =NA)
+  left_join(grids,
+            by = c("index","lon","lat")
+            ) %>%
+  filter(!is.na(spatial))
+
+# historic_spp %>% 
+#   filter(is.na(spatial)) %>% 
+#   filter(year == 1973,
+#          region == "Northeast US Fall") %>% 
+#   ggplot() +
+#     geom_tile(
+#       aes(
+#         x = lon,
+#         y = lat,
+#         fill = index
+#       )
+#     ) +
+#   facet_grid(spp~state) + 
+#   geom_sf(data = land_sf,aes()) +
+#   geom_sf(data = eez_sf, aes(), fill =NA)
 
@@
   arrange(desc(order)) %>% 
-  mutate(order= letters[1:11])
+  mutate(lat = order,
+    order = letters[1:11])
 
@@
   path = my_path("R","Figures"),
-  "proportion_chg_diff.jpg",
+  "proportion_chg_diffN.jpg",
   p,
@@
   spread(label,mean_per) %>% 
-  mutate(change = (today-reference)/(today)*100,
-         change = ifelse(change > 100,100,
-                         ifelse(change < -100,-100,change)
+  mutate(raw_change = (today-reference)/(today)*100,
+         change = ifelse(raw_change > 100,100,
+                         ifelse(raw_change < -100,-100,raw_change)
          )
@@
 
+#### Average
+state_change %>% 
+  mutate(
+    wl = ifelse(change < 0, "L",
+                ifelse(change == 0, "NC","W"))
+  ) %>% 
+  # View()
+  # group_by(wl) %>% 
+  group_by(region,spatial,wl) %>% 
+  summarise(
+    states = paste(unique(state),collapse = ", "),
+    mean(raw_change),
+    sd(raw_change)
+  ) %>% 
+  write_csv("../Results/state_relative_chng.csv")
+  View()
+
   # Estimate spatial differences in percentage change
+spatial_diff <- state_change %>% 
+  spread(spatial,change) %>% 
+  mutate(spatial_diff = abs(fp-sw)) %>% 
+  select(state, category = region, diff = spatial_diff)
+
+# Estimate seasonal differences in percentage change
 season_diff <- state_change %>% 
-  spread(spatial,change) %>% 
-  mutate(difference_season = (fp-sw)/((fp+sw)/2)*100,
-         difference_season = ifelse(difference_season > 100,100,
-                                  ifelse(difference_season < -100,-100,difference_season)
-         )
-  ) %>% 
-  select(state, category = region, diff = difference_season)
-
-# Estimate regional differences in percentage change
-spatial_diff <- state_change %>% 
   spread(region,change) %>%  
-  mutate(difference_spat = (`Northeast US Fall`-`Northeast US Spring`)/((`Northeast US Fall`+`Northeast US Spring`)/2)*100,
-         difference_spat = ifelse(difference_spat > 100,100,
-                                 ifelse(difference_spat < -100,-100,difference_spat)
-         )
-  ) %>% 
-  select(state,category = spatial,diff = difference_spat)
+  mutate(season_diff = abs(`Northeast US Fall`-`Northeast US Spring`)) %>% 
+  select(state,category = spatial,diff = season_diff)
 
@@
   )
+
+# For in text differences
+differences %>% 
+  group_by(category) %>%
+  summarise_at(vars(diff),
+    c(mean = mean,
+      sd =sd,
+      min = min,
+      max= max))
 
@@
 
-ggsave(filename = "proportion_chng_agg.jpg",
+ggsave(filename = "proportion_chng_agg.png",
          plot = prop_chng_map,
@@
                               option = "C",
-                              limits = c(-100,100),
-                              breaks = seq(-100,100,25),
-                              labels = c(seq(-100,75,25),">100")
+                              limits = c(0,50),
+                              breaks = seq(0,50,10)
                               ) +
@@
 
-ggsave(filename = "spat_diff.jpg",
+ggsave(filename = "spat_diff.png",
          plot = spat_diff,
@@
 
-ggsave(filename = "seas_diff.jpg",
+ggsave(filename = "seas_diff.png",
          plot = seas_diff,

### 2021-08-26 Scripts/manuscript_acrossboundaries.Rmd
First draft for olaf

--- 2021-07-14 Scripts/manuscript_acrossboundaries.Rmd
@@
 title: "Challenges on quantifying fish range shifts across management boundaries"
-subtitle: "*target journal* PlosOne"
-output: word_document
+subtitle: "DRAFT. Target journal *PlosOne*"
+output: 
+  bookdown::word_document2:
+    number_section: no
+    toc: no
 ---
@@
 
+```{r setup, include=FALSE}
+
+library(MyFunctions)
+MyFunctions::my_lib(c("dplyr","tibble","knitr","kableExtra","png","grid"))
+
+```
+
 # Introduction
 
-Fish range shifts have been occurring rapidly.
+Range shifts are among the most documented responses of marine fauna to the effects of climate change in the ocean [@Poloczanska].
+From zooplankton to bony fish to seabirds, marine fauna have been documented to expand their distribution up to 800 km per decade or to contract it for about 200 km per decade [@Poloczanska].
+Such change is often due to marine species following a poleward temperature gradient in the search for colder waters, although, in some cases such species are following local environmental factors such as upwelling systems [@Clarke:2020], or moving to deeper colder waters [@Pinsky:2013].
+Regardless of the shift direction, species distributions are projected to continue to happen in the incoming years [@Cheung:2010; @Barange2014; @IPCC2019], even if society engages in a strong mitigation climate change scenario (i.e., limiting increased global temperature to $1.5^o$) as proposed by the Paris Agreement [@Cheung:2016].
 
-When harvested species shift across management boundaries, there can be a growing disconnect between the management jurisdictions in which fish are found and the management jurisdictions which hold harvest rights.
+The change in species distribution will be particularly challenging for the management of stocks shared across management jurisdictions [@PalaciosAbrantes:2020sr].
+When a stock is subjected to two or more spatial regulatory regions, managers must often coordinate efforts to maintain sustainability of the stock [@Clark1979; @Munro2004].
+However, there can be a growing disconnect between the region of the ocean where fish are found and the management jurisdictions which hold harvest rights [@PalaciosAbrantes:2020sr].
+Such mismatch is of specific concern as species shift their known distribution due to climate change [@PalaciosAbrantes_2020pn; @oremus_2020, @pinsky_2018; @Baudron2020; @Miller2013].
+Historical shifts in important fish stocks have resulted in both unsustainable harvest and international conflict as in the case of the United States and Canada over sockeye salmon (*Oncorhynchus nerka*) and the European Union and Ireland over mackerel (*Scomber scombrus*) [@miller2013; @spijkers2017].
 
-While the problem is increasingly well known, quantifying it is difficult for two reasons: (1) management jurisdiction in the ocean is often ill-defined, especially at the subnational level or beyond exclusive economic zones, and (2) quantifying fish distributions in relation to these boundaries is difficult, even where fishery-independent surveys exist, because of seasonal and interannual variation.
+In the United States (US) North East (NE) Atlantic, many important fished species such as american lobster (*Homarus americanus*), yellowtail flounder (*Limanda ferruginea*), summer flounder (*Paralichthys dentatus*) and red hake (*Urophycis chuss*) have been shifting their distribution poleward  [@pinsky_fogarty_2012], and modelling exercises suggest that NE Atlantic species will shift will average over 600 km towards the end of the $21^{st}$ century under a high emission climate change scenario [@Morley:2018].
+The mismatch between implemented management strategies and shifts in stocks across management jurisdictions compromises management and sustainability [@Baudron2020; @pinsky_fogarty_2012].
+Fishers in the NE Atlantic have been adapting to such shifts by following the fish, in some cases, or changing target speices, in others [@polo_2021].
+While this problem of shifting stocks across management jurisdictions is increasingly well known, quantifying it is difficult for two main reasons: (*i*) management jurisdiction in the ocean are often ill-defined, especially at the sub-national level or beyond Exclusive Economic Zones (EEZ), and (*ii*) quantifying fish distributions in relation to these boundaries is difficult, even where fishery-independent surveys exist, because of seasonal and interannual variation.
 
-Here we examine both of these challenges using fish distributions relative to states in the Northeast U.S. as an example.
+Here, we examine both of these challenges by quantifying the historical distributions of three important fished species relative to 11 states of the Northeast Atlantic U.S that jointly manage these stocks.
+Specifically, we set two main objectives.
+First, we examine the difference between two different approaches to define spatial management jurisdictions within the U.S.
+Federal waters.
+Second, we examine differences in the species' historical distribution between Spring and Fall to examine seasonal variation in these stock's distributions.
+We use bottom trawl surveys for Spring and Fall from 1971 to 2019 and apply a triangular irregular surface method to extrapolate fish biomass across the U.S.
+North East EEZ.
+We then draw spatial polygons for each State up to the EEZ from two different starting points; the state waters and main fishing ports.
+Our results suggest that...
+
+# Methods
+
+The current analysis focused on black sea bass (*Centropristis striata*), summer flounder (*Paralichthys dentatus*) and scup (*Stenotomus chrysops*), all species managed under the Mid-Atlantic Council Management Plans [(MAFMC)](https://www.fisheries.noaa.gov/new-england-mid-atlantic/commercial-fishing/new-england-mid-atlantic-fishery-management-plans) since 1996.
+The management unit extends from the U.S.-Canadian border to the southern border of North Carolina for summer flounder, and Cape Hatteras (North Carolina) for scup and black sea bass [MAFMC](https://www.mafmc.org/sf-s-bsb/).
+The fisheries are managed cooperatively by the States through the Commission in state waters (0-3 miles), and through the MAFMC and NOAA Fisheries in federal waters (3-200 miles).
+An annual coast wide commercial quota is implemented and since 2003 further allocated to the States of Maine, New Hampshire, Massachusetts, Rhode Island, Connecticut, New York, New Jersey, Delaware, Maryland, Virginia and North Carolina [@REFMACMP-memorandum] (Table \@ref(tab:QuotaTable)).
+The State-wide quota allocation is based on the historical landings from 1980-2001, approximately.
+
+```{r QuotaTable, eval = F, echo = F}
+
+tibble(
+  "State" = c(
+    "Maine (ME)",
+    "New Hampshire (NH)",
+    "Massachusetts (MA)",
+    "Rhode Island (RI)",
+    "Connecticut (CT)",
+    "New York (NY)",
+    "New Jersey (NJ)",
+    "Delaware (DE)",
+    "Maryland (MD)",
+    "Virginia (VA)",
+    "North Carolina (NC)"
+  ),
+    "Centropristis striata" = c(
+      0.0040, #ME
+      0.0040, #NH
+      0.1564, #MA
+      0.1323, #RI
+      0.0367, #CT
+      0.0857, #NY
+      0.2010, #NJ
+      0.0411, #DE
+      0.0888, #MD
+      0.1614, #VA
+      0.0888 #NC
+    ),
+    "Paralichthys dentatus" = c(
+      0.0004756, #ME 
+      0.0000046, #NH 
+      0.0682046, #MA 
+      0.1568298, #RI 
+      0.0225708, #CT 
+      0.0764699, #NY 
+      0.1672499, #NJ 
+      0.0001779, #DE 
+      0.0203910, #MD
+      0.2131676, #VA
+      0.2744584 #NC
+    ),
+    "Stenotomus chrysops" = c(
+      0.0012101, #ME
+      0.0000000, #HN
+      0.2158729, #MA
+      0.5619456, #RI
+      0.0315399, #CT
+      0.1582466, #NY
+      0.0291667, #NJ
+      0.0000000, #DE
+      0.0001190, #MD
+      0.0016502, #VA
+      0.0002490 #NC
+    )
+) %>% 
+  mutate_if(is.numeric,round,3) %>% 
+  mutate_if(is.numeric,~.*100) %>% 
+  # readr::write_csv("quota_table.csv")
+  # group_by() %>% #just checking they add up
+  # summarise_if(is.numeric,sum)
+  kable("latex",
+        caption = "State wide commercial quota allocation for black sea bass (*Centropristis striata*), summer flounder (*Paralichthys dentatus*) and scup (*Stenotomus chrysops*) according to the 2003 implementation.
+Values shown as percentage of total quota.
+States ordered latitudinally"
+        )
+```
+
+Biomass data for all three species was gathered from NOAA's yearly Northeast Fisheries Science Center Spring and Fall Bottom Trawl Surveys [data](https://www.fisheries.noaa.gov/region/new-england-mid-atlantic#science) provided by [Ocean adapt](https://oceanadapt.rutgers.edu/) and standardized as catch per unit of effort (CPUE) [@Pinsky2013].
+The analysis was retrospective in nature, covering the time period from 1971 to 2019 with two comparative periods; the average of 1980 to 2000 representing the state allocations of the commercial fisheries originally implemented in 2003 [@RefDocument], and the average of 2009 to 2019 representing a more recent time period.
+
+We extrapolated fish CPUE observational data to the NE Atlantic EEZ from the southern border of North Carolina to the US-Canadian border by following a triangular irregular surface (TIS) method using the *R* package *interp* [@REFInterp].
+Overall, the TIS method creates multiple non-overlapping triangles that cover the entire extrapolated region (i.e., the EEZ) from an initial set of sample points (i.e., NOAAs survey) generating a spatially-continuous surface [@REF; @REF].
+
+Federal U.S.
+waters are not sub-dived into state-owned fisheries management regions.
+Thus, we created state-polygons to allocate the extrapolated CPUE to each fishing State.
+This step allowed us to further determine what proportion of the species distribution was in each state-polygon.
+The state-polygons were created by first expanding multiple polygons within the 200 nautical miles of the EEZ using the *st* package in *R* [@REF].
+Second, we gridded the EEZ into 3 x 3 gridcells and overlay the grid with the state-polygons to then estimate the number of grids that each expanded polygon occupied.
+Note that a gridcell would be allocated to multiple States in cases where state-polygons overlay.
+Finally, the buffers were limited to the size and shape of the North East US EEZ.
+
+Creating these state-polygons was key to allocate the distribution of any stock directly influencing the proportion of the stock linked to a state.
+For example, the amount of the distribution that each State has will be influenced by the size of the state-polygon.
+Here, we used two different sources as starting points for the state-polygons expansion; state waters and US ports (Figure \@ref(fig:bufferFig)).
+For the state waters approach we used the [NOAA-data.gov](https://catalog.data.gov/dataset/federal-and-state-waters) shapefile.
+Note that in this case, the extent of the final state-polygons was related to the size of the State's coast with North Carolina and Maine having the largest polygons.
+For the ports approach we used the [Global Fishing Watch](https://globalfishingwatch.org/datasets-and-code-anchorages/)'s database on Anchorages, Ports and Voyages.
+We only considered ports classified within the World Port Index ([WPI](https://msi.nga.mil/NGAPortal/MSI.portal?_nfpb=true&_pageLabel=msi_portal_page_62&pubCode=0015)).
+In this case, the number of ports varied among States with New Jersey and Massachusetts having the largest amounts (117 and 187, respectively) and Delaware and New Hampshire having the leaser (2 and 14, respectively).
+However, rather than the number of ports per State, in this case what influences the size of the state-polygon was the distribution of ports within the State's waters as two ports in opposite latitudes will result in a larger polygon than two ports closed together (Figure \@ref(fig:bufferFig)).
+
+```{r bufferFig, eval = F, echo = T, fig.width = 3, fig.height = 2, echo=FALSE, fig.cap="Spatial regions within the United States' North East Exclusive Economic Zone.
+A) Spatial buffers from each State's waters.
+B) Spatial buffers from the main fishing ports.
+States are aligned by average latitude from north to south.
+ME, Maine; NH, New Hampshire; MA, Massachusetts; RI, Rhode Island; CT, Connecticut; NY, New York; NY, New Jersey; DE, Delaware; MD, Maryland; VA Virginia; North Carolina."}
+
+# Call the image
+img <- readPNG("/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F1_buffer_figure.png")
+# Print the image
+grid.raster(img)
+```
+
+![Figure 1.
+Spatial regions within the United States' North East Exclusive Economic Zone.
+A) Spatial buffers from each State's waters.
+B) Spatial buffers from the main fishing ports.
+States are aligned by average latitude from north to south.
+ME, Maine; NH, New Hampshire; MA, Massachusetts; RI, Rhode Island; CT, Connecticut; NY, New York; NY, New Jersey; DE, Delaware; MD, Maryland; VA Virginia; North Carolina.
+](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F1_buffer_figure.png)
+
+For each approach we then overlay each specie's interpolation with the state-polygons and estimated the distribution and biomass proportion of each state.
+The interpolated biomass was divided equally in cases where two or more States had the same grid.
+For example, if New York and New Jersey both shared one grid, then the proportion of that grid would be allocated 50% to each state, alternatively, if Connecticut was also sharing the grid, then the proportion would be 33.3% to each state.
+Note that this step does not affect the interpolation method but the way the biomass is allocated by State.
+
+All of the analysis was done on RStudio statistical software and *R* version 4.1.0 (*Camp Pontanezen*) and associated packages *ggmap*, *sf* [@REF], *st* [@REF], *tidyverse* [@REF], *tools* [@REF], *readr* [@REF], *data.table* [@REF], *maps* [@REF], *viridis* [@REF], *wesanderson* [@REF], *knitr* [@REF], *kableExtra* [@REF], *plotly* [@REF], *ggrepel* [@REF], *ggsflabel* [@REF], *janitor* [@REF], *interp* [@REF], *rnaturalearth* [@REF], and *readxl* [@REF].
+All code can be found in https://github.com/jepa/AcrossBoundaries.
 
 # Results
--	Two boundaries methods
--	Two surveys
+
+Our results suggest that the current distribution of all three species has changed relative to 1980-2001 from North Carolina to Maine.
+Biomass has increased in average 30% $\pm$ 11% in Connecticut, Maine, Massachusetts, New hampshire, Rhode island relative to the historical proportion regardless of the season and the spatial approach.
+On the other hand, Delaware, Maryland, New jersey, New york, North carolina, and Virginia have seen an average biomass loss of 39% $\pm$ 29% relative to the historical proportion for all approaches and seasons (Supplement Table 1).
+Specific cases of no change exist for Connecticut and New Jersey in the fishing ports approach for Spring and Fall, respectiveley, and New York in all but the Spring-fishig ports approach.
+
+Differences in the intensity of change varies among spatial and seasonal estimations (Figure \@ref{fig:figaggpropcnhg}).
+Aggregated biomass seems to have changed more drastically in Spring following the State waters approach with a max reduction of over -100% for North Carolina (a 40% difference between seasons) and increase of 50% for Maine (a 17% difference between seasons).
+On the other hand, Fall proportion max reduction was -66% for Maryland (a 44% difference between seasons) and max increase was 33% for Maine regardless of the approach (Figure \@ref{fig:figaggpropcnhg}A).
+Differences between approaches (i.e., State Waters v.s.
+Fishing Ports and Spring v.s.
+Fall) were larger for the State water approach (mean 14% $\pm$ 15%; max  44%) and smallest in Spring (mean 9% $\pm$ 7%; max 23%).
+It is worth noticing that all approaches had cases with no difference between options (Figure \@ref{fig:figaggpropcnhg}BC).
+
+```{r figaggpropcnhg, eval = F, echo = T, fig.width = 3, fig.height = 2, echo=FALSE, fig.cap= "Change in the proportion of the distribution today (2014-2019) relative to 1973-1985.
+A) row-wise showing seasonal changes, column-wise showing changes by spatial approach.
+B) Differnces between seasons for each spatial approach.
+C) Differences between spatial approaches for each season."}
+
+# Call the image
+img <- readPNG("/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F2_proportion_chng_agg")
+# Print the image
+grid.raster(img)
+```
+
+![Figure 2.
+Change in the proportion of the distribution today (2014-2019) relative to 1973-1985.
+A) row-wise showing seasonal changes, column-wise showing changes by spatial approach.
+B) Differnces between seasons for each spatial approach.
+C) Differences between spatial approaches for each season.](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F2_proportion_chng_agg)
+
+The historical proportion of State-shared aggregated biomass is sensitive to the spatial approach.
+When looking at the fishing ports apprach we can see that the main shifts in proportion are between northern and southern States (Figure \@ref{fig:figAggHist}- Fishing ports).
+While southern States like Virginia and North Carolina have lost substantial proportion of the shared biomass over time, northern states like Maine, New Hampshire and Massachusetts have stand to win.
+Changes in the biomass proportion of the in-between states are very subtle.
+Yet the State waters approach offers another picture.
+Here, there seems to be clear biomass proportion winners and losers over the last 40 years (Figure \@ref{fig:figAggHist}-State Waters).
+New Jersey, Delaware, Maryland, Virginia and North Carolina have all seen a constant decrease in the proportion of the shared biomass while States from New York to Maine have seen a year-by-year increase (Figure \@ref{fig:figAggHist}).
+
+```{r figAggHist, eval = F, echo = T, fig.width = 3, fig.height = 2, echo=FALSE, fig.cap = "Historical proportion of aggregated biomass per state and spatial approach.
+States organized latitudinally.
+Grey-white box showing the quota-based historical period"}
+
+# Call the image
+img <- readPNG("/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F3_area_plot_avg_agg_sptl.png")
+# Print the image
+grid.raster(img)
+```
+
+![Figure 3.
+Aggregated distribution proportion per state of Paralichthys dentatus, Stenotomus chrysops and Centropristis striata over time.
+Each color represent a State ordered latitudinal.
+Grey box represents the base-period used for the fisheries quota allocation ](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F3_area_plot_avg_agg_sptl.png)
+
+Changes will be different when looked at the species level (Figure \@ref{fig:figSppHist}).
+All three species show a reduction in biomass proportion for southern states (namely Virginia and North Carolina) with black sea bass and scup having the larger declines.
+Biomass increases are less clear.
+For black sea bass, biomass has increased from Maine all the way down to Rhode Island in the Fishing ports approach, and New York for the State waters approach.
+In the State waters approach the species has just recently "arrived" to Maine and New Hampshire waters (Figure \@ref{fig:figSppHist}- State waters).
+For scup, only Maine and New Hampshire seem to have gain biomass following the Fishing ports approach while the State waters approach resulted in gains for all States northern than New York.
+Similar to black sea bass, Virginia and North Carolina are the main biomass losers in both approaches.
+Finally, there does not appear to be clear evidence of shifts in biomass for summer flounder.
+Decreases are seen for Virginia and North Carolina for both approaches and increases for Maine and New Hampshire for the fishing ports approach, yet, these are almost imperceptible (Figure \@ref{fig:figSppHist}).
+
+```{r figSppHist, eval = F, echo = T, fig.width = 3, fig.height = 2, echo=FALSE, fig.cap = "Historical proportion of each species' biomass per state and spatial approach.
+States organized latitudinally.
+Grey-white box showing the quota-based historical period"}
+
+# Call the image
+img <- readPNG("/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F4_area_plot_avg_spp_sptl.png")
+# Print the image
+grid.raster(img)
+```
+
+![Figure 4.
+Proportion of the distribution of Paralichthys dentatus, Stenotomus chrysops and Centropristis striata over time.
+Each color represent a State ordered latitudinal.
+Grey box represents the base-period used for the fisheries quota allocation ](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F4_area_plot_avg_spp_sptl.png)
+
+# Discussion

### 2021-08-26 Scripts/manuscript_acrossboundaries.Rmd
included authors

@@
 subtitle: "DRAFT. Target journal *PlosOne*"
+author: "Palacios-Abrantes Juliano, Crosson Scott, Dumas Chris, Fujita Rod, Jensen Olaf, Levine Arielle, Longo Catherine"
 output: 
@@
 Range shifts are among the most documented responses of marine fauna to the effects of climate change in the ocean [@Poloczanska].
-From zooplankton to bony fish to seabirds, marine fauna have been documented to expand their distribution up to 800 km per decade or to contract it for about 200 km per decade [@Poloczanska].
+From zooplankton to bony fish to seabirds, marine fauna has been documented to expand their distribution up to 800 km per decade or to contract it for about 200 km per decade [@Poloczanska].
 Such change is often due to marine species following a poleward temperature gradient in the search for colder waters, although, in some cases such species are following local environmental factors such as upwelling systems [@Clarke:2020], or moving to deeper colder waters [@Pinsky:2013].
@@
 Fishers in the NE Atlantic have been adapting to such shifts by following the fish, in some cases, or changing target speices, in others [@polo_2021].
-While this problem of shifting stocks across management jurisdictions is increasingly well known, quantifying it is difficult for two main reasons: (*i*) management jurisdiction in the ocean are often ill-defined, especially at the sub-national level or beyond Exclusive Economic Zones (EEZ), and (*ii*) quantifying fish distributions in relation to these boundaries is difficult, even where fishery-independent surveys exist, because of seasonal and interannual variation.
+While this problem of shifting stocks across management jurisdictions is increasingly well known, quantifying it is difficult for two main reasons: (*i*) management jurisdictions in the ocean are often ill-defined, especially at the sub-national level or beyond Exclusive Economic Zones (EEZ), and (*ii*) quantifying fish distributions in relation to these boundaries is difficult, even where fishery-independent surveys exist, because of seasonal and interannual variation.
 
@@
 We use bottom trawl surveys for Spring and Fall from 1971 to 2019 and apply a triangular irregular surface method to extrapolate fish biomass across the U.S.
-North East EEZ.
+Northeast EEZ.
 We then draw spatial polygons for each State up to the EEZ from two different starting points; the state waters and main fishing ports.
@@
 Biomass data for all three species was gathered from NOAA's yearly Northeast Fisheries Science Center Spring and Fall Bottom Trawl Surveys [data](https://www.fisheries.noaa.gov/region/new-england-mid-atlantic#science) provided by [Ocean adapt](https://oceanadapt.rutgers.edu/) and standardized as catch per unit of effort (CPUE) [@Pinsky2013].
-The analysis was retrospective in nature, covering the time period from 1971 to 2019 with two comparative periods; the average of 1980 to 2000 representing the state allocations of the commercial fisheries originally implemented in 2003 [@RefDocument], and the average of 2009 to 2019 representing a more recent time period.
+
+with two comparative periods; the average of 1980 to 2000 representing the state allocations of the commercial fisheries originally implemented in 2003 [@RefDocument], and the average of 2009 to 2019 representing a more recent time period.
 
@@
 Overall, the TIS method creates multiple non-overlapping triangles that cover the entire extrapolated region (i.e., the EEZ) from an initial set of sample points (i.e., NOAAs survey) generating a spatially-continuous surface [@REF; @REF].
+The extrapolation was done separately  for both Fall and Spring seasons covering the time period of 1971 to 2019.
 
@@
 The state-polygons were created by first expanding multiple polygons within the 200 nautical miles of the EEZ using the *st* package in *R* [@REF].
-Second, we gridded the EEZ into 3 x 3 gridcells and overlay the grid with the state-polygons to then estimate the number of grids that each expanded polygon occupied.
-Note that a gridcell would be allocated to multiple States in cases where state-polygons overlay.
-Finally, the buffers were limited to the size and shape of the North East US EEZ.
-
 Creating these state-polygons was key to allocate the distribution of any stock directly influencing the proportion of the stock linked to a state.
@@
 
+We then gridded the EEZ into 3 x 3 grid-cells and overlay it with the state-polygons to identify the grids that each state-polygon occupied.
+Note that a grid-cell would be allocated to multiple States in cases where state-polygons overlay.
 For each approach we then overlay each specie's interpolation with the state-polygons and estimated the distribution and biomass proportion of each state.
@@
 Note that this step does not affect the interpolation method but the way the biomass is allocated by State.
+
+Finally, we estimated the biomass percentage change today relative to the historic period.
+For that matter we define the historic period as 1980 to 2000 representing the state allocations of the commercial fisheries originally implemented in 2003 [@RefDocument], and “today” as the average of 2009 to 2019 representing a more recent data available.
+The parentage changes between the historic and present biomass ($\Delta{B}$) was estimate for each of the four approaches as;
+
+$$ \Delta B=\frac{(B_t-B_h)}{|B_h|}*100$$
+
+Where $B_t$ is the biomass today (average of 2009 to 2019) and $B_h$ is the biomass at the historical period (average of 1980 to 2000).
+In addition, we estimated the differences in ($\Delta{B}$) between the seasonal ($\Delta{B}_{seas}$) and the spatial ($\Delta{B}_{spat}$) approach by subtracting from each other:
+
+$$ \Delta B_{seas} = |\Delta B_{fp}-\Delta B_{sw}| $$
+$$ \Delta B_{spat} = |\Delta B_{f}-\Delta B_{s}| $$
+
+Where $\Delta{B}_{fp}$, $\Delta{B}_{sw}$, $\Delta{B}_{f}$, and $\Delta{B}_{s}$ represent the biomass parentage change today relative to historical value for fishing ports, state waters, Fall and Summer approaches, respectively.
 
@@
 # Call the image
-img <- readPNG("/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F2_proportion_chng_agg")
+img <- readPNG("/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F2_proportion_chng_agg.png")
 # Print the image
@@
 B) Differnces between seasons for each spatial approach.
-C) Differences between spatial approaches for each season.](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F2_proportion_chng_agg)
+C) Differences between spatial approaches for each season.](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F2_proportion_chng_agg.png)
 
@@
 
-Changes will be different when looked at the species level (Figure \@ref{fig:figSppHist}).
-All three species show a reduction in biomass proportion for southern states (namely Virginia and North Carolina) with black sea bass and scup having the larger declines.
+All three species show a reduction in biomass proportion for southern states (namely Virginia and North Carolina) with black sea bass and scup having the larger declines (Figure \@ref{fig:figSppHist}).
 Biomass increases are less clear.

### 2021-09-24 Scripts/spatial_analisis.Rmd
Re-analyzing using Sarah's data

@@
 
-We used [Global Fishing Watch](https://globalfishingwatch.org/datasets-and-code-anchorages/)'s database on 
-Anchorages, Ports and Voyages.
-
-*The Global Fishing Watch anchorages dataset is a global database of anchorage locations where vessels congregate.
-The dataset contains over 160,000 individual anchorage locations, which are further grouped into nearly 32,000 ports when applicable.*
-
-```{r ports_sf, eval = T, echo = T}
-
-# Get Global Fishig Watch data
-gfw_data <- my_path("D","Spatial",name = "gfw_portdata.csv", read = T) %>% 
-  filter(iso3 == "USA")
-
-# Visualize data (o.k!)
-# ggplot(gfw_data) +
-#   geom_point(
-#     aes(
-#     x = lon,
-#     y = lat
-#   )
-#   )
-
-# Convert data to sf for mergig
-gfw_sf <- st_as_sf(gfw_data,
-             coords = c("lon", "lat"),
-             crs = 4326)
-
-# Merge data with state waters to,locate ports 
-port_sf <- st_join(gfw_sf,state_sf) %>% 
-  filter(!is.na(jurisdicti)) # remove points outside stat waters
-
-ggplot(port_sf)  +
-  geom_sf(aes(color = distance_from_shore_m)) +
-  theme_dark()
-
-```
-So...Looks like some ports are "far from shore" which I don't really know what it means. For now, I am only selecting those ports that ar 0 meter from shore.
-
-```{r ports_inshore, eval = T, echo = F}
-
-# Get number of ports per state
-ports_n_data <- port_sf %>% 
-  as.data.frame() %>% 
-    filter(distance_from_shore_m == 0) %>% 
-    group_by(state) %>% 
-    summarise(n_ports = n())
-
-# plot it
-gridExtra::grid.arrange(
-  port_sf %>% 
-    filter(distance_from_shore_m == 0) %>% 
-    ggplot()  +
-    geom_sf(aes(color = jurisdicti)) +
-    scale_color_manual(values = state_pallet) +
-    theme_dark() +
-    theme(legend.position = ""),
-  tableGrob(ports_n_data),
-  ncol = 2
-)
-
-```
-
-There are still too many ports in each state (?). Specially New Jersey! One approach is to use NOAA's landing-per-port data to filter out...
-
 ###### 4.1 NOAA's data
@@
               ~ str_to_lower(.)) %>%
-  mutate(landing_port = str_remove(landing_port,"[:blank:]\\(state\\)"))
+    filter(species_name %in% c("summer flounder","black sea bass","scup"))
 
@@
 
-This approach removes a lot of ports to the point that Delaware is completely port-less
-
-###### 4.2 World Port Index
-
-In this approach we only use the ports categorized within the [WPI](https://msi.nga.mil/NGAPortal/MSI.portal?_nfpb=true&_pageLabel=msi_portal_page_62&pubCode=0015) and with `distance_from_shore_m == 0`  and `at_dock == TRUE`.
-
-- `at_dock` == Anchorages within a 450 meter buffer around a combined land shape file are considered at dock.
-
-```{r wpi_approach, eval = T, echo = F}
-
-gridExtra::grid.arrange(
-  port_sf %>% 
-    filter(distance_from_shore_m == 0,
-           label_source %in% c("WPI_ports"),
-           at_dock == TRUE) %>% 
-    ggplot()  +
-    geom_sf(aes(color = jurisdicti)) +
-    scale_color_manual(values = state_pallet) +
-    theme_dark(),
-  port_sf %>% 
-    as.data.frame() %>% 
-    filter(distance_from_shore_m == 0,
-           label_source %in% c("WPI_ports"),
-           at_dock == TRUE) %>% 
-    group_by(state) %>% 
-    summarise(n_ports = n()) %>% 
-    tableGrob(),
-  ncol = 2
-)
-
-```
-
-This approach might be better suited. It also has teh advantage that we are using the WPI.
-
-This is how all the shapefiles look like together
+######4.2 Data from NOAA fisheries 
+https://www.fisheries.noaa.gov/foss/f?p=215:11:15514950376034::NO:::
+
+Delaware data was colected from NOAA's [Snapshots of Human Communities and Fisheries in the Northeast
+](https://apps-nefsc.fisheries.noaa.gov/read/socialsci/communitySnapshots.php)
+
+NOTES:
+
+- There is no Maine, Delaware, nor New Hamshire in the data. Took them from NOAA as main ports of all fisheries
+
+```{r sarahs_word_data}
+
+noaa_ports <- data.table(
+  port =str_to_sentence(c(
+    "POINT JUDITH, RI", #41.359907914553574,-71.48323250872187,
+    "BEAUFORT, NC", #34.7138879654054,-76.66239630117921,
+    "HAMPTON, VA", #36.98600366773327, -76.35038306859545,
+    "PT. PLEASANT, NJ", #40.08351847675102,-73.99190094110679,
+    "NEWPORT NEWS, VA", #37.00933919295183, -76.48565862613168,
+    "BELFORD, NJ", # 40.43918784734024, -74.0763054899462
+    "MONTAUK, NY", #41.07342262868038, -71.93585836088813
+    "HOBUCKEN, NC", #34.94844567982384, -76.74333419560425
+    "WANCHESE, NC", #35.83524984550334, -75.61121671722921
+    "NEW BEDFORD, MA", # 41.630494052326306, -70.91580669134055
+    "CAPE MAY, NJ", # 38.94979719126508, -74.90280944790463
+    "ORIENTAL, NC", # 35.013571084373126, -76.66793114333704
+    "CHINCOTEAGUE, VA", # 37.91788094070204, -75.35947580478219
+    "ENGELHARD, NC", # 35.262929243118776, -76.08680452670508
+    "STONINGTON, CT", # 41.327282204484035, -71.9223721359251
+    "LONG BEACH/BARNEGAT LIGHT, NJ", #39.752855929900484, -74.11329310115902
+    "OCEAN CITY, MD", #38.3802922004859, -75.05089736920318
+    "Indian river, DE",
+    "Portland, ME", #43.66344794728992, -70.22937554378885
+    "Portsmouth, NH" #43.05334694203953, -70.7126760833714
+  )),
+  lat = c(
+    41.359907914553574,
+    34.7138879654054,
+    36.98600366773327, 
+    40.08351847675102,
+    37.00933919295183, 
+    40.43918784734024, 
+    41.07342262868038,
+    34.94844567982384, 
+    35.83524984550334,
+    41.630494052326306,
+    38.94979719126508,
+    35.013571084373126,
+    37.91788094070204, 
+    35.262929243118776, 
+    41.327282204484035, 
+    39.752855929900484, 
+    38.3802922004859,
+    38.62113593403746,
+    43.66344794728992,
+    43.05334694203953
+  ),
+  lon = c(
+    -71.48323250872187,
+    -76.66239630117921,
+    -76.35038306859545,
+    -73.99190094110679,
+    -76.48565862613168,
+    -74.0763054899462,
+    -71.93585836088813,
+    -76.74333419560425,
+    -75.61121671722921,
+    -70.91580669134055,
+    -74.90280944790463,
+    -76.66793114333704,
+    -75.35947580478219,
+    -76.08680452670508,
+    -71.9223721359251,
+    -74.11329310115902,
+    -75.05089736920318,
+    -75.06397021718345,
+     -70.22937554378885,
+    -70.7126760833714
+  )
+) %>% 
+  separate(port, into = c("port","abrev"), sep = ',') %>% 
+  mutate(abrev = str_squish(str_to_upper(abrev))) %>% 
+  left_join(as.data.frame(land_sf)) %>% 
+  left_join(noaa_ports) %>% 
+  select(port,state = ID,lat,lon) %>% 
+  mutate(state = str_to_sentence(state))
+
+noaa_ports
+
+```
+
+<!-- This is how all the shapefiles look like together -->
 
 ```{r all_sf, eval = T, echo = T}
-
-port_sf <- port_sf %>% 
-    filter(distance_from_shore_m == 0,
-           label_source %in% c("WPI_ports"),
-           at_dock == TRUE)
 
@@
   geom_sf(data = state_sf, aes(color = state), fill = NA) +
-  geom_sf(data = port_sf, aes(color = state)) +
+  geom_point(data = noaa_ports, aes(x = lon, y = lat)) +
   scale_color_manual(values = state_pallet) +
@@
 ```{r fp_buffer, eval = T, echo = T}
+
+port_sf <- st_as_sf(noaa_ports,
+                    coords =c("lon","lat"),
+                    crs = 4326)
 
@@
 
-write_csv(inter_grid_df, paste0(my_path("D", "Spatial"),"inter_grid_df.csv"))
+# write_csv(inter_grid_df, paste0(my_path("D", "Spatial"),"inter_grid_df.csv"))
 
@@
 
-write_sf(grid_eez_sw_sf, paste0(my_path("D", "Spatial/grid_eez_sw_sf"),"grid_eez_sw_sf.shp"))
+# write_sf(grid_eez_sw_sf, paste0(my_path("D", "Spatial/grid_eez_sw_sf"),"grid_eez_sw_sf.shp"))
+grid_eez_sw_sf <- my_path("D","Spatial/grid_eez_sw_sf", name = "grid_eez_sw_df.csv",read = T)
 
 # Get final df with index
-grid_eez_sw_df <- as.data.frame(grid_eez_sf_sw) %>%
+grid_eez_sw_df <- as.data.frame(grid_eez_sw_sf) %>%
   select(state,index) %>%
@@
 
-write_csv(grid_eez_sw_df, paste0(my_path("D", "Spatial/grid_eez_sw_sf","grid_eez_sw_df.csv")))
+# write_csv(grid_eez_sw_df, paste0(my_path("D", "Spatial/grid_eez_sw_sf","grid_eez_sw_df.csv")))
 
@@
 
-grid_eez_sf_sw %>%
+grid_eez_sw_df %>%
   ggplot() +
@@
 # Load grid of state waters
-grid_eez_sw_sf <- grid_eez_sw_sf %>% 
-  # st_read(my_path("D","Spatial/grid_eez_sw_sf", name = "grid_eez_sw_sf.shp")) %>%
+grid_eez_sw_sf <-  st_read(my_path("D","Spatial/grid_eez_sw_sf", name = "grid_eez_sw_sf.shp")) %>%
   select(index,state,geometry) %>% 
@@
 # Load grid of fishing ports
-grid_eez_fp_sf <- grid_eez_sf_fp %>% 
-  # st_read(my_path("D","Spatial/grid_eez_fp_sf", name = "grid_eez_fp.shp")) %>% 
+grid_eez_fp_sf <-  st_read(my_path("D","Spatial/grid_eez_fp_sf", name = "grid_eez_fp.shp")) %>%
   select(index,state,geometry) %>% 
@@
 
-ggsave(filename = "buffer_figureb.jpg",
+ggsave(filename = "buffer_figurec.jpg",
        plot = combined_plot,
@@
     spatial = ifelse(is.na(spatial),"sw",spatial)
-  ) %>% 
-  spread(spatial,index)
+  )# %>% 
+  # spread(spatial,index)
 
@@
 unique(historic_spp$spp)
-unique(historic_spp$spatial)
 unique(historic_spp$region)
@@
 ![Proportion change aggregated all species map for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/area_plot_avg_spp_sptl.jpg)
+
+# Old code
+
+## Fishing ports WPI
+
+We used [Global Fishing Watch](https://globalfishingwatch.org/datasets-and-code-anchorages/)'s database on 
+Anchorages, Ports and Voyages.
+
+*The Global Fishing Watch anchorages dataset is a global database of anchorage locations where vessels congregate.
+The dataset contains over 160,000 individual anchorage locations, which are further grouped into nearly 32,000 ports when applicable.*
+
+```{r ports_sf, eval = T, echo = T}
+
+# Get Global Fishig Watch data
+gfw_data <- my_path("D","Spatial",name = "gfw_portdata.csv", read = T) %>% 
+  filter(iso3 == "USA")
+
+# Visualize data (o.k!)
+# ggplot(gfw_data) +
+#   geom_point(
+#     aes(
+#     x = lon,
+#     y = lat
+#   )
+#   )
+
+# Convert data to sf for mergig
+gfw_sf <- st_as_sf(gfw_data,
+             coords = c("lon", "lat"),
+             crs = 4326)
+
+# Merge data with state waters to,locate ports 
+port_sf <- st_join(gfw_sf,state_sf) %>% 
+  filter(!is.na(jurisdicti)) # remove points outside stat waters
+
+ggplot(port_sf)  +
+  geom_sf(aes(color = distance_from_shore_m)) +
+  theme_dark()
+
+```
+So...Looks like some ports are "far from shore" which I don't really know what it means. For now, I am only selecting those ports that ar 0 meter from shore.
+
+```{r ports_inshore, eval = T, echo = F}
+
+# Get number of ports per state
+ports_n_data <- port_sf %>% 
+  as.data.frame() %>% 
+    filter(distance_from_shore_m == 0) %>% 
+    group_by(state) %>% 
+    summarise(n_ports = n())
+
+# plot it
+gridExtra::grid.arrange(
+  port_sf %>% 
+    filter(distance_from_shore_m == 0) %>% 
+    ggplot()  +
+    geom_sf(aes(color = jurisdicti)) +
+    scale_color_manual(values = state_pallet) +
+    theme_dark() +
+    theme(legend.position = ""),
+  tableGrob(ports_n_data),
+  ncol = 2
+)
+
+```
+
+There are still too many ports in each state (?). Specially New Jersey! One approach is to use NOAA's landing-per-port data to filter out...
+
+###### 4.2 World Port Index
+
+In this approach we only use the ports categorized within the [WPI](https://msi.nga.mil/NGAPortal/MSI.portal?_nfpb=true&_pageLabel=msi_portal_page_62&pubCode=0015) and with `distance_from_shore_m == 0`  and `at_dock == TRUE`.
+
+- `at_dock` == Anchorages within a 450 meter buffer around a combined land shape file are considered at dock.
+
+```{r wpi_approach, eval = T, echo = F}
+
+gridExtra::grid.arrange(
+  port_sf %>% 
+    filter(distance_from_shore_m == 0,
+           label_source %in% c("WPI_ports"),
+           at_dock == TRUE) %>% 
+    ggplot()  +
+    geom_sf(aes(color = jurisdicti)) +
+    scale_color_manual(values = state_pallet) +
+    theme_dark(),
+  port_sf %>% 
+    as.data.frame() %>% 
+    filter(distance_from_shore_m == 0,
+           label_source %in% c("WPI_ports"),
+           at_dock == TRUE) %>% 
+    group_by(state) %>% 
+    summarise(n_ports = n()) %>% 
+    tableGrob(),
+  ncol = 2
+)
+
+```
 
@@
 ```
+
+## NOAAs port approach
+
+```{r noaa_landings, eval = F, echo = F}
+
+noaa_landings <- read.csv("/Volumes/Enterprise/Data/AcrossBoundaries/Data/NOAA/landings_by_top_us_ports.csv")
+
+noaa_landings %>% 
+  clean_names() %>% 
+  View()
+
+state_totals <- as.data.frame(str_split_fixed(noaa_landings$Port., ",",2)) %>% 
+  rename(name = V1,
+         abrv = V2) %>% 
+  bind_cols(noaa_landings) %>% 
+  mutate(abrv = str_squish(abrv)) %>% 
+  clean_names() %>% 
+  filter(abrv %in%  c("CT","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VA")) %>% 
+  filter(year >= 2010) %>% 
+  group_by(abrv) %>% 
+  summarise(total_pounds_million = sum(millions_of_pounds),
+            total_dlr_million = sum(x_millions_of_dollars)
+  )
+
+# Estimate percentages
+port_data <- as.data.frame(str_split_fixed(noaa_landings$Port., ",",2)) %>% 
+  rename(name = V1,
+         abrv = V2) %>% 
+  bind_cols(noaa_landings) %>% 
+  mutate(abrv = str_squish(abrv)) %>% 
+  clean_names() %>% 
+  filter(abrv %in%  c("CT","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VA")) %>% 
+  filter(year >= 2010) %>% 
+  group_by(abrv,name,port) %>% 
+  summarise(sum_pounds_million = sum(millions_of_pounds),
+            sum_dlr_million = sum(x_millions_of_dollars)
+            ) %>% 
+  left_join(state_totals) %>% 
+  mutate(
+    per_sum = sum_dlr_million/total_dlr_million*100,
+    per_pnds = sum_pounds_million/total_pounds_million*100,
+    cum_per_sum = cumsum(sum_dlr_million/total_dlr_million*100),
+    cum_per_pnds = cumsum(sum_pounds_million/total_pounds_million*100)
+  )
+
+  # Function to get percentiles
+      # https://www.tidyverse.org/blog/2020/03/dplyr-1-0-0-summarise/
+      quibble <- function(x, q = p) {
+        tibble(x = quantile(x, q), q = q)
+      }
+      # Get the percentile treshold per year, ensemble and neighbour id
+    percentile <- port_data %>% 
+        group_by(abrv) %>%
+        do(quibble(.$com_sum, 0.50)) %>% 
+      left_join(port_data) %>% 
+      mutate(drop = ifelse(x < sum_dlr_million,"drop","keep" )) %>% 
+      filter(drop == "keep")
+
+# Number of ports per state
+percentile %>%
+  group_by(abrv) %>%
+  summarise(n()) %>% 
+  left_join(original_n) %>% View()
+
+unique(port_data$abrv)
+length(unique(port_data$abrv))
+
+# Get rank by dolar
+top_dlr <- port_data %>% 
+  group_by(abrv) %>%
+  # View()
+  top_n(10,sum_dlr_million)
+
+# Get rank by landing
+top_pnd <- port_data %>% 
+  group_by(abrv) %>%
+  # View()
+  top_n(10,sum_pounds_million)
+
+# Bind ports and manually set corrdinates
+top_ports <- top_dlr %>% 
+  full_join(top_pnd) %>% 
+  arrange(abrv) %>% 
+  group_by(abrv) %>% 
+  summarise(n())
+
+  # Manually estimated from google maps
+  bind_cols(
+    lat = c(41.3345476816744,
+            41.34138388600569,
+            41.636467065626505,
+            38.32347787720262, 
+            44.15386541519202, 
+            43.66617357876293,
+            35.90400984508054, 
+            43.1123838312889,
+            38.971394018750296, 
+            41.05268318179009, 
+            41.37054800823896, 
+            36.992858601329836, 
+            37.839637137249234
+            ),
+    long = c(-71.91332744028196,
+             -72.08202556545858,
+             -70.91964446265216,
+             -75.1014183484163,
+             -68.66402196775981,
+             -70.2288380196981,
+             -75.55554059613718,
+             -70.85815866495484,
+             -74.8122413826507,
+             -71.9688254628936,
+             -71.48032452726083,
+             -76.26817146730399,
+              -76.24292771914955
+             )
+  ) %>% 
+  # Delaware
+  bind_rows(
+    data.frame(abrv = "DE",
+      name = "Indian river",
+      port = "Indian river, DE",
+      lat = as.double(38.62113593403746),
+      long = -75.06397021718345
+      )
+  )
+
+# write_csv(top_ports,"top_neus_ports.csv")
+
+  port_data %>% 
+    filter(com_mean >= 75) %>% 
+    group_by(abrv) %>% 
+    View()
+    summarise(n())
+
+```

### 2021-09-28 Scripts/spatial_analisis.Rmd
Created Figure one and two based on new port analysis. (Top 74th per)

@@
 library(MyFunctions)
-MyFunctions::my_lib(c("ggmap","sf","st","tidyverse","tools","readr","data.table","maps","viridis","wesanderson","knitr","kableExtra","plotly","ggrepel","ggsflabel","janitor","interp","rnaturalearth","readxl"))
+MyFunctions::my_lib(c("ggmap","sf","st","tidyverse","tools","readr","data.table","maps","viridis","wesanderson","knitr","kableExtra","plotly","ggrepel","ggsflabel","janitor","interp","rnaturalearth","readxl","cowplot"))
 
@@
 
-This dataset includes all landings from 2015-July 2021. It includes the species landed, the port, and the Hull ID and vessel name for black sea bass and summer flounder.
-
-*License, from Sarah Smith: This is confidential data, so please do not share this file with others.
-You may need to contact NOAA directly just to request permission.
-My contact has been Alison Ferguson (Alison.Ferguson@noaa.gov) in their data department.*
-
-```{r}
-
-### SRAH LANDING DATA
-read_excel_allsheets <- function(filename, tibble = TRUE) {
-    # I prefer straight data.frames
-    # but if you like tidyverse tibbles (the default with read_excel)
-    # then just pass tibble = TRUE
-    sheets <- readxl::excel_sheets(filename)[2:8]
-    x <- lapply(sheets, function(X) readxl::read_excel(filename, sheet = X))
-    if(!tibble) x <- lapply(x, as.data.frame)
-    names(x) <- sheets
-    x
-}
-# Get data path
-ports_path <- my_path("D","NOAA", name = "SSmith_2015-2021 Landings_JUN 2021.xlsx")
-
-# 
-ports_data <- bind_rows(read_excel_allsheets(ports_path)) %>%
-  clean_names() %>%
-  mutate_if(is.character,
-              ~ str_to_lower(.)) %>%
-    filter(species_name %in% c("summer flounder","black sea bass","scup"))
-
-noaa_ports <- unique(ports_data$landing_port)
-
-noaa_port <- port_sf %>% 
-  filter(distance_from_shore_m == 0) %>% 
-  mutate(label = str_to_lower(label)) %>% 
-  filter(label %in% noaa_ports)
-
-# Get number of ports per state
-noaa_ports_n_data <- noaa_port %>% 
-  as.data.frame() %>% 
-    group_by(state) %>% 
-    summarise(noaa_ports = n())
-
-# Get number of ports in the NOAA database
-
-n_ports_data <- ports_data %>% 
-  group_by(landing_state) %>% 
-  summarise(noaa_ports = length(unique(landing_port))) %>% 
-  mutate(abrev = str_to_upper(landing_state)) %>% 
-  left_join(land_sf) %>% 
-  select(state,noaa_ports) %>% 
-  filter(!is.na(state)) %>% 
-  left_join(noaa_ports_n_data)
-
-# plot it
-gridExtra::grid.arrange(
-  port_sf %>% 
-    mutate(label = str_to_lower(label)) %>% 
-    filter(distance_from_shore_m == 0,
-           label %in% noaa_ports
-           ) %>% 
-    ggplot()  +
-    geom_sf(aes(color = jurisdicti)) +
-    scale_color_manual(values = state_pallet) +
-    theme_dark(),
-    # theme(legend.position = ""),
-  tableGrob(n_ports_data),
-  ncol = 2
-)
-
-```
-
-######4.2 Data from NOAA fisheries 
-https://www.fisheries.noaa.gov/foss/f?p=215:11:15514950376034::NO:::
-
-Delaware data was colected from NOAA's [Snapshots of Human Communities and Fisheries in the Northeast
-](https://apps-nefsc.fisheries.noaa.gov/read/socialsci/communitySnapshots.php)
-
-NOTES:
-
-- There is no Maine, Delaware, nor New Hamshire in the data. Took them from NOAA as main ports of all fisheries
+###### 4.1.1 Ports coordinates
 
@@
     "HAMPTON, VA", #36.98600366773327, -76.35038306859545,
-    "PT. PLEASANT, NJ", #40.08351847675102,-73.99190094110679,
+    "POINT PLEASANT, NJ", #40.08351847675102,-73.99190094110679,
     "NEWPORT NEWS, VA", #37.00933919295183, -76.48565862613168,
@@
     "LONG BEACH/BARNEGAT LIGHT, NJ", #39.752855929900484, -74.11329310115902
-    "OCEAN CITY, MD", #38.3802922004859, -75.05089736920318
+    "OCEAN CITY harbor, MD", #38.3802922004859, -75.05089736920318
+    # Manually included these ports as top State ports from NOAA
     "Indian river, DE",
     "Portland, ME", #43.66344794728992, -70.22937554378885
-    "Portsmouth, NH" #43.05334694203953, -70.7126760833714
+    "Portsmouth, NH", #43.05334694203953, -70.7126760833714
+    # More ports
+    "Chincoteague, VA", # 37.94295896302465, -75.38415668579887
+    "sea isle city,NJ ", # 39.14912656323854, -74.68797202847871
+    "lewes, DE, ", # 38.78943640990542, -75.06343692610851
+    "virginia beach, VA" # 36.859343385722504, -75.94328398140065
   )),
@@
     43.66344794728992,
-    43.05334694203953
+    43.05334694203953,
+    37.94295896302465,
+    39.14912656323854,
+    38.78943640990542,
+    36.859343385722504
   ),
@@
     -70.22937554378885,
-    -70.7126760833714
-  )
-) %>% 
-  separate(port, into = c("port","abrev"), sep = ',') %>% 
-  mutate(abrev = str_squish(str_to_upper(abrev))) %>% 
-  left_join(as.data.frame(land_sf)) %>% 
+    -70.7126760833714,
+    -75.38415668579887,
+    -74.68797202847871,
+    -75.06343692610851,
+    -75.94328398140065
+  )
+) %>% 
+  separate(port, into = c("landing_port","landing_state"), sep = ',') %>% 
+  mutate(landing_state = str_squish(str_to_upper(landing_state)),
+         landing_port = str_to_lower(landing_port))
+
+noaa_ports
+
+```
+
+###### 4.1.1 Top ports
+
+This dataset includes all landings from 2015-July 2021. It includes the species landed, the port, and the Hull ID and vessel name for black sea bass and summer flounder.
+
+*License, from Sarah Smith: This is confidential data, so please do not share this file with others.
+You may need to contact NOAA directly just to request permission.
+My contact has been Alison Ferguson (Alison.Ferguson@noaa.gov) in their data department.*
+
+NOTES:
+
+- There is no Maine, Delaware, nor New Hamshire in the data. Took them from NOAA as main ports of all fisheries
+
+```{r}
+
+### SRAH LANDING DATA
+read_excel_allsheets <- function(filename, tibble = TRUE) {
+    # I prefer straight data.frames
+    # but if you like tidyverse tibbles (the default with read_excel)
+    # then just pass tibble = TRUE
+    sheets <- readxl::excel_sheets(filename)[2:8]
+    x <- lapply(sheets, function(X) readxl::read_excel(filename, sheet = X))
+    if(!tibble) x <- lapply(x, as.data.frame)
+    names(x) <- sheets
+    x
+}
+# Get data path
+ports_path <- my_path("D","NOAA", name = "SSmith_2015-2021 Landings_JUN 2021.xlsx")
+
+# Load ports
+ports_data <- bind_rows(read_excel_allsheets(ports_path)) %>%
+  clean_names() %>%
+  mutate_if(is.character,
+              ~ str_to_lower(.)) %>%
+    filter(species_name %in% c("summer flounder","black sea bass","scup"))
+
+noaa_ports <- unique(ports_data$landing_port)
+
+# Get number of ports in the NOAA database
+top10_ports <- ports_data %>% 
+  mutate(landing_state = str_to_upper(landing_state)) %>% 
+  filter(landing_state %in% c("CT","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VA")) %>% 
+  group_by(year,landing_port,landing_state,species_name) %>% 
+  summarise(
+    year_ton = sum(landed_weight),
+    year_value = sum(value),
+    noaa_ports = length(unique(landing_port))
+    ) %>% 
+  group_by(landing_port,landing_state,species_name) %>% 
+  summarise_if(is.numeric,sum) %>% 
+  group_by(species_name) %>% 
+  top_n(10,year_ton)
+
+```
+
+###### 4.1.1 Visualization
+
+```{r}
+
+top10_ports %>% 
   left_join(noaa_ports) %>% 
-  select(port,state = ID,lat,lon) %>% 
-  mutate(state = str_to_sentence(state))
-
-noaa_ports
+  ggplot() +
+  geom_point(
+    aes(
+      x = lon,
+      y = lat,
+      shape = species_name, 
+      color = species_name
+    ),
+    size = 5
+  )
+
+```
+
+```{r}
+# Get number of ports in the NOAA database
+total_ports <- ports_data %>% 
+  mutate(landing_state = str_to_upper(landing_state)) %>% 
+  filter(landing_state %in% c("CT","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VA")) %>% 
+  group_by(species_name) %>% 
+  summarise(
+    total_ton = sum(landed_weight, na.rm = T),
+    total_value = sum(value, na.rm = T)
+    )
+
+# Per landings
+
+per_ports <-
+  ports_data %>% 
+  mutate(landing_state = str_to_upper(landing_state)) %>% 
+  filter(landing_state %in% c("CT","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VA")) %>% 
+  group_by(landing_port,species_name) %>% 
+  summarise(
+    port_ton = sum(landed_weight),
+    port_value = sum(value)
+    ) %>% 
+  left_join(total_ports,
+            by = "species_name") %>% 
+    mutate(
+      per_tons = round((port_ton/total_ton)*100,2),
+      per_value = round((port_value/total_value)*100,2)
+    ) %>% 
+    # select(landing_port,species_name,per_tons,everything()) %>% 
+    ungroup() %>% 
+    arrange(desc(per_tons)) %>% 
+    group_by(species_name) %>% 
+    mutate(cum_per = cumsum(per_tons)) %>% 
+    filter(cum_per <= 75) %>% 
+  select(landing_port,species_name,port_ton,per_tons,cum_per,everything()) %>% 
+  arrange(desc(species_name,cum_per))
+
+per_ports
+
+```
+
+```{r}
+
+per_ports %>% 
+  left_join(noaa_ports) %>% 
+  # Double ceck coordinates are all there
+  # filter(is.na(lon))
+  ggplot() +
+  geom_point(
+    aes(
+      x = lon,
+      y = lat,
+      shape = species_name,
+      color = species_name
+    ),
+    size = 5
+  )
+
+ports_df <-  per_ports %>% 
+  left_join(noaa_ports)
 
@@
   geom_sf(data = state_sf, aes(color = state), fill = NA) +
-  geom_point(data = noaa_ports, aes(x = lon, y = lat)) +
+  geom_point(data = ports_df, aes(x = lon, y = lat,
+                                  shape = species_name), size = 3, alpha = 0.7) +
   scale_color_manual(values = state_pallet) +
@@
 
-port_sf <- st_as_sf(noaa_ports,
+port_sf <- st_as_sf(ports_df,
                     coords =c("lon","lat"),
@@
   geom_sf(data = eez_sf, aes(),fill = NA) +
-  geom_sf(data = port_bf, aes(color = state), fill = NA) +
+  geom_sf(data = port_bf, aes(color = species_name), fill = NA) +
   scale_color_manual(values = state_pallet)+
@@
   st_join(port_bf) %>% # join to port sf
-  filter(!is.na(state)) %>% 
-  distinct(index,state, .keep_all = TRUE) #removes like 400K overlapping rows
+  filter(!is.na(landing_port)) %>%
+  distinct(index,landing_port, .keep_all = TRUE) #removes like 400K overlapping rows
 
@@
 grid_fp_bf_dt <- as.data.frame(grid_fp_sf) %>%
-    select(index,state)
+    select(index,landing_port,species_name)
 
@@
 grid_eez_fp_df <- as.data.frame(grid_eez_sf_fp) %>%
-  select(state,index) %>%
+  select(index,landing_port,species_name) %>% 
   left_join(ne_grid,
@@
 grid_eez_fp_sf <-  st_read(my_path("D","Spatial/grid_eez_fp_sf", name = "grid_eez_fp.shp")) %>%
-  select(index,state,geometry) %>% 
-  mutate(method = "fishing_port",
-         state = str_to_sentence(state))%>% 
+  select(index,abrev=lndng_s,geometry) %>% 
+  mutate(method = "fishing_port"#,
+         # state = str_to_sentence(landing_port)
+         )%>% 
   left_join(state_order)
@@
 
+grid_eez_fp_sf <-
+  grid_eez_sw_sf %>% 
+  filter(!group %in% grid_eez_fp_sf$group) %>% 
+  mutate(index = NA) %>% 
+  bind_rows(grid_eez_fp_sf)
+
 p_fp <- gridExtra::grid.arrange(
   # Overall (overlapping) position
-  ggplot(grid_eez_fp_sf) +
+  ggplot(data = subset(grid_eez_fp_sf, index != "NA")) +
     geom_sf(data = eez_sf, aes(), fill = "white") + 
@@
                                    hjust = 1) +
-    scale_color_manual(values = state_pallet) +
-    scale_fill_manual(values = state_pallet) +
+    # scale_color_manual(values = state_pallet) +
+    # scale_fill_manual(values = state_pallet) +
+    scale_color_manual(values = c(state_pallet[3:4],state_pallet[6:13])) +
+    scale_fill_manual(values = c(state_pallet[3:4],state_pallet[6:13])) +
     my_ggtheme_p(leg_pos = "",
@@
   # Showing each state separately
-  ggplot(grid_eez_fp_sf) +
+  ggplot() +
+    geom_sf(data = subset(grid_eez_fp_sf, index = "NA"), color = "white") +
+    geom_sf(data = subset(grid_eez_fp_sf, index != "NA"), aes(color = group),size = 0.1, alpha = 0.3) +
     geom_sf(data = land_sf, aes(), fill = "grey80") +
-    geom_sf(aes(color = group),size = 0.1, alpha = 0.3) +
     facet_wrap(~ group) +
+    geom_point(data = rename(ports_df, group = landing_state), aes(x = lon, y = lat), color = "#E6A0C4") +
     theme(legend.position = "top") +
-    scale_color_manual(values = state_pallet,
+    # scale_color_manual(values = state_pallet,
+    scale_color_manual(values = c(state_pallet[3:4],state_pallet[6:13]),
                        # labels = unique(grid_eez_fp_sf$group)) +
@@
 
-ggsave(filename = "buffer_figurec.jpg",
+ggsave(filename = "buffer_figure.jpg",
        plot = combined_plot,
@@
 ![Buffer figure for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/buffer_figure_b.jpg)
-
-```{r remove_pen, eval = F, echo = F}
-
-####____________________________________________### 
-# Solving for Issue #8 Pennsylvania has NO coast
-####____________________________________________###
-
-# Remove Pennsylvania from sf
-grid_eez_sf <-  st_read("/Volumes/Enterprise/Data/AcrossBoundaries/Data/Spatial/grid_sf/grid_eez_sf.shp") %>%
-  filter(state != "pennsylvania")
-
-# Make sure no Penn.
-unique(grid_eez_sf$state)
-
-# over write sf
-write_sf(grid_eez_sf, paste0(my_path("D", "Spatial"),"grid_eez_sf.shp"))
-
-#Make sure of things
-
-# grid_eez_sf <-  st_read("/Volumes/Enterprise/Data/AcrossBoundaries/Data/Spatial/grid_sf/grid_eez_sf.shp")
-
-# unique(grid_eez_sf$state)
-
-# Now save it as a DF too
-
-# grid_eez_df <- as.data.frame(grid_eez_sf) %>%
-  # select(state,index) %>%
-  # left_join(ne_grid,
-            # by = "index")
-
-# write_csv(grid_eez_df, paste0(my_path("R", "Partial"),"grid_eez_df.csv"))
-```
 
@@
 unique(historic_spp$spp)
+unique(historic_spp$region)
 unique(historic_spp$region)
@@
   ) %>% 
+  filter(!is.na(state)) %>% 
   mutate(abrev = c("CT","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VA")
@@
 head(historic_spp)
+```
+
+# Interpolation result
+
+```{r}
+
+# Interpolation data
+interpol_result <- historic_spp %>% 
+  mutate(
+    label = ifelse(year >= 1980 & year <= 2001,"Reference",
+                   ifelse(year > 2001,"Today",NA)
+    )
+  ) %>% 
+  filter(!is.na(label),
+         region == "Northeast US Spring") %>% 
+  group_by(label,index,spp,lat,lon) %>% 
+  summarise(mean_cpue = mean(value,na.rm=T)) %>% 
+  filter(!is.na(mean_cpue))
+
+# --------------------- #
+# Biomass Centroid shift
+# --------------------- #
+
+# Estimate total interpolation
+total_inter <- historic_spp %>% 
+  mutate(
+    label = ifelse(year >= 1980 & year <= 2001,"Reference",
+                   ifelse(year > 2001,"Today",NA)
+    )
+  ) %>% 
+  filter(!is.na(label),
+         region == "Northeast US Spring") %>% 
+  group_by(spp,index) %>% 
+  summarise(mean_cpue = mean(value,na.rm=T)) %>% 
+  group_by(spp) %>% 
+  summarise(total_cpue = sum(mean_cpue, na.rm = T))
+
+# Estimate centroid based on top 10 grids with higer abundance
+centroid_db <- historic_spp %>% 
+  mutate(
+    label = ifelse(year >= 1980 & year <= 2001,"Reference",
+                   ifelse(year > 2001,"Today",NA)
+    )
+  ) %>% 
+  filter(!is.na(label),
+         region == "Northeast US Spring") %>% 
+  group_by(label,index,spp,lat,lon) %>% 
+  summarise(mean_cpue = mean(value,na.rm=T)) %>% 
+  filter(!is.na(mean_cpue)) %>% 
+  left_join(total_inter) %>% 
+  mutate(
+    per_cpue = round((mean_cpue/total_cpue)*100,2)
+  ) %>% 
+  group_by(spp,label) %>% 
+  top_n(10,per_cpue) %>% 
+  group_by(spp,label) %>% 
+  summarise(
+    lat = mean(lat),
+    lon = mean(lon)
+  )
+
+inter_map <- ggplot() +
+   geom_tile(data = subset(interpol_result, mean_cpue == 0),
+            aes(
+              x = lon,
+              y = lat
+            ),
+            fill = "grey90",
+              color = "grey90"
+  ) + 
+  geom_tile(data = subset(interpol_result, mean_cpue > 0),
+            aes(
+              x = lon,
+              y = lat,
+              fill = mean_cpue,
+              color = mean_cpue
+            )
+  ) + 
+  geom_point(data = centroid_db,
+            aes(
+              x = lon,
+              y = lat
+            ),
+            shape = 3,
+            color = "white"
+  ) + 
+  geom_sf(data = land_sf,aes()) +
+  labs(x = "Longitude",
+         y = "Latitude") +
+  # ggsflabel::geom_sf_label_repel(data = land_sf, aes(label= abrev), 
+  #                                  size = 4,
+  #                                  box.padding = 0.10,
+  #                                  hjust = 1) +
+  scale_fill_viridis("Mean Interpolation", alpha = 0.8,
+                     limits = c(0,40)) +
+  scale_color_viridis("Mean Interpolation", alpha = 0.8, 
+                      limits = c(0,40)) +
+  facet_grid(label ~ spp) +
+  my_ggtheme_m(map_type = "na", leg_pos = "bottom",ax_tx_s = 10,ax_tl_s = 12,leg_tx_s = 12) +
+  theme(legend.key.width = unit(3,"line"))
+
+ggsave("interpolation_fig.jpg",
+       inter_map,
+       path = my_path("R","Figures"),
+       width = 8,
+       height = 6)
+
 ```
@@
   spread(spatial,mean_per) %>% 
-  mutate(difference = (fp-sw)/((fp+sw)/2)*100,
+  mutate(
+    difference = (fp-sw)/((fp+sw)/2)*100,
+    # difference = fp-sw,
          difference = ifelse(difference > 100,100,
@@
          spatial = ifelse(spatial == "fp","Fishing ports",
-                          ifelse(spatial == "sw","State Waters","Difference")
+                          ifelse(spatial == "sw","State waters","Difference")
          )
@@
   geom_sf(aes(fill = mean_per)) +
-  viridis::scale_fill_viridis("Average proportion per State", alpha = 0.8) +
+  viridis::scale_fill_viridis("Average proportion per State", alpha = 0.8, 
+                              breaks = seq(0,15,5),
+                              limits=(c(0,15))
+                              )+
   facet_grid(spatial~ spp+label) +
@@
   geom_sf(aes(fill = mean_per)) +
-  viridis::scale_fill_viridis("Percentage difference", alpha = 0.8) +
+  viridis::scale_fill_viridis("Percentage difference", alpha = 0.8,option = "C",
+                              breaks = seq(-20,70,10),
+                              limits=(c(-20,70))
+                              ) +
   facet_grid(spatial~ spp+label) +
@@
          ) %>% 
-  # left_join(periods,
-            # by = "year") %>% 
   group_by(state,label,region,spp,spatial) %>% 
   summarise(mean_per = round(mean(percentage)),.groups = "drop") %>% 
-  #Only show results for spring
+  # Only show results for spring
   filter(str_detect(region,"Spring"),
@@
                           ifelse(spatial == "sw","State Waters","Difference")
-         )
+         ),
+         mean_per= replace_na(mean_per,0)# for those 0/0
   )
@@
   geom_sf(aes(fill = mean_per)) +
-  viridis::scale_fill_viridis("Change in proportion today\n relative to 1973-1984\n(%)", alpha = 0.8,
+  viridis::scale_fill_viridis("Change in proportion today\nrelative to 1980-2001\n(%)", alpha = 0.8,
                               limits = c(-100,100),
                               breaks = seq(-100,100,25),
-                              labels = c(seq(-100,75,25),">100")
+                              labels = c("<-100",seq(-75,75,25),">100")
                               ) +
@@
 
-ggsave(filename = "temp_proportion_chng.jpg",
-         plot = prop_chng_map,
-         path = my_path("R","Figures"),
-         width = 10,
-         height = 10
-  )
+# ggsave(filename = "temp_proportion_chng.jpg",
+#          plot = prop_chng_map,
+#          path = my_path("R","Figures"),
+#          width = 10,
+#          height = 10
+#   )
 
@@
   geom_sf(aes(fill = mean_per)) +
-  viridis::scale_fill_viridis("Change in proportion\n relative to 1980-2001 (%)", 
-                              alpha = 0.8,
-                              # option = "C"
+  viridis::scale_fill_viridis("Change in proportion today\nrelative to 1980-2001\n(%)", alpha = 0.8,
+                              option = "C"
                               limits = c(-100,100),
                               breaks = seq(-100,100,25),
-                              labels = c(seq(-100,75,25),">100")
+                              labels = c("<-100",seq(-75,75,25),">100")
                               ) +
@@
 ```
+
+```{r remove_pen, eval = F, echo = F}
+
+####____________________________________________### 
+# Solving for Issue #8 Pennsylvania has NO coast
+####____________________________________________###
+
+# Remove Pennsylvania from sf
+grid_eez_sf <-  st_read("/Volumes/Enterprise/Data/AcrossBoundaries/Data/Spatial/grid_sf/grid_eez_sf.shp") %>%
+  filter(state != "pennsylvania")
+
+# Make sure no Penn.
+unique(grid_eez_sf$state)
+
+# over write sf
+write_sf(grid_eez_sf, paste0(my_path("D", "Spatial"),"grid_eez_sf.shp"))
+
+#Make sure of things
+
+# grid_eez_sf <-  st_read("/Volumes/Enterprise/Data/AcrossBoundaries/Data/Spatial/grid_sf/grid_eez_sf.shp")
+
+# unique(grid_eez_sf$state)
+
+# Now save it as a DF too
+
+# grid_eez_df <- as.data.frame(grid_eez_sf) %>%
+  # select(state,index) %>%
+  # left_join(ne_grid,
+            # by = "index")
+
+# write_csv(grid_eez_df, paste0(my_path("R", "Partial"),"grid_eez_df.csv"))
+```

### 2021-09-28 Scripts/spatial_analisis.Rmd
Re-made figures 3 and 4 with new ports data

@@
 grid_eez_sw_df <- as.data.frame(grid_eez_sw_sf) %>%
-  select(state,index) %>%
+  select(state,abrev,index) %>%
   left_join(ne_grid,
@@
 
+state_names <- grid_eez_sw_df %>% 
+  select(state,abrev) %>% 
+  distinct(.keep_all = T)
+
 # Get the overlapping segments 
@@
 grid_eez_fp_df <- as.data.frame(grid_eez_sf_fp) %>%
-  select(index,landing_port,species_name) %>% 
+  select(index,landing_port,abrev=landing_state,spp=species_name) %>% 
   left_join(ne_grid,
-            by = "index")
+            by = "index") %>% 
+  left_join(state_names)
 
@@
 
+# Spatial data
+States <- c("maine", "new hampshire", "massachusetts", "connecticut", "rhode island", "new york", "new jersey", "delaware", "maryland", "virginia", "north carolina")
+
+# US State Map (land)
+land_sf <- st_as_sf(map("state", plot = FALSE, fill = TRUE)) %>% 
+  filter(ID %in% States) %>% 
+  mutate(abrev = c("CT","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VA"),
+         state = str_to_sentence(ID)
+         )
+
 ### Previouslly created grids
@@
   ) %>% 
+  select(-spp) %>% 
   mutate(
     spatial = ifelse(is.na(spatial),"sw",spatial)
-  )# %>% 
-  # spread(spatial,index)
+  ) %>% 
+  distinct(.keep_all = T)
 
@@
 unique(historic_spp$region)
-
-# Spatial data
-States <- c("maine", "new hampshire", "massachusetts", "connecticut", "rhode island", "new york", "new jersey", "delaware", "maryland", "virginia", "north carolina")
-
-# US State Map (land)
-land_sf <- st_as_sf(map("state", plot = FALSE, fill = TRUE)) %>% 
-  filter(ID %in% States) %>% 
-  mutate(abrev = c("CT","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VA"),
-         state = str_to_sentence(ID)
-         )
 
@@
   mutate(lat = order,
-    order = letters[1:11])
+    # order = letters[1:11],
+    order = c("b","a",letters[3:11]),)
 
@@
        height = 6)
-
 ```
@@
   summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
+  # View()
   left_join(total_fited,
@@
          ) %>% 
-  # left_join(periods,
-  #           by = "year") %>% 
   group_by(state,label,region,spp,spatial) %>% 
@@
   spread(spatial,mean_per) %>% 
+  # Set NA's to 0 because no data found on FP
+  mutate(fp = replace_na(fp,0)) %>% 
+  # View()
   mutate(
-    difference = (fp-sw)/((fp+sw)/2)*100,
-    # difference = fp-sw,
+    # difference = ifelse(fp == 0,100, (fp-sw)/((fp+sw)/2)*100),
+    difference = abs(fp-sw),
          difference = ifelse(difference > 100,100,
@@
   viridis::scale_fill_viridis("Average proportion per State", alpha = 0.8, 
-                              breaks = seq(0,15,5),
-                              limits=(c(0,15))
+                              breaks = seq(0,35,5),
+                              limits=(c(0,35))
                               )+
@@
   geom_sf(aes(fill = mean_per)) +
-  viridis::scale_fill_viridis("Percentage difference", alpha = 0.8,option = "C",
-                              breaks = seq(-20,70,10),
-                              limits=(c(-20,70))
+  viridis::scale_fill_viridis("Difference (%)", alpha = 0.8,option = "C",
+                              breaks = seq(0,20,5),
+                              limits=(c(0,22)),
+                              # labels = c("<-10",seq(-75,75,25),">100")
                               ) +
@@
   path = my_path("R","Figures"),
-  "proportion_chg_spp_spatialN.jpg",
+  "proportion_chg.jpg",
   p,
@@
 
-### Paper figure: Aggregated Proportional change
+### Aggregated Proportional change
 
@@
          path = my_path("R","Figures"),
-         width = 12,
-         height = 10
+         width = 14,
+         height = 8
   )

### 2021-10-04 Scripts/spatial_analisis.Rmd
Interpolation figure

@@
   #                                  hjust = 1) +
-  scale_fill_viridis("Mean Interpolation", alpha = 0.8,
+  scale_fill_viridis("Mean\nInterpolation",
                      limits = c(0,40)) +
-  scale_color_viridis("Mean Interpolation", alpha = 0.8, 
+  scale_color_viridis("Mean\nInterpolation",
                       limits = c(0,40)) +
-  facet_grid(label ~ spp) +
-  my_ggtheme_m(map_type = "na", leg_pos = "bottom",ax_tx_s = 10,ax_tl_s = 12,leg_tx_s = 12) +
-  theme(legend.key.width = unit(3,"line"))
+  facet_grid(spp~label) +
+  my_ggtheme_m(map_type = "na", leg_pos = "right",ax_tx_s = 7,ax_tl_s = 10,leg_tx_s = 10) #+
+  # theme(legend.key.width = unit(3,"line"))
 
@@
        path = my_path("R","Figures"),
-       width = 8,
+       width = 6,
        height = 6)

### 2021-10-04 Scripts/manuscript_acrossboundaries.Rmd
Methods better explained

@@
 ---
-title: "Challenges on quantifying fish range shifts across management boundaries"
+title: "Quantifying fish range shifts across poorly defined management boundaries"
 subtitle: "DRAFT. Target journal *PlosOne*"
-author: "Palacios-Abrantes Juliano, Crosson Scott, Dumas Chris, Fujita Rod, Jensen Olaf, Levine Arielle, Longo Catherine"
+author: "Palacios-Abrantes Juliano, Crosson Scott, Dumas Chris, Fujita Rod, Levine Arielle, Longo Catherine, Jensen Olaf"
 output: 
@@
 
-<!-- - Expanding from US to international -->
+<!-- - Expanding from U.S. to international -->
 <!-- - Fishing communities and processing plans are fixed in time and space (e.g., Salmon in Canada, Peruvian anchoveta) -->
@@
 The change in species distribution will be particularly challenging for the management of stocks shared across management jurisdictions [@PalaciosAbrantes:2020sr].
-When a stock is subjected to two or more spatial regulatory regions, managers must often coordinate efforts to maintain sustainability of the stock [@Clark1979; @Munro2004].
+When a stock falls within to two or more spatial regulatory regions, managers must often coordinate efforts to maintain sustainability of the stock [@Clark1979; @Munro2004].
 However, there can be a growing disconnect between the region of the ocean where fish are found and the management jurisdictions which hold harvest rights [@PalaciosAbrantes:2020sr].
@@
 
-In the United States (US) North East (NE) Atlantic, many important fished species such as american lobster (*Homarus americanus*), yellowtail flounder (*Limanda ferruginea*), summer flounder (*Paralichthys dentatus*) and red hake (*Urophycis chuss*) have been shifting their distribution poleward  [@pinsky_fogarty_2012], and modelling exercises suggest that NE Atlantic species will shift will average over 600 km towards the end of the $21^{st}$ century under a high emission climate change scenario [@Morley:2018].
+In the United States (U.S.) North East (NE) Atlantic, many important fished species such as american lobster (*Homarus americanus*), yellowtail flounder (*Limanda ferruginea*), summer flounder (*Paralichthys dentatus*) and red hake (*Urophycis chuss*) have been shifting their distribution poleward  [@pinsky_fogarty_2012], and modelling exercises suggest that NE Atlantic species will shift will average over 600 km towards the end of the $21^{st}$ century under a high emission climate change scenario [@Morley:2018].
 The mismatch between implemented management strategies and shifts in stocks across management jurisdictions compromises management and sustainability [@Baudron2020; @pinsky_fogarty_2012].
@@
 While this problem of shifting stocks across management jurisdictions is increasingly well known, quantifying it is difficult for two main reasons: (*i*) management jurisdictions in the ocean are often ill-defined, especially at the sub-national level or beyond Exclusive Economic Zones (EEZ), and (*ii*) quantifying fish distributions in relation to these boundaries is difficult, even where fishery-independent surveys exist, because of seasonal and interannual variation.
+
+**[Short paragraph on the ill-defined boundary challeng - do we privilege a state's geographic claims or the inherent claims to the resource of existing fishing ports?]**
+
+**[Short paragraph on the seasonality of fish distributions in temperate waters - when do we measure fish distributions?]**
 
@@
 Second, we examine differences in the species' historical distribution between Spring and Fall to examine seasonal variation in these stock's distributions.
-We use bottom trawl surveys for Spring and Fall from 1971 to 2019 and apply a triangular irregular surface method to extrapolate fish biomass across the U.S.
-Northeast EEZ.
-We then draw spatial polygons for each State up to the EEZ from two different starting points; the state waters and main fishing ports.
-Our results suggest that...
+
+ "How does the choice of survey timing and boundary extrapolation method influence our perception of fish distribution changes relative to management boundaries?"
 
@@
 An annual coast wide commercial quota is implemented and since 2003 further allocated to the States of Maine, New Hampshire, Massachusetts, Rhode Island, Connecticut, New York, New Jersey, Delaware, Maryland, Virginia and North Carolina [@REFMACMP-memorandum] (Table \@ref(tab:QuotaTable)).
-The State-wide quota allocation is based on the historical landings from 1980-2001, approximately.
+[OJ](I don't this is right.
+For summer flounder, at least, I thought there was a specific year that the quota allocation was based on.) The State-wide quota allocation is based on the historical landings from 1980-2001, approximately.
 
@@
   kable("latex",
-        caption = "State wide commercial quota allocation for black sea bass (*Centropristis striata*), summer flounder (*Paralichthys dentatus*) and scup (*Stenotomus chrysops*) according to the 2003 implementation.
+        caption = "State wide commercial quota allocation for black sea bass (*Centropristis striata*), summer flounder (*Paralichthys dentatus*) and scup (*Stenotomus chrysops*) according to the Mid-Atlantic Fishery Management Council.
 Values shown as percentage of total quota.
@@
 
-Biomass data for all three species was gathered from NOAA's yearly Northeast Fisheries Science Center Spring and Fall Bottom Trawl Surveys [data](https://www.fisheries.noaa.gov/region/new-england-mid-atlantic#science) provided by [Ocean adapt](https://oceanadapt.rutgers.edu/) and standardized as catch per unit of effort (CPUE) [@Pinsky2013].
-
-with two comparative periods; the average of 1980 to 2000 representing the state allocations of the commercial fisheries originally implemented in 2003 [@RefDocument], and the average of 2009 to 2019 representing a more recent time period.
-
-We extrapolated fish CPUE observational data to the NE Atlantic EEZ from the southern border of North Carolina to the US-Canadian border by following a triangular irregular surface (TIS) method using the *R* package *interp* [@REFInterp].
+Distribution data for all three species was gathered from NOAA's yearly Northeast Fisheries Science Center Spring and Fall Bottom Trawl Surveys [data](https://www.fisheries.noaa.gov/region/new-england-mid-atlantic#science) provided by [Ocean adapt](https://oceanadapt.rutgers.edu/) and standardized as catch per unit of effort (CPUE) [@Pinsky2013].
+CPUE was defined as trawl-catch in weight per area swept (kg/ha).
+For the extrapolation and subsequent analysis we focused on the Atlantic U.S.
+EEZ spatial division using the *Sea Around Us* shape file (updated 2020; http://www.seaaroundus.org).
+The EEZ shapefile was gridded to a 3 x 3 degrees matrix.
+We extrapolated trawl CPUE data to the U.S.
+EEZ from the southern border of North Carolina to the U.S.-Canadian border by following a triangular irregular surface (TIS) method using the *R* package *interp* [@REFInterp].
 Overall, the TIS method creates multiple non-overlapping triangles that cover the entire extrapolated region (i.e., the EEZ) from an initial set of sample points (i.e., NOAAs survey) generating a spatially-continuous surface [@REF; @REF].
@@
 
-Federal U.S.
-waters are not sub-dived into state-owned fisheries management regions.
-Thus, we created state-polygons to allocate the extrapolated CPUE to each fishing State.
-This step allowed us to further determine what proportion of the species distribution was in each state-polygon.
-The state-polygons were created by first expanding multiple polygons within the 200 nautical miles of the EEZ using the *st* package in *R* [@REF].
-Creating these state-polygons was key to allocate the distribution of any stock directly influencing the proportion of the stock linked to a state.
-For example, the amount of the distribution that each State has will be influenced by the size of the state-polygon.
-Here, we used two different sources as starting points for the state-polygons expansion; state waters and US ports (Figure \@ref(fig:bufferFig)).
-For the state waters approach we used the [NOAA-data.gov](https://catalog.data.gov/dataset/federal-and-state-waters) shapefile.
-Note that in this case, the extent of the final state-polygons was related to the size of the State's coast with North Carolina and Maine having the largest polygons.
-For the ports approach we used the [Global Fishing Watch](https://globalfishingwatch.org/datasets-and-code-anchorages/)'s database on Anchorages, Ports and Voyages.
-We only considered ports classified within the World Port Index ([WPI](https://msi.nga.mil/NGAPortal/MSI.portal?_nfpb=true&_pageLabel=msi_portal_page_62&pubCode=0015)).
-In this case, the number of ports varied among States with New Jersey and Massachusetts having the largest amounts (117 and 187, respectively) and Delaware and New Hampshire having the leaser (2 and 14, respectively).
-However, rather than the number of ports per State, in this case what influences the size of the state-polygon was the distribution of ports within the State's waters as two ports in opposite latitudes will result in a larger polygon than two ports closed together (Figure \@ref(fig:bufferFig)).
+## Determining regulatory units
+
+Although the stock-wide quota for our three target species is allocated among the states, U.S.
+Federal waters are not sub-divided into state-owned fisheries management regions (**hereafter refereed as regulatory units**).
+This lack of regulatory units within federal waters creates a challenge for assessing a stock's distribution with respect to individual states.
+There are a potentially infinite number of ways to geographically determine regulatory units with the EEZ's 200 nautical miles.
+Here we focus on two methods based which likely bracket much of the range of options.
+
+### State waters expansion
+
+<!-- Office for Coastal Management, 2021: Federal and State Waters from 2010-06-15 to 2010-08-15.
+NOAA National Centers for Environmental Information, https://www.fisheries.noaa.gov/inport/item/54383.
+-->
+
+The first approach consists on expanding the current geographical distribution of States and their statutory state waters.
+For this approach we adapted the State waters boundaries determined by the Federal and State Waters shapefile created for the Ocean Reporting Tool in April, 2018 ([NOAA's Office for Coastal Management, 2021](https://catalog.data.gov/dataset/federal-and-state-waters)).
+This shapefile consists in multiple polygons each one representing the statutory 3 miles waters that each state owns (Figure \@ref{fig:figureS1}).
+Each state's polygon  from Maine to Virginia was expanded to the 200 nm EEZ boundary using the *st* package in *R* [@REF].
+The resulting polygons were also gridded into a 3 x 3 deg.
+matrix.
+The regions where the grid cells overlapped were equally allocated to the sharing states.
+
+### Fishing ports approach
+
+The second approach to determine regulatory units gives greater weight to the historical landings of each fishing port.
+For this approach we used NOAA Fisheries landings-by-port data [@REF_NOAA].
+Landings from each species and port were averaged from 2010 to 2019 noting that 2020-2021 were removed to avoid using COVID19-impacted years.
+We then estimated the total port-wide landings of the averaged period and the participation that each port had in terms of landings *per* species.
+We selected the main ports landing each species, defined as those concentrating the top $75{^th}$ percentile of landings.
+Note that, while species often shared top ports, their final number and location varied acording to each species (Figure \@ref{fig:figureS1}).
+Moreover, we tested the sensitivity of our results to the arbitrary $75{^th}$ percentile threshold and found that...
+(*to be done*).
+Each port represented a point in the map (i.e., latitude and longitude degrees) whose coordinates were manually collected using [googlemaps](www.googlemaps.com).
+We then drew a polygon from each port to the EEZ and gridded the expanded polygon following the same method as the *Fishing ports approach*.
+The expanded polygon of each port was associated to the State where the port is located and overlapping grids were equally allocated to the sharing states.
+
+While each approach follows a fairly similar method (e.g., expanding an initial area towards the EEZ) the fundamental difference of the starting point results in different regulatory units for each State (Figure \@ref(fig:bufferFig)).
+Such difference is an important THING as such regularity units were used to estimate the proportion of the distribution that each species had in each state.
 
@@
 
-We then gridded the EEZ into 3 x 3 grid-cells and overlay it with the state-polygons to identify the grids that each state-polygon occupied.
-Note that a grid-cell would be allocated to multiple States in cases where state-polygons overlay.
+## Estimating each State's CPUE
+
 For each approach we then overlay each specie's interpolation with the state-polygons and estimated the distribution and biomass proportion of each state.
@@
 # Discussion
+
+# Supplements
+
+```{r figsone, eval = T, echo = F}
+
+```

### 2021-10-05 Scripts/manuscript_acrossboundaries.Rmd
inlcuded first results paragraph on spatial units

@@
 The management unit extends from the U.S.-Canadian border to the southern border of North Carolina for summer flounder, and Cape Hatteras (North Carolina) for scup and black sea bass [MAFMC](https://www.mafmc.org/sf-s-bsb/).
-The fisheries are managed cooperatively by the States through the Commission in state waters (0-3 miles), and through the MAFMC and NOAA Fisheries in federal waters (3-200 miles).
+The fisheries are managed cooperatively by the States through the Commission in state waters (0-3 miles), and through the MAFMC and NOAA Fisheries in federal waters (3-200 nautical miles).
 An annual coast wide commercial quota is implemented and since 2003 further allocated to the States of Maine, New Hampshire, Massachusetts, Rhode Island, Connecticut, New York, New Jersey, Delaware, Maryland, Virginia and North Carolina [@REFMACMP-memorandum] (Table \@ref(tab:QuotaTable)).
 [OJ](I don't this is right.
-For summer flounder, at least, I thought there was a specific year that the quota allocation was based on.) The State-wide quota allocation is based on the historical landings from 1980-2001, approximately.
+For summer flounder, at least, I thought there was a specific year that the quota allocation was based on.) The state-wide quota allocation is based on the historical landings from 1980-2001, approximately.
 
@@
 The first approach consists on expanding the current geographical distribution of States and their statutory state waters.
-For this approach we adapted the State waters boundaries determined by the Federal and State Waters shapefile created for the Ocean Reporting Tool in April, 2018 ([NOAA's Office for Coastal Management, 2021](https://catalog.data.gov/dataset/federal-and-state-waters)).
+For this approach we adapted the state's waters boundaries determined by the Federal and State Waters shapefile created for the Ocean Reporting Tool in April, 2018 ([NOAA's Office for Coastal Management, 2021](https://catalog.data.gov/dataset/federal-and-state-waters)).
 This shapefile consists in multiple polygons each one representing the statutory 3 miles waters that each state owns (Figure \@ref{fig:figureS1}).
@@
 
-The second approach to determine regulatory units gives greater weight to the historical landings of each fishing port.
+The second approach to determine regulatory units gives greater weight to the historical landings of fishing ports.
 For this approach we used NOAA Fisheries landings-by-port data [@REF_NOAA].
 Landings from each species and port were averaged from 2010 to 2019 noting that 2020-2021 were removed to avoid using COVID19-impacted years.
-We then estimated the total port-wide landings of the averaged period and the participation that each port had in terms of landings *per* species.
+We then estimated the total port-wide landings of the averaged period and the proportion that each port had in terms of landings *per* species.
 We selected the main ports landing each species, defined as those concentrating the top $75{^th}$ percentile of landings.
-Note that, while species often shared top ports, their final number and location varied acording to each species (Figure \@ref{fig:figureS1}).
+Note that, while species often shared top ports, their final number and location varied according to each species (Figure \@ref{fig:figureS1}).
 Moreover, we tested the sensitivity of our results to the arbitrary $75{^th}$ percentile threshold and found that...
@@
 We then drew a polygon from each port to the EEZ and gridded the expanded polygon following the same method as the *Fishing ports approach*.
-The expanded polygon of each port was associated to the State where the port is located and overlapping grids were equally allocated to the sharing states.
+The expanded polygon of each port was associated to the state where the port is located and overlapping grids were equally allocated to the sharing states.
 
-While each approach follows a fairly similar method (e.g., expanding an initial area towards the EEZ) the fundamental difference of the starting point results in different regulatory units for each State (Figure \@ref(fig:bufferFig)).
-Such difference is an important THING as such regularity units were used to estimate the proportion of the distribution that each species had in each state.
+## Estimating each state's CPUE
+
+We overlay the specie's interpolation with the regulatory units and estimated the distribution and CPUE proportion that each state had under both approaches.
+The interpolated CPUE was divided equally in cases where two or more states had the same grid.
+For example, if New York and New Jersey both shared one grid, then the proportion of that grid would be allocated 50% to each state, alternatively, if Connecticut was also sharing the grid, then the proportion would be 33.3% to each state.
+Note that this step does not affect the interpolation method but the way the CPUE is allocated by state.
+
+Finally, we estimated the CPUE percentage change today relative to the historic period.
+For that matter we define the historic period as 1980 to 2000 representing the state allocations of the commercial fisheries originally implemented in 2003 [@RefDocument], and “today” as the average of 2009 to 2019 representing the more recent data available.
+The parentage changes between the historic and present CPUE ($\Delta{B}$) was estimate for each of the two regulatory units approaches as;
+
+$$ \Delta \alpha=\frac{(\alpha_t-\alpha_h)}{|\alpha_h|}*100$$
+
+Where $\alpha_t$ is the CPUE today (average of 2009 to 2019) and $\alpha_h$ is the CPUE at the historical period (average of 1980 to 2000).
+In addition, we estimated the differences in ($\Delta{\alpha}$) between survey seasons ($\Delta{\alpha}_{seas}$) and between regulatory units ($\Delta{\alpha}_{reg}$) approach by subtracting from each other:
+
+$$ \Delta \alpha_{seas} = |\Delta \alpha_{fp}-\Delta \alpha_{sw}| $$
+$$ \Delta \alpha_{reg} = |\Delta \alpha_{f}-\Delta \alpha_{s}| $$
+
+Where $\Delta{\alpha}_{fp}$, $\Delta{\alpha}_{sw}$, $\Delta{\alpha}_{f}$, and $\Delta{\alpha}_{s}$ represent the CPUE percentage change today relative to historical value for fishing ports, state waters, Fall and Summer approaches, respectively.
+
+All of the analysis was done on R-Studio statistical software and *R* version 4.1.0 (*Camp Pontanezen*) [@REF_Rstudio] and associated packages (Table S1).
+All code can be found in https://github.com/jepa/AcrossBoundaries.
+<!-- *ggmap*, *sf* [@REF], *st* [@REF], *tidyverse* [@REF], *tools* [@REF], *readr* [@REF], *data.table* [@REF], *maps* [@REF], *viridis* [@REF], *wesanderson* [@REF], *knitr* [@REF], *kableExtra* [@REF], *plotly* [@REF], *ggrepel* [@REF], *ggsflabel* [@REF], *janitor* [@REF], *interp* [@REF], *rnaturalearth* [@REF], and *readxl* [@REF].
+-->
+
+# Results
+
+The choice of boundary expansion method (e.g., fishing ports or state waters) is highly consequential for determining the spatial extent of each state's regulatory unit (Figure \@ref{fig:bufferFig}).
+For example, using the state water approach, Delaware and Maryland have regulatory units of *XX* and *YY* hectares, respectively.
+Because neither state has a port with commercial landings of black sea bass, scup, or summer flounder that exceeds the $75^{th}$ threshold, their regulatory units based on the fishing ports approach include only their state waters out to 3 nm.
+In contrast, New Jersey's regulatory unit is *X%* larger under the fishing port approach because New Jersey has *XX* ports meeting the $75^{th}$ landings threshold, and they are separated by *XX* km.
 
 ```{r bufferFig, eval = F, echo = T, fig.width = 3, fig.height = 2, echo=FALSE, fig.cap="Spatial regions within the United States' North East Exclusive Economic Zone.
-A) Spatial buffers from each State's waters.
+A) Spatial buffers from each state's waters.
 B) Spatial buffers from the main fishing ports.
@@
 
-![Figure 1.
+<!-- ![Figure 1.
 Spatial regions within the United States' North East Exclusive Economic Zone.
-A) Spatial buffers from each State's waters.
+A) Spatial buffers from each state's waters.
 B) Spatial buffers from the main fishing ports.
@@
 ME, Maine; NH, New Hampshire; MA, Massachusetts; RI, Rhode Island; CT, Connecticut; NY, New York; NY, New Jersey; DE, Delaware; MD, Maryland; VA Virginia; North Carolina.
-](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F1_buffer_figure.png)
+](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F1_buffer_figure.png) -->
 
-## Estimating each State's CPUE
+<!-- **[Add another paragraph here on how different the Spring vs. Fall distributions are]** -->
+The spatial distribution of the CPUE interpolation for each species varied by season (Figure \@ref{fig:figInterpolation}.
 
-For each approach we then overlay each specie's interpolation with the state-polygons and estimated the distribution and biomass proportion of each state.
-The interpolated biomass was divided equally in cases where two or more States had the same grid.
-For example, if New York and New Jersey both shared one grid, then the proportion of that grid would be allocated 50% to each state, alternatively, if Connecticut was also sharing the grid, then the proportion would be 33.3% to each state.
-Note that this step does not affect the interpolation method but the way the biomass is allocated by State.
+```{r figInterpolation, eval = F, echo = F}
 
-Finally, we estimated the biomass percentage change today relative to the historic period.
-For that matter we define the historic period as 1980 to 2000 representing the state allocations of the commercial fisheries originally implemented in 2003 [@RefDocument], and “today” as the average of 2009 to 2019 representing a more recent data available.
-The parentage changes between the historic and present biomass ($\Delta{B}$) was estimate for each of the four approaches as;
-
-$$ \Delta B=\frac{(B_t-B_h)}{|B_h|}*100$$
-
-Where $B_t$ is the biomass today (average of 2009 to 2019) and $B_h$ is the biomass at the historical period (average of 1980 to 2000).
-In addition, we estimated the differences in ($\Delta{B}$) between the seasonal ($\Delta{B}_{seas}$) and the spatial ($\Delta{B}_{spat}$) approach by subtracting from each other:
-
-$$ \Delta B_{seas} = |\Delta B_{fp}-\Delta B_{sw}| $$
-$$ \Delta B_{spat} = |\Delta B_{f}-\Delta B_{s}| $$
-
-Where $\Delta{B}_{fp}$, $\Delta{B}_{sw}$, $\Delta{B}_{f}$, and $\Delta{B}_{s}$ represent the biomass parentage change today relative to historical value for fishing ports, state waters, Fall and Summer approaches, respectively.
-
-All of the analysis was done on RStudio statistical software and *R* version 4.1.0 (*Camp Pontanezen*) and associated packages *ggmap*, *sf* [@REF], *st* [@REF], *tidyverse* [@REF], *tools* [@REF], *readr* [@REF], *data.table* [@REF], *maps* [@REF], *viridis* [@REF], *wesanderson* [@REF], *knitr* [@REF], *kableExtra* [@REF], *plotly* [@REF], *ggrepel* [@REF], *ggsflabel* [@REF], *janitor* [@REF], *interp* [@REF], *rnaturalearth* [@REF], and *readxl* [@REF].
-All code can be found in https://github.com/jepa/AcrossBoundaries.
-
-# Results
+```
 
@@
 Differences in the intensity of change varies among spatial and seasonal estimations (Figure \@ref{fig:figaggpropcnhg}).
-Aggregated biomass seems to have changed more drastically in Spring following the State waters approach with a max reduction of over -100% for North Carolina (a 40% difference between seasons) and increase of 50% for Maine (a 17% difference between seasons).
-On the other hand, Fall proportion max reduction was -66% for Maryland (a 44% difference between seasons) and max increase was 33% for Maine regardless of the approach (Figure \@ref{fig:figaggpropcnhg}A).
-Differences between approaches (i.e., State Waters v.s.
-Fishing Ports and Spring v.s.
-Fall) were larger for the State water approach (mean 14% $\pm$ 15%; max  44%) and smallest in Spring (mean 9% $\pm$ 7%; max 23%).
-It is worth noticing that all approaches had cases with no difference between options (Figure \@ref{fig:figaggpropcnhg}BC).
-
-```{r figaggpropcnhg, eval = F, echo = T, fig.width = 3, fig.height = 2, echo=FALSE, fig.cap= "Change in the proportion of the distribution today (2014-2019) relative to 1973-1985.
-A) row-wise showing seasonal changes, column-wise showing changes by spatial approach.
-B) Differnces between seasons for each spatial approach.
-C) Differences between spatial approaches for each season."}
-
-# Call the image
-img <- readPNG("/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F2_proportion_chng_agg.png")
-# Print the image
-grid.raster(img)
-```
-
-![Figure 2.
-Change in the proportion of the distribution today (2014-2019) relative to 1973-1985.
-A) row-wise showing seasonal changes, column-wise showing changes by spatial approach.
-B) Differnces between seasons for each spatial approach.
-C) Differences between spatial approaches for each season.](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F2_proportion_chng_agg.png)
-
-The historical proportion of State-shared aggregated biomass is sensitive to the spatial approach.
-When looking at the fishing ports apprach we can see that the main shifts in proportion are between northern and southern States (Figure \@ref{fig:figAggHist}- Fishing ports).
-While southern States like Virginia and North Carolina have lost substantial proportion of the shared biomass over time, northern states like Maine, New Hampshire and Massachusetts have stand to win.
-Changes in the biomass proportion of the in-between states are very subtle.
-Yet the State waters approach offers another picture.
-Here, there seems to be clear biomass proportion winners and losers over the last 40 years (Figure \@ref{fig:figAggHist}-State Waters).
-New Jersey, Delaware, Maryland, Virginia and North Carolina have all seen a constant decrease in the proportion of the shared biomass while States from New York to Maine have seen a year-by-year increase (Figure \@ref{fig:figAggHist}).
-
-```{r figAggHist, eval = F, echo = T, fig.width = 3, fig.height = 2, echo=FALSE, fig.cap = "Historical proportion of aggregated biomass per state and spatial approach.
-States organized latitudinally.
-Grey-white box showing the quota-based historical period"}
-
-# Call the image
-img <- readPNG("/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F3_area_plot_avg_agg_sptl.png")
-# Print the image
-grid.raster(img)
-```
-
-![Figure 3.
-Aggregated distribution proportion per state of Paralichthys dentatus, Stenotomus chrysops and Centropristis striata over time.
-Each color represent a State ordered latitudinal.
-Grey box represents the base-period used for the fisheries quota allocation ](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F3_area_plot_avg_agg_sptl.png)
 
@@
 Biomass increases are less clear.
-For black sea bass, biomass has increased from Maine all the way down to Rhode Island in the Fishing ports approach, and New York for the State waters approach.
-In the State waters approach the species has just recently "arrived" to Maine and New Hampshire waters (Figure \@ref{fig:figSppHist}- State waters).
-For scup, only Maine and New Hampshire seem to have gain biomass following the Fishing ports approach while the State waters approach resulted in gains for all States northern than New York.
+For black sea bass, biomass has increased from Maine all the way down to Rhode Island in the Fishing ports approach, and New York for the state waters approach.
+In the state waters approach the species has just recently "arrived" to Maine and New Hampshire waters (Figure \@ref{fig:figSppHist}- state waters).
+For scup, only Maine and New Hampshire seem to have gain biomass following the Fishing ports approach while the state waters approach resulted in gains for all States northern than New York.
 Similar to black sea bass, Virginia and North Carolina are the main biomass losers in both approaches.
@@
 Proportion of the distribution of Paralichthys dentatus, Stenotomus chrysops and Centropristis striata over time.
-Each color represent a State ordered latitudinal.
+Each color represent a state ordered latitudinal.
 Grey box represents the base-period used for the fisheries quota allocation ](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F4_area_plot_avg_spp_sptl.png)

### 2021-10-05 Scripts/spatial_analisis.Rmd
interpolation figure (i.e. figure 2)

@@
             ) %>%
-  filter(!is.na(spatial))
+  filter(!is.na(spatial)) %>% 
+  mutate(
+    season = ifelse(str_detect(region,"Spring"),"Spring","Fall")
+  )
 
@@
 unique(historic_spp$region)
-unique(historic_spp$region)
+unique(historic_spp$season)
 
@@
   ) %>% 
-  filter(!is.na(label),
-         region == "Northeast US Spring") %>% 
-  group_by(label,index,spp,lat,lon) %>% 
+  filter(!is.na(label)) %>% 
+  group_by(label,index,spp,season,lat,lon) %>% 
   summarise(mean_cpue = mean(value,na.rm=T)) %>% 
@@
   ) %>% 
-  filter(!is.na(label),
-         region == "Northeast US Spring") %>% 
-  group_by(spp,index) %>% 
+  filter(!is.na(label)) %>% 
+  group_by(spp,index,season) %>% 
   summarise(mean_cpue = mean(value,na.rm=T)) %>% 
-  group_by(spp) %>% 
+  group_by(spp,season) %>% 
   summarise(total_cpue = sum(mean_cpue, na.rm = T))
@@
   ) %>% 
-  group_by(spp,label) %>% 
+  group_by(spp,label,season) %>% 
   top_n(10,per_cpue) %>% 
-  group_by(spp,label) %>% 
+  group_by(spp,label,season) %>% 
   summarise(
@@
   )
+
+pal <- wes_palette("Zissou1",100,type = "continuous")
 
@@
               y = lat,
+              # fill = log10(mean_cpue),
+              # color = log10(mean_cpue)
               fill = mean_cpue,
@@
   #                                  hjust = 1) +
-  scale_fill_viridis("Mean\nInterpolation",
-                     limits = c(0,40)) +
-  scale_color_viridis("Mean\nInterpolation",
-                      limits = c(0,40)) +
-  facet_grid(spp~label) +
-  my_ggtheme_m(map_type = "na", leg_pos = "right",ax_tx_s = 7,ax_tl_s = 10,leg_tx_s = 10) #+
+  # Viridis option
+scale_fill_viridis("CPUE",
+                   limits = c(0,40),
+                   # limits = c(-5,1), # for log10
+                   direction = -1,
+                    end = 0.9
+                   ) +
+scale_color_viridis("CPUE",
+                    limits = c(0,40),
+                    # limits = c(-5,1), # for log10
+                    direction = -1,
+                    end = 0.9
+                    ) +
+# wes anderson option
+# scale_fill_gradientn("CPUE",
+#                      colours = pal,
+#                      limits = c(0,40) # For cpue
+#                      # limits = c(-5,1) # for log10
+#                      
+# ) +
+#   scale_color_gradientn("CPUE",
+#                         colours = pal,
+#                         limits = c(0,40) # for cpue
+#                         # limits = c(-5,1) # for log10
+#   ) +
+  facet_grid(spp~season+label) +
+  my_ggtheme_m(map_type = "na", leg_pos = "right",ax_tx_s = 7,ax_tl_s = 10,leg_tx_s = 12) #+
 # theme(legend.key.width = unit(3,"line"))
 
-ggsave("interpolation_fig.jpg",
+ggsave("interpolation_vi.jpg",
        inter_map,
        path = my_path("R","Figures"),
-       width = 6,
-       height = 6)
+       width = 9,
+       height = 7)
 ```

### 2021-10-05 Scripts/manuscript_acrossboundaries.Rmd
Included seasonality analysis and plot

@@
 
-<!-- ![Figure 1.
+![Figure 1.
 Spatial regions within the United States' North East Exclusive Economic Zone.
@@
 ME, Maine; NH, New Hampshire; MA, Massachusetts; RI, Rhode Island; CT, Connecticut; NY, New York; NY, New Jersey; DE, Delaware; MD, Maryland; VA Virginia; North Carolina.
-](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F1_buffer_figure.png) -->
+](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F1_buffer_figure.png)
 
-<!-- **[Add another paragraph here on how different the Spring vs. Fall distributions are]** -->
-The spatial distribution of the CPUE interpolation for each species varied by season (Figure \@ref{fig:figInterpolation}.
+Seasonality plays an important role in determine the spatial distribution of CPUE (Figure \@ref{fig:figInterpolation}.
+Specific latitudinal variations in the overall distribution is seen for all species.
+This is evident for scup, whose historical northern distribution limit varied from Massachusetts (latitude ~42.4) in spring to the northern coast of Maine (latitude ~44) in the fall.
+Such seasonality has shifted northward over the last couple of decades for both scup and black sea bass.
+For example, black sea bass has substantially expanded its range over the spring from and initial Northern limit at New Jersey (latitude ~$40.6^o$) to the border of Maine and New Hampshire (latitude ~$43^o$).
+In addition to presenting the larger latitudinal shift in CPUE centroid (i.e., the region with the highest CPUE) relative to the historical centroid, a $2.1^0$ shift in fall distribution).
+In the case of summer flounder, however, such latitudinal seasonality is less evident.
+Instead, interpolation results suggests a longitudinal (or depth) shift in the species range from a largely coastal concentration in the fall to a eastward shift in the spring.
+Such pattern seems to become even more pronounced in current spring distributions, realtive to historical levels.
 
-```{r figInterpolation, eval = F, echo = F}
+```{r figInterpolation, eval = F, echo = T, fig.width = 3, fig.height = 2, echo=FALSE, fig.cap="Interpolation results for all species and seasons.
+Scale showing Catch per Unit of Effort (CPUE) at a log 10 scale.
+White cross represents the species' centroid defined as the region with the largest CPUE.
+Grey regions represent no CPUE"}
 
+# Call the image
+img <- readPNG("/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F2_Interpolation.jpg")
+# Print the image
+grid.raster(img)
 ```
+
+![Figure 2.
+Interpolation results for all species and seasons.
+Scale showing Catch per Unit of Effort (CPUE) at a log 10 scale.
+White cross represents the species' centroid defined as the region with the largest CPUE.
+Grey regions represent no CPUE](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F2_Interpolation.jpg)
 

### 2021-10-05 Scripts/spatial_analisis.Rmd
Included seasonality analysis and plot

@@
 
+# Paper numbers
+
+# interpol_result %>% 
+#   filter(mean_cpue >0) %>% 
+#   View()
+
 # --------------------- #
@@
 
+# Paper numbers
+centroid_db %>% 
+  select(-lon) %>% 
+  spread(label,lat) %>% 
+  mutate(diff = Today-Reference) %>% 
+  View()
+
+# For alternative color pallet
 pal <- wes_palette("Zissou1",100,type = "continuous")
@@
        height = 7)
+
 ```

### 2021-10-05 Scripts/manuscript_acrossboundaries.Rmd
included alocation maps for spatial and season differences

--- 2021-10-05 Scripts/manuscript_acrossboundaries.Rmd
@@
 ME, Maine; NH, New Hampshire; MA, Massachusetts; RI, Rhode Island; CT, Connecticut; NY, New York; NY, New Jersey; DE, Delaware; MD, Maryland; VA Virginia; North Carolina.
-](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F1_buffer_figure.png) -->
+](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F1_buffer_figure.jpg)
 
-<!-- **[Add another paragraph here on how different the Spring vs. Fall distributions are]** -->
-The spatial distribution of the CPUE interpolation for each species varied by season (Figure \@ref{fig:figInterpolation}.
+Seasonality plays an important role in determine the distributional range of black sea bass, scup, and summer flounder (Figure \@ref{fig:figInterpolation}).
+Latitudinal variations in distributions are notable for scup, whose historical northern limit goes from Massachusetts (latitude ~42.4) in spring to the northern coast of Maine (latitude ~44) in the fall.
+Moreover both scup and black sea bass have expanded their distribution northward.
+For example, black sea bass Northern limit in spring expanded from New Jersey (latitude ~$40.6^o$) in the late 1980s to the border of Maine and New Hampshire (latitude ~$43^o$) in recent years.
+In addition, black sea bass centroid (i.e., the region with the highest CPUE) shifted $2.1$ degrees north since 1980, more than any of the three species.
+In the case of summer flounder, however, such latitudinal seasonality is less evident.
+Instead, the interpolation results suggests a longitudinal (or depth) expansion in the species range from a largely coastal concentration in the fall to an eastward shift in the spring.
+Such pattern seems to become even more pronounced in current spring conditions, relative to historical levels (Figure \@ref{fig:figInterpolation}).
 
-```{r figInterpolation, eval = F, echo = F}
+```{r figInterpolation, eval = F, echo = T, fig.width = 3, fig.height = 2, echo=FALSE, fig.cap="Interpolation results for all species and seasons.
+Scale showing Catch per Unit of Effort (CPUE) at a log 10 scale.
+White cross represents the species' centroid defined as the region with the largest CPUE.
+Grey regions represent no CPUE"}
 
+# Call the image
+img <- readPNG("/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F2_Interpolation.jpg")
+# Print the image
+grid.raster(img)
 ```
 
-Our results suggest that the current distribution of all three species has changed relative to 1980-2001 from North Carolina to Maine.
-Biomass has increased in average 30% $\pm$ 11% in Connecticut, Maine, Massachusetts, New hampshire, Rhode island relative to the historical proportion regardless of the season and the spatial approach.
-On the other hand, Delaware, Maryland, New jersey, New york, North carolina, and Virginia have seen an average biomass loss of 39% $\pm$ 29% relative to the historical proportion for all approaches and seasons (Supplement Table 1).
-Specific cases of no change exist for Connecticut and New Jersey in the fishing ports approach for Spring and Fall, respectiveley, and New York in all but the Spring-fishig ports approach.
+![Figure 2.
+Interpolation results for all species and seasons.
+Scale showing Catch per Unit of Effort (CPUE) at a log 10 scale.
+White cross represents the species' centroid defined as the region with the largest CPUE.
+Grey regions represent no CPUE](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F2_Interpolation.jpg)
 
-Differences in the intensity of change varies among spatial and seasonal estimations (Figure \@ref{fig:figaggpropcnhg}).
+We overlay the developed regulatory units with the interpolated CPUE of black sea bass, summer flounder and scup to estimate each state's proportion of the total CPUE (Figures \@ref{fig:figSpatialDiff}).
+Under the state waters approach, each state has a regulatory unit and thus captures a part of the CPUE of each species.
+However, under the fishing ports approach some states end up without regulatory units resulting in no CPUE.
+This is the case of Maine, New Hampshire and Connecticut.
+On the contrary, New Jersey and Virginia end up with the largest benefits of the fishing ports approach.
+There are very few cases where the spatial approach does not affect the CPUE proportion of each state (Delaware, Massachusetts and North Carolina for black sea bass, North Carolina for summer flounder and Maryland for scup).
 
-All three species show a reduction in biomass proportion for southern states (namely Virginia and North Carolina) with black sea bass and scup having the larger declines (Figure \@ref{fig:figSppHist}).
-Biomass increases are less clear.
-For black sea bass, biomass has increased from Maine all the way down to Rhode Island in the Fishing ports approach, and New York for the state waters approach.
-In the state waters approach the species has just recently "arrived" to Maine and New Hampshire waters (Figure \@ref{fig:figSppHist}- state waters).
-For scup, only Maine and New Hampshire seem to have gain biomass following the Fishing ports approach while the state waters approach resulted in gains for all States northern than New York.
-Similar to black sea bass, Virginia and North Carolina are the main biomass losers in both approaches.
-Finally, there does not appear to be clear evidence of shifts in biomass for summer flounder.
-Decreases are seen for Virginia and North Carolina for both approaches and increases for Maine and New Hampshire for the fishing ports approach, yet, these are almost imperceptible (Figure \@ref{fig:figSppHist}).
-
-```{r figSppHist, eval = F, echo = T, fig.width = 3, fig.height = 2, echo=FALSE, fig.cap = "Historical proportion of each species' biomass per state and spatial approach.
-States organized latitudinally.
-Grey-white box showing the quota-based historical period"}
+```{r figSpatialDiff, eval = F, echo = T, fig.width = 3, fig.height = 2, echo=FALSE, fig.cap = "Proportion of the Catch per Unit of Effort (CPUE) for each species by state undert two time periods.
+Top and middle rows represent the fishing port and state waters approach, respectiveley.
+Bottom row is the difference between each approach.
+All values in percentage"}
 
 # Call the image
-img <- readPNG("/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F4_area_plot_avg_spp_sptl.png")
+img <- readPNG("/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F3_proportion_chg.jpg")
+# Print the image
+grid.raster(img)
+```
+
+![Figure 3.
+Proportion of the Catch per Unit of Effort (CPUE) for each species by state undert two time periods.
+Top and middle rows represent the fishing port and state waters approach, respectiveley.
+Bottom row is the difference between each approach.
+All values in percentage.
+Differences in absolute values](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F3_proportion_chg.jpg)
+
+Seasonal differences are also evident, although smaller than regulatory unit differences, when estimate each state's CPUE proportion for all species (Figures \@ref{fig:figSeasonlDiff}).
+Here, half of the cases represent 1% or no seasonality difference like Connecticut's CPUE proportion of summer flounder.
+The largest difference are in the latitudinal extremes with Maine currently getting 4% more CPUE in the fall than in spring as opposite to Virginia who gets 4% more in the spring than in the fall.
+
+```{r figSeasonlDiff, eval = F, echo = T, fig.width = 3, fig.height = 2, echo=FALSE, fig.cap = "Proportion of the Catch per Unit of Effort (CPUE) for each species by state undert two time periods.
+Top and middle rows represent the fishing port and state waters approach, respectiveley.
+Bottom row is the difference between each approach.
+All values in percentage"}
+
+# Call the image
+img <- readPNG("/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/proportion_chg_seas.jpg")
 # Print the image
@@
 ![Figure 4.
-Proportion of the distribution of Paralichthys dentatus, Stenotomus chrysops and Centropristis striata over time.
-Each color represent a state ordered latitudinal.
-Grey box represents the base-period used for the fisheries quota allocation ](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F4_area_plot_avg_spp_sptl.png)
+Historical Catch Per Unit of Efort (CPUE) proportion of each species by season.
+Proportion presented in 10 years running mean percentage.
+States presented latitudinally from north to south.
+Differences in absolute values.
+](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/proportion_chg_seas.jpg)
+
+The proportion of the CPUE has increased for northern states
+
+```{r figAreaPlot, eval = F, echo = T, fig.width = 3, fig.height = 2, echo=FALSE, fig.cap = "Proportion of the Catch per Unit of Effort (CPUE) for each species by state undert two time periods.
+Top and middle rows represent the fishing port and state waters approach, respectiveley.
+Bottom row is the difference between each approach.
+All values in percentage"}
+
+# Call the image
+img <- readPNG("/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F4_area_plot_avg_spp_sptl.jpg")
+# Print the image
+grid.raster(img)
+```
+
+![Figure 5.
+Historical Catch Per Unit of Efort (CPUE) proportion of each species by spatial approach.
+Proportion presented in 10 years running mean percentage.
+States presented latitudinally from north to south ](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F4_area_plot_avg_spp_sptl.jpg)
 

### 2021-10-05 Scripts/spatial_analisis.Rmd
included alocation maps for spatial and season differences

@@
 
-#### 3.4 Paper plot; Buffer plot
+### Interpolation rutine
+
+In this step we [interpolate](https://swilke-geoscience.net/post/spatial_interpolation/) the survey data within the previously created grid following a Triangular Irregular Surface method.
+
+#### Functions needed
+
+We need to create a couple of functions to run the whole process
+
+##### Interpolation main fx (tis).
+
+This is the main function used to interpolate the data per year. It follows a Triangular Irregular Surface method using the `interp::interp()` function. If you want to see the function clic on `code`
+
+```{r interpol_function, eval = T, echo = T}
+
+tis <- function(input_data, grid, yr, taxa, reg){
+
+  # --------------- #
+  # Testing
+  # print(paste(yr))
+  # yr = 1976
+  # --------------- #
+
+  # Filter data
+  data <- input_data %>% 
+    filter(year == yr,
+           spp == taxa,
+           region == reg
+    ) %>% 
+    # Average duplicated hauls in the same spot
+    group_by(region,year,spp,lat,lon) %>%
+    summarise_at(vars(wtcpue),
+                 mean,na.rm = T)
+
+  # Only interpolate cases where there is more than 3 rows
+  # Marked by the function 
+    if(nrow(data) <= 3){
+      fit_tin <- tibble()
+    }else{
+
+      # Triangular Irregular Surface
+      fit_tin <- interp::interp( # using {interp}
+        x = data$lon,           # the function actually accepts coordinate vectors
+        y = data$lat,
+        z = data$wtcpue,
+        xo = grid$lon,     # here we already define the target grid
+        yo = grid$lat,
+        output = "points"
+      ) %>% 
+        bind_cols() %>% 
+        bind_cols(grid) %>%
+        mutate(year = yr,
+               region = reg,
+               spp = taxa) %>% 
+        select(index, 
+               # state,
+               year, region, spp, lon=x, lat=y, value = z)
+
+    }
+
+    return(fit_tin)
+}
+
+# Test me
+# Needs variables in Control panel
+# Test no data: "Alosa aestivalis", reg = "Northeast US Fall", yr = 1974 
+# tis(input_data = ocean_data, grid = grid_eez_df, taxa = "Illex illecebrosus", reg = "Northeast US Fall", yr = 1973)
+
+# lapply(years,tis,input_data = ocean_data, grid = grid_eez_df, taxa = "Illex illecebrosus", reg = regions[2])
+
+```
+
+##### Run function
+
+This is a sub-function that runs the `tis()` function by taxa and region. It saves the output as a .csv file for each species.
+
+```{r interpol_run_fun, eval = T, echo = T}
+
+run_tis <- function(input_data, grid, years, taxa, reg){
+
+  # Run tis for species and surveys
+  for(r in 1:2){
+
+    partial_df <- bind_rows(
+      lapply(years,tis,input_data = input_data, grid = grid, taxa = taxa, reg = reg[r])
+    )
+
+    if(r == 1){
+      historic_tif <- partial_df
+    }else{
+      historic_tif <- bind_rows(historic_tif,partial_df)
+    }
+
+  }
+
+  # ----------------------- #
+  # Save dataset per species
+  # ----------------------- #
+
+  # Set file name
+  name <- paste0("tif_",str_replace(taxa," ","_"),".csv")
+
+  complement <- paste0("Partial/Interpolation/")
+
+  # Set path name
+  save_path <- my_path("R",complement)
+
+  # Set complete path
+  save_name <- paste0(save_path,name)
+
+  # Create folder if it does not exist
+  if(file.exists(save_path) == F){
+    dir.create(save_path)
+  }
+
+  #  Save file
+  write_csv(historic_tif,save_name)
+
+  return_msg <- paste("Interpolation done for", taxa)
+
+  return(return_msg)
+
+}
+
+# Test me
+    # run_tis(input_data = ocean_data, grid = grid_eez_fp_df, taxa = "Centropristis striata", years = seq(1970,1980), reg = regions, method = "testa")
+
+```
+
+#### Survey data
+
+The interpolation was done with NOAA Northeast Fisheries Science Center Spring and Fall Bottom Trawl Surveys [data](https://www.fisheries.noaa.gov/region/new-england-mid-atlantic#science) provided by [Ocean adapt](https://oceanadapt.rutgers.edu/).
+Data was accessed trough the [Github](https://github.com/pinskylab/OceanAdapt).
+
+*In primary publications using data from the database, please cite Pinsky et al.
+2013.
+Marine taxa track local climate velocities.
+Science 341: 1239-1242 doi: 10.1126/science.1239352, as well as the original data sources.*
+
+- Using only the Northeast US Fall and Spring bottom trawl survey data for now
+
+##### Splitting up data
+
+- No part on spatial analysis. Can be ignored.
+
+This is just a sub-step to split up the data into single species files. This makes the app faster as it only needs to load species specific data, rather than all the data at de beginning.
+
+```{r dat_exploded, eval = F, echo = F, fig.width = 9}
+
+ocean_data <- readRDS("/Volumes/Enterprise/Data/pinskylab-OceanAdapt-966adf0/data_clean/dat_exploded.rds") #%>% 
+  # filter(spp == "Centropristis striata",
+       # region %in% c("Northeast US Fall" , "Northeast US Spring")) #No more seasons
+
+spp_data <- function(spp){
+
+  name_save <- paste0(my_path("D","Spp/Observation"),"obs_",str_replace(spp[1], " ", "_"),".csv")
+
+ocean_data %>% 
+  filter(spp == spp,
+       region %in% c("Northeast US Fall" , "Northeast US Spring")
+       ) %>% 
+  write_csv(., name_save)
+
+}
+
+spp_list <- ocean_data %>% 
+  filter(region %in% regions,
+         spp != "NA") %>% 
+  pull(spp) %>% 
+  unique()
+
+lapply(spp_list, spp_data)
+
+subset_data <- ocean_data %>% 
+  filter(spp == "Centropristis striata",
+       region %in% c("Northeast US Fall" , "Northeast US Spring")
+       )
+
+ggplot() +
+  geom_point(data = subset(subset_data, wtcpue = 0.0),
+             aes(
+               x = lon,
+               y = lat
+             ),
+             color = "grey95"
+  ) +
+  geom_point(data = subset(subset_data, wtcpue > 0),
+             aes(
+               x = lon,
+               y = lat,
+               color = log10(wtcpue)
+             ),
+             size = 1
+  ) +
+  scale_color_distiller(palette = "Spectral", 
+                        guide_legend(title = "WCPUE per Haul (log10)")) + 
+  coord_sf(xlim = c(-76, -65),ylim = c(35, 45)) +
+  MyFunctions::my_ggtheme_m() +
+  facet_wrap(~region)
+
+```
+
+#### Control Pannel
+
+This is where we load the required data and prepare to run the interpolation function. Note that some of the data here has been previously created
+
+```{r contro_pannel, eval = T, echo = T}
+
+# Load grid df
+# For fishing ports
+inter_grid <- my_path("D","Spatial","inter_grid_df.csv", read = T)
+
+# Run interpolation for all years
+years <- seq(1973,2019,1)
+
+# regions
+regions <- c("Northeast US Fall" , "Northeast US Spring")
+
+# species list
+spp <- ocean_data %>% 
+  filter(region %in% regions,
+         spp != "NA") %>% 
+  pull(spp) %>% 
+  unique()
+
+# Double check runs
+
+spp_runs <- tibble(taxa = (list.files(my_path("R","Partial/Interpolation/fp")))) %>%
+  mutate(
+    taxa = str_remove(taxa, "tif_"),
+    taxa = str_remove(taxa, ".csv"),
+    taxa = str_replace(taxa, "_", " ")
+  )
+
+# Missing runs
+spp <- tibble(taxa=spp) %>% 
+  anti_join(spp_runs) %>% 
+  pull(taxa)
+
+```
+
+#### Run routine
+
+Here we just run the routine for each of the species present in the Northeast US Fall and Spring surveys between 1973 and 2019.
+
+- Note there are 43 identified taxa
+- Some taxa do not have presence data in some years
+
+```{r run_routine, eval = T, echo = T}
+
+# # single species run
+run_tis(input_data = ocean_data,
+        grid = grid_eez_fp_df,
+        years = years,
+        reg = regions,
+        taxa = "Stenotomus chrysops",
+        method = "fp"
+)
+
+# Run them all in parallel
+lapply(Species,
+       run_tis, 
+       input_data = ocean_data,
+       grid = inter_grid,
+       years = years,
+       reg = regions
+)
+
+```
+
+# Results
+
+Results are now for eight species managed under Mid-Atlantic Council Management Plans according to [NOAA](https://www.fisheries.noaa.gov/new-england-mid-atlantic/commercial-fishing/new-england-mid-atlantic-fishery-management-plans).
+
+State allocations of the commercial black sea bass coastwide quota were originally implemented in 2003 as part of Amendment 13, loosely based on historical landings from 1980- 2001.
+
+*Scomber scombrus*, *Peprilus triacanthus* (butterfish), *Illex illecebrosus* (shortfin squid), *Paralichthys dentatus* (summer flounder), *Stenotomus chrysops* (Scoop), *Centropristis striata* (black sea bass), *Pomatomus saltatrix* (Bluefish), *Lopholatilus chamaeleonticeps* (Golden tilefish), *Caulolatilus microps* (blueline tilefish) and *Clupea harengus*
+
+```{r load_data, eval = T, echo = T}
+
+# Spatial data
+States <- c("maine", "new hampshire", "massachusetts", "connecticut", "rhode island", "new york", "new jersey", "delaware", "maryland", "virginia", "north carolina")
+
+# US State Map (land)
+land_sf <- st_as_sf(map("state", plot = FALSE, fill = TRUE)) %>% 
+  filter(ID %in% States) %>% 
+  mutate(abrev = c("CT","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VA"),
+         state = str_to_sentence(ID)
+         )
+
+# US EEZ map
+path_world <- my_path("G", extra_path = "Spatial/SAU/SAU_Shapefile", name = "SAUEEZ_July2015.shp")
+
+### Previouslly created grids
+
+grids <- my_path("D", "Spatial/grid_eez_fp_sf", name = "grid_eez_fp_df.csv", read = T) %>%
+  mutate(
+    spatial = "fp"
+  ) %>% 
+  bind_rows(
+    my_path("D", "Spatial/grid_eez_sw_sf", name = "grid_eez_sw_df.csv", read = T)
+  ) %>% 
+  select(-spp) %>% 
+  mutate(
+    spatial = ifelse(is.na(spatial),"sw",spatial)
+  ) %>% 
+  distinct(.keep_all = T)
+
+# Species data
+
+# Managed species by Mid-Atlantic Council Management Plans, and State waters
+# https://www.fisheries.noaa.gov/new-england-mid-atlantic/commercial-fishing/new-england-mid-atlantic-fishery-management-plans
+
+Species <- c(
+  "Paralichthys dentatus", #summer flounder
+  "Stenotomus chrysops", #Scup"
+  "Centropristis striata"#, # black sea bass
+  )
+
+spp_paths <- list.files(my_path("R",extra_path = "Partial/Interpolation/"))
+
+# Some gibiris for names
+taxon_list <- gsub("_"," ",spp_paths)
+taxon_list <- gsub("tif ","",taxon_list)
+taxon_list <- gsub(".csv","",taxon_list)
+
+taxon_list <- taxon_list[taxon_list %in% Species]
+
+# Now set a list of files to read
+taxon_read <- paste0("tif_",taxon_list,".csv")
+taxon_read <- gsub(" ","_",taxon_read)
+
+taxon_read <- spp_paths[spp_paths %in% taxon_read]
+
+#### Load sw interpolation
+
+taxon_sw <- my_path("R",extra_path = "Partial/Interpolation/", name = taxon_read)
+
+# Load all sp in one table
+historic_spp <- bind_rows(lapply(taxon_sw, fread)) %>% 
+  left_join(grids,
+            by = c("index","lon","lat")
+            ) %>%
+  filter(!is.na(spatial)) %>% 
+  mutate(
+    season = ifelse(str_detect(region,"Spring"),"Spring","Fall")
+  )
+
+# historic_spp %>% 
+#   filter(is.na(spatial)) %>% 
+#   filter(year == 1973,
+#          region == "Northeast US Fall") %>% 
+#   ggplot() +
+#     geom_tile(
+#       aes(
+#         x = lon,
+#         y = lat,
+#         fill = index
+#       )
+#     ) +
+#   facet_grid(spp~state) + 
+#   geom_sf(data = land_sf,aes()) +
+#   geom_sf(data = eez_sf, aes(), fill =NA)
+
+unique(historic_spp$spp)
+unique(historic_spp$region)
+unique(historic_spp$season)
+
+# Periods
+periods <-tibble(
+  order = c(rep("a",12),
+            rep("b",12),
+            rep("c",12),
+            rep("d",11)
+  ),
+  label = c(rep("1973-1984",12),
+            rep("1985-1996",12),
+            rep("1997-2008",12),
+            rep("2009-2019",11)
+  ),
+  year = c(seq(1973,1984,1),
+           seq(1985,1996,1),
+           seq(1997,2008,1),
+           seq(2009,2019,1)
+  )
+  )
+
+state_lat <- historic_spp %>%
+  group_by(state) %>% 
+  summarise(
+    order = mean(lat)
+  ) %>% 
+  filter(!is.na(state)) %>% 
+  mutate(abrev = c("CT","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VA")
+  ) %>% 
+  arrange(desc(order)) %>% 
+  mutate(lat = order,
+    # order = letters[1:11],
+    order = c("b","a",letters[3:11]),)
+
+# State pallet
+
+state_pallet <- c(wes_palette(n = 5, name = "Darjeeling1"),
+                               wes_palette(n = 5, name = "Darjeeling2"),
+                               # wes_palette(n = 2, name = "GrandBudapest1")
+                  "#FD6467"
+                  )
+
+# print for notebook
+head(historic_spp)
+```
+
+## Regulatory units result
 
@@
 
-![Buffer figure for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/buffer_figure_b.jpg)
-
-### Interpolation rutine
-
-In this step we [interpolate](https://swilke-geoscience.net/post/spatial_interpolation/) the survey data within the previously created grid following a Triangular Irregular Surface method.
-
-#### Functions needed
-
-We need to create a couple of functions to run the whole process
-
-##### Interpolation main fx (tis).
-
-This is the main function used to interpolate the data per year. It follows a Triangular Irregular Surface method using the `interp::interp()` function. If you want to see the function clic on `code`
-
-```{r interpol_function, eval = T, echo = T}
-
-tis <- function(input_data, grid, yr, taxa, reg){
-
-  # --------------- #
-  # Testing
-  # print(paste(yr))
-  # yr = 1976
-  # --------------- #
-
-  # Filter data
-  data <- input_data %>% 
-    filter(year == yr,
-           spp == taxa,
-           region == reg
-    ) %>% 
-    # Average duplicated hauls in the same spot
-    group_by(region,year,spp,lat,lon) %>%
-    summarise_at(vars(wtcpue),
-                 mean,na.rm = T)
-
-  # Only interpolate cases where there is more than 3 rows
-  # Marked by the function 
-    if(nrow(data) <= 3){
-      fit_tin <- tibble()
-    }else{
-
-      # Triangular Irregular Surface
-      fit_tin <- interp::interp( # using {interp}
-        x = data$lon,           # the function actually accepts coordinate vectors
-        y = data$lat,
-        z = data$wtcpue,
-        xo = grid$lon,     # here we already define the target grid
-        yo = grid$lat,
-        output = "points"
-      ) %>% 
-        bind_cols() %>% 
-        bind_cols(grid) %>%
-        mutate(year = yr,
-               region = reg,
-               spp = taxa) %>% 
-        select(index, 
-               # state,
-               year, region, spp, lon=x, lat=y, value = z)
-
-    }
-
-    return(fit_tin)
-}
-
-# Test me
-# Needs variables in Control panel
-# Test no data: "Alosa aestivalis", reg = "Northeast US Fall", yr = 1974 
-# tis(input_data = ocean_data, grid = grid_eez_df, taxa = "Illex illecebrosus", reg = "Northeast US Fall", yr = 1973)
-
-# lapply(years,tis,input_data = ocean_data, grid = grid_eez_df, taxa = "Illex illecebrosus", reg = regions[2])
-
-```
-
-##### Run function
-
-This is a sub-function that runs the `tis()` function by taxa and region. It saves the output as a .csv file for each species.
-
-```{r interpol_run_fun, eval = T, echo = T}
-
-run_tis <- function(input_data, grid, years, taxa, reg){
-
-  # Run tis for species and surveys
-  for(r in 1:2){
-
-    partial_df <- bind_rows(
-      lapply(years,tis,input_data = input_data, grid = grid, taxa = taxa, reg = reg[r])
-    )
-
-    if(r == 1){
-      historic_tif <- partial_df
-    }else{
-      historic_tif <- bind_rows(historic_tif,partial_df)
-    }
-
-  }
-
-  # ----------------------- #
-  # Save dataset per species
-  # ----------------------- #
-
-  # Set file name
-  name <- paste0("tif_",str_replace(taxa," ","_"),".csv")
-
-  complement <- paste0("Partial/Interpolation/")
-
-  # Set path name
-  save_path <- my_path("R",complement)
-
-  # Set complete path
-  save_name <- paste0(save_path,name)
-
-  # Create folder if it does not exist
-  if(file.exists(save_path) == F){
-    dir.create(save_path)
-  }
-
-  #  Save file
-  write_csv(historic_tif,save_name)
-
-  return_msg <- paste("Interpolation done for", taxa)
-
-  return(return_msg)
-
-}
-
-# Test me
-    # run_tis(input_data = ocean_data, grid = grid_eez_fp_df, taxa = "Centropristis striata", years = seq(1970,1980), reg = regions, method = "testa")
-
-```
-
-#### Survey data
-
-The interpolation was done with NOAA Northeast Fisheries Science Center Spring and Fall Bottom Trawl Surveys [data](https://www.fisheries.noaa.gov/region/new-england-mid-atlantic#science) provided by [Ocean adapt](https://oceanadapt.rutgers.edu/).
-Data was accessed trough the [Github](https://github.com/pinskylab/OceanAdapt).
-
-*In primary publications using data from the database, please cite Pinsky et al.
-2013.
-Marine taxa track local climate velocities.
-Science 341: 1239-1242 doi: 10.1126/science.1239352, as well as the original data sources.*
-
-- Using only the Northeast US Fall and Spring bottom trawl survey data for now
-
-##### Splitting up data
-
-- No part on spatial analysis. Can be ignored.
-
-This is just a sub-step to split up the data into single species files. This makes the app faster as it only needs to load species specific data, rather than all the data at de beginning.
-
-```{r dat_exploded, eval = F, echo = F, fig.width = 9}
-
-ocean_data <- readRDS("/Volumes/Enterprise/Data/pinskylab-OceanAdapt-966adf0/data_clean/dat_exploded.rds") #%>% 
-  # filter(spp == "Centropristis striata",
-       # region %in% c("Northeast US Fall" , "Northeast US Spring")) #No more seasons
-
-spp_data <- function(spp){
-
-  name_save <- paste0(my_path("D","Spp/Observation"),"obs_",str_replace(spp[1], " ", "_"),".csv")
-
-ocean_data %>% 
-  filter(spp == spp,
-       region %in% c("Northeast US Fall" , "Northeast US Spring")
-       ) %>% 
-  write_csv(., name_save)
-
-}
-
-spp_list <- ocean_data %>% 
-  filter(region %in% regions,
-         spp != "NA") %>% 
-  pull(spp) %>% 
-  unique()
-
-lapply(spp_list, spp_data)
-
-subset_data <- ocean_data %>% 
-  filter(spp == "Centropristis striata",
-       region %in% c("Northeast US Fall" , "Northeast US Spring")
-       )
-
-ggplot() +
-  geom_point(data = subset(subset_data, wtcpue = 0.0),
-             aes(
-               x = lon,
-               y = lat
-             ),
-             color = "grey95"
-  ) +
-  geom_point(data = subset(subset_data, wtcpue > 0),
-             aes(
-               x = lon,
-               y = lat,
-               color = log10(wtcpue)
-             ),
-             size = 1
-  ) +
-  scale_color_distiller(palette = "Spectral", 
-                        guide_legend(title = "WCPUE per Haul (log10)")) + 
-  coord_sf(xlim = c(-76, -65),ylim = c(35, 45)) +
-  MyFunctions::my_ggtheme_m() +
-  facet_wrap(~region)
-
-```
-
-#### Control Pannel
-
-This is where we load the required data and prepare to run the interpolation function. Note that some of the data here has been previously created
-
-```{r contro_pannel, eval = T, echo = T}
-
-# Load grid df
-# For fishing ports
-inter_grid <- my_path("D","Spatial","inter_grid_df.csv", read = T)
-
-# Run interpolation for all years
-years <- seq(1973,2019,1)
-
-# regions
-regions <- c("Northeast US Fall" , "Northeast US Spring")
-
-# species list
-spp <- ocean_data %>% 
-  filter(region %in% regions,
-         spp != "NA") %>% 
-  pull(spp) %>% 
-  unique()
-
-# Double check runs
-
-spp_runs <- tibble(taxa = (list.files(my_path("R","Partial/Interpolation/fp")))) %>%
-  mutate(
-    taxa = str_remove(taxa, "tif_"),
-    taxa = str_remove(taxa, ".csv"),
-    taxa = str_replace(taxa, "_", " ")
-  )
-
-# Missing runs
-spp <- tibble(taxa=spp) %>% 
-  anti_join(spp_runs) %>% 
-  pull(taxa)
-
-```
-
-#### Run routine
-
-Here we just run the routine for each of the species present in the Northeast US Fall and Spring surveys between 1973 and 2019.
-
-- Note there are 43 identified taxa
-- Some taxa do not have presence data in some years
-
-```{r run_routine, eval = T, echo = T}
-
-# # single species run
-run_tis(input_data = ocean_data,
-        grid = grid_eez_fp_df,
-        years = years,
-        reg = regions,
-        taxa = "Stenotomus chrysops",
-        method = "fp"
-)
-
-# Run them all in parallel
-lapply(Species,
-       run_tis, 
-       input_data = ocean_data,
-       grid = inter_grid,
-       years = years,
-       reg = regions
-)
-
-```
-
-# Results
-
-Results are now for eight species managed under Mid-Atlantic Council Management Plans according to [NOAA](https://www.fisheries.noaa.gov/new-england-mid-atlantic/commercial-fishing/new-england-mid-atlantic-fishery-management-plans).
-
-State allocations of the commercial black sea bass coastwide quota were originally implemented in 2003 as part of Amendment 13, loosely based on historical landings from 1980- 2001.
-
-*Scomber scombrus*, *Peprilus triacanthus* (butterfish), *Illex illecebrosus* (shortfin squid), *Paralichthys dentatus* (summer flounder), *Stenotomus chrysops* (Scoop), *Centropristis striata* (black sea bass), *Pomatomus saltatrix* (Bluefish), *Lopholatilus chamaeleonticeps* (Golden tilefish), *Caulolatilus microps* (blueline tilefish) and *Clupea harengus*
-
-```{r load_data, eval = T, echo = T}
-
-# Spatial data
-States <- c("maine", "new hampshire", "massachusetts", "connecticut", "rhode island", "new york", "new jersey", "delaware", "maryland", "virginia", "north carolina")
-
-# US State Map (land)
-land_sf <- st_as_sf(map("state", plot = FALSE, fill = TRUE)) %>% 
-  filter(ID %in% States) %>% 
-  mutate(abrev = c("CT","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VA"),
-         state = str_to_sentence(ID)
-         )
-
-### Previouslly created grids
-
-grids <- my_path("D", "Spatial/grid_eez_fp_sf", name = "grid_eez_fp_df.csv", read = T) %>%
-  mutate(
-    spatial = "fp"
-  ) %>% 
-  bind_rows(
-    my_path("D", "Spatial/grid_eez_sw_sf", name = "grid_eez_sw_df.csv", read = T)
-  ) %>% 
-  select(-spp) %>% 
-  mutate(
-    spatial = ifelse(is.na(spatial),"sw",spatial)
-  ) %>% 
-  distinct(.keep_all = T)
-
-# Species data
-
-# Managed species by Mid-Atlantic Council Management Plans, and State waters
-# https://www.fisheries.noaa.gov/new-england-mid-atlantic/commercial-fishing/new-england-mid-atlantic-fishery-management-plans
-
-Species <- c(
-  "Paralichthys dentatus", #summer flounder
-  "Stenotomus chrysops", #Scup"
-  "Centropristis striata"#, # black sea bass
-  )
-
-spp_paths <- list.files(my_path("R",extra_path = "Partial/Interpolation/"))
-
-# Some gibiris for names
-taxon_list <- gsub("_"," ",spp_paths)
-taxon_list <- gsub("tif ","",taxon_list)
-taxon_list <- gsub(".csv","",taxon_list)
-
-taxon_list <- taxon_list[taxon_list %in% Species]
-
-# Now set a list of files to read
-taxon_read <- paste0("tif_",taxon_list,".csv")
-taxon_read <- gsub(" ","_",taxon_read)
-
-taxon_read <- spp_paths[spp_paths %in% taxon_read]
-
-#### Load sw interpolation
-
-taxon_sw <- my_path("R",extra_path = "Partial/Interpolation/", name = taxon_read)
-
-# Load all sp in one table
-historic_spp <- bind_rows(lapply(taxon_sw, fread)) %>% 
-  left_join(grids,
-            by = c("index","lon","lat")
-            ) %>%
-  filter(!is.na(spatial)) %>% 
-  mutate(
-    season = ifelse(str_detect(region,"Spring"),"Spring","Fall")
-  )
-
-# historic_spp %>% 
-#   filter(is.na(spatial)) %>% 
-#   filter(year == 1973,
-#          region == "Northeast US Fall") %>% 
-#   ggplot() +
-#     geom_tile(
-#       aes(
-#         x = lon,
-#         y = lat,
-#         fill = index
-#       )
-#     ) +
-#   facet_grid(spp~state) + 
-#   geom_sf(data = land_sf,aes()) +
-#   geom_sf(data = eez_sf, aes(), fill =NA)
-
-unique(historic_spp$spp)
-unique(historic_spp$region)
-unique(historic_spp$season)
-
-# Periods
-periods <-tibble(
-  order = c(rep("a",12),
-            rep("b",12),
-            rep("c",12),
-            rep("d",11)
-  ),
-  label = c(rep("1973-1984",12),
-            rep("1985-1996",12),
-            rep("1997-2008",12),
-            rep("2009-2019",11)
-  ),
-  year = c(seq(1973,1984,1),
-           seq(1985,1996,1),
-           seq(1997,2008,1),
-           seq(2009,2019,1)
-  )
-  )
-
-state_lat <- historic_spp %>%
-  group_by(state) %>% 
-  summarise(
-    order = mean(lat)
-  ) %>% 
-  filter(!is.na(state)) %>% 
-  mutate(abrev = c("CT","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VA")
-  ) %>% 
-  arrange(desc(order)) %>% 
-  mutate(lat = order,
-    # order = letters[1:11],
-    order = c("b","a",letters[3:11]),)
-
-# State pallet
-
-state_pallet <- c(wes_palette(n = 5, name = "Darjeeling1"),
-                               wes_palette(n = 5, name = "Darjeeling2"),
-                               # wes_palette(n = 2, name = "GrandBudapest1")
-                  "#FD6467"
-                  )
-
-# print for notebook
-head(historic_spp)
-```
-
-# Interpolation result
+## Interpolation result
 
@@
 # Paper numbers
-centroid_db %>% 
-  select(-lon) %>% 
-  spread(label,lat) %>% 
-  mutate(diff = Today-Reference) %>% 
-  View()
+# centroid_db %>% 
+#   select(-lon) %>% 
+#   spread(label,lat) %>% 
+#   mutate(diff = Today-Reference) %>% 
+#   View()
 
@@
 
-### Dynamic figure: Aggregated Proportional change per survey
-
-```{r area_map_aggregated, eval = T, echo = T, fig.width = 10, fig.height=6}
+### Data preparation
+
+```{r paper_figure_area_map, eval = F, echo = T, results='hide'}
 
 total_fited <- historic_spp %>% 
-  group_by(year,region,spatial) %>% 
+  group_by(year,season,spp,spatial) %>% 
   summarise(total_value = sum(value,na.rm=T),.groups = "drop")
@@
 state_fit <- historic_spp %>% 
-  group_by(state,year,region,spatial) %>% 
-  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
-  left_join(total_fited,
-            by = c("year","region","spatial")) %>%
-  mutate(percentage = state_value/total_value*100) %>% 
-  left_join(periods,
-            by = "year") %>% 
-  group_by(state,order,label,region,spatial) %>% 
-  summarise(mean_per = round(mean(percentage)),.groups = "drop")
-
-# check percentages
-# state_fit %>% 
-#   group_by(period) %>% 
-#   summarise(sum(mean_per))
-
-p <- land_sf %>% 
-  left_join(state_fit,
-            by = "state") %>% 
-  ggplot() +
-  # geom_sf(aes(fill = mean_per)) +
-  geom_sf(aes(fill = mean_per, text = paste(state, mean_per,"% of proportion"))) +
-  viridis::scale_fill_viridis("Average proportion per State", alpha = 0.8) +
-  facet_wrap(~ region + label +spatial, 
-             nrow = 2) +
-  labs(x = "Latitude", 
-       y = "Longitude") +
-  my_ggtheme_p(facet_tx_s = 12,
-               leg_pos = "bottom") +
-  theme(legend.key.width = unit(1,"line")) +
-  theme_dark()
-
-ggplotly(p,
-         tooltip = "text",
-         dynamicTicks = FALSE) %>% 
-    style(hoverlabel = list(bgcolor = "white"), hoveron = "fill")
-
-```
-
-### Paper figure; Per species maps
-
-```{r paper_figure_area_map, eval = F, echo = T, results='hide'}
-
-total_fited <- historic_spp %>% 
-  group_by(year,region,spp,spatial) %>% 
-  summarise(total_value = sum(value,na.rm=T),.groups = "drop")
-
-state_fit <- historic_spp %>% 
-  group_by(state,year,region,spp,spatial) %>% 
+  group_by(state,year,season,spp,spatial) %>% 
   summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
@@
   left_join(total_fited,
-            by = c("year","region","spp","spatial")) %>%
+            by = c("year","season","spp","spatial")) %>%
   mutate(percentage = state_value/total_value*100,
@@
          ) %>% 
-  group_by(state,label,region,spp,spatial) %>% 
+  group_by(state,label,season,spp,spatial) %>% 
   summarise(mean_per = round(mean(percentage)),.groups = "drop") %>% 
   #Only show results for spring
-  filter(str_detect(region,"Spring"),
-         !is.na(label)) %>% 
+  filter(!is.na(label))
+
+```
+
+#### Regulatory units map
+
+```{r reg_unit_map_diff, eval = F, echo = T, results='hide'}
+
+reg_unit <- state_fit %>% 
+  filter(season == "Spring") %>% 
   spread(spatial,mean_per) %>% 
@@
   mutate(
-    # difference = ifelse(fp == 0,100, (fp-sw)/((fp+sw)/2)*100),
     difference = abs(fp-sw),
@@
 map_plot <- land_sf %>% 
-  left_join(state_fit,
+  left_join(reg_unit,
             by = "state") %>% 
@@
 diff_plot <- land_sf %>% 
-  left_join(state_fit,
+  left_join(reg_unit,
             by = "state") %>% 
@@
   path = my_path("R","Figures"),
-  "proportion_chg.jpg",
+  "proportion_chg_reg.jpg",
   p,
@@
 
-### Proportion change realtive to past
-
-```{r paper_figure_area_map, eval = F, echo = T, results='hide'}
-
-total_fited <- historic_spp %>%
-  group_by(year,region,spp,spatial) %>%
-  summarise(total_value = sum(value,na.rm=T),.groups = "drop")
-
-state_change <-historic_spp %>% 
-  group_by(state,year,region,spp,spatial) %>% 
-  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
-  left_join(total_fited,
-            by = c("year","region","spp","spatial")) %>%
-  mutate(percentage = state_value/total_value*100,
-         label = ifelse(year >= 1980 & year <= 2001,"Reference",
-                         ifelse(year > 2001,"Today",NA)
-                         )
-         ) %>% 
-  group_by(state,label,region,spp,spatial) %>% 
-  summarise(mean_per = round(mean(percentage)),.groups = "drop") %>% 
-  # Only show results for spring
-  filter(str_detect(region,"Spring"),
-         !is.na(label)
-         ) %>% 
-  select(-region) %>% 
-  spread(label,mean_per) %>% 
-  mutate(change = (Today-Reference)/(Today)*100,
-         change = ifelse(change > 100,100,
-                         ifelse(change < -100,-100,change)
-         )
-  ) %>%
-  select(-4,-5) %>% 
-  spread(spatial,change) %>% 
-  mutate(difference = (fp-sw)/((fp+sw)/2)*100,
-         difference = ifelse(difference > 100,100,
-                             ifelse(difference < -100,-100,difference)
-         )
-  ) %>% 
-  gather("spatial","mean_per",fp:difference) %>% 
+#### Seasonal units map
+
+```{r reg_unit_map_diff, eval = F, echo = T, results='hide'}
+
+# Get seasonal data
+season_fit <- state_fit %>% 
+  filter(spatial != "fp") %>% 
+  spread(season,mean_per) %>% 
   mutate(
-         spatial = ifelse(spatial == "fp","Fishing ports",
-                          ifelse(spatial == "sw","State Waters","Difference")
-         ),
-         mean_per= replace_na(mean_per,0)# for those 0/0
-  )
+    Difference = abs(Fall-Spring),
+    Difference = ifelse(Difference > 100,100,
+                        ifelse(Difference < -100,-100,Difference)
+    )
+  ) %>% 
+  gather("season","mean_per",Fall:Difference) %>% 
+  mutate(spp = gsub(" ","\n",spp))
 
 # The plot
-prop_chng_map <- land_sf %>% 
-  left_join(state_change,
+map_plot <- land_sf %>% 
+  left_join(season_fit,
             by = "state") %>% 
-  filter(spatial != "Difference") %>% 
+  filter(season != "Difference") %>% 
   ggplot() +
   geom_sf(aes(fill = mean_per)) +
-  viridis::scale_fill_viridis("Change in proportion today\nrelative to 1980-2001\n(%)", alpha = 0.8,
-                              limits = c(-100,100),
-                              breaks = seq(-100,100,25),
-                              labels = c("<-100",seq(-75,75,25),">100")
-                              ) +
-  facet_grid(spatial~ spp) +
+  viridis::scale_fill_viridis("Average proportion per State", alpha = 0.8, 
+                              breaks = seq(0,15,5),
+                              limits=(c(0,15))
+                              )+
+  facet_grid(season~ spp+label) +
+  labs(x = "", 
+       y = "") +
+  my_ggtheme_p(facet_tx_s = 20,
+               leg_pos = "bottom",
+               axx_tx_ang = 45,
+               ax_tx_s = 12,
+               ax_tl_s = 18,
+               hjust = 1) +
+  theme(legend.key.width = unit(4,"line"))
+
+diff_plot <- land_sf %>% 
+  left_join(season_fit,
+            by = "state") %>% 
+  filter(season == "Difference") %>% 
+  ggplot() +
+  geom_sf(aes(fill = mean_per)) +
+  viridis::scale_fill_viridis("Difference (%)", alpha = 0.8,option = "C",
+                              breaks = seq(0,5,1),
+                              limits=(c(0,5)),
+                              # labels = c("<-10",seq(-75,75,25),">100")
+                              ) +
+  facet_grid(season~ spp+label) +
   labs(x = "", 
@@
   theme(legend.key.width = unit(4,"line"),
-        legend.title.align=0.5)
-
-# ggsave(filename = "temp_proportion_chng.jpg",
-#          plot = prop_chng_map,
-#          path = my_path("R","Figures"),
-#          width = 10,
-#          height = 10
-#   )
-
-#### Option with differences
-
-prop_chng_map_diff <- land_sf %>% 
-  left_join(state_change,
-            by = "state") %>% 
-  filter(spatial == "Difference") %>% 
-  ggplot() +
-  geom_sf(aes(fill = mean_per)) +
-  viridis::scale_fill_viridis("Change in proportion today\nrelative to 1980-2001\n(%)", alpha = 0.8,
-                              option = "C"
-                              limits = c(-100,100),
-                              breaks = seq(-100,100,25),
-                              labels = c("<-100",seq(-75,75,25),">100")
-                              ) +
-  facet_grid(spatial~ spp) +
-  labs(x = "", 
-       y = "") +
-  my_ggtheme_p(facet_tx_s = 20,
-               leg_pos = "bottom",
-               axx_tx_ang = 45,
-               ax_tx_s = 12,
-               ax_tl_s = 18,
-               hjust = 1) +
-  theme(legend.key.width = unit(4,"line"),
-        legend.title.align=0.5,
         strip.background = element_blank(),
-        strip.text.x = element_blank())
+        strip.text.x = element_blank()
+        )
 
@@
   # Revenue circular
-  draw_plot(prop_chng_map, x = 0, y = 0.25, width = 1, height = 0.65) +
+  draw_plot(map_plot, x = 0, y = 0.2, width = 1, height = 0.8) +
   # Catch circular
-  draw_plot(prop_chng_map_diff, x = 0.101, y = 0, width = 0.798, height = 0.4) +
+  draw_plot(diff_plot, x = 0, y = 0, width = 1, height = 0.4) +
   draw_plot_label(label = c("Latitude", "Longitude"), 
-                  size = 16,
+                  size = 18,
                   angle = c(90,0),
-                  x = c(0.1,0.45), 
-                  y = c(0.45,0.11)
+                  x = c(0,0.45), 
+                  y = c(0.45,0.15)
   )
@@
   path = my_path("R","Figures"),
-  "proportion_chg_diffN.jpg",
+  "proportion_chg_seas_.jpg",
   p,
@@
 ```
-
-![Proportion change per species map for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/temp_proportion_chng.jpg)
-
-### Aggregated Proportional change
-
-```{r area_map_aggregated_formans, eval = T, echo = T, fig.width = 10, fig.height=6}
-
-total_fited <- historic_spp %>%
-  group_by(year,region,spatial) %>%
-  summarise(total_value = sum(value,na.rm=T),.groups = "drop")
-
-state_change <- historic_spp %>% 
-  group_by(state,year,region,spatial) %>% 
-  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
-  left_join(total_fited,
-            by = c("year","region","spatial")) %>%
-  mutate(percentage = state_value/total_value*100,
-         label = ifelse(year >= 1980 & year <= 2001,"reference",
-                         ifelse(year > 2001,"today",NA)
-                         )
-         ) %>% 
-  # left_join(periods,
-            # by = "year") %>% 
-  group_by(state,label,region,spatial) %>% 
-  summarise(mean_per = round(mean(percentage)),.groups = "drop") %>% 
-  #Only show results for spring
-  filter(#str_detect(region,"Spring"),
-         !is.na(label)
-         ) %>% 
-  # select(-region) %>% 
-  # Estimate percentage change
-  spread(label,mean_per) %>% 
-  mutate(raw_change = (today-reference)/(today)*100,
-         change = ifelse(raw_change > 100,100,
-                         ifelse(raw_change < -100,-100,raw_change)
-         )
-  ) %>%
-  select(-reference,-today)
-
-#### Average
-state_change %>% 
-  mutate(
-    wl = ifelse(change < 0, "L",
-                ifelse(change == 0, "NC","W"))
-  ) %>% 
-  # View()
-  # group_by(wl) %>% 
-  group_by(region,spatial,wl) %>% 
-  summarise(
-    states = paste(unique(state),collapse = ", "),
-    mean(raw_change),
-    sd(raw_change)
-  ) %>% 
-  write_csv("../Results/state_relative_chng.csv")
-  View()
-
-  # Estimate spatial differences in percentage change
-spatial_diff <- state_change %>% 
-  spread(spatial,change) %>% 
-  mutate(spatial_diff = abs(fp-sw)) %>% 
-  select(state, category = region, diff = spatial_diff)
-
-# Estimate seasonal differences in percentage change
-season_diff <- state_change %>% 
-  spread(region,change) %>%  
-  mutate(season_diff = abs(`Northeast US Fall`-`Northeast US Spring`)) %>% 
-  select(state,category = spatial,diff = season_diff)
-
-differences <- season_diff %>% 
-  bind_rows(spatial_diff) %>% 
-  mutate(
-    label = ifelse(category == "fp","Fishing ports",
-                          ifelse(category == "sw","State Waters",category)
-         )
-  )
-
-# For in text differences
-differences %>% 
-  group_by(category) %>%
-  summarise_at(vars(diff),
-    c(mean = mean,
-      sd =sd,
-      min = min,
-      max= max))
-
-# The main plot
-prop_chng_map <- land_sf %>% 
-  left_join(state_change,
-            by = "state") %>% 
-  # filter(spatial != "Difference" & cat != "difference_reg") %>% 
-  ggplot() +
-  geom_sf(aes(fill = change)) +
-  viridis::scale_fill_viridis("Change in proportion today\n relative to 1973-1984\n(%)", alpha = 0.8,
-                              limits = c(-100,100),
-                              breaks = seq(-100,100,25),
-                              labels = c(seq(-100,75,25),">100")
-                              ) +
-  facet_grid(spatial~ region) +
-  labs(x = "", 
-       y = "") +
-  my_ggtheme_p(facet_tx_s = 20,
-               leg_pos = "bottom",
-               axx_tx_ang = 45,
-               ax_tx_s = 12,
-               ax_tl_s = 18,
-               hjust = 1) +
-  theme(legend.key.width = unit(4,"line"),
-        legend.title.align=0.5,
-        strip.text.y = element_blank(),
-        strip.background = element_blank(),
-        )
-
-ggsave(filename = "proportion_chng_agg.png",
-         plot = prop_chng_map,
-         path = my_path("R","Figures"),
-         width = 10,
-         height = 10
-  )
-
-#### Option with differences
-
-# Season differencce
-
-spat_diff <- land_sf %>% 
-  left_join(differences,
-            by = "state") %>% 
-  filter(!category %in% c("fp","sw")) %>% 
-  ggplot() +
-  geom_sf(aes(fill = diff)) +
-  viridis::scale_fill_viridis("Differences", 
-                              alpha = 0.8,
-                              option = "C",
-                              limits = c(0,50),
-                              breaks = seq(0,50,10)
-                              ) +
-  facet_wrap(~ label,
-             ncol = 2) +
-  labs(x = "", 
-       y = "") +
-  my_ggtheme_p(facet_tx_s = 20,
-               leg_pos = "bottom",
-               axx_tx_ang = 45,
-               ax_tx_s = 12,
-               ax_tl_s = 18,
-               hjust = 1) +
-  theme(legend.key.width = unit(4,"line"),
-        legend.title.align=0.5,
-        strip.background = element_blank(),
-        strip.text.x = element_blank())
-
-ggsave(filename = "spat_diff.png",
-         plot = spat_diff,
-         path = my_path("R","Figures"),
-         width = 8,
-         height = 6
-  )
-
-# seasonal
-seas_diff <- land_sf %>% 
-  left_join(differences,
-            by = "state") %>% 
-  filter(category %in% c("fp","sw")) %>% 
-  ggplot() +
-  geom_sf(aes(fill = diff)) +
-  viridis::scale_fill_viridis("Differences", 
-                              alpha = 0.8,
-                              option = "C",
-                              limits = c(0,50),
-                              breaks = seq(0,50,10)
-                              ) +
-  facet_wrap(~ label,
-             ncol = 1,
-             strip.position="right") +
-  labs(x = "", 
-       y = "") +
-  my_ggtheme_p(facet_tx_s = 20,
-               leg_pos = "",
-               axx_tx_ang = 45,
-               ax_tx_s = 12,
-               ax_tl_s = 18,
-               hjust = 1) +
-  theme(strip.background = element_blank(),
-        # strip.text.x = element_blank(),
-        axis.text.y = element_blank(),
-        axis.line.y = element_blank()
-        )
-
-ggsave(filename = "seas_diff.png",
-         plot = seas_diff,
-         path = my_path("R","Figures"),
-         width = 8,
-         height = 6
-  )
-
-```
-
-![Proportion change aggregated all species map for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/proportion_chg_agg.jpg)
 
@@
 ```
+
+### Dynamic figure: Aggregated Proportional change per survey
+
+```{r area_map_aggregated, eval = T, echo = T, fig.width = 10, fig.height=6}
+
+total_fited <- historic_spp %>% 
+  group_by(year,region,spatial) %>% 
+  summarise(total_value = sum(value,na.rm=T),.groups = "drop")
+
+state_fit <- historic_spp %>% 
+  group_by(state,year,region,spatial) %>% 
+  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
+  left_join(total_fited,
+            by = c("year","region","spatial")) %>%
+  mutate(percentage = state_value/total_value*100) %>% 
+  left_join(periods,
+            by = "year") %>% 
+  group_by(state,order,label,region,spatial) %>% 
+  summarise(mean_per = round(mean(percentage)),.groups = "drop")
+
+# check percentages
+# state_fit %>% 
+#   group_by(period) %>% 
+#   summarise(sum(mean_per))
+
+p <- land_sf %>% 
+  left_join(state_fit,
+            by = "state") %>% 
+  ggplot() +
+  # geom_sf(aes(fill = mean_per)) +
+  geom_sf(aes(fill = mean_per, text = paste(state, mean_per,"% of proportion"))) +
+  viridis::scale_fill_viridis("Average proportion per State", alpha = 0.8) +
+  facet_wrap(~ region + label +spatial, 
+             nrow = 2) +
+  labs(x = "Latitude", 
+       y = "Longitude") +
+  my_ggtheme_p(facet_tx_s = 12,
+               leg_pos = "bottom") +
+  theme(legend.key.width = unit(1,"line")) +
+  theme_dark()
+
+ggplotly(p,
+         tooltip = "text",
+         dynamicTicks = FALSE) %>% 
+    style(hoverlabel = list(bgcolor = "white"), hoveron = "fill")
+
+```
+
+```{r paper_figure_area_map, eval = F, echo = T, results='hide'}
+
+total_fited <- historic_spp %>%
+  group_by(year,region,spp,spatial) %>%
+  summarise(total_value = sum(value,na.rm=T),.groups = "drop")
+
+state_change <-historic_spp %>% 
+  group_by(state,year,region,spp,spatial) %>% 
+  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
+  left_join(total_fited,
+            by = c("year","region","spp","spatial")) %>%
+  mutate(percentage = state_value/total_value*100,
+         label = ifelse(year >= 1980 & year <= 2001,"Reference",
+                         ifelse(year > 2001,"Today",NA)
+                         )
+         ) %>% 
+  group_by(state,label,region,spp,spatial) %>% 
+  summarise(mean_per = round(mean(percentage)),.groups = "drop") %>% 
+  # Only show results for spring
+  filter(str_detect(region,"Spring"),
+         !is.na(label)
+         ) %>% 
+  select(-region) %>% 
+  spread(label,mean_per) %>% 
+  mutate(change = (Today-Reference)/(Today)*100,
+         change = ifelse(change > 100,100,
+                         ifelse(change < -100,-100,change)
+         )
+  ) %>%
+  select(-4,-5) %>% 
+  spread(spatial,change) %>% 
+  mutate(
+    #difference = (fp-sw)/((fp+sw)/2)*100,
+    difference = abs(fp-sw)#,
+         # difference = ifelse(difference > 100,100,
+         #                     ifelse(difference < -100,-100,difference)
+         # )
+  ) %>% 
+  gather("spatial","mean_per",fp:difference) %>% 
+  mutate(
+         spatial = ifelse(spatial == "fp","Fishing ports",
+                          ifelse(spatial == "sw","State Waters","Difference")
+         ),
+         mean_per= replace_na(mean_per,0)# for those 0/0
+  )
+
+# The plot
+prop_chng_map <- land_sf %>% 
+  left_join(state_change,
+            by = "state") %>% 
+  filter(spatial != "Difference") %>% 
+  ggplot() +
+  geom_sf(aes(fill = mean_per)) +
+  viridis::scale_fill_viridis("Change in proportion today\nrelative to 1980-2001\n(%)", alpha = 0.8,
+                              limits = c(-100,100),
+                              breaks = seq(-100,100,25),
+                              labels = c("<-100",seq(-75,75,25),">100")
+                              ) +
+  facet_grid(spatial~ spp) +
+  labs(x = "", 
+       y = "") +
+  my_ggtheme_p(facet_tx_s = 20,
+               leg_pos = "bottom",
+               axx_tx_ang = 45,
+               ax_tx_s = 12,
+               ax_tl_s = 18,
+               hjust = 1) +
+  theme(legend.key.width = unit(4,"line"),
+        legend.title.align=0.5)
+
+# ggsave(filename = "temp_proportion_chng.jpg",
+#          plot = prop_chng_map,
+#          path = my_path("R","Figures"),
+#          width = 10,
+#          height = 10
+#   )
+
+#### Option with differences
+
+prop_chng_map_diff <- land_sf %>% 
+  left_join(state_change,
+            by = "state") %>% 
+  filter(spatial == "Difference") %>% 
+  ggplot() +
+  geom_sf(aes(fill = mean_per)) +
+  viridis::scale_fill_viridis("Change in proportion today\nrelative to 1980-2001\n(%)", alpha = 0.8,
+                              option = "C"
+                              limits = c(-100,100),
+                              breaks = seq(-100,100,25),
+                              labels = c("<-100",seq(-75,75,25),">100")
+                              ) +
+  facet_grid(spatial~ spp) +
+  labs(x = "", 
+       y = "") +
+  my_ggtheme_p(facet_tx_s = 20,
+               leg_pos = "bottom",
+               axx_tx_ang = 45,
+               ax_tx_s = 12,
+               ax_tl_s = 18,
+               hjust = 1) +
+  theme(legend.key.width = unit(4,"line"),
+        legend.title.align=0.5,
+        strip.background = element_blank(),
+        strip.text.x = element_blank())
+
+# Cowplot option
+p <- ggdraw() +
+  # Revenue circular
+  draw_plot(prop_chng_map, x = 0, y = 0.25, width = 1, height = 0.65) +
+  # Catch circular
+  draw_plot(prop_chng_map_diff, x = 0.101, y = 0, width = 0.798, height = 0.4) +
+  draw_plot_label(label = c("Latitude", "Longitude"), 
+                  size = 16,
+                  angle = c(90,0),
+                  x = c(0.1,0.45), 
+                  y = c(0.45,0.11)
+  )
+
+save_plot(
+  path = my_path("R","Figures"),
+  "proportion_chg_diffN.jpg",
+  p,
+  base_height = 14,
+  base_width = 14
+)
+
+```
+
+### Proportion change realtive to past
+
+```{r paper_figure_area_map, eval = F, echo = T, results='hide'}
+
+total_fited <- historic_spp %>%
+  group_by(year,season,spp,spatial) %>%
+  summarise(total_value = sum(value,na.rm=T),.groups = "drop")
+
+state_change <-historic_spp %>% 
+  group_by(state,year,season,spp,spatial) %>% 
+  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
+  left_join(total_fited,
+            by = c("year","region","spp","spatial")) %>%
+  mutate(percentage = state_value/total_value*100,
+         label = ifelse(year >= 1980 & year <= 2001,"Reference",
+                         ifelse(year > 2001,"Today",NA)
+                         )
+         ) %>% 
+  group_by(state,label,region,spp,spatial) %>% 
+  summarise(mean_per = round(mean(percentage)),.groups = "drop") %>% 
+  # Only show results for spring
+  filter(str_detect(region,"Spring"),
+         !is.na(label)
+         ) %>% 
+  select(-region) %>% 
+  spread(label,mean_per) %>% 
+  mutate(change = (Today-Reference)/(Today)*100,
+         change = ifelse(change > 100,100,
+                         ifelse(change < -100,-100,change)
+         )
+  ) %>%
+  select(-4,-5) %>% 
+  spread(spatial,change) %>% 
+  mutate(
+    #difference = (fp-sw)/((fp+sw)/2)*100,
+    difference = abs(fp-sw)#,
+         # difference = ifelse(difference > 100,100,
+         #                     ifelse(difference < -100,-100,difference)
+         # )
+  ) %>% 
+  gather("spatial","mean_per",fp:difference) %>% 
+  mutate(
+         spatial = ifelse(spatial == "fp","Fishing ports",
+                          ifelse(spatial == "sw","State Waters","Difference")
+         ),
+         mean_per= replace_na(mean_per,0)# for those 0/0
+  )
+
+# The plot
+prop_chng_map <- land_sf %>% 
+  left_join(state_change,
+            by = "state") %>% 
+  filter(spatial != "Difference") %>% 
+  ggplot() +
+  geom_sf(aes(fill = mean_per)) +
+  viridis::scale_fill_viridis("Change in proportion today\nrelative to 1980-2001\n(%)", alpha = 0.8,
+                              limits = c(-100,100),
+                              breaks = seq(-100,100,25),
+                              labels = c("<-100",seq(-75,75,25),">100")
+                              ) +
+  facet_grid(spatial~ spp) +
+  labs(x = "", 
+       y = "") +
+  my_ggtheme_p(facet_tx_s = 20,
+               leg_pos = "bottom",
+               axx_tx_ang = 45,
+               ax_tx_s = 12,
+               ax_tl_s = 18,
+               hjust = 1) +
+  theme(legend.key.width = unit(4,"line"),
+        legend.title.align=0.5)
+
+# ggsave(filename = "temp_proportion_chng.jpg",
+#          plot = prop_chng_map,
+#          path = my_path("R","Figures"),
+#          width = 10,
+#          height = 10
+#   )
+
+#### Option with differences
+
+prop_chng_map_diff <- land_sf %>% 
+  left_join(state_change,
+            by = "state") %>% 
+  filter(spatial == "Difference") %>% 
+  ggplot() +
+  geom_sf(aes(fill = mean_per)) +
+  viridis::scale_fill_viridis("Change in proportion today\nrelative to 1980-2001\n(%)", alpha = 0.8,
+                              option = "C"
+                              limits = c(-100,100),
+                              breaks = seq(-100,100,25),
+                              labels = c("<-100",seq(-75,75,25),">100")
+                              ) +
+  facet_grid(spatial~ spp) +
+  labs(x = "", 
+       y = "") +
+  my_ggtheme_p(facet_tx_s = 20,
+               leg_pos = "bottom",
+               axx_tx_ang = 45,
+               ax_tx_s = 12,
+               ax_tl_s = 18,
+               hjust = 1) +
+  theme(legend.key.width = unit(4,"line"),
+        legend.title.align=0.5,
+        strip.background = element_blank(),
+        strip.text.x = element_blank())
+
+# Cowplot option
+p <- ggdraw() +
+  # Revenue circular
+  draw_plot(prop_chng_map, x = 0, y = 0.25, width = 1, height = 0.65) +
+  # Catch circular
+  draw_plot(prop_chng_map_diff, x = 0.101, y = 0, width = 0.798, height = 0.4) +
+  draw_plot_label(label = c("Latitude", "Longitude"), 
+                  size = 16,
+                  angle = c(90,0),
+                  x = c(0.1,0.45), 
+                  y = c(0.45,0.11)
+  )
+
+save_plot(
+  path = my_path("R","Figures"),
+  "proportion_chg_diffN.jpg",
+  p,
+  base_height = 14,
+  base_width = 14
+)
+
+```
+
+![Proportion change per species map for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/temp_proportion_chng.jpg)
+
+### Aggregated Proportional change
+
+```{r area_map_aggregated_formans, eval = T, echo = T, fig.width = 10, fig.height=6}
+
+total_fited <- historic_spp %>%
+  group_by(year,region,spatial) %>%
+  summarise(total_value = sum(value,na.rm=T),.groups = "drop")
+
+state_change <- historic_spp %>% 
+  group_by(state,year,region,spatial) %>% 
+  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
+  left_join(total_fited,
+            by = c("year","region","spatial")) %>%
+  mutate(percentage = state_value/total_value*100,
+         label = ifelse(year >= 1980 & year <= 2001,"reference",
+                         ifelse(year > 2001,"today",NA)
+                         )
+         ) %>% 
+  # left_join(periods,
+            # by = "year") %>% 
+  group_by(state,label,region,spatial) %>% 
+  summarise(mean_per = round(mean(percentage)),.groups = "drop") %>% 
+  #Only show results for spring
+  filter(#str_detect(region,"Spring"),
+         !is.na(label)
+         ) %>% 
+  # select(-region) %>% 
+  # Estimate percentage change
+  spread(label,mean_per) %>% 
+  mutate(raw_change = (today-reference)/(today)*100,
+         change = ifelse(raw_change > 100,100,
+                         ifelse(raw_change < -100,-100,raw_change)
+         )
+  ) %>%
+  select(-reference,-today)
+
+#### Average
+state_change %>% 
+  mutate(
+    wl = ifelse(change < 0, "L",
+                ifelse(change == 0, "NC","W"))
+  ) %>% 
+  # View()
+  # group_by(wl) %>% 
+  group_by(region,spatial,wl) %>% 
+  summarise(
+    states = paste(unique(state),collapse = ", "),
+    mean(raw_change),
+    sd(raw_change)
+  ) %>% 
+  write_csv("../Results/state_relative_chng.csv")
+  View()
+
+  # Estimate spatial differences in percentage change
+spatial_diff <- state_change %>% 
+  spread(spatial,change) %>% 
+  mutate(spatial_diff = abs(fp-sw)) %>% 
+  select(state, category = region, diff = spatial_diff)
+
+# Estimate seasonal differences in percentage change
+season_diff <- state_change %>% 
+  spread(region,change) %>%  
+  mutate(season_diff = abs(`Northeast US Fall`-`Northeast US Spring`)) %>% 
+  select(state,category = spatial,diff = season_diff)
+
+differences <- season_diff %>% 
+  bind_rows(spatial_diff) %>% 
+  mutate(
+    label = ifelse(category == "fp","Fishing ports",
+                          ifelse(category == "sw","State Waters",category)
+         )
+  )
+
+# For in text differences
+differences %>% 
+  group_by(category) %>%
+  summarise_at(vars(diff),
+    c(mean = mean,
+      sd =sd,
+      min = min,
+      max= max))
+
+# The main plot
+prop_chng_map <- land_sf %>% 
+  left_join(state_change,
+            by = "state") %>% 
+  # filter(spatial != "Difference" & cat != "difference_reg") %>% 
+  ggplot() +
+  geom_sf(aes(fill = change)) +
+  viridis::scale_fill_viridis("Change in proportion today\n relative to 1973-1984\n(%)", alpha = 0.8,
+                              limits = c(-100,100),
+                              breaks = seq(-100,100,25),
+                              labels = c(seq(-100,75,25),">100")
+                              ) +
+  facet_grid(spatial~ region) +
+  labs(x = "", 
+       y = "") +
+  my_ggtheme_p(facet_tx_s = 20,
+               leg_pos = "bottom",
+               axx_tx_ang = 45,
+               ax_tx_s = 12,
+               ax_tl_s = 18,
+               hjust = 1) +
+  theme(legend.key.width = unit(4,"line"),
+        legend.title.align=0.5,
+        strip.text.y = element_blank(),
+        strip.background = element_blank(),
+        )
+
+ggsave(filename = "proportion_chng_agg.png",
+         plot = prop_chng_map,
+         path = my_path("R","Figures"),
+         width = 10,
+         height = 10
+  )
+
+#### Option with differences
+
+# Season differencce
+
+spat_diff <- land_sf %>% 
+  left_join(differences,
+            by = "state") %>% 
+  filter(!category %in% c("fp","sw")) %>% 
+  ggplot() +
+  geom_sf(aes(fill = diff)) +
+  viridis::scale_fill_viridis("Differences", 
+                              alpha = 0.8,
+                              option = "C",
+                              limits = c(0,50),
+                              breaks = seq(0,50,10)
+                              ) +
+  facet_wrap(~ label,
+             ncol = 2) +
+  labs(x = "", 
+       y = "") +
+  my_ggtheme_p(facet_tx_s = 20,
+               leg_pos = "bottom",
+               axx_tx_ang = 45,
+               ax_tx_s = 12,
+               ax_tl_s = 18,
+               hjust = 1) +
+  theme(legend.key.width = unit(4,"line"),
+        legend.title.align=0.5,
+        strip.background = element_blank(),
+        strip.text.x = element_blank())
+
+ggsave(filename = "spat_diff.png",
+         plot = spat_diff,
+         path = my_path("R","Figures"),
+         width = 8,
+         height = 6
+  )
+
+# seasonal
+seas_diff <- land_sf %>% 
+  left_join(differences,
+            by = "state") %>% 
+  filter(category %in% c("fp","sw")) %>% 
+  ggplot() +
+  geom_sf(aes(fill = diff)) +
+  viridis::scale_fill_viridis("Differences", 
+                              alpha = 0.8,
+                              option = "C",
+                              limits = c(0,50),
+                              breaks = seq(0,50,10)
+                              ) +
+  facet_wrap(~ label,
+             ncol = 1,
+             strip.position="right") +
+  labs(x = "", 
+       y = "") +
+  my_ggtheme_p(facet_tx_s = 20,
+               leg_pos = "",
+               axx_tx_ang = 45,
+               ax_tx_s = 12,
+               ax_tl_s = 18,
+               hjust = 1) +
+  theme(strip.background = element_blank(),
+        # strip.text.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.line.y = element_blank()
+        )
+
+ggsave(filename = "seas_diff.png",
+         plot = seas_diff,
+         path = my_path("R","Figures"),
+         width = 8,
+         height = 6
+  )
+
+```
+
+![Proportion change aggregated all species map for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/proportion_chg_agg.jpg)

### 2021-10-08 Allocation_tool/server.R
updated tool to show historic and quaota

@@ -54,14 +54,38 @@ shinyServer(function(input, output) {
         
         name <- paste0("tif_",str_replace(input$SppSelection," ","_"),".csv")
         
-        data <- my_path("R","Partial/Interpolation/sw",name = name, read = T)
+        data <- my_path("R","Partial/Interpolation/",name = name, read = T)
+        
+        # For testing
+        # data <- my_path("R","Partial/Interpolation/",name = "tif_Centropristis_striata.csv", read = T)
+        # tif_plot_data <- data %>%
+        # filter(
+        # region %in% "Northeast US Fall")
         
     })
     
-    
+    # ---------------------------- #
+    # Grid data from the SW and FP approaches
+    # ---------------------------- #
+    grids_data <- reactive({
+        
+        
+        
+        grids <- my_path("D", "Spatial/grid_eez_fp_sf", name = "grid_eez_fp_df.csv", read = T) %>% 
+            mutate(
+                spatial = "fp"
+            ) %>% 
+            bind_rows(
+                my_path("D", "Spatial/grid_eez_sw_sf", name = "grid_eez_sw_df.csv", read = T)
+            ) %>% 
+            mutate(
+                spatial = ifelse(is.na(spatial),"sw",spatial)
+            )
+        
+    })
     
     # ---------------------------- #
-    # Main plot ####
+    # Quota allocation plots ####
     # ---------------------------- #
     output$distPlot <- renderPlot({
         # Set the filters
@@ -80,7 +104,11 @@ shinyServer(function(input, output) {
         tif_plot_data <- tif_data() %>%
             filter(spp %in% species,
                    region %in% survey,
-                   year %in% years)
+                   year %in% years) %>% 
+            mutate(
+                cpue_log10 = log10(value)
+            ) %>% 
+            gather("type","cpue",value:cpue_log10)
         
         # ---------------------------- #
         ## Latitudinal plot ######
@@ -145,7 +173,7 @@ shinyServer(function(input, output) {
                     scale_color_distiller(palette = "Spectral",
                                           guide_legend(title = "WCPUE per Haul (log10)")) +
                     coord_sf(xlim = c(-76, -65),ylim = c(35, 45)) +
-                    MyFunctions::my_ggtheme_m() +
+                    MyFunctions::my_ggtheme_m(leg_pos = "right") +
                     facet_wrap(~region) +
                     ggtitle(paste(min(years),max(years)))
             }else{
@@ -182,8 +210,8 @@ shinyServer(function(input, output) {
[…]

### 2021-10-08 Allocation_tool/ui.R

@@ -37,15 +37,15 @@ shinyUI(
                    tabPanel("About",
                             fluidRow(
                                 column(12,
-                                    align = "center",
-                                    h1("Managing across boundaries: preventing interjurisdictional conflicts arising from shifting fish stocks"),
+                                       align = "center",
+                                       h1("Managing across boundaries: preventing interjurisdictional conflicts arising from shifting fish stocks"),
                                 ),
                                 br(),
                                 column(
                                     8,
                                     offset = 2,
                                     align = "justified",
-                                includeMarkdown("./scripts/about.Rmd") # Call the About info
+                                    includeMarkdown("./scripts/about.Rmd") # Call the About info
                                 ),
                                 br(),
                                 column(
@@ -104,11 +104,11 @@ shinyUI(
                                               p("(iv) discrete high seas stocks whose distribution is limited to the high seas.")
                                        ),
                                        column(8,
-                                           offset = 2,
-                                           align = "center",
-                                           img(src= 'shared_stocks.png',
-                                               height = 400,
-                                               width = 800),
+                                              offset = 2,
+                                              align = "center",
+                                              img(src= 'shared_stocks.png',
+                                                  height = 400,
+                                                  width = 800),
                                        ),
                                        column(8,
                                               offset = 2,
@@ -135,118 +135,229 @@ shinyUI(
                                            8,
                                            offset = 2,
                                            align = "justified",
-                                       includeMarkdown("./scripts/climate_change.Rmd")
+                                           includeMarkdown("./scripts/climate_change.Rmd")
                                        )
-                                       ),
+                              ),
                               tabPanel("Dynamic management")
                               
                    ), # close information tab
                    # ----------------------- #
                    # Tool UI ####
                    # ----------------------- #
-                   tabPanel("Quota allocation",
-                            fluidRow(
-                                column(
-                                    12,
-                                    align = "justified",
-                                    h1("Control panel"),
-                                ),
-                                # Sidebar with a slider input for number of bins
-                                sidebarLayout(
-                                    sidebarPanel(
-                                        # Select which Gender(s) to plot
-                                        checkboxGroupInput(inputId = "SurveySelection",
-                                                           label = "Select Survey(s)",
-                                                           choices = unique(spp_survey$region),
-                                                           selected = unique(spp_survey$region)[1]
-                                        ),
-                                        # Select Species
-                                        selectInput(inputId = "SppSelection",
-                                                    label = "Select Species",
[…]

### 2021-10-08 Allocation_tool/server.R
Potential new tool version

@@ -22,6 +22,45 @@ state_pallet <- c(wes_palette(n = 5, name = "Darjeeling1"),
                   wes_palette(n = 3, name = "Royal1")
 )
 
+# Set the filters
+state_order <- my_path("D", "Spatial/grid_eez_sw", name = "grid_eez_sw_df.csv", read = T) %>%
+    group_by(state) %>%
+    summarise(
+        order = mean(lat)
+    ) %>%
+    mutate(abrev = c("CT","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VA")
+    ) %>%
+    arrange(desc(order)) %>%
+    mutate(order= c("b","a",letters[3:11])) %>% # weirdly maine goes below
+    arrange(order)
+
+# ---------------------------- #
+# Grid data from the SW and FP approaches
+# ---------------------------- #
+# Load grid of state waters
+grid_eez_sw_sf <- st_read(my_path("D","Spatial/grid_eez_sw", name = "grid_eez_sw_sf.shp")) %>%
+    select(index,state,geometry) %>%
+    mutate(method = "state_waters",
+           state = str_to_sentence(state)) %>%
+    left_join(state_order)
+
+grid_eez_sw_sf$group <- factor(grid_eez_sw_sf$abrev,      # Reordering group factor levels
+                               levels = state_order$abrev)
+
+# Load grid of fishing ports
+grid_eez_fp_sf <-  st_read(my_path("D","Spatial/grid_eez_fp", name = "grid_eez_fp.shp")) %>%
+    select(index,abrev=lndng_s,geometry) %>%
+    mutate(method = "fishing_port"#,
+           # state = str_to_sentence(landing_port)
+    )%>%
+    left_join(state_order)
+
+grid_eez_fp_sf$group <- factor(grid_eez_fp_sf$abrev,      # Reordering group factor levels
+                               levels = state_order$abrev)
+
+grid_eez_fp_sf <- arrange(grid_eez_fp_sf,group)
+
+
 
 # ---------------------------- #
 # Tool start ####
@@ -37,11 +76,11 @@ shinyServer(function(input, output) {
         
         data <- my_path("D","Spp/Observation",name = name, read = T)
         
-        # data <- readRDS("/Volumes/Enterprise/Data/pinskylab-OceanAdapt-966adf0/data_clean/dat_exploded.rds") %>%
-        #     filter(
-        #         # spp %in% c ("Centropristis striata","Gadus morhua"),
-        #         region %in% c("Northeast US Fall" , "Northeast US Spring")
[…]

### 2021-10-08 Allocation_tool/ui.R

@@ -142,223 +142,367 @@ shinyUI(
                               
                    ), # close information tab
                    # ----------------------- #
-                   # Tool UI ####
+                   # Option A ####
                    # ----------------------- #
-                   navbarMenu("Tool",
-                              tabPanel("Historic allocation",
-                                       fluidRow(
-                                           column(
-                                               12,
-                                               align = "justified",
-                                               h1("Control panel"),
-                                           ),
-                                           # Sidebar with a slider input for number of bins
-                                           sidebarLayout(
-                                               sidebarPanel(
-                                                   # Select which Gender(s) to plot
-                                                   checkboxGroupInput(inputId = "SurveySelection",
-                                                                      label = "Select Survey Season(s)",
-                                                                      choices = unique(spp_survey$region),
-                                                                      selected = unique(spp_survey$region)[1]
-                                                   ),
-                                                   # Select Species
-                                                   selectInput(inputId = "SppSelection",
-                                                               label = "Select Species",
-                                                               choices = unique(spp_survey$spp),
-                                                               selected = "Centropristis striata",
-                                                               width = "220px"
-                                                   ),
-                                                   # Select sf Area
-                                                   selectInput(inputId = "SpatSelection",
-                                                               label = "Select Management Unit",
-                                                               choices = c("State waters","Fishing ports","Both"),
-                                                               selected = "State waters",
-                                                               width = "220px"
-                                                   ),
-                                                   # Set Time Range
-                                                   sliderInput("PortTreshold",
-                                                               "Port threshold",
-                                                               min = 5,
-                                                               max = 95,
-                                                               value = 75),
-                                                   # Choose the years you want to plot
-                                                   sliderInput(inputId = "YearSelection",
-                                                               label = "Select Year Range",
-                                                               min = 1972,
-                                                               max = 2019,
-                                                               step = 1,
-                                                               sep = "",
-                                                               animate = FALSE,
-                                                               value = c(1972,2019),
-                                                               width = "220px"),
-                                                   # Select which plot you want to create
-                                                   # checkboxGroupInput(inputId = "PlotStyle",
-                                                   #                    label = "Select Result",
-                                                   #                    choices = c(
-                                                   #                        "Latitudinal Shift (P)" = 1,
-                                                   #                        "Survey Points (P)" = 2, 
-                                                   #                        "Distribution (M)" = 3,
-                                                   #                        "Proportion change (M)" = 5,
[…]

### 2021-10-11 Scripts/manuscript_acrossboundaries.Rmd
Inclued  missing intro paragraphs

@@
 The mismatch between implemented management strategies and shifts in stocks across management jurisdictions compromises management and sustainability [@Baudron2020; @pinsky_fogarty_2012].
-Fishers in the NE Atlantic have been adapting to such shifts by following the fish, in some cases, or changing target speices, in others [@polo_2021].
+Fishers in the NE Atlantic have been adapting to such shifts by following the fish, in some cases, or changing target species, in others [@polo_2021].
 While this problem of shifting stocks across management jurisdictions is increasingly well known, quantifying it is difficult for two main reasons: (*i*) management jurisdictions in the ocean are often ill-defined, especially at the sub-national level or beyond Exclusive Economic Zones (EEZ), and (*ii*) quantifying fish distributions in relation to these boundaries is difficult, even where fishery-independent surveys exist, because of seasonal and interannual variation.
 
-**[Short paragraph on the ill-defined boundary challeng - do we privilege a state's geographic claims or the inherent claims to the resource of existing fishing ports?]**
+<!-- ## Management jurisdictions in the ocean are often ill-defined -->
 
-**[Short paragraph on the seasonality of fish distributions in temperate waters - when do we measure fish distributions?]**
+<!-- **[Short paragraph on the ill-defined boundary challenge - do we privilege a state's geographic claims or the inherent claims to the resource of existing fishing ports?]** -->
+
+<!-- Both defining and ill-defined management boundaries represent a challenge to fisheries management [@REF].
+For example, territory dispute is among the most frequent sources of conflict between Asian countries [@spijkers_globalpatterns_2019], specially in the South China [@Beckman].
+-->
+
+Fisheries scientists and common-resource economist have long pledge for establishing property rights of a common-pull resource [@REF].
+However, allocating such rights is not allays straightforward [@REF].
+There are multiple ways to allocate property rights within country's EEZ.
+For example, regulatory units can be allocated considering fishing ports or communities as exemplified by many small scale fisheries across Latin America.
+In Mexico, spatial property rights are often given to fishing communities based on historical exploitation and investment in specific fisheries [@PalaciosAbrantes2018; @Basurto2005].
+Moreover, the Chilean's government adopted the use of Territorial Use Rights for Fisheries (TURFs) for the management of benthic fisheries.
+Under this policy, fishers organizations are allocated a TURF based on port location and historical landings, among others [@González_2006; @gelcich_2010].
+Within the U.S., state waters give clear fisheries rights to each state, federal waters (i.e, the 200 n, EEZ), on the other hand are not subdivided in sub-regulatory units, except for some specific cases.
+Pacific halibut (*Hippoglossus stenolepis*) managed by Canada and the United States from California to Alaska is based on regulatory units that extend along the countries' EEZs [@IPHC].
+In this case, such regulatory units cross multiple states, like division 2A that goes from California to Washington [@REF].
+
+<!-- **[Short paragraph on the seasonality of fish distributions in temperate waters - when do we measure fish distributions?]** -->
+
+Seasonality of fish distributions in temperate waters is key for proper management of marine ressources [@Bell2014].
+Along the U.S.
+Northeast EEZ, muny species like black sea bass (*Centropristis striata*) and scup (*Stenotomus chrysops*) present substantial latitudinal migration in response to water temperature fluctuation [@Bell2015; @Henderson2017].
+Changes in distribution also follow a depth patter like the case of summer flounder (*Paralichthys dentatus*) who undergoes annual migrations from shallow coastal habitats in the fall to deeper habitats over winter (Terceiro, 2001; Sackett et al., 2007).
+The consideration of such natural migration is key in the proper management of marine resources [@Bell2014].
 
@@
 There are a potentially infinite number of ways to geographically determine regulatory units with the EEZ's 200 nautical miles.
-Here we focus on two methods based which likely bracket much of the range of options.
+Here we focus on two methods which likely bracket much of the range of options.
 
@@
 
-The first approach consists on expanding the current geographical distribution of States and their statutory state waters.
+The first approach consists of expanding the current geographical distribution of states and their statutory state waters.
 For this approach we adapted the state's waters boundaries determined by the Federal and State Waters shapefile created for the Ocean Reporting Tool in April, 2018 ([NOAA's Office for Coastal Management, 2021](https://catalog.data.gov/dataset/federal-and-state-waters)).
@@
 Each state's polygon  from Maine to Virginia was expanded to the 200 nm EEZ boundary using the *st* package in *R* [@REF].
-The resulting polygons were also gridded into a 3 x 3 deg.
+The resulting polygons (i.e., regulatory units) were also gridded into a 3 x 3 deg.
 matrix.
@@
 Note that, while species often shared top ports, their final number and location varied according to each species (Figure \@ref{fig:figureS1}).
-Moreover, we tested the sensitivity of our results to the arbitrary $75{^th}$ percentile threshold and found that...
-(*to be done*).
 Each port represented a point in the map (i.e., latitude and longitude degrees) whose coordinates were manually collected using [googlemaps](www.googlemaps.com).
 We then drew a polygon from each port to the EEZ and gridded the expanded polygon following the same method as the *Fishing ports approach*.
-The expanded polygon of each port was associated to the state where the port is located and overlapping grids were equally allocated to the sharing states.
+The resulting regulatory unit of each port was associated to the state where the port is located and overlapping grids were equally allocated to the sharing states.
+
+Moreover, we tested the sensitivity of our results to the arbitrary $75{^th}$ percentile threshold and found that... (*to be done*).
 
@@
 
-Finally, we estimated the CPUE percentage change today relative to the historic period.
+Next, we estimated the CPUE percentage change today relative to the historic period.
 For that matter we define the historic period as 1980 to 2000 representing the state allocations of the commercial fisheries originally implemented in 2003 [@RefDocument], and “today” as the average of 2009 to 2019 representing the more recent data available.
@@
 
-Seasonal differences are also evident, although smaller than regulatory unit differences, when estimate each state's CPUE proportion for all species (Figures \@ref{fig:figSeasonlDiff}).
+Seasonal differences in state’s CPUE proportion are also evident, although smaller than regulatory units differences (Figures \@ref{fig:figSeasonlDiff}).
 Here, half of the cases represent 1% or no seasonality difference like Connecticut's CPUE proportion of summer flounder.
@@
 
-The proportion of the CPUE has increased for northern states
+Over the last 40 years, the proportion of the CPUE has increased for northern states and decreased for southern states for all species (Figure 6).
+North Carolina and Virginia have been the most affected for all three species, regardless of the regulatory unit approach.
+Under the state waters approach, states from Rhode Island to Maine have increased their proportion of black sea bass and scup while the fishing ports approach favors Massachusetts, Rhode Island, and New York.
+States located “at middle” latitude do not seem to be affected by shifting distributions.
+While the regulatory unit approach will completely remove some states (e.g., Maine) of the allocation beneficing others (e.g., New Jersey), it does not seem to affect historical trends.
+That is, gainers and losers in terms of historical trend will be the same, regardless of the approach.
 

### 2021-10-21 Allocation_tool/server.R
Dashbord version of the app

@@ -13,7 +13,7 @@
 
 # Get functions and shapefiles
 library(MyFunctions)
-MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","DT","plotly","wesanderson","zoo","formattable"))
+MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","DT","plotly","wesanderson","zoo","formattable","viridis"))
 
 us_map <- st_as_sf(map("state", plot = FALSE, fill = TRUE))
 
@@ -60,6 +60,19 @@ grid_eez_fp_sf$group <- factor(grid_eez_fp_sf$abrev,      # Reordering group fac
 
 grid_eez_fp_sf <- arrange(grid_eez_fp_sf,group)
 
+grids <- my_path("D", "Spatial/grid_eez_fp", name = "grid_eez_fp_df.csv", read = T) %>%
+    mutate(
+        spatial = "fp"
+    ) %>% 
+    bind_rows(
+        my_path("D", "Spatial/grid_eez_sw", name = "grid_eez_sw_df.csv", read = T)
+    ) %>% 
+    select(-spp) %>% 
+    mutate(
+        spatial = ifelse(is.na(spatial),"sw",spatial)
+    ) %>% 
+    distinct(.keep_all = T)
+
 
 
 # ---------------------------- #
@@ -76,11 +89,11 @@ shinyServer(function(input, output) {
         
         data <- my_path("D","Spp/Observation",name = name, read = T)
         
-        data <- readRDS("/Volumes/Enterprise/Data/AcrossBoundaries/Data/pinskylab-OceanAdapt-966adf0/data_clean/dat_exploded.rds") %>%
-            filter(
-                spp %in% c("Centropristis striata","Paralichthys dentatus","Stenotomus chrysops"),
-                region %in% c("Northeast US Fall" , "Northeast US Spring")
-            ) #No more seasons
+        # data <- readRDS("/Volumes/Enterprise/Data/AcrossBoundaries/Data/pinskylab-OceanAdapt-966adf0/data_clean/dat_exploded.rds") %>%
+        #     filter(
+        #         spp %in% c("Centropristis striata","Paralichthys dentatus","Stenotomus chrysops"),
+        #         region %in% c("Northeast US Fall" , "Northeast US Spring")
+        #     ) #No more seasons
         
     })
     
@@ -89,521 +102,40 @@ shinyServer(function(input, output) {
[…]

### 2021-10-21 Allocation_tool/ui.R

@@ -19,490 +19,204 @@ spp_survey <- read.csv("./data/spp_region.csv") %>%
 
 
 # Define UI for application that draws a histogram
-shinyUI(
-    fluidPage( 
-        # remove shiny "red" warning messages on GUI
-        tags$style(type="text/css",
-                   ".shiny-output-error { visibility: hidden; }",
-                   ".shiny-output-error:before { visibility: hidden; }"
+
+dashboardPage(
+    dashboardHeader(title = "Across Boundaries Project"),
+    dashboardSidebar(
+        selectizeInput(
+            'SppSelection', '1. Species', choices = c("Centropristis striata","Paralichthys dentatus","Stenotomus chrysops"),
+            options = list(
+                placeholder = 'Type to search for species',
+                onInitialize = I('function() { this.setValue(""); }')
+            )
         ),
-        navbarPage(id = "MMM_Nav_Bar",
-                   # Set a theme for the tool
-                   theme = shinythemes::shinytheme("spacelab"),
-                   # Page title
-                   "Across Boundaries",
-                   # ---------------------------- #
-                   # About tab ######
-                   # ---------------------------- #
-                   tabPanel("About",
-                            fluidRow(
-                                column(12,
-                                       align = "center",
-                                       h1("Managing across boundaries: preventing interjurisdictional conflicts arising from shifting fish stocks"),
-                                ),
-                                br(),
-                                column(
-                                    8,
-                                    offset = 2,
-                                    align = "justified",
-                                    includeMarkdown("./scripts/about.Rmd") # Call the About info
-                                ),
-                                br(),
-                                column(
-                                    10,
-                                    align = "center",
-                                    h5("This is a project funded by The Lenfest Ocean Program"),
-                                    p("Know more about the Lenfest program", a(img(src= 'logo_lenfest.jpeg',
-                                                                                   height = 30,
-                                                                                   width = 50),
-                                                                               href="https://www.lenfestocean.org/en/about-us")
-                                    )
-                                ),
-                            ) # close fluid row
-                   ), # tabPanel About close
-                   # ----------------------- #
-                   # General info ####
-                   # ----------------------- #
-                   navbarMenu("Information",
-                              tabPanel("Shared stocks",
-                                       column(8,
-                                              offset = 2,
-                                              align = "justified",
-                                              p(h3("Shared fisheries management")),
-                                              p(
-                                                  "From 1973 to 1982, members of the United Nations (UN) held a series of meetings to discuss 
[…]

### 2021-10-21 Scripts/spatial_analisis.Rmd
misc.

@@
 
-grids <- my_path("D", "Spatial/grid_eez_fp_sf", name = "grid_eez_fp_df.csv", read = T) %>%
+grids <- my_path("D", "Spatial/grid_eez_fp", name = "grid_eez_fp_df.csv", read = T) %>%
   mutate(
@@
   bind_rows(
-    my_path("D", "Spatial/grid_eez_sw_sf", name = "grid_eez_sw_df.csv", read = T)
+    my_path("D", "Spatial/grid_eez_sw", name = "grid_eez_sw_df.csv", read = T)
   ) %>% 
@@
     season = ifelse(str_detect(region,"Spring"),"Spring","Fall")
-  )
+  ) %>% 
+  filter(spp == "Centropristis striata")
 

### 2021-10-23 Allocation_tool/server.R
Advances on tool dashbord

@@ -5,7 +5,7 @@
 # Find out more about building applications with Shiny here:
 #
 #    http://shiny.rstudio.com/
-#
+# https://shiny.rstudio.com/gallery/nutrition-calculator.html
 
 # ---------------------------- #
 # Setup
@@ -13,7 +13,7 @@
 
 # Get functions and shapefiles
 library(MyFunctions)
-MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","DT","plotly","wesanderson","zoo","formattable","viridis"))
+MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","DT","plotly","wesanderson","zoo","formattable","viridis","shinydashboard"))
 
 us_map <- st_as_sf(map("state", plot = FALSE, fill = TRUE))
 
@@ -114,25 +114,25 @@ shinyServer(function(input, output) {
             ) %>%
             filter(!is.na(spatial)) %>% 
             mutate(
-            spatial = ifelse(spatial == "fp","Fishing ports",
-                             ifelse(spatial == "sw","State waters","Difference")
-            )
-            )
-        
-        # For testing
-        data <- my_path("R","Partial/Interpolation/",name = "tif_Centropristis_striata.csv", read = T)
-
-        tif_data <- data %>%
-            filter(region %in% "Northeast US Fall") %>%
-            left_join(grids,
-                      by = c("index","lat","lon")
-            ) %>%
-            filter(!is.na(spatial)) %>%
-            mutate(
                 spatial = ifelse(spatial == "fp","Fishing ports",
                                  ifelse(spatial == "sw","State waters","Difference")
                 )
             )
+        
+        # For testing
+        # data <- my_path("R","Partial/Interpolation/",name = "tif_Centropristis_striata.csv", read = T)
+        # 
+        # tif_data <- data %>%
+        #     filter(region %in% "Northeast US Fall") %>%
+        #     left_join(grids,
+        #               by = c("index","lat","lon")
+        #     ) %>%
+        #     filter(!is.na(spatial)) %>%
+        #     mutate(
+        #         spatial = ifelse(spatial == "fp","Fishing ports",
+        #                          ifelse(spatial == "sw","State waters","Difference")
+        #         )
+        #     )
         
     })
     
@@ -330,45 +330,39 @@ shinyServer(function(input, output) {
             ) %>% 
             gather("type","cpue",value,cpue_log10)
         
-                    
-                    ggplot(us_map) +
[…]

### 2021-10-23 Allocation_tool/ui.R

@@ -8,7 +8,7 @@
 #
 
 # Load libraries and data
-MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","plotly","formattable"))
+MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","plotly","formattable","shinydashboard"))
 
 spp_survey <- read.csv("./data/spp_region.csv") %>% 
     filter(
@@ -48,7 +48,7 @@ dashboardPage(
             )
         ),
         sliderInput(inputId = "YearSelection",
-                    label = "Select Year Range",
+                    label = "Select year range of distribution",
                     min = 1972,
                     max = 2019,
                     step = 1,
@@ -80,40 +80,32 @@ dashboardPage(
             ## Regulatory units map -----------------
             box(title = "Regulatory Units",
                 solidHeader = T,
-                width = 4,
+                width = 6,
                 collapsible = T,
                 plotOutput("RegUnit")
-                ),
+            ),
             ## Distribution map -----------------
             box(title = "Distribution", solidHeader = T,
-                width = 8, collapsible = T,
+                width = 6, collapsible = T,
                 plotOutput("distPlot"))
-        ), #First fluid row
+        ), 
         fluidRow(
             ## Proportion map -----------------
             box(title = "Proportion", solidHeader = T,
-                width = 8, collapsible = T,
+                width = 6, collapsible = T,
                 plotOutput("propPlot")),
             ## Area plot -----------------
-            box(title = "Historical proportion", solidHeader = T,
-                width = 8, collapsible = T,
-                plotlyOutput("mineral_plot"))
+            box(title = "Proportion Difference", solidHeader = T,
+                width = 6, collapsible = T,
+                plotOutput("propDiffPlot"))
         ),# row
         fluidRow(
-            box(title = "Vitamins", solidHeader=T,
+            box(title = "Proportion", solidHeader = T,
                 width = 12, collapsible = T,
-                plotlyOutput("vitamin_plot"))
-            
-            #     box(title = "Proportions",
-            #         solidHeader = T,
-            #         width = 4, 
-            #         collapsible = T,
-            #         collapsed = F,
-            #         tags$p(textOutput("serving", inline = T)),
-            #         div(DT::DTOutput("nutrient_table"), style = "font-size: 70%;")),
+                formattableOutput("Allocation_tbl")
+                )
         ) # row
     ) # body
-    
 )
 
 

### 2021-10-25 Scripts/spatial_analisis.Rmd
Fix buggs

@@
 # Get state order from North to south
-state_order <- my_path("D","Spatial/grid_eez_sw_sf", name = "grid_eez_sw_df.csv",read = T) %>%
+state_order <- my_path("D","Spatial/grid_eez_sw", name = "grid_eez_sw_df.csv",read = T) %>%
   group_by(state) %>% 
@@
 # Load grid of state waters
-grid_eez_sw_sf <-  st_read(my_path("D","Spatial/grid_eez_sw_sf", name = "grid_eez_sw_sf.shp")) %>%
+grid_eez_sw_sf <-  st_read(my_path("D","Spatial/grid_eez_sw", name = "grid_eez_sw_sf.shp")) %>%
   select(index,state,geometry) %>% 
@@
 # Load grid of fishing ports
-grid_eez_fp_sf <-  st_read(my_path("D","Spatial/grid_eez_fp_sf", name = "grid_eez_fp.shp")) %>%
+grid_eez_fp_sf <-  st_read(my_path("D","Spatial/grid_eez_fp", name = "grid_eez_fp.shp")) %>%
   select(index,abrev=lndng_s,geometry) %>% 
@@
 )
+
+reg_unit %>% 
+  # filter(spatial == "fp") %>%
+  select(-fp) %>% 
+  spread(label,sw) %>% 
+  mutate(
+    difference = Today-Reference
+    ) %>% 
+  gther(Reference:difference)
 

### 2021-10-25 Allocation_tool/server.R

@@ -35,7 +35,7 @@ state_order <- my_path("D", "Spatial/grid_eez_sw", name = "grid_eez_sw_df.csv", 
     arrange(order)
 
 # ---------------------------- #
-# Grid data from the SW and FP approaches
+# Grid data ####
 # ---------------------------- #
 # Load grid of state waters
 grid_eez_sw_sf <- st_read(my_path("D","Spatial/grid_eez_sw", name = "grid_eez_sw_sf.shp")) %>%
@@ -72,6 +72,21 @@ grids <- my_path("D", "Spatial/grid_eez_fp", name = "grid_eez_fp_df.csv", read =
         spatial = ifelse(is.na(spatial),"sw",spatial)
     ) %>% 
     distinct(.keep_all = T)
+
+
+# ---------------------------- #
+# Quota - reference years ####
+# ---------------------------- #
+# Summer flounder
+# ref_yrs <- c(1980,1989)
+
+# Black sea bass
+# https://static1.squarespace.com/static/511cdc7fe4b00307a2628ac6/t/5176dea1e4b083b631f27236/1366744737698/SFSCBSB_Amend_13_Vol_1compressed.pdf 
+# a) a federal coastwide quota with satate-by-state allocation system Alternative 5f; setion 2.1.5.6 (Pages 3, 14, and 304-Table 5)
+# ref_yrs <- c(1980:2001)
+
+
+# Scup
 
 
 
@@ -120,19 +135,18 @@ shinyServer(function(input, output) {
             )
         
         # For testing
-        # data <- my_path("R","Partial/Interpolation/",name = "tif_Centropristis_striata.csv", read = T)
-        # 
-        # tif_data <- data %>%
-        #     filter(region %in% "Northeast US Fall") %>%
-        #     left_join(grids,
-        #               by = c("index","lat","lon")
-        #     ) %>%
-        #     filter(!is.na(spatial)) %>%
-        #     mutate(
-        #         spatial = ifelse(spatial == "fp","Fishing ports",
-        #                          ifelse(spatial == "sw","State waters","Difference")
-        #         )
-        #     )
+        data <- my_path("R","Partial/Interpolation/",name = "tif_Centropristis_striata.csv", read = T)
+        
+        tif_data <- data %>%
+            left_join(grids,
+                      by = c("index","lat","lon")
+            ) %>%
+            filter(!is.na(spatial)) %>%
+            mutate(
+                spatial = ifelse(spatial == "fp","Fishing ports",
[…]

### 2021-10-25 Allocation_tool/server.R
working on making both apporaches work

@@ -123,6 +123,12 @@ shinyServer(function(input, output) {
         
         name <- paste0("tif_",str_replace(input$SppSelection," ","_"),".csv")
         
+        # Set the filters
+        species <- input$SppSelection #"Centropristis striata"
+        survey <-input$SurveySelection # "Northeast US Fall"
+        reg_area <- input$SpatSelection # "State waters"
+        
+
         data <- my_path("R","Partial/Interpolation/",name = name, read = T) %>% 
             left_join(grids,
                       by = c("index","lon","lat")
@@ -132,21 +138,29 @@ shinyServer(function(input, output) {
                 spatial = ifelse(spatial == "fp","Fishing ports",
                                  ifelse(spatial == "sw","State waters","Difference")
                 )
-            )
+            ) %>% 
+            filter(spp %in% species,
+                   region %in% survey,
+                   spatial %in% reg_area)
         
         # For testing
-        data <- my_path("R","Partial/Interpolation/",name = "tif_Centropristis_striata.csv", read = T)
+        # data <- my_path("R","Partial/Interpolation/",name = "tif_Centropristis_striata.csv", read = T)
         
-        tif_data <- data %>%
-            left_join(grids,
-                      by = c("index","lat","lon")
-            ) %>%
-            filter(!is.na(spatial)) %>%
-            mutate(
-                spatial = ifelse(spatial == "fp","Fishing ports",
-                                 ifelse(spatial == "sw","State waters","Difference")
-                )
-            )
+        
+        # tif_data <- data %>%
+        #     left_join(grids,
+        #               by = c("index","lat","lon")
+        #     ) %>%
+        #     filter(!is.na(spatial)) %>%
+        #     mutate(
+        #         spatial = ifelse(spatial == "fp","Fishing ports",
+        #                          ifelse(spatial == "sw","State waters","Difference")
+        #         )
+        #     ) %>%
+        #     filter(#spp %in% species,
+        #            region %in% survey,
+        #            # spatial %in% reg_area
+        #            )
         
     })
     
@@ -319,33 +333,25 @@ shinyServer(function(input, output) {
     # TIF distribution map ####
     # ---------------------------- #
     output$distPlot <- renderPlot({
+        
         # Set the filters
-        species <- input$SppSelection #"Centropristis striata"
-        survey <-input$SurveySelection #"Northeast US Fall"
[…]

### 2021-10-25 Allocation_tool/ui.R

@@ -41,7 +41,7 @@ dashboardPage(
         ),
         selectizeInput(
             'SpatSelection',
-            '2. Select Management Unit', choices = c("State waters","Fishing ports","Both apporaches"),
+            '2. Select Regulatory Unit', choices = c("State waters","Fishing ports","Both apporaches"),
             options = list(
                 placeholder = 'Select an approach',
                 onInitialize = I('function() { this.setValue(""); }')
@@ -84,11 +84,11 @@ dashboardPage(
                 collapsible = T,
                 plotOutput("RegUnit")
             ),
-            ## Distribution map -----------------
-            box(title = "Distribution", solidHeader = T,
-                width = 6, collapsible = T,
-                plotOutput("distPlot"))
-        ), 
+        ## Distribution map -----------------
+        box(title = "Distribution", solidHeader = T,
+            width = 6, collapsible = T,
+            plotOutput("distPlot"))
+        ),
         fluidRow(
             ## Proportion map -----------------
             box(title = "Proportion", solidHeader = T,
@@ -103,7 +103,7 @@ dashboardPage(
             box(title = "Proportion", solidHeader = T,
                 width = 12, collapsible = T,
                 formattableOutput("Allocation_tbl")
-                )
+            )
         ) # row
     ) # body
 )
@@ -210,5 +210,22 @@ dashboardPage(
 #                    )
 #                    
 #         )
+#     )
+# )
+
+
+# Condition between plot and plotly
+# conditionalPanel(
+#     condition = "SpatSelection == Both apporaches",
+#     box(title = "Distribution", solidHeader = T,
+#         width = 6, collapsible = T,
+#         plotOutput("DiffpropPlot")
+#     )
+# ),
+# conditionalPanel(
+#     condition = "SpatSelection != Both apporaches",
+#     box(title = "Distribution", solidHeader = T,
+#         width = 6, collapsible = T,
+#         plotOutput("distPlot")
 #     )
 # )

### 2021-10-26 Scripts/spatial_analisis.Rmd
Set reference points for each stock

@@
   mutate(
-    season = ifelse(str_detect(region,"Spring"),"Spring","Fall")
-  ) %>% 
-  filter(spp == "Centropristis striata")
+    season = ifelse(str_detect(region,"Spring"),"Spring","Fall"),
+    label = ifelse(spp == "Paralichthys dentatus" & year >= 1980 & year <= 1986,"Reference",
+                   ifelse(spp == "Stenotomus chrysops" & year >= 1988 & year <= 1992,"Reference",
+                          ifelse( spp =="Centropristis striata" & year >= 1980 & year <= 2001,"Reference",
+                                 ifelse(year > 2001,"Today",NA)
+                          )
+                   )
+    )
+  )
 
@@
 interpol_result <- historic_spp %>% 
-  mutate(
-    label = ifelse(year >= 1980 & year <= 2001,"Reference",
-                   ifelse(year > 2001,"Today",NA)
-    )
-  ) %>% 
   filter(!is.na(label)) %>% 
@@
 total_inter <- historic_spp %>% 
-  mutate(
-    label = ifelse(year >= 1980 & year <= 2001,"Reference",
-                   ifelse(year > 2001,"Today",NA)
-    )
-  ) %>% 
   filter(!is.na(label)) %>% 
@@
 centroid_db <- historic_spp %>% 
-  mutate(
-    label = ifelse(year >= 1980 & year <= 2001,"Reference",
-                   ifelse(year > 2001,"Today",NA)
-    )
-  ) %>% 
   filter(!is.na(label)) %>% 
@@
               y = lat,
-              # fill = log10(mean_cpue),
-              # color = log10(mean_cpue)
-              fill = mean_cpue,
-              color = mean_cpue
+              fill = log10(mean_cpue),
+              color = log10(mean_cpue)
+              # fill = mean_cpue,
+              # color = mean_cpue
             )
@@
   # Viridis option
-scale_fill_viridis("CPUE",
-                   limits = c(0,40),
-                   # limits = c(-5,1), # for log10
-                   direction = -1,
-                    end = 0.9
-                   ) +
-scale_color_viridis("CPUE",
-                    limits = c(0,40),
-                    # limits = c(-5,1), # for log10
-                    direction = -1,
-                    end = 0.9
-                    ) +
+# scale_fill_viridis("CPUE",
+#                    limits = c(0,40),
+#                    # limits = c(-5,1), # for log10
+#                    direction = -1,
+#                     end = 0.9
+#                    ) +
+# scale_color_viridis("CPUE",
+#                     limits = c(0,40),
+#                     # limits = c(-5,1), # for log10
+#                     direction = -1,
+#                     end = 0.9
+#                     ) +
 # wes anderson option
-# scale_fill_gradientn("CPUE",
-#                      colours = pal,
+scale_fill_gradientn("CPUE",
+                     colours = pal,
                      # limits = c(0,40) # For cpue
-#                      # limits = c(-5,1) # for log10
-#                      
-# ) +
-#   scale_color_gradientn("CPUE",
-#                         colours = pal,
+                     limits = c(-5,1) # for log10
+
+) +
+  scale_color_gradientn("CPUE",
+                        colours = pal,
                         # limits = c(0,40) # for cpue
-#                         # limits = c(-5,1) # for log10
-#   ) +
+                        limits = c(-5,1) # for log10
+  ) +
   facet_grid(spp~season+label) +
@@
 
-ggsave("interpolation_vi.jpg",
+ggsave("interpolation_wa.jpg",
        inter_map,
@@
 state_fit <- historic_spp %>% 
-  group_by(state,year,season,spp,spatial) %>% 
+  group_by(state,year,label,season,spp,spatial) %>% 
   summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
@@
             by = c("year","season","spp","spatial")) %>%
-  mutate(percentage = state_value/total_value*100,
-         label = ifelse(year >= 1980 & year <= 2001,"Reference",
-                         ifelse(year > 2001,"Today",NA)
-                         )
-         ) %>% 
+  mutate(percentage = state_value/total_value*100) %>% 
   group_by(state,label,season,spp,spatial) %>% 
@@
 state_fit <- historic_spp %>% 
-  group_by(state,year,region,spp,spatial) %>% 
+  group_by(state,year,label,region,spp,spatial) %>% 
   summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
@@
 
+# Shaded period 
+historic_periods <- historic_spp %>% 
+  filter(label == "Reference") %>% 
+  group_by(spp,label,year) %>% 
+  summarise(n = n()-n()+100) %>% 
+  mutate(period = "Reference period")
+
 # Plot me
-ssp_area <- ggplot(state_fit) +
+ssp_area <-
+  ggplot(state_fit) +
   geom_area(
@@
   ) +
-  annotate(geom= "rect",
-           xmin = 1980, xmax = 2001, 
-           ymin = 0, ymax = 100,
-            fill = "gray90",
-           colour = NA,
-           alpha = 0.5) +
+  geom_area(data = historic_periods,
+             aes(
+               x = year,
+               y = n,
+               color = period
+             ),
+             # fill = "gray90",
+             alpha = 0.3,
+            stat = "identity"
+             ) +
+  # annotate(geom= "rect",
+  #          xmin = 1980, xmax = 2001, 
+  #          ymin = 0, ymax = 100,
+  #           fill = "gray90",
+  #          colour = NA,
+  #          alpha = 0.5) +
   ylab("Propotion (10 yrs running average)") +
@@
     labels = state_fit %>% arrange(order) %>%  pull(state) %>% unique()
+  ) +
+    scale_color_manual("",values = "grey90"
   ) +

### 2021-10-26 Scripts/manuscript_acrossboundaries.Rmd
Included reference dates for each stock

@@
 
-Seasonality of fish distributions in temperate waters is key for proper management of marine ressources [@Bell2014].
+Seasonality of fish distributions in temperate waters is key for proper management of marine resources [@Bell2014].
 Along the U.S.
-Northeast EEZ, muny species like black sea bass (*Centropristis striata*) and scup (*Stenotomus chrysops*) present substantial latitudinal migration in response to water temperature fluctuation [@Bell2015; @Henderson2017].
+Northeast EEZ, many species like black sea bass (*Centropristis striata*) and scup (*Stenotomus chrysops*) present substantial latitudinal migration in response to water temperature fluctuation [@Bell2015; @Henderson2017].
 Changes in distribution also follow a depth patter like the case of summer flounder (*Paralichthys dentatus*) who undergoes annual migrations from shallow coastal habitats in the fall to deeper habitats over winter (Terceiro, 2001; Sackett et al., 2007).
@@
 Here, we examine both of these challenges by quantifying the historical distributions of three important fished species relative to 11 states of the Northeast Atlantic U.S that jointly manage these stocks.
-Specifically, we set two main objectives.
-First, we examine the difference between two different approaches to define spatial management jurisdictions within the U.S.
+Specifically, we ask *how does the choice of survey timing and boundary extrapolation method influence our perception of fish distribution changes relative to management boundaries?* To answer this question we first, examine the difference between two different approaches to define spatial management jurisdictions within the U.S.
 Federal waters.
 Second, we examine differences in the species' historical distribution between Spring and Fall to examine seasonal variation in these stock's distributions.
-
- "How does the choice of survey timing and boundary extrapolation method influence our perception of fish distribution changes relative to management boundaries?"
 
@@
 
-Next, we estimated the CPUE percentage change today relative to the historic period.
-For that matter we define the historic period as 1980 to 2000 representing the state allocations of the commercial fisheries originally implemented in 2003 [@RefDocument], and “today” as the average of 2009 to 2019 representing the more recent data available.
-The parentage changes between the historic and present CPUE ($\Delta{B}$) was estimate for each of the two regulatory units approaches as;
+Next, we estimated the CPUE percentage change today relative to the period used to determine the current quota for each stock.
+Today is defined as the average of 2009 to 2019 representing the more recent data available.
+
+For summer flounder, the quota allocation period covers 1980 to 1986 determined in the original management plan [@Ammendment4; 9.1.2.3.1.
+Commercial quota page 12], for scup the period covers 1988 to 1992 according to Amendment 8 of the original management plan ([@Ammendment8]; **Section 9.1.2.3.7.
+Commercial quota, page 48 and Table 40**) and for black sea bass Amendment 13 sets the state-wide quota based on historic landings from 1980 to 2001 (@REF; **Amendment 13- Alternative 5f; section 2.1.5.6 (Pages 3, 14, and 304-Table 5**).
+The parentage changes between the historic and present CPUE ($\Delta{B}$) was estimate per stock for each of the two regulatory units approaches as;
+
+**NOTE: There is a "complicated" estimation for summer flounder in Connecticut we are currently ignoring.
+Commercial landings of summer flounder would be adjusted to account for undocumented commercial landings of summer flounder in the State of Connecticut for the years 1980 to 1986.
+The 1987-91 proportion of Connecticut's landings relative to the combined landings of Massachusetts, Rhode Island, New York and New Jersey would be derived and applied to the combined landings of these four States for the years 1980-86 to derive an adjusted Connecticut value for each year 1980-86 (Table 2).
+These adjusted values would be used to derive the state-specific shares of the coastwide summer flounder quota.
+The adjusted allocation formula would be implemented in 1993.**
 
@@
 All values in percentage.
-Differences in absolute values](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F3_proportion_chg.jpg)
+Differences in absolute values](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F3_proportion_chg_reg.jpg)
 
@@
 Differences in absolute values.
-](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/proportion_chg_seas.jpg)
+](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F4_proportion_chg_seas.jpg)
 
-Over the last 40 years, the proportion of the CPUE has increased for northern states and decreased for southern states for all species (Figure 6).
+Over the last 40 years, the proportion of the CPUE has increased for northern states and decreased for southern states for all species (Figures \@ref{fig:figAreaPlot}).
 North Carolina and Virginia have been the most affected for all three species, regardless of the regulatory unit approach.

### 2021-10-26 Allocation_tool/server.R
First set of figures ready

@@ -329,9 +329,9 @@ shinyServer(function(input, output) {
         }
     })
     
-    # ---------------------------- #
-    # TIF distribution map ####
-    # ---------------------------- #
+# ---------------------------- #
+### TIF distribution map ####
+# ---------------------------- #
     output$distPlot <- renderPlot({
         
         # Set the filters
@@ -389,7 +389,7 @@ shinyServer(function(input, output) {
     })
     
     # ---------------------------- #
-    # Proportion map ######
+    ### Proportion map ######
     # ---------------------------- #
     output$propPlot <- renderPlot({
         
@@ -459,7 +459,7 @@ shinyServer(function(input, output) {
     
     
     # ---------------------------- #
-    # Difference map ######
+    ### Difference map ######
     # ---------------------------- #
     output$propDiffPlot <- renderPlot({
         
@@ -512,7 +512,7 @@ shinyServer(function(input, output) {
     })
     
     # ---------------------------- #
-    # Allocation Table ####
+    ### Allocation Table ####
     # https://www.littlemissdata.com/blog/prettytables
     # ---------------------------- #
     
@@ -562,4 +562,7 @@ shinyServer(function(input, output) {
         )
     })  # close formattable
     
+    # ---------------------------- #
+    # Tool end ####
+    # ---------------------------- #
 }) # app closure

### 2021-10-26 Allocation_tool/ui.R

@@ -107,125 +107,3 @@ dashboardPage(
         ) # row
     ) # body
 )
-
-
-
-#                                         checkboxGroupInput(inputId = "PlotStyle",
-#                                                            label = "Select Result",
-#                                                            choices = c(
-#                                                                "Survey Points" = 1,
-#                                                                "Latitudinal Shift" = 2,
-#                                                                "Distribution" = 3
-#                                                            ),
-#                                                            selected = 1
-#                                         )
-#                                     ),
-#                                     mainPanel(
-#                                         
-#                                     ) # main panel
-#                                 ),
-#                                 br(),
-#                                 column(
-#                                     12,
-#                                     align = "justified",
-#                                     h1("Determine the reugulatory unit approach")
-#                                 ),
-#                                 # ----------------------- #
-#                                 ## Regulatory Unit ####
-#                                 # ----------------------- #
-#                                 # Sidebar with a slider input for number of bins
-#                                 sidebarLayout(
-#                                     sidebarPanel(
-#                                         # Select sf Area
-#                                         selectInput(inputId = "SpatSelection",
-#                                                     label = "Select Management Unit",
-#                                                     choices = c("State waters" = 1,
-#                                                                 "Fishing ports" = 2,
-#                                                                 "Both apporaches" = 3),
-#                                                     # selected = "State waters",
-#                                                     width = "220px"
-#                                         ),
-#                                         p("If you chosed the port approach, determine a treshold"),
-#                                         # Set Time Range
-#                                         sliderInput("PortTreshold",
-#                                                     "Port threshold",
-#                                                     min = 5,
-#                                                     max = 95,
-#                                                     value = 75)
-#                                     ), # Close side panel
-#                                     # Show a plot of the generated distribution
-#                                     mainPanel(plotOutput("RegUnit")) # main panel
-#                                 ), # Side bar
-#                                 # ----------- #
-#                                 # Allocations results
-#                                 # ----------- #
-#                                 br(),
-#                                 column(
-#                                     12,
-#                                     align = "justified",
-#                                     h1("Allocation Results")
-#                                 ),
-#                                 # Sidebar with a slider input for number of bins
-#                                 sidebarLayout(
-#                                     sidebarPanel(
-#                                         # Select which plot you want to create
-#                                         checkboxGroupInput(inputId = "ResultType",
[…]

### 2021-10-27 Scripts/manuscript_acrossboundaries.Rmd
FIrst discussion draft

@@
 
-Next, we estimated the CPUE percentage change today relative to the period used to determine the current quota for each stock.
-Today is defined as the average of 2009 to 2019 representing the more recent data available.
-
+Next, we estimated the CPUE percentage change today relative to a historic time period.
+We defined today as the average of 2009 to 2019 representing the more recent data available.
+The historic time period is determine by the years used to set the state-wide quota for each stock.
 For summer flounder, the quota allocation period covers 1980 to 1986 determined in the original management plan [@Ammendment4; 9.1.2.3.1.
@@
 
+Marine species have been shifting globally in response to climate change [@Bell; @Pinsky] and are expected to continue towards the end of the century [@Morey; @Pinsky].
+Such shifts challenge ocean governance, particularly when dealing with shared stocks that cross international and national management boundaries [@PalaciosAbrantes2020; @Pisnky2018; @Oremus2020 @Pinsky2014; @Pinsky2014].
+Managers are having to design new management strategies as is the case presented here of the Mid-Atlantic Fishery Management Council (MAFMC) who oversees black sea bass, summer flounder, and scup in the Northeast Atlantic Coast of the US [@MidAtlantic; @Link2010].
+However, as our results show, designing these new strategies is not straightforward under the current MAFMC governance framework.
+Moreover, as species shift their distribution, quota allocations need to be dynamic which means they also have to account for the natural variability of the stock's distribution.
+
+The joint management of shared stocks relies on defined boundaries (i.e., regulatory units) where each share-holder has right to fishing [@Munro].
+In the northeast Pacific, for example, the joint management of Pacific halibut (*Hippoglossus stenolepis*) by Canada and the US relies on multiple regulatory areas that covers the EEZ's of both countries [@IPHC].
+In the case of the MAFMC, the method for designing regulatory areas in Federal waters will have large consequences in the allocation of quota to each state (Figs.
+3-5).
+The fishing ports approach relates to many cases around the world, where spatial fishing rights are allocated to share-holders based on historical landings [@Chile; @EU] or location of fishing grounds [@Mexico].
+These methods are seen fair in that they respect the historical investment of individuals in the fishery [@REF].
+However, such approach has the potential to exclude users from the fishery, like the case of Maine, New Hampshire and Connecticut (Figure 1).
+Moreover, because it is based on historical landings, it does not necessarily account for biomass changes across regulatory areas, nor expansion to new regulatory areas [@Pinsky2018].
+The exclusion of both historic and new share-holders can result in conflict and unsustainable harvest as seen in multiple fisheries across the world and within the US [@Pinsky2018; @Pinsky2014; @ChileLoco; @Spijkers].
+
+Designing regulatory units by expanding current state waters approach would not exclude share-holders that historically have fish less of a certain stock.
+In our study, by giving regulatory units to Maine, Connecticut and New Hampshire we account for the shifts in stock biomass allowing these states to benefit from the fishery as the stocks move poleward (Figures 3 and 5).
+However, such a definition might not be seen as fair to those share-holders that have historically invested in the fishery [@REF].
+Fishers might still be willing to navigate longer distances to "follow the fish" rather than changing target species or even drooping out of the fishery [@Polcanza].
+
+Allocating quota based on current distributions, rather than historical reference points, should improve the resilience of management plans to climate change driven shifts in stocks distribution.
+Modelling exercises suggest that the management plan for pacific halibut is resilient to climate change as quota is allocated to each regulatory area based on the current distribution of the stock [@Palacios-Abrantes2020; @Sumaila2020].
+A combination of both historic and current distributions has also been used to manage shared stocks.
+The TRAC in the Gulf of Maine recommends quota for cod (*Gadus morhua*), haddock (*a*) and yellowtail flounder (*ss*) employing an algorithm that accounts 90% of stocks current distribution and 10% of historic distribution.
+Here, we found differences in the distribution of the stocks between the years when the quota was determined (i.e., historical period) and current values (Figures 2 and 3).
+This results suggest that current allocation policies might not be efficient in terms of biomass, this is specially true for black sea bass and scup.
+
+**Uncertainty (management challenges)**
+
+- Federal vs state waters legal perspectives
+- Multiple agencies / states
+- Multiple-species fisheries
+
+**Moving forward (recommendations)**
+
+**Conclusion**
+
 # Supplements

### 2021-10-27 Allocation_tool/ui.R
Completley changed UI. Included segments and a home apge

@@ -7,103 +7,274 @@
 #    http://shiny.rstudio.com/
 #
 
-# Load libraries and data
+
 MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","plotly","formattable","shinydashboard"))
 
 spp_survey <- read.csv("./data/spp_region.csv") %>% 
-    filter(
-        # spp %in% c ("Centropristis striata","Gadus morhua"),
-        region %in% c("Northeast US Fall" , "Northeast US Spring")) #No more seasons
+  filter(
+    # spp %in% c ("Centropristis striata","Gadus morhua"),
+    region %in% c("Northeast US Fall" , "Northeast US Spring")) #No more seasons
 
 
-
-
-# Define UI for application that draws a histogram
 
 dashboardPage(
-    dashboardHeader(title = "Across Boundaries Project"),
-    dashboardSidebar(
-        selectizeInput(
-            'SppSelection', '1. Species', choices = c("Centropristis striata","Paralichthys dentatus","Stenotomus chrysops"),
-            options = list(
-                placeholder = 'Type to search for species',
-                onInitialize = I('function() { this.setValue(""); }')
-            )
-        ),
-        selectizeInput(
-            'SurveySelection', 
-            '2. Select Survey Season(s)', 
-            choices = unique(spp_survey$region),
-            options = list(
-                placeholder = 'Type to select a season',
-                onInitialize = I('function() { this.setValue(""); }')
-            )
-        ),
-        selectizeInput(
-            'SpatSelection',
-            '2. Select Regulatory Unit', choices = c("State waters","Fishing ports","Both apporaches"),
-            options = list(
-                placeholder = 'Select an approach',
-                onInitialize = I('function() { this.setValue(""); }')
-            )
-        ),
-        sliderInput(inputId = "YearSelection",
-                    label = "Select year range of distribution",
-                    min = 1972,
-                    max = 2019,
-                    step = 1,
-                    sep = "",
-                    animate = FALSE,
-                    value = c(2010,2019)
-        ),
-        sliderInput(inputId = "treshold",
-                    label = "Choose port trshold",
-                    min =75,
-                    max = 100,
-                    step = 1,
-                    sep = "",
-                    animate = FALSE,
-                    value = 75
-        ),
-        tags$p("Note: The treshold input will only apply for the Port Aproach. It determines the top ports to be included in the analysis."),
-        
[…]

### 2021-10-27 Allocation_tool/ui.R
Created home and inromation page

@@ -31,79 +31,87 @@ dashboardPage(
   # Body ####
   dashboardBody(
     tabItems(
-      ## Information Body ####
+      ## Home Body ####
       tabItem(tabName = "home",
               column(12,
                      align = "center",
-                     h1("Welcome to the quota allocation tool!"),
+                     h1("Welcome to the Across Boundaries quota allocation tool!"),
               ),
               column(
-                width = 8,
-                offset = 2,
+                width = 10,
+                offset = 1,
                 align = "justified",
-                h4("This is a dynamic tool. It was build with the objective of exploring different
+                h4("This tool was build with the objective of exploring different
                   management apporaches to address changes in stocks distribution across management boundaries
-                    in response to a chanign climate. The tool focuses on three stocks of the Northeast United 
-                    States and is part of the project, Managing across boundaries: preventing interjurisdictional
-                     conflicts arising from shifting fish stocks")
+                    in response to a changing climate. The tool focuses on three stocks of the Northeast United 
+                    States and is part of the project", em("Managing across boundaries: preventing interjurisdictional
+                     conflicts arising from shifting fish stocks"))
               ),
               column(
-                width = 8,
-                offset = 2,
-                alijn = "justified",
-                h4("Navigate below to know more about the project. Or go to Tool in the left pannel to access 
-                     the dynamic tool")
+                width = 10,
+                offset = 1,
+                align = "justified",
+                h4("Below you can find information on the stocks available to explore in the tool.
+                  Navigate to",em("Tool"),"in the left pannel to access 
+                   the dynamic tool", em("Information"), "to know more about the project and", em("Instructions"),
+                   "to get familiarized with the tool.")
               ), # Close fluid row
+              column(
+                width = 12,
+                align = "justified",
+                h2("Info on availabel stocks"),
+                h4("Click in each picture to go to NOAAs site for the management of the stock")
+              ),
               fluidRow(
                 box(
                   width = 4,
                   solidHeader = TRUE,
                   collapsible = FALSE,
                   title = "Black sea bass",
-                  status = "primary", # blue color
+                  background = "black",
                   a(img(src= 'https://media.fisheries.noaa.gov/styles/original/s3/dam-migration/640x427-black-sea-bass.png?itok=7Ax8suz_',
                         height = 200,
                         width = 300),
                     title = "Go to NOAA",
                     href="https://www.fisheries.noaa.gov/species/black-sea-bass"),
[…]

### 2021-10-27 Allocation_tool/ui.R
Tool looks good. inlcuded dowload option

@@ -19,19 +19,71 @@ spp_survey <- read.csv("./data/spp_region.csv") %>%
 
 dashboardPage(
   dashboardHeader(title = "Across Boundaries Project"),
+  #______________________________________________________________________#
   # Sidebar  ####
+  #______________________________________________________________________#
   dashboardSidebar(
     sidebarMenu(
       menuItem("Home", tabName = "home", icon = icon("home")),
+      br(),
+      br(),
       menuItem("Information", tabName = "info", icon = icon("info")),
+      br(),
+      br(),
       menuItem("Tool", tabName = "dashboard", icon = icon("dashboard")),
-      menuItem("Instructions", tabName = "instructions", icon = icon("gear"))
-    )
+      br(),
+      br(),
+      menuItem("Instructions", tabName = "instructions", icon = icon("gear")),
+      menuItem(
+        "Download report",
+        tabName = "download",
+        icon = icon("download"),
+        textInput(
+          inputId = "filename",
+          placeholder = "Name download file",
+          label = ""
+        ),
+        div(
+          downloadButton(
+            outputId = "downloadData",
+            label = "Download report",
+            icon = icon("download"),
+            style = "color: black; margin-left: 15px; margin-bottom: 5px;"
+          )
+        ),
+        div(
+          downloadButton(
+            outputId = "downloadMicroData",
+            label = "Download processed data",
+            icon = icon("download"),
+            style = "color: black; margin-left: 15px; margin-bottom: 5px;"
+          )
+        )
+      ),
+      br(),
+      br(),
+      br(),
+      br(),
+      br(),
+      br(),
+      br()
+    ),
+    hr(style = "border-top: 3px dashed lightgrey;"),
+    p("For any inquery regarding this tool, please email us at 
+    jpalacios2[at]wisc.edu"),
+    a(img(src= 'https://github.githubassets.com/images/modules/logos_page/Octocat.png',
+          height = 50,
+          width = 50),
+      href="https://github.com/jepa/AcrossBoundaries")
   ),
+  #______________________________________________________________________#
   # Body ####
+  #______________________________________________________________________#
   dashboardBody(
     tabItems(
-      ## Home Body ####
+      #______________________________________________________________________#
+      ## Home ####
+      #______________________________________________________________________#
       tabItem(tabName = "home",
               column(12,
                      align = "center",
@@ -54,7 +106,7 @@ dashboardPage(
                 h4("Below you can find information on the stocks available to explore in the tool.
[…]

### 2021-10-27 Allocation_tool/ui.R
misc.

@@ -26,14 +26,12 @@ dashboardPage(
     sidebarMenu(
       menuItem("Home", tabName = "home", icon = icon("home")),
       br(),
-      br(),
       menuItem("Information", tabName = "info", icon = icon("info")),
-      br(),
       br(),
       menuItem("Tool", tabName = "dashboard", icon = icon("dashboard")),
       br(),
-      br(),
       menuItem("Instructions", tabName = "instructions", icon = icon("gear")),
+      br(),
       menuItem(
         "Download report",
         tabName = "download",
@@ -60,6 +58,9 @@ dashboardPage(
           )
         )
       ),
+      br(),
+      br(),
+      br(),
       br(),
       br(),
       br(),
@@ -248,10 +249,12 @@ dashboardPage(
                   status = "primary", # blue color
                   # p("Inst. Select here the species you want to explore"),
                   selectizeInput(
-                    'SppSelection',"", choices = c("Centropristis striata","Paralichthys dentatus","Stenotomus chrysops"),
+                    'SppSelection',"",
+                    choices = c("Centropristis striata","Paralichthys dentatus","Stenotomus chrysops"),
                     options = list(
                       placeholder = 'Type or click to search for species',
                       onInitialize = I('function() { this.setValue(""); }')
+                      
                     )
                   )
                 ),
@@ -268,7 +271,8 @@ dashboardPage(
                     options = list(
                       placeholder = 'Type or click to select a season',
                       onInitialize = I('function() { this.setValue(""); }')
-                    )
+                    ),
+                    selected = unique(spp_survey$region)[1]
                   )
                 ),
                 box(
@@ -283,7 +287,8 @@ dashboardPage(
                     options = list(
                       placeholder = 'Type or click to select an approach',
                       onInitialize = I('function() { this.setValue(""); }')
-                    )
+                    ),
+                    selected = "State waters"
                   )
                 ),
                 box(
@@ -323,8 +328,6 @@ dashboardPage(
               hr(style = "border-top: 3px dashed lightgrey;"),
               h1("Results"),
               h4("Here you will see the results from your query.", em("Note some graphs can take some time to apear depending on your internet connection")),
-              fluidRow(
-              ),
               #______________________________________________________________________#
               ### Results ####
               #______________________________________________________________________#

### 2021-10-27 Allocation_tool/server.R
Created a button to clear all oputputs

@@ -93,132 +93,94 @@ grids <- my_path("D", "Spatial/grid_eez_fp", name = "grid_eez_fp_df.csv", read =
 # ---------------------------- #
 # Tool start ####
 # ---------------------------- #
-shinyServer(function(input, output) {
+shinyServer(function(input, output,session) {
     
-    # ---------------------------- #
-    # Biological Survey Data ####
-    # ---------------------------- #
-    raw_data <- reactive({
-        
-        name <- paste0("obs_",str_replace(input$SppSelection," ","_"),".csv")
-        
-        data <- my_path("D","Spp/Observation",name = name, read = T)
-        
-        # data <- readRDS("/Volumes/Enterprise/Data/AcrossBoundaries/Data/pinskylab-OceanAdapt-966adf0/data_clean/dat_exploded.rds") %>%
-        #     filter(
-        #         spp %in% c("Centropristis striata","Paralichthys dentatus","Stenotomus chrysops"),
-        #         region %in% c("Northeast US Fall" , "Northeast US Spring")
-        #     ) #No more seasons
-        
-    })
-    
-    
-    # ---------------------------- #
-    # Extrapolated data
-    # Triangular Irregular Surface  
-    # ---------------------------- #
-    
-    
-    tif_data <- reactive({
-        
-        name <- paste0("tif_",str_replace(input$SppSelection," ","_"),".csv")
-        
-        # Set the filters
-        species <- input$SppSelection #"Centropristis striata"
-        survey <-input$SurveySelection # "Northeast US Fall"
-        reg_area <- input$SpatSelection # "State waters"
-        
-
-        data <- my_path("R","Partial/Interpolation/",name = name, read = T) %>% 
-            left_join(grids,
-                      by = c("index","lon","lat")
-            ) %>%
-            filter(!is.na(spatial)) %>% 
-            mutate(
-                spatial = ifelse(spatial == "fp","Fishing ports",
-                                 ifelse(spatial == "sw","State waters","Difference")
-                )
-            ) %>% 
-            filter(spp %in% species,
-                   region %in% survey,
-                   spatial %in% reg_area)
-        
-        # For testing
-        # data <- my_path("R","Partial/Interpolation/",name = "tif_Centropristis_striata.csv", read = T)
-        
-        
-        # tif_data <- data %>%
-        #     left_join(grids,
-        #               by = c("index","lat","lon")
-        #     ) %>%
-        #     filter(!is.na(spatial)) %>%
-        #     mutate(
[…]

### 2021-10-27 Allocation_tool/ui.R

@@ -8,7 +8,7 @@
 #
 
 
-MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","plotly","formattable","shinydashboard"))
+MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","plotly","formattable","shinydashboard","shinyjs"))
 
 spp_survey <- read.csv("./data/spp_region.csv") %>% 
   filter(
@@ -234,6 +234,7 @@ dashboardPage(
       ## Tool ####
       #______________________________________________________________________#
       tabItem(tabName = "dashboard",
+              useShinyjs(),
               h1("Control panel"),
               h4("Please select from the following options in the blue boxes.", em("Note that all options need to be selected in order for results to apear")),
               #______________________________________________________________________#
@@ -249,12 +250,11 @@ dashboardPage(
                   status = "primary", # blue color
                   # p("Inst. Select here the species you want to explore"),
                   selectizeInput(
-                    'SppSelection',"",
+                    "SppSelection","",
                     choices = c("Centropristis striata","Paralichthys dentatus","Stenotomus chrysops"),
                     options = list(
                       placeholder = 'Type or click to search for species',
                       onInitialize = I('function() { this.setValue(""); }')
-                      
                     )
                   )
                 ),
@@ -325,6 +325,19 @@ dashboardPage(
                   tags$p("Note: The treshold input will only apply for the Port Aproach. It determines the top ports to be included in the analysis."),
                 )
               ),
+              column(12,
+                     align = "center",
+              actionButton("do",
+                           "Run Query",
+                           icon = icon("gear"),
+                           class = "btn-warning"
+                           ),
+              actionButton("reset",
+                           "Clear all",
+                           icon = icon("clean"),
+                           class = "btn-warning"
+              ),
+              ),
               hr(style = "border-top: 3px dashed lightgrey;"),
               h1("Results"),
               h4("Here you will see the results from your query.", em("Note some graphs can take some time to apear depending on your internet connection")),
@@ -386,3 +399,4 @@ dashboardPage(
     )
   )# Close instructions
 )
+# )

### 2021-10-29 Scripts/spatial_analisis.Rmd
updated top ports using NOAA's data

@@
 
-###### 4.1.1 Ports coordinates
+Dataset provider: Joe Myers Joseph.Myers@accsp.org NOAA
+
+Non-confidential dataset containing annual landings/value summaries by port for black sea bass, scup and summer flounder, from NC-ME for 1970-2020.
+
+In order to make the report non-confidential, I am displaying as much of the port-level summary data as I can – and for cases where the port-level was confidential, I have first attempted to roll-up any confidential port-level summaries into state-level summaries within the same year.
+If those state-level summaries continue to be confidential, I have further rolled-up those confidential ports across states into a coast-level summary.
+Even at the coast level, there were several cases where not enough confidential ports could be combined to produce a non-confidential summary – and so for those rows it was necessary to redact the final landings/value data.
+Fortunately, this only amounts to less than 0.5% of the total landings data (characterized in the “Pivot by Confidentiality” tab of the spreadsheet).
+
+*License???.*
+
+```{r}
+# NOAA DATA
+
+ports_path <- my_path("D","NOAA", name = "PalaciosJ - BSB, SFlounder, Scup by Port 1970-2020 - 2021.10.25.xlsx")
+
+# Load ports
+ports_data <- read_excel(ports_path,sheet = 2) %>% 
+  clean_names() %>%
+  mutate_if(is.character,
+            ~ str_to_lower(.)
+  ) %>% 
+  mutate(
+    species_name = ifelse(str_detect(common_name,"black"),"black sea bass",
+                 ifelse(str_detect(common_name,"summer"),"summer flounder",
+                        common_name)
+    ),
+    total_live_pounds = as.numeric(total_live_pounds),
+    total_value = as.numeric(total_value)
+  ) %>% 
+  filter(
+    !port_name %in% c("**roll-up to state-wide**","**roll-up to coast-wide**","unknown")
+  )
+```
+
+###### 4.1.1 Top ports
+
+```{r}
+# Get number of ports in the NOAA database
+overall_port_data <- ports_data %>%
+  filter(year >= 2010 & year <= 2019) %>% 
+  group_by(species_name,port_name,state_postal) %>% 
+  summarise(
+    year_ton = sum(total_live_pounds),
+    year_value = sum(total_value)
+  )
+
+top_ports <- bind_rows(
+  # 75th percentile used in project
+  overall_port_data %>% 
+    group_by(species_name) %>% 
+    top_frac(0.25,year_ton) %>%  # top 75
+    mutate(tresh = "75th"),
+  # -------------------- #
+  # For sensitivity values
+  # -------------------- #
+  # 95%
+  overall_port_data %>% 
+    group_by(species_name) %>% 
+    top_frac(0.5,year_ton) %>%  
+    mutate(tresh = "95th"),
+  # 85%
+  overall_port_data %>% 
+    group_by(species_name) %>% 
+    top_frac(0.15,year_ton) %>% 
+    mutate(tresh = "85th"),
+  # 65%
+  overall_port_data %>% 
+    group_by(species_name) %>% 
+    top_frac(0.35,year_ton) %>%  # top 75
+    mutate(tresh = "65th"),
+  # 50%
+  overall_port_data %>% 
+    group_by(species_name) %>% 
+    top_frac(0.5,year_ton) %>%  # top 75
+    mutate(tresh = "50th")
+)
+
+```
+
+###### 4.1.2 Ports coordinates
 
@@
     "lewes, DE, ", # 38.78943640990542, -75.06343692610851
-    "virginia beach, VA" # 36.859343385722504, -75.94328398140065
+    "virginia beach, VA", # 36.859343385722504, -75.94328398140065
+    "hampton bays, ny", #40.84229040189204, -72.50987544040999
+    "mattituck, ny", # 41.05342836192293, -72.59899214258269
+    "little compton, ri", # 41.4765103461213, -71.19474641579107
+    "new london, CT", #41.341577207467914, -72.0829697106489
+    "amagansett, ny", # 40.96173008633569, -72.11879306740798
+    "barnegat light, nj", #39.75291152662383, -74.09927831868308
+    "chatham (census name for chatham center), MA", # 41.658695421122474, -69.95466452556448
+    "dennis, ma", #41.65121037263873, -70.13193663798509
+    "falmouth (census name for falmouth center), ma", #41.53956327146526, -70.60001340709665,
+    "freeport, ny", #40.62242387473109, -73.59162509402208
+    "nantucket (census name for nantucket center), MA", #41.26616088210985, -69.95617277257985
+    "newport, RI",
+    "point lookout, ny", #40.587646134955875, -73.5763748512927
+    "shinnecock indian reservation, ny", #40.865873983968754, -72.4420929172018
+    "westport, ma"
   )),
@@
     38.78943640990542,
-    36.859343385722504
+    36.859343385722504,
+    40.84229040189204,
+    41.05342836192293,
+    41.4765103461213, 
+    41.341577207467914,
+    40.96173008633569, 
+    39.75291152662383, 
+    41.658695421122474,
+    41.65121037263873, 
+    41.53956327146526, 
+    40.62242387473109,
+    41.26616088210985, 
+    41.485514346683956,
+    40.587646134955875,
+    40.865873983968754,
+    41.49267875746873
   ),
@@
     -75.06343692610851,
-    -75.94328398140065
-  )
-) %>% 
-  separate(port, into = c("landing_port","landing_state"), sep = ',') %>% 
-  mutate(landing_state = str_squish(str_to_upper(landing_state)),
-         landing_port = str_to_lower(landing_port))
-
-noaa_ports
-
-```
-
-###### 4.1.1 Top ports
-
-This dataset includes all landings from 2015-July 2021. It includes the species landed, the port, and the Hull ID and vessel name for black sea bass and summer flounder.
-
-*License, from Sarah Smith: This is confidential data, so please do not share this file with others.
-You may need to contact NOAA directly just to request permission.
-My contact has been Alison Ferguson (Alison.Ferguson@noaa.gov) in their data department.*
-
-NOTES:
-
-- There is no Maine, Delaware, nor New Hamshire in the data. Took them from NOAA as main ports of all fisheries
-
-```{r}
-
-### SRAH LANDING DATA
-read_excel_allsheets <- function(filename, tibble = TRUE) {
-    # I prefer straight data.frames
-    # but if you like tidyverse tibbles (the default with read_excel)
-    # then just pass tibble = TRUE
-    sheets <- readxl::excel_sheets(filename)[2:8]
-    x <- lapply(sheets, function(X) readxl::read_excel(filename, sheet = X))
-    if(!tibble) x <- lapply(x, as.data.frame)
-    names(x) <- sheets
-    x
-}
-# Get data path
-ports_path <- my_path("D","NOAA", name = "SSmith_2015-2021 Landings_JUN 2021.xlsx")
-
-# Load ports
-ports_data <- bind_rows(read_excel_allsheets(ports_path)) %>%
-  clean_names() %>%
-  mutate_if(is.character,
-              ~ str_to_lower(.)) %>%
-    filter(species_name %in% c("summer flounder","black sea bass","scup"))
-
-noaa_ports <- unique(ports_data$landing_port)
-
-# Get number of ports in the NOAA database
-top10_ports <- ports_data %>% 
-  mutate(landing_state = str_to_upper(landing_state)) %>% 
-  filter(landing_state %in% c("CT","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VA")) %>% 
-  group_by(year,landing_port,landing_state,species_name) %>% 
-  summarise(
-    year_ton = sum(landed_weight),
-    year_value = sum(value),
-    noaa_ports = length(unique(landing_port))
-    ) %>% 
-  group_by(landing_port,landing_state,species_name) %>% 
-  summarise_if(is.numeric,sum) %>% 
-  group_by(species_name) %>% 
-  top_n(10,year_ton)
+    -75.94328398140065,
+    -72.50987544040999,
+    -72.59899214258269,
+    -71.19474641579107, 
+    -72.0829697106489,
+    -72.11879306740798,
+    -74.09927831868308,
+     -69.95466452556448,
+    -70.13193663798509,
+    -70.60001340709665,
+     -73.59162509402208,
+    -69.95617277257985,
+     -71.32263326975122,
+     -73.5763748512927,
+     -72.4420929172018,
+    -71.05551342392039
+  )
+) %>% 
+  separate(port, into = c("port_name","state_postal"), sep = ',') %>% 
+  mutate(port_name = str_to_lower(port_name),
+         state_postal = str_squish(state_postal))
+
+# Include coordinates
+noaa_ports_complete <- top_ports %>% 
+  left_join(noaa_ports,
+             by = c("port_name", "state_postal"))
+
+# Check for missing ports
+noaa_ports_complete %>% 
+  filter(tresh == "75th",
+    is.na(lat)) %>% 
+  group_by(port_name,state_postal) %>% 
+  summarise(n()) %>% 
+  View()
+
+# Save data for future analysis
+
+write_csv(noaa_ports_complete,
+          my_path("D","NOAA", name = "top_ports.csv")
+          )
 
@@
     ),
-    size = 5
-  )
-
-```
-
-```{r}
-# Get number of ports in the NOAA database
-total_ports <- ports_data %>% 
-  mutate(landing_state = str_to_upper(landing_state)) %>% 
-  filter(landing_state %in% c("CT","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VA")) %>% 
-  group_by(species_name) %>% 
-  summarise(
-    total_ton = sum(landed_weight, na.rm = T),
-    total_value = sum(value, na.rm = T)
-    )
-
-# Per landings
-
-per_ports <-
-  ports_data %>% 
-  mutate(landing_state = str_to_upper(landing_state)) %>% 
-  filter(landing_state %in% c("CT","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VA")) %>% 
-  group_by(landing_port,species_name) %>% 
-  summarise(
-    port_ton = sum(landed_weight),
-    port_value = sum(value)
-    ) %>% 
-  left_join(total_ports,
-            by = "species_name") %>% 
-    mutate(
-      per_tons = round((port_ton/total_ton)*100,2),
-      per_value = round((port_value/total_value)*100,2)
-    ) %>% 
-    # select(landing_port,species_name,per_tons,everything()) %>% 
-    ungroup() %>% 
-    arrange(desc(per_tons)) %>% 
-    group_by(species_name) %>% 
-    mutate(cum_per = cumsum(per_tons)) %>% 
-    filter(cum_per <= 75) %>% 
-  select(landing_port,species_name,port_ton,per_tons,cum_per,everything()) %>% 
-  arrange(desc(species_name,cum_per))
-
-per_ports
-
-```
-
-```{r}
-
-per_ports %>% 
-  left_join(noaa_ports) %>% 
-  # Double ceck coordinates are all there
-  # filter(is.na(lon))
-  ggplot() +
-  geom_point(
-    aes(
-      x = lon,
-      y = lat,
-      shape = species_name,
-      color = species_name
-    ),
-    size = 5
-  )
-
-ports_df <-  per_ports %>% 
-  left_join(noaa_ports)
+    size = 5,
+    alpha = 0.5
+  )
 
@@
 ![Proportion change aggregated all species map for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/proportion_chg_agg.jpg)
+```{r sarah_landings_data}
+
+### SRAH LANDING DATA
+# read_excel_allsheets <- function(filename, tibble = TRUE) {
+#     # I prefer straight data.frames
+#     # but if you like tidyverse tibbles (the default with read_excel)
+#     # then just pass tibble = TRUE
+#     sheets <- readxl::excel_sheets(filename)[2:8]
+#     x <- lapply(sheets, function(X) readxl::read_excel(filename, sheet = X))
+#     if(!tibble) x <- lapply(x, as.data.frame)
+#     names(x) <- sheets
+#     x
+# }
+# Get data path
+# ports_path <- my_path("D","NOAA", name = "SSmith_2015-2021 Landings_JUN 2021.xlsx")
+
+# Load ports
+# ports_data <- bind_rows(read_excel_allsheets(ports_path)) %>%
+#   clean_names() %>%
+#   mutate_if(is.character,
+#               ~ str_to_lower(.)) %>%
+#     filter(species_name %in% c("summer flounder","black sea bass","scup"))
+
+```

### 2021-10-29 Scripts/spatial_analisis.Rmd
saved top port data for future analysis

@@
   left_join(noaa_ports,
-             by = c("port_name", "state_postal"))
+             by = c("port_name", "state_postal")) %>% 
+  mutate(
+    state_postal = str_to_upper(state_postal)
+  )
 
@@
 # Save data for future analysis
-
-write_csv(noaa_ports_complete,
-          my_path("D","NOAA", name = "top_ports.csv")
-          )
+# write_csv(noaa_ports_complete,
+#           my_path("D","NOAA", name = "top_ports.csv")
+#           )
+
+noaa_ports_complete
 
@@
 
-top10_ports %>% 
-  left_join(noaa_ports) %>% 
+noaa_ports_complete %>% 
+  filter(tresh == "75th") %>% 
   ggplot() +
@@
   geom_sf(data = state_sf, aes(color = state), fill = NA) +
-  geom_point(data = ports_df, aes(x = lon, y = lat,
+  geom_point(data = subset(noaa_ports_complete, tresh == "75th"), aes(x = lon, y = lat,
                                   shape = species_name), size = 3, alpha = 0.7) +

### 2021-10-29 Scripts/spatial_analisis.Rmd
misc.
updated webpage with new ports

@@
 # write_csv(noaa_ports_complete,
-#           my_path("D","NOAA", name = "top_ports.csv")
+#           my_path("D","Partial", name = "top_ports.csv")
 #           )
@@
 
+#Load top port data 
+ports_df <- my_path("D","Partial", "top_ports.csv", read = T) %>% 
+  filter(tresh == "75th") %>%
+  distinct(port_name, .keep_all = T) # No need for duplication
+
 port_sf <- st_as_sf(ports_df,
@@
   geom_sf(data = eez_sf, aes(),fill = NA) +
-  geom_sf(data = port_bf, aes(color = species_name), fill = NA) +
+  geom_sf(data = port_bf, aes(), fill = NA) +
   scale_color_manual(values = state_pallet)+
@@
 
-# write_csv(inter_grid_df, paste0(my_path("D", "Spatial"),"inter_grid_df.csv"))
+# Save grid for future analysis
+# write_csv(inter_grid_df, paste0(my_path("R", "Partial"),"inter_grid_df.csv"))
 
@@
   st_join(port_bf) %>% # join to port sf
-  filter(!is.na(landing_port)) %>%
-  distinct(index,landing_port, .keep_all = TRUE) #removes like 400K overlapping rows
+  filter(!is.na(port_name)) %>%
+  distinct(index,port_name, .keep_all = TRUE) #removes like 400K overlapping rows
 
@@
 grid_fp_bf_dt <- as.data.frame(grid_fp_sf) %>%
-    select(index,landing_port,species_name)
+    select(index,port_name,species_name)
 
@@
     geom_sf(data = port_sf, aes(), fill = NA) +
-    geom_sf(aes(color = state), alpha = 0.3) +
+    geom_sf(aes(color = state_postal), alpha = 0.3) +
     geom_sf(data = eez_sf, aes(),fill =NA) + 
@@
   ggplot() +
-    geom_sf(data = grid_fp_sf, aes(color = state),size = 0.1, alpha = 0.5) +
-    facet_wrap(~state) +
+    geom_sf(data = grid_fp_sf, aes(color = state_postal),size = 0.1, alpha = 0.5) +
+    facet_wrap(~state_postal) +
     theme_dark() +
@@
 
-write_sf(grid_eez_sf_fp, paste0(my_path("D", "Spatial/grid_eez_fp_sf"),"grid_eez_fp.shp"))
+write_sf(grid_eez_sf_fp, my_path("R", "Partial",name="grid_eez_fp.shp"))
 
@@
 grid_eez_fp_df <- as.data.frame(grid_eez_sf_fp) %>%
-  select(index,landing_port,abrev=landing_state,spp=species_name) %>% 
+  select(index,port_name,abrev=state_postal,spp=species_name) %>% 
   left_join(ne_grid,
-            by = "index") %>% 
-  left_join(state_names)
-
-write_csv(grid_eez_fp_df, paste0(my_path("D", "Spatial/grid_eez_fp_sf"),"grid_eez_fp_df.csv"))
+            by = "index")
+
+write_csv(grid_eez_fp_df, my_path("R", "Partial/grid_fp",name = "grid_eez_fp_df.csv"))
 
@@
   ggplot() +
-  geom_sf(aes(color = state), alpha = 0.3) +
+  geom_sf(aes(color = state_postal), alpha = 0.3) +
   scale_color_manual(values = state_pallet) +
@@
 
-```{r paper_figure_area_map, eval = F, echo = T, results='hide'}
+```{r data_prep, eval = F, echo = T, results='hide'}
 
@@
 
-```{r reg_unit_map_diff, eval = F, echo = T, results='hide'}
+```{r sea_unit_map_diff, eval = F, echo = T, results='hide'}
 
@@
 
-![Proportion change aggregated all species map for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/area_plot_avg_agg_sptl.jpg)
-
 ### Paper figure: Per Species Proportional change
@@
 ```
-![Proportion change aggregated all species map for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/area_plot_avg_spp_sptl.jpg)
+<!-- ![Proportion change aggregated all species map for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/area_plot_avg_spp_sptl.jpg) -->
 
@@
 
-```{r paper_figure_area_map, eval = F, echo = T, results='hide'}
+```{r eval = F, echo = T, results='hide'}
 
@@
 ```
-
-![Proportion change per species map for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/temp_proportion_chng.jpg)
 
@@
 
-![Proportion change aggregated all species map for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/proportion_chg_agg.jpg)
-```{r sarah_landings_data}
+```{r}
 

### 2021-11-01 Allocation_tool/server.R
Fixed bugs

@@ -342,7 +342,7 @@ shinyServer(function(input, output,session) {
             
             # Set the plot data
             plot_data <- raw_data() %>%
-                filter(spp %in% species,
+                filter(spp %in% input$SppSelection,
                        year %in% years)
             
             
@@ -542,11 +542,13 @@ shinyServer(function(input, output,session) {
                 filter(!is.na(mean_per)) %>%
                 select(state,year,mean_per) %>%
                 spread(year,mean_per) %>%
-                mutate(Change = ifelse(`1973` < `2019`,"Increase","Decrease")) %>%
+                mutate(Change = ifelse(`1973` < `2019`,"Increase",
+                                       ifelse(`1973` > `2019`,"Decrease","No change"))
+                       )%>%
                 left_join(state_order) %>% 
                 arrange(order) %>% 
                 mutate(State = paste0(state," (",abrev,")")) %>% 
-                select(State,2:6,43:47,Change)
+                select(State,2:6,43:47,Change, -order)
             
             customGreen = "#71CA97"
             
@@ -558,9 +560,14 @@ shinyServer(function(input, output,session) {
                             `1973`= color_bar(customGreen),
                             `2019` = color_bar(customGreen),
                             Change = formatter("span",
-                                               x ~ icontext(ifelse(x == "Increase", "arrow-up", "arrow-down"), 
-                                                            ifelse(x == "Increase", "Increase", "Decrease")),
-                                               style = x ~ style(color = ifelse(x == "Increase", "green", "red")))
+                                               x ~ icontext(ifelse(x == "Increase", "arrow-up",
+                                                                   ifelse(x == "Decrease", "arrow-down", NA)
+                                                                   ), 
+                                                            ifelse(x == "Increase", "Increase",
+                                                                   ifelse(x == "Decrease", "Decrease","No change"))
+                                                            ),
+                                               style = x ~ style(color = ifelse(x == "Increase", "green",
+                                                                                ifelse(x == "Decrease", "red", "grey"))))
                         )
             )
         })  # close formattable

### 2021-11-01 Allocation_tool/ui.R
Misc. ui instructions

@@ -236,7 +236,7 @@ dashboardPage(
       tabItem(tabName = "dashboard",
               useShinyjs(),
               h1("Control panel"),
-              h4("Please select from the following options in the blue boxes.", em("Note that all options need to be selected in order for results to apear")),
+              h4(strong("Read me:"),"Please select from the following options in the blue boxes.", em("Note that all options need to be selected in order for results to apear")),
               #______________________________________________________________________#
               ### Control panel ####
               #______________________________________________________________________#
@@ -327,6 +327,7 @@ dashboardPage(
               ),
               column(12,
                      align = "center",
+                     h4(strong("Read me:"), "Before running the query, select the outputs you want to show by clicking in the + sign of each box. Note that this step might take a couple of seconds"),
               actionButton("do",
                            "Run Query",
                            icon = icon("gear"),
@@ -349,6 +350,7 @@ dashboardPage(
                 box(width = 6,
                     solidHeader = TRUE,
                     collapsible = TRUE,
+                    collapsed = TRUE,
                     title = "Regulatory Units",
                     status = "success", # green color
                     plotOutput("RegUnit")
@@ -357,6 +359,7 @@ dashboardPage(
                 box(width = 6, 
                     solidHeader = TRUE,
                     collapsible = TRUE,
+                    collapsed = TRUE,
                     title = "Stock's distribution",
                     status = "success", # green color
                     plotOutput("distPlot")
@@ -367,6 +370,7 @@ dashboardPage(
                 box(width = 6, 
                     solidHeader = TRUE,
                     collapsible = TRUE,
+                    collapsed = TRUE,
                     title = "State's proportion",
                     status = "success", # green color
                     plotOutput("propPlot")),
@@ -374,6 +378,7 @@ dashboardPage(
                 box(width = 6, 
                     solidHeader = TRUE,
                     collapsible = TRUE,
+                    collapsed = TRUE,
                     title = "Difference between historic and current distribution",
                     status = "success", # green color
                     plotOutput("propDiffPlot")
@@ -383,6 +388,7 @@ dashboardPage(
                 box(width = 12, 
                     solidHeader = TRUE,
                     collapsible = TRUE,
+                    collapsed = TRUE,
                     title = "Historical proportion of the stock",
                     status = "success", # green color
                     formattableOutput("Allocation_tbl")

### 2021-11-01 Allocation_tool/server.R
Spatial numbers dincluded

@@ -171,6 +171,83 @@ shinyServer(function(input, output,session) {
         # ---------------------------- #
         # Regulatory Units ####
         # ---------------------------- #
+        output$gridN <- renderFormattable({
+            
+            
+            # ---------------------------- #
+            # State waters ######
+            # ---------------------------- #
+            
+            if(input$SpatSelection == "State waters"){
+                
+                n_grids <- grids %>%
+                    filter(spatial == "sw") %>% 
+                    group_by(state) %>% 
+                    summarise(n_grids = length(unique(index))) %>% 
+                    arrange(n_grids) %>% 
+                    spread(state,n_grids)
+                
+                
+            } 
+            # ---------------------------- #
+            # Fishing Ports ######
+            # ---------------------------- #
+            if(input$SpatSelection == "Fishing ports"){
+                
+                
+                n_grids <- grids %>%
+                    filter(spatial == "fp") %>% 
+                    group_by(state) %>% 
+                    summarise(Grids = length(unique(index)),
+                              Ports = length(unique(landing_port))
+                    ) %>% 
+                    arrange(Ports) %>% 
+                    gather("Category","type",Grids,Ports) %>% 
+                    spread(state,type)
+                
+            }
+            
+            if(input$SpatSelection == "Both apporaches"){
+                
+                
+                n_grids <-
+                    grids %>%
+                    group_by(state,spatial) %>% 
+                    summarise(Grids = length(unique(index)),
+                              Ports = length(unique(landing_port))
+                    ) %>% 
+                    gather("Category","type",Grids,Ports) %>% 
+                    spread(spatial,type) %>% 
+                    filter(Category != "Grids") %>% 
+                    arrange(Category,state) %>% 
+                    mutate(
+                        Difference = abs(replace_na(fp,0) - sw)
+                    ) %>% 
+                    left_join(state_order) %>% 
+                    arrange(order) %>% 
+                    select(State = state,
+                           ISO = abrev,
+                           "Fishing ports" = fp,
+                           "State waters" = sw,
+                           Difference)
+                    
+                
+            }
+            
+            formattable(n_grids,
+                        align =c("l",rep("c",9),"r"),
+                        list(
+                        Difference = color_bar(customGreen)
+                        )
+            )
+
+        })
+        
+        
+        
+        # ---------------------------- #
+        # Regulatory Units ####
+        # ---------------------------- #
[…]

### 2021-11-01 Allocation_tool/ui.R

@@ -345,6 +345,17 @@ dashboardPage(
               #______________________________________________________________________#
               ### Results ####
               #______________________________________________________________________#
+                fluidRow(
+                  box(width = 12, 
+                      solidHeader = TRUE,
+                      collapsible = TRUE,
+                      collapsed = FALSE,
+                      title = "Number of grids per regulatory area",
+                      status = "success", # green color
+                      
+                      formattableOutput("gridN")
+              )
+              ),
               fluidRow(
                 #### Regulatory units map -----------------
                 box(width = 6,

### 2021-11-01 Allocation_tool/server.R
Formatting table of area

@@ -183,10 +183,15 @@ shinyServer(function(input, output,session) {
                 n_grids <- grids %>%
                     filter(spatial == "sw") %>% 
                     group_by(state) %>% 
-                    summarise(n_grids = length(unique(index))) %>% 
-                    arrange(n_grids) %>% 
-                    spread(state,n_grids)
+                    summarise(Grids = length(unique(index))) %>% 
+                    arrange(Grids)
                 
+                
+                x <- formattable(n_grids,
+                            list(
+                                Grids = color_bar(customGreen)
+                            )
+                )
                 
             } 
             # ---------------------------- #
@@ -201,9 +206,14 @@ shinyServer(function(input, output,session) {
                     summarise(Grids = length(unique(index)),
                               Ports = length(unique(landing_port))
                     ) %>% 
-                    arrange(Ports) %>% 
-                    gather("Category","type",Grids,Ports) %>% 
-                    spread(state,type)
+                    arrange(Ports) 
+                
+                x <- formattable(n_grids,
+                            align =c("l",rep("c",9),"r"),
+                            list(
+                                Ports = color_bar(customGreen)
+                            )
+                )
                 
             }
             
@@ -231,15 +241,15 @@ shinyServer(function(input, output,session) {
                            "State waters" = sw,
                            Difference)
                     
-                
+                x <- formattable(n_grids,
+                            align =c("l",rep("c",9),"r"),
+                            list(
+                                Difference = color_bar(customGreen)
+                            )
+                )
+                   
             }
-            
-            formattable(n_grids,
-                        align =c("l",rep("c",9),"r"),
-                        list(
-                        Difference = color_bar(customGreen)
-                        )
-            )
+            x
 
         })
         

### 2021-11-01 Allocation_tool/ui.R

@@ -346,15 +346,15 @@ dashboardPage(
               ### Results ####
               #______________________________________________________________________#
                 fluidRow(
-                  box(width = 12, 
+                  #### Distribution map -----------------
+                  box(width = 6, 
                       solidHeader = TRUE,
                       collapsible = TRUE,
-                      collapsed = FALSE,
-                      title = "Number of grids per regulatory area",
+                      collapsed = TRUE,
+                      title = "Stock's distribution",
                       status = "success", # green color
-                      
-                      formattableOutput("gridN")
-              )
+                      plotOutput("distPlot")
+                  )
               ),
               fluidRow(
                 #### Regulatory units map -----------------
@@ -366,14 +366,13 @@ dashboardPage(
                     status = "success", # green color
                     plotOutput("RegUnit")
                 ),
-                #### Distribution map -----------------
                 box(width = 6, 
                     solidHeader = TRUE,
                     collapsible = TRUE,
-                    collapsed = TRUE,
-                    title = "Stock's distribution",
+                    collapsed = FALSE,
+                    title = "Number of grids per regulatory area",
                     status = "success", # green color
-                    plotOutput("distPlot")
+                    formattableOutput("gridN")
                 )
               ), # close firs fluid row
               fluidRow(

### 2021-11-01 Allocation_tool/server.R
Grid table looks good

@@ -173,6 +173,7 @@ shinyServer(function(input, output,session) {
         # ---------------------------- #
         output$gridN <- renderFormattable({
             
+            customGreen = "#71CA97"
             
             # ---------------------------- #
             # State waters ######
@@ -228,19 +229,20 @@ shinyServer(function(input, output,session) {
                     ) %>% 
                     gather("Category","type",Grids,Ports) %>% 
                     spread(spatial,type) %>% 
-                    filter(Category != "Grids") %>% 
+                    filter(Category == "Grids") %>% 
                     arrange(Category,state) %>% 
                     mutate(
                         Difference = abs(replace_na(fp,0) - sw)
                     ) %>% 
                     left_join(state_order) %>% 
-                    arrange(order) %>% 
                     select(State = state,
-                           ISO = abrev,
                            "Fishing ports" = fp,
                            "State waters" = sw,
-                           Difference)
+                           Difference) %>% 
+                    arrange(desc(Difference))
                     
+
+                
                 x <- formattable(n_grids,
                             align =c("l",rep("c",9),"r"),
                             list(

### 2021-11-08 Scripts/spatial_analisis.Rmd
fixed grid

@@
   st_transform(crs = 4326) %>% # 4326
-  filter(eez_name == "USA (East Coast)")
+  filter(eez_name == "USA (East Coast)") %>%
 
@@
 
-grid_eez_sw_df %>% 
+my_path("R", "Partial",name = "grid_eez_sw_sf.csv", read = T) %>% 
   mutate(approach = "state_waters") %>% 
-  bind_rows(grid_eez_fp_df) %>%
+  bind_rows(my_path("R", "Partial/grid_fp",name = "grid_eez_fp_df.csv", read = T)) %>%
   mutate(approach = ifelse(is.na(approach),"fishing_port",approach)) %>% 
@@
 
-# US EEZ map
-path_world <- my_path("G", extra_path = "Spatial/SAU/SAU_Shapefile", name = "SAUEEZ_July2015.shp")
-
-### Previouslly created grids
-
-grids <- my_path("D", "Spatial/grid_eez_fp", name = "grid_eez_fp_df.csv", read = T) %>%
-  mutate(
-    spatial = "fp"
-  ) %>% 
+# US EEZ shapefile
+eez_sf <- st_read(my_path("G", extra_path = "Spatial/SAU/SAU_Shapefile", name = "SAUEEZ_July2015.shp")) %>% 
+  st_transform(crs = 4326) %>% # 4326
+  filter(Name == "USA (East Coast)") %>% 
+  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) #0.1 for paper
+
+### Previously created grids
+
+grids <- bind_rows(
+  my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
+    mutate(spp = "Paralichthys dentatus"),
+  my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
+    mutate(spp = "Stenotomus chrysops"),
+  my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
+    mutate(spp = "Centropristis striata")
+) %>% 
+  mutate(spatial = "sw") %>% 
   bind_rows(
-    my_path("D", "Spatial/grid_eez_sw", name = "grid_eez_sw_df.csv", read = T)
-  ) %>% 
-  select(-spp) %>% 
-  mutate(
-    spatial = ifelse(is.na(spatial),"sw",spatial)
+    my_path("D", "Partial/grid_fp", name = "grid_eez_fp_df.csv", read = T)
+  ) %>% 
+  mutate(spatial = ifelse(is.na(spatial),"fp",spatial),
+         spp = ifelse(spp == "summer flounder","Paralichthys dentatus", 
+                 ifelse(spp == "scup", "Stenotomus chrysops", 
+                        "Centropristis striata"
+                 )
+    )
   ) %>% 
   distinct(.keep_all = T)
+
+# unique(grids$spp)
+
+# Ports data
+ports_df <- my_path("R","Partial", "top_ports.csv", read = T) %>% 
+  filter(tresh == "75th") %>%
+  distinct(port_name, .keep_all = T) # No need for duplication
 
@@
   left_join(grids,
-            by = c("index","lon","lat")
+            by = c("index","lon","lat","spp")
   ) %>%
@@
                    ifelse(spp == "Stenotomus chrysops" & year >= 1988 & year <= 1992,"Reference",
-                          ifelse( spp =="Centropristis striata" & year >= 1980 & year <= 2001,"Reference",
+                          ifelse( spp == "Centropristis striata" & year >= 1980 & year <= 2001,"Reference",
                                  ifelse(year > 2001,"Today",NA)
@@
 
-grid_eez_fp_sf <-
-  grid_eez_sw_sf %>% 
+grid_eez_fp_sf <- grid_eez_sw_sf %>% 
   filter(!group %in% grid_eez_fp_sf$group) %>% 
   mutate(index = NA) %>% 
-  bind_rows(grid_eez_fp_sf)
+  bind_rows(grid_eez_fp_sf) %>% 
+  distinct(.keep_all = T)
 
@@
     facet_wrap(~ group) +
-    geom_point(data = rename(ports_df, group = landing_state), aes(x = lon, y = lat), color = "#E6A0C4") +
+    # geom_point(data = rename(ports_df, group = state_postal), aes(x = lon, y = lat), color = "#E6A0C4") +
     theme(legend.position = "top") +

### 2021-11-09 Allocation_tool/server.R
misc

@@ -98,9 +98,10 @@ shinyServer(function(input, output,session) {
     # Action button. App will only run after all options are selected
     observeEvent(input$do, {
         
-        # ---------------------------- #
-        # Biological Survey Data ####
-        # ---------------------------- #
+# ---------------------------- #
+# Data ####
+# ---------------------------- #
+        
         raw_data <- reactive({
             
             name <- paste0("obs_",str_replace(input$SppSelection," ","_"),".csv")
@@ -120,7 +121,6 @@ shinyServer(function(input, output,session) {
         # Extrapolated data
         # Triangular Irregular Surface  
         # ---------------------------- #
-        
         
         tif_data <- reactive({
             
@@ -168,9 +168,9 @@ shinyServer(function(input, output,session) {
         })
         
         
-        # ---------------------------- #
-        # Regulatory Units ####
-        # ---------------------------- #
+# ---------------------------- #
+# Regulatory Units Table ####
+# ---------------------------- #
         output$gridN <- renderFormattable({
             
             customGreen = "#71CA97"
@@ -258,7 +258,7 @@ shinyServer(function(input, output,session) {
         
         
         # ---------------------------- #
-        # Regulatory Units ####
+        # Regulatory Units Maps ####
         # ---------------------------- #
         output$RegUnit <- renderPlot({
             
@@ -485,6 +485,7 @@ shinyServer(function(input, output,session) {
         # ---------------------------- #
         output$propPlot <- renderPlot({
             
+            
             total_fited <- tif_data() %>% 
                 group_by(year,region,spp,spatial) %>% 
                 summarise(total_value = sum(value,na.rm=T),.groups = "drop")
@@ -632,12 +633,13 @@ shinyServer(function(input, output,session) {
                 select(state,year,mean_per) %>%
                 spread(year,mean_per) %>%
                 mutate(Change = ifelse(`1973` < `2019`,"Increase",
-                                       ifelse(`1973` > `2019`,"Decrease","No change"))
-                       )%>%
+                                       ifelse(`1973` > `2019`,"Decrease","No change")),
+                       Difference =  `2019`-`1973`
+                       ) %>%
                 left_join(state_order) %>% 
                 arrange(order) %>% 
                 mutate(State = paste0(state," (",abrev,")")) %>% 
-                select(State,2:6,43:47,Change, -order)
+                select(State,2:6,43:47,Difference,Change, -order)
             
             customGreen = "#71CA97"
             

### 2021-11-09 Allocation_tool/ui.R

@@ -369,7 +369,7 @@ dashboardPage(
                 box(width = 6, 
                     solidHeader = TRUE,
                     collapsible = TRUE,
-                    collapsed = FALSE,
+                    collapsed = TRUE,
                     title = "Number of grids per regulatory area",
                     status = "success", # green color
                     formattableOutput("gridN")

### 2021-11-11 Scripts/spatial_analisis.Rmd
included new grid data with selected fishing ports

@@
 
+```{r}
+
+x <- as.data.frame(st_read(my_path("D", "Partial/grid_fp",name="grid_eez_fp.shp"))) %>% 
+  select(index,spp = spcs_nm,port_name = port_nm, abrev = stt_pst) %>% 
+  bind_cols(
+    as.data.frame(st_coordinates(st_read(my_path("D", "Partial/grid_fp",name="grid_eez_fp.shp"))))
+  ) %>% 
+  rename(lon = X, lat = Y) %>% 
+  left_join(as.data.frame(land_sf),
+            by = "abrev") %>% 
+  mutate(state= str_to_sentence(ID)) %>% 
+  select(1:6,state) %>% 
+  mutate(
+     spp = ifelse(spp == "summer flounder","Paralichthys dentatus", 
+                 ifelse(spp == "scup", "Stenotomus chrysops", 
+                        "Centropristis striata"
+                 )
+    )
+  )
+
+write_csv(x,my_path("D", "Partial/grid_fp",name="grid_eez_fp_df.csv"))
+
+```
+
 ```{r load_data, eval = T, echo = T}
@@
 
-grids <- bind_rows(
+grids_sw <- bind_rows(
   my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
@@
 ) %>% 
-  mutate(spatial = "sw") %>% 
-  bind_rows(
-    my_path("D", "Partial/grid_fp", name = "grid_eez_fp_df.csv", read = T)
-  ) %>% 
-  mutate(spatial = ifelse(is.na(spatial),"fp",spatial),
-         spp = ifelse(spp == "summer flounder","Paralichthys dentatus", 
-                 ifelse(spp == "scup", "Stenotomus chrysops", 
-                        "Centropristis striata"
-                 )
-    )
-  ) %>% 
-  distinct(.keep_all = T)
+  mutate(spatial = "sw",
+         port_name = NA,
+         abrev = NA
+         )
+
+grids_fp <- my_path("D", "Partial/grid_fp", name = "grid_eez_fp_df.csv", read = T
+) %>%
+  mutate(spatial = "fp")
+
+# Join both approaches
+grids <- bind_rows(grids_sw,grids_fp)
 
@@
 # Ports data
-ports_df <- my_path("R","Partial", "top_ports.csv", read = T) %>% 
+ports_df <- my_path("D","Partial", "top_ports.csv", read = T) %>% 
   filter(tresh == "75th") %>%
@@
   viridis::scale_fill_viridis("Average proportion per State", alpha = 0.8, 
-                              breaks = seq(0,35,5),
-                              limits=(c(0,35))
+                              breaks = seq(0,55,5),
+                              limits=(c(0,55))
                               )+
@@
   viridis::scale_fill_viridis("Difference (%)", alpha = 0.8,option = "C",
-                              breaks = seq(0,20,5),
-                              limits=(c(0,22)),
+                              breaks = seq(0,45,5),
+                              limits=(c(0,45)),
                               # labels = c("<-10",seq(-75,75,25),">100")
@@
 )
-
-reg_unit %>% 
-  # filter(spatial == "fp") %>%
-  select(-fp) %>% 
-  spread(label,sw) %>% 
-  mutate(
-    difference = Today-Reference
-    ) %>% 
-  gther(Reference:difference)
 

### 2021-11-11 Scripts/spatial_analisis.Rmd
re-arranged code
Ran port analysis but realize NC has no BSB data.. weird

@@
 ports_df <- my_path("D","Partial", "top_ports.csv", read = T) %>% 
-  filter(tresh == "75th") %>%
-  distinct(port_name, .keep_all = T) # No need for duplication
+  filter(tresh == "75th")
 
@@
   st_join(port_bf) %>% # join to port sf
-  filter(!is.na(port_name)) %>%
-  distinct(index,port_name, .keep_all = TRUE) #removes like 400K overlapping rows
+  filter(!is.na(port_name)) #%>%
+  # distinct(index,port_name, .keep_all = TRUE) #removes like 400K overlapping rows
 
@@
     geom_sf(data = grid_fp_sf, aes(color = state_postal),size = 0.1, alpha = 0.5) +
-    facet_wrap(~state_postal) +
+    facet_wrap(~state_postal+species_name) +
     theme_dark() +
@@
 
-write_sf(grid_eez_sf_fp, my_path("R", "Partial",name="grid_eez_fp.shp"))
+write_sf(grid_eez_sf_fp, my_path("D", "Partial/grid_fp",name="grid_eez_fp.shp"))
 
@@
 
-write_csv(grid_eez_fp_df, my_path("R", "Partial/grid_fp",name = "grid_eez_fp_df.csv"))
+write_csv(grid_eez_fp_df, my_path("D", "Partial/grid_fp",name = "grid_eez_fp_df.csv"))
 
@@
 
+# x %>% filter() %>% group_by(spp,abrev) %>% tally()
+
 ```
@@
   filter(tresh == "75th") %>%
-  distinct(port_name, .keep_all = T) # No need for duplication
+  group_by(species_name,state_postal) %>% 
+  summarise(n =n()) %>% 
+  select(-n)
+  # distinct(c(,state_postal), .keep_all = T) # No need for duplication
 
@@
 
-#### Regulatory units map
+#### F3 - Regulatory units map
 
@@
   viridis::scale_fill_viridis("Average proportion per State", alpha = 0.8, 
-                              breaks = seq(0,55,5),
-                              limits=(c(0,55))
+                              breaks = seq(0,35,5),
+                              limits=(c(0,35))
                               )+
@@
   viridis::scale_fill_viridis("Difference (%)", alpha = 0.8,option = "C",
-                              breaks = seq(0,45,5),
-                              limits=(c(0,45)),
+                              breaks = seq(0,25,5),
+                              limits=(c(0,25)),
                               # labels = c("<-10",seq(-75,75,25),">100")
@@
 
-#### Seasonal units map
+#### F4 - Seasonal units map
 
@@
 
-## Area plot
+## F5 - Area plot
 
@@
 
-*Note:* This plot is interactive. For ease comparison between States you can;
-
-- *One* click on any State to *remove* it from the plot 
-- *Two* clicks on any State to *isolate it* from the plot (other states can then be added by just clicking on them).
-- The bottom panel allows you to reduce the time frame
-
-### Dynamic aggregated plot
-
-```{r dynamic_area_plot, eval = T, echo = T, fig.height = 10, fig.width = 10}
-
-total_fited <- historic_spp %>% 
-  group_by(year,region) %>% 
-  summarise(total_value = sum(value,na.rm=T),.groups = "drop")
-
-# group by state
-state_fit <- historic_spp %>% 
-  group_by(state,year,region) %>% 
-  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
-  left_join(total_fited,
-            by = c("year","region")) %>%
-  mutate(percentage = state_value/total_value*100)
-
-# Plot me
-p <- ggplot(state_fit) +
-  geom_area(
-    aes(
-      x = year,
-      y = round(percentage),
-      fill = state
-    )
-  ) +
-  ylab("Percentage (%)") +
-  # viridis::scale_fill_viridis(discrete = T, alpha = 0.8) +
-  scale_fill_manual(values = state_pallet) +
-  MyFunctions::my_ggtheme_p() +
-  facet_wrap(~region, ncol = 1) +
-  theme_dark()
-
-ggplotly(p,
-         dynamicTicks = TRUE) %>% 
-  layout(hovermode = "x") %>%
-  rangeslider()
-
-```
-
-## Area plot (running mean)
+### Area plot (running mean)
 
@@
 
-### Dynamic aggregated plot
-
-*Note:* This plot is also interactive and thus, follows the same options of the previous one.
-
-```{r area_plot, eval = T, echo = T, fig.height = 10, fig.width = 10}
-
-# group by state
-state_fit <- historic_spp %>% 
-  group_by(state,year,region,.groups = "drop") %>% 
-  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
-  left_join(total_fited,
-            by = c("year","region")) %>%
-  mutate(percentage = state_value/total_value*100) %>% 
-  group_by(state,region) %>% 
-  mutate(RMean = zoo::rollmean(x = percentage, 
-                            10,
-                            fill = NA,
-                            na.rm=T)
-    ) %>%  
-  left_join(state_lat)
-
-# Plot me
-p <- ggplot(state_fit) +
-  geom_area(
-    aes(
-      x = year,
-      y = round(RMean),
-      fill = state
-      # fill = order
-    )
-  ) +
-  ylab("10 yrs running average (%)") +
-  scale_fill_manual(
-    "State",
-    values = state_pallet,
-    # labels = state_fit %>% arrange(order) %>%  pull(state) %>% unique()
-  ) +
-  MyFunctions::my_ggtheme_p() +
-  facet_wrap(~region, ncol = 1) +
-  theme_dark()
-
-suppressWarnings(
-ggplotly(p,
-         dynamicTicks = TRUE) %>% 
-  layout(hovermode = "x") %>% 
-  # add_trace() %>% 
-  rangeslider()
-)
-
-```
-
-### Aggregated Proportional change
-
-```{r plot_area_ave_agg, eval = F, echo = F, results='hide'}
-
-total_fited <- historic_spp %>% 
-  group_by(year,region,spatial) %>% 
-  summarise(total_value = sum(value,na.rm=T),.groups = "drop")
-
-# group by state
-state_fit <- historic_spp %>% 
-  group_by(state,year,region,spatial) %>% 
-  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
-  left_join(total_fited,
-            by = c("year","region","spatial")) %>%
-  mutate(percentage = state_value/total_value*100) %>% 
-  group_by(state,region,spatial) %>% 
-  mutate(RMean = zoo::rollmean(x = percentage, 
-                            10,
-                            fill = NA,
-                            na.rm=T)
-    ) %>% 
-  #Only show results for spring
-  filter(str_detect(region,"Spring"),
-         !is.na(RMean) # Remove NAs from rollmean
-         ) %>%  
-  left_join(state_lat) %>% 
-  mutate(
-         spatial = ifelse(spatial == "fp","Fishing ports",
-                          ifelse(spatial == "sw","State Waters","Difference")
-         )
-  )
-
-# Plot me
-agg_area <- ggplot(state_fit) +
-  geom_area(
-    aes(
-      x = year,
-      y = round(RMean),
-      fill = order
-      # fill = state
-    )
-  ) +
-  annotate(geom= "rect",
-           xmin = 1980, xmax = 2001, 
-           ymin = 0, ymax = 100,
-            fill = "gray90",
-           colour = NA,
-           alpha = 0.5) +
-  ylab("Propotion (10 yrs running average)") +
-  # viridis::scale_fill_viridis(discrete = T, alpha = 0.8) +
-  scale_fill_manual(
-    "State\n(Latitudinal order)",
-    values = state_pallet,
-    labels = state_fit %>% arrange(order) %>%  pull(state) %>% unique()
-  ) +
-  scale_x_continuous(breaks = seq(1979,2015,9),limits = c(1979,2015))+
-  xlab("Year") +
-  my_ggtheme_p(leg_pos = "right", hjust = 1,ax_tx_s = 10,leg_tx_s = 10, leg_tl_s = 12,ax_tl_s = 12) +
-  theme(legend.key.width = unit(1,"line"),
-        legend.title.align=0.5) +
-  facet_wrap(~spatial)
-
-    ggsave(filename = "area_plot_avg_agg_sptl.jpg",
-         plot = agg_area,
-         path = my_path("R","Figures"),
-         width = 8,
-         height = 6
-         )
-
-```
-
-### Paper figure: Per Species Proportional change
-
-```{r paper_plot_area_ave_spp, eval = F, echo = F, results='hide'}
+#### Data preparation
+
+```{r area_plot_Data_prep}
 
@@
 state_fit <- historic_spp %>% 
-  group_by(state,year,label,region,spp,spatial) %>% 
+  group_by(state,year,region,spp,spatial) %>% 
   summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
+  # View()
   left_join(total_fited,
@@
   )
+
+```
+
+### Paper figure: Per Species Proportional change
+
+```{r paper_plot_area_ave_spp, eval = F, echo = F, results='hide'}
 
@@
              ) +
-  # annotate(geom= "rect",
-  #          xmin = 1980, xmax = 2001, 
-  #          ymin = 0, ymax = 100,
-  #           fill = "gray90",
-  #          colour = NA,
-  #          alpha = 0.5) +
+
   ylab("Propotion (10 yrs running average)") +
@@
 ```
+
+*Note:* This plot is interactive. For ease comparison between States you can;
+
+- *One* click on any State to *remove* it from the plot 
+- *Two* clicks on any State to *isolate it* from the plot (other states can then be added by just clicking on them).
+- The bottom panel allows you to reduce the time frame
+
+### Dynamic aggregated plot
+
+```{r dynamic_area_plot, eval = T, echo = T, fig.height = 10, fig.width = 10}
+
+total_fited <- historic_spp %>% 
+  group_by(year,region) %>% 
+  summarise(total_value = sum(value,na.rm=T),.groups = "drop")
+
+# group by state
+state_fit <- historic_spp %>% 
+  group_by(state,year,region) %>% 
+  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
+  left_join(total_fited,
+            by = c("year","region")) %>%
+  mutate(percentage = state_value/total_value*100)
+
+# Plot me
+p <- ggplot(state_fit) +
+  geom_area(
+    aes(
+      x = year,
+      y = round(percentage),
+      fill = state
+    )
+  ) +
+  ylab("Percentage (%)") +
+  # viridis::scale_fill_viridis(discrete = T, alpha = 0.8) +
+  scale_fill_manual(values = state_pallet) +
+  MyFunctions::my_ggtheme_p() +
+  facet_wrap(~region, ncol = 1) +
+  theme_dark()
+
+ggplotly(p,
+         dynamicTicks = TRUE) %>% 
+  layout(hovermode = "x") %>%
+  rangeslider()
+
+```
+
+### Dynamic aggregated plot
+
+*Note:* This plot is also interactive and thus, follows the same options of the previous one.
+
+```{r area_plot, eval = T, echo = T, fig.height = 10, fig.width = 10}
+
+# group by state
+state_fit <- historic_spp %>% 
+  group_by(state,year,region,.groups = "drop") %>% 
+  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
+  left_join(total_fited,
+            by = c("year","region")) %>%
+  mutate(percentage = state_value/total_value*100) %>% 
+  group_by(state,region) %>% 
+  mutate(RMean = zoo::rollmean(x = percentage, 
+                            10,
+                            fill = NA,
+                            na.rm=T)
+    ) %>%  
+  left_join(state_lat)
+
+# Plot me
+p <- ggplot(state_fit) +
+  geom_area(
+    aes(
+      x = year,
+      y = round(RMean),
+      fill = state
+      # fill = order
+    )
+  ) +
+  ylab("10 yrs running average (%)") +
+  scale_fill_manual(
+    "State",
+    values = state_pallet,
+    # labels = state_fit %>% arrange(order) %>%  pull(state) %>% unique()
+  ) +
+  MyFunctions::my_ggtheme_p() +
+  facet_wrap(~region, ncol = 1) +
+  theme_dark()
+
+suppressWarnings(
+ggplotly(p,
+         dynamicTicks = TRUE) %>% 
+  layout(hovermode = "x") %>% 
+  # add_trace() %>% 
+  rangeslider()
+)
+
+```
+
+#### Aggregated Area plot for all species
+
+```{r plot_area_ave_agg, eval = F, echo = F, results='hide'}
+
+total_fited <- historic_spp %>% 
+  group_by(year,region,spatial) %>% 
+  summarise(total_value = sum(value,na.rm=T),.groups = "drop")
+
+# group by state
+state_fit <- historic_spp %>% 
+  group_by(state,year,region,spatial) %>% 
+  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
+  left_join(total_fited,
+            by = c("year","region","spatial")) %>%
+  mutate(percentage = state_value/total_value*100) %>% 
+  group_by(state,region,spatial) %>% 
+  mutate(RMean = zoo::rollmean(x = percentage, 
+                            10,
+                            fill = NA,
+                            na.rm=T)
+    ) %>% 
+  #Only show results for spring
+  filter(str_detect(region,"Spring"),
+         !is.na(RMean) # Remove NAs from rollmean
+         ) %>%  
+  left_join(state_lat) %>% 
+  mutate(
+         spatial = ifelse(spatial == "fp","Fishing ports",
+                          ifelse(spatial == "sw","State Waters","Difference")
+         )
+  )
+
+# Plot me
+agg_area <- ggplot(state_fit) +
+  geom_area(
+    aes(
+      x = year,
+      y = round(RMean),
+      fill = order
+      # fill = state
+    )
+  ) +
+  annotate(geom= "rect",
+           xmin = 1980, xmax = 2001, 
+           ymin = 0, ymax = 100,
+            fill = "gray90",
+           colour = NA,
+           alpha = 0.5) +
+  ylab("Propotion (10 yrs running average)") +
+  # viridis::scale_fill_viridis(discrete = T, alpha = 0.8) +
+  scale_fill_manual(
+    "State\n(Latitudinal order)",
+    values = state_pallet,
+    labels = state_fit %>% arrange(order) %>%  pull(state) %>% unique()
+  ) +
+  scale_x_continuous(breaks = seq(1979,2015,9),limits = c(1979,2015))+
+  xlab("Year") +
+  my_ggtheme_p(leg_pos = "right", hjust = 1,ax_tx_s = 10,leg_tx_s = 10, leg_tl_s = 12,ax_tl_s = 12) +
+  theme(legend.key.width = unit(1,"line"),
+        legend.title.align=0.5) +
+  facet_wrap(~spatial)
+
+    ggsave(filename = "area_plot_avg_agg_sptl.jpg",
+         plot = agg_area,
+         path = my_path("R","Figures"),
+         width = 8,
+         height = 6
+         )
+
+```

### 2021-11-12 Allocation_tool/server.R
fix paths (dhu!)

@@ -23,7 +23,7 @@ state_pallet <- c(wes_palette(n = 5, name = "Darjeeling1"),
 )
 
 # Set the filters
-state_order <- my_path("D", "Spatial/grid_eez_sw", name = "grid_eez_sw_df.csv", read = T) %>%
+state_order <- my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>%
     group_by(state) %>%
     summarise(
         order = mean(lat)
@@ -38,7 +38,7 @@ state_order <- my_path("D", "Spatial/grid_eez_sw", name = "grid_eez_sw_df.csv", 
 # Grid data ####
 # ---------------------------- #
 # Load grid of state waters
-grid_eez_sw_sf <- st_read(my_path("D","Spatial/grid_eez_sw", name = "grid_eez_sw_sf.shp")) %>%
+grid_eez_sw_sf <- st_read(my_path("D","Partial/grid_sw", name = "grid_eez_sw_sf.shp")) %>%
     select(index,state,geometry) %>%
     mutate(method = "state_waters",
            state = str_to_sentence(state)) %>%
@@ -48,8 +48,8 @@ grid_eez_sw_sf$group <- factor(grid_eez_sw_sf$abrev,      # Reordering group fac
                                levels = state_order$abrev)
 
 # Load grid of fishing ports
-grid_eez_fp_sf <-  st_read(my_path("D","Spatial/grid_eez_fp", name = "grid_eez_fp.shp")) %>%
-    select(index,abrev=lndng_s,geometry) %>%
+grid_eez_fp_sf <-  st_read(my_path("D","Partial/grid_fp", name = "grid_eez_fp.shp")) %>%
+    select(index,abrev=stt_pst,geometry) %>%
     mutate(method = "fishing_port"#,
            # state = str_to_sentence(landing_port)
     )%>%
@@ -60,18 +60,19 @@ grid_eez_fp_sf$group <- factor(grid_eez_fp_sf$abrev,      # Reordering group fac
 
 grid_eez_fp_sf <- arrange(grid_eez_fp_sf,group)
 
-grids <- my_path("D", "Spatial/grid_eez_fp", name = "grid_eez_fp_df.csv", read = T) %>%
+grids <- my_path("D", "Partial/grid_fp", name = "grid_eez_fp_df.csv", read = T) %>%
     mutate(
         spatial = "fp"
     ) %>% 
     bind_rows(
[…]

### 2021-11-17 Allocation_tool/summary_report.Rmd
Fixed tool typos and added a functioning report

---
title: "Test me report"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2021-11-17 Allocation_tool/server.R

@@ -13,7 +13,7 @@
 
 # Get functions and shapefiles
 library(MyFunctions)
-MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","DT","plotly","wesanderson","zoo","formattable","viridis","shinydashboard"))
+MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","DT","plotly","wesanderson","zoo","formattable","viridis","shinydashboard","rmarkdown"))
 
 us_map <- st_as_sf(map("state", plot = FALSE, fill = TRUE))
 
@@ -96,8 +96,25 @@ grids <- my_path("D", "Partial/grid_fp", name = "grid_eez_fp_df.csv", read = T) 
 # ---------------------------- #
 shinyServer(function(input, output,session) {
     
+    
+    # ---------------------------- #
+    ### Run and Clear all button ####
+    # ---------------------------- #
+    
     # Action button. App will only run after all options are selected
     observeEvent(input$do, {
+        
+        # Clear all plots 
+        observeEvent(input$reset,{
+            
+            # Remove outputs
+            output$RegUnit <- renderPlot(NULL)
+            output$Allocation_tbl <- renderFormattable(NULL)
+            output$distPlot <- renderPlot(NULL)
+            output$propPlot <- renderPlot(NULL)
+            output$propDiffPlot <- renderPlot(NULL)
+            output$Allocation_tbl <- renderFormattable(NULL)
+        })
         
 # ---------------------------- #
 # Data ####
@@ -666,17 +683,66 @@ shinyServer(function(input, output,session) {
         
     }) # close action button
     
-    observeEvent(input$reset,{
-        
-        # Remove outputs
-        output$RegUnit <- renderPlot(NULL)
-        output$Allocation_tbl <- renderFormattable(NULL)
-        output$distPlot <- renderPlot(NULL)
-        output$propPlot <- renderPlot(NULL)
-        output$propDiffPlot <- renderPlot(NULL)
-        output$Allocation_tbl <- renderFormattable(NULL)
-        })
     
+    # ---------------------------- #
+    ### Download report ####
+    # ---------------------------- #
+    
+    output$downloadReport = downloadHandler(
+        filename<- function(){
+            paste0(input$filename,Sys.Date(),switch(
+                input$format, PDF = '.pdf', Word = '.docx', HRML = '.html'
+            ))
+        },
+        # Report content
[…]

### 2021-11-17 Allocation_tool/ui.R

@@ -43,11 +43,15 @@ dashboardPage(
         ),
         div(
           downloadButton(
-            outputId = "downloadData",
+            outputId = "downloadReport",
             label = "Download report",
             icon = icon("download"),
             style = "color: black; margin-left: 15px; margin-bottom: 5px;"
           )
+        ),
+        div(
+        radioButtons('format', 'Document format', c('PDF', 'Word',"HTML"),
+                     inline = TRUE)
         ),
         div(
           downloadButton(
@@ -70,7 +74,7 @@ dashboardPage(
       br()
     ),
     hr(style = "border-top: 3px dashed lightgrey;"),
-    p("For any inquery regarding this tool, please email us at 
+    p("For any inquiry regarding this tool, please email us at 
     jpalacios2[at]wisc.edu"),
     a(img(src= 'https://github.githubassets.com/images/modules/logos_page/Octocat.png',
           height = 50,
@@ -95,7 +99,7 @@ dashboardPage(
                 offset = 1,
                 align = "justified",
                 h4("This tool was build with the objective of exploring different
-                  management apporaches to address changes in stocks distribution across management boundaries
+                  management approaches to address changes in stocks distribution across management boundaries
                     in response to a changing climate. The tool focuses on three stocks of the Northeast United 
                     States and is part of the project", em("Managing across boundaries: preventing interjurisdictional
                      conflicts arising from shifting fish stocks"))
@@ -105,14 +109,14 @@ dashboardPage(
                 offset = 1,
                 align = "justified",
                 h4("Below you can find information on the stocks available to explore in the tool.
-                  Navigate to",em("Tool"),"in the left pannel to access 
+                  Navigate to",em("Tool"),"in the left panel to access 
                    the dynamic tool", em("Information"), "to know more about the project and", em("Instructions"),
                   "to get familiarized with the tool.")
               ), # Close fluid row
               column(
                 width = 12,
                 align = "justified",
-                h2("Info on availabel stocks"),
+                h2("Info on available stocks"),
                 h4("Click in each picture to go to NOAAs site for the management of the stock")
               ),
               fluidRow(
@@ -182,7 +186,7 @@ dashboardPage(
                   offset = 2,
                   align = "center",
                   collapsible = TRUE,
-                  h4("In this section you will find information about the project including some background information, the project's obectives,
+                  h4("In this section you will find information about the project including some background information, the project's objectives,
[…]

### 2021-11-17 Allocation_tool/server.R
change to report file name

@@ -690,7 +690,7 @@ shinyServer(function(input, output,session) {
     
     output$downloadReport = downloadHandler(
         filename<- function(){
-            paste0(input$filename,Sys.Date(),switch(
+            paste0(input$filename,"_",Sys.Date(),switch(
                 input$format, PDF = '.pdf', Word = '.docx', HRML = '.html'
             ))
         },

### 2021-11-17 Allocation_tool/ui.R
Includede report UI user, file name, results options (not working), document format

@@ -36,11 +36,28 @@ dashboardPage(
         "Download report",
         tabName = "download",
         icon = icon("download"),
+        div(
         textInput(
           inputId = "filename",
           placeholder = "Name download file",
-          label = ""
+          label = "File name",
+          value = "Report"
+        )
         ),
+          textInput(
+            inputId = "UserName",
+            placeholder = "Name of user",
+            label = "User name",
+            value = "Annon"
+            
+          ),
+        checkboxGroupInput('results', 'Choose results', c("All",'Grid table', 'Grid plot',"Distribution map"),
+                           selected = "All",
+                     inline = FALSE
+        ),
+          radioButtons('format', 'Document format', c('PDF', 'Word',"HTML"),
+                       inline = TRUE
+                       ),
         div(
           downloadButton(
             outputId = "downloadReport",
@@ -48,10 +65,6 @@ dashboardPage(
             icon = icon("download"),
             style = "color: black; margin-left: 15px; margin-bottom: 5px;"
           )
-        ),
-        div(
-        radioButtons('format', 'Document format', c('PDF', 'Word',"HTML"),
-                     inline = TRUE)
         ),
         div(
           downloadButton(

### 2021-11-17 Allocation_tool/summary_report.Rmd
report example

@@
 ---
-title: "Test me report"
-output: pdf_document
+title: "Across boundaries quota allocation tool report"
+date: "`r format(Sys.time(), '%d %B, %Y')`"
+author: "This report was generated by `r input$UserName`"
+output: 
+  pdf_document:
+    toc: yes
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = F)
+
+library(ggplot2)
+library(MyFunctions)
 ```
 
-## R Markdown
+*`r input$SppSelection`*
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+```{r stock_image, fig.width=5, fig.height=4}
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
+if(input$SppSelection == "Centropristis striata"){
 
-```{r cars}
-summary(cars)
+  source <- 'https://media.fisheries.noaa.gov/styles/original/s3/dam-migration/640x427-black-sea-bass.png?itok=7Ax8suz_'
+  common_name <-  "Black sea bass"
+}
+
+if(input$SppSelection == "Stenotomus chrysops"){
+
+  source= 'https://media.fisheries.noaa.gov/styles/original/s3/dam-migration/scup.png?itok=noMUoDe0'
+  common_name <- "Scupt"
+}
+
+if(input$SppSelection == "Paralichthys dentatus"){
+
+  source  <-  'https://media.fisheries.noaa.gov/styles/original/s3/2021-03/640x427-summer-flounder.png?itok=B6G4jkW7'
+  common_name <- "Summer flounder"
+}
+
+  img <- png::readPNG(RCurl::getURLContent(source))
+grid::grid.raster(img)
+
 ```
 
-## Including Plots
+- **Stock:** *`r input$SppSelection`* (`r common_name`)
 
-You can also embed plots, for example:
+- **Survey** `r input$SurveySelection`
 
-```{r pressure, echo=FALSE}
-plot(pressure)
+- **Regulatory unit approach**: `r input$SpatSelection`
+
+- **Year range for distribution** `r min(input$YearSelection)` to `r max(input$YearSelection)`
+
+\clearpage
+
+# Introduction
+
+The following report is a product of your selections in the [Across Boundary app](www.link.com) on "`r format(Sys.time(), '%d %B, %Y')`". Specifically, you made the following selections:
+
+- **Stock:** *`r input$SppSelection`* (`r common_name`)
+
+- **Survey** `r input$SurveySelection`
+
+- **Regulatory unit approach**: `r input$SpatSelection`
+
+- **Year range for distribution** `r min(input$YearSelection)` to `r max(input$YearSelection)`
+
+# Results
+
+## Number of grids per regulatory area
+
+```{r}
+
+if(input$SpatSelection == "State waters"){
+  n_grids <- grids %>%
+    filter(spatial == "sw") %>% 
+    group_by(state) %>% 
+    summarise(Grids = length(unique(index))) %>% 
+    arrange(Grids)
+}
+
+if(input$SpatSelection == "Fishing ports"){
+  n_grids <- grids %>%
+    filter(spatial == "fp") %>% 
+    group_by(state) %>% 
+    summarise(Grids = length(unique(index))) %>% 
+    arrange(Grids)
+
+}
+
+if(input$SpatSelection == "Both apporaches"){
+
+  n_grids <-
+    grids %>%
+    group_by(state,spatial) %>% 
+    summarise(Grids = length(unique(index)),
+              Ports = length(unique(landing_port))
+    ) %>% 
+    gather("Category","type",Grids,Ports) %>% 
+    spread(spatial,type) %>% 
+    filter(Category == "Grids") %>% 
+    arrange(Category,state) %>% 
+    mutate(
+      Difference = abs(replace_na(fp,0) - sw)
+    ) %>% 
+    left_join(state_order) %>% 
+    select(State = state,
+           "Fishing ports" = fp,
+           "State waters" = sw,
+           Difference) %>% 
+    arrange(desc(Difference))
+
+}
+
+knitr::kable(n_grids)
+
 ```
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+## Graph
+
+```{r grid_fig, fig.width=10, fig.height=10}
+
+if(input$SpatSelection == "State waters"){
+
+                gridExtra::grid.arrange(
+                    # Overall (overlapping) position
+                    ggplot(grid_eez_sw_sf) +
+                        geom_sf(aes(color =group , fill = group), alpha = 0.3) +
+                        geom_sf(data = subset(us_map,ID %in% c("maine", "new hampshire", "massachusetts", "connecticut",
+                                                               "rhode island", "new york", "new jersey", "delaware", "maryland",
+                                                               "virginia", "north carolina"))
+                        ) +
+                        scale_color_manual(values = state_pallet) +
+                        scale_fill_manual(values = state_pallet) +
+                        my_ggtheme_p(leg_pos = "",
+                                     ax_tx_s = 13) +
+                        coord_sf(ylim = c(30,48)) +
+                        scale_y_continuous(breaks = c(30,35,40,45))+
+                        labs(x = "", y = "", title = "") +
+                        theme(plot.title = element_text(size = 20)),
+                    # Showing each state separately
+                    ggplot(grid_eez_sw_sf) +
+                        geom_sf(data = subset(us_map,ID %in% c("maine", "new hampshire", "massachusetts", "connecticut",
+                                                               "rhode island", "new york", "new jersey", "delaware", "maryland",
+                                                               "virginia", "north carolina"))
+                        ) +
+                        geom_sf(aes(color = group),size = 0.1, alpha = 0.3) +
+                        facet_wrap(~ group) +
+                        theme(legend.position = "top") +
+                        scale_color_manual(values = state_pallet,
+                                           labels = grid_eez_sw_sf %>% arrange(order) %>%  pull(state) %>% unique()) +
+                        ggtitle("") +
+                        my_ggtheme_p(leg_pos = "",
+                                     ax_tx_s = 11,
+                                     axx_tx_ang = 45,
+                                     hjust = 1
+                        ),
+                    nrow = 1)
+
+            }
+                # ---------------------------- #
+                # Fishing Ports ######
+                # ---------------------------- #
+                if(input$SpatSelection == "Fishing ports"){
+
+                    gridExtra::grid.arrange(
+                        # Overall (overlapping) position
+                        ggplot(grid_eez_fp_sf) +
+                            geom_sf(aes(color =group , fill = group), alpha = 0.3) +
+                            geom_sf(data = subset(us_map,ID %in% c("maine", "new hampshire", "massachusetts", "connecticut",
+                                                                   "rhode island", "new york", "new jersey", "delaware", "maryland",
+                                                                   "virginia", "north carolina"))
+                            ) +
+                            scale_color_manual(values = state_pallet) +
+                            scale_fill_manual(values = state_pallet) +
+                            my_ggtheme_p(leg_pos = "",
+                                         ax_tx_s = 13) +
+                            coord_sf(ylim = c(30,48)) +
+                            scale_y_continuous(breaks = c(30,35,40,45))+
+                            labs(x = "", y = "", title = "") +
+                            theme(plot.title = element_text(size = 20)),
+                        # Showing each state separately
+                        ggplot(grid_eez_fp_sf) +
+                            geom_sf(data = subset(us_map,ID %in% c("maine", "new hampshire", "massachusetts", "connecticut",
+                                                                   "rhode island", "new york", "new jersey", "delaware", "maryland",
+                                                                   "virginia", "north carolina"))
+                            ) +
+                            geom_sf(aes(color = group),size = 0.1, alpha = 0.3) +
+                            facet_wrap(~ group) +
+                            theme(legend.position = "top") +
+                            scale_color_manual(values = state_pallet,
+                                               labels = grid_eez_fp_sf %>% arrange(order) %>%  pull(state) %>% unique()) +
+                            ggtitle("") +
+                            my_ggtheme_p(leg_pos = "",
+                                         ax_tx_s = 11,
+                                         axx_tx_ang = 45,
+                                         hjust = 1
+                            ),
+                        nrow = 1)
+
+                }
+                    # ---------------------------- #
+                    # Both maps ######
+                    # ---------------------------- #
+                    if(input$SpatSelection == "Both apporaches"){
+
+                        sw_map <- gridExtra::grid.arrange(
+                            # Overall (overlapping) position
+                            ggplot(grid_eez_sw_sf) +
+                                geom_sf(aes(color =group , fill = group), alpha = 0.3) +
+                                geom_sf(data = subset(us_map,ID %in% c("maine", "new hampshire", "massachusetts", "connecticut",
+                                                                       "rhode island", "new york", "new jersey", "delaware", "maryland",
+                                                                       "virginia", "north carolina"))
+                                ) +
+                                scale_color_manual(values = state_pallet) +
+                                scale_fill_manual(values = state_pallet) +
+                                my_ggtheme_p(leg_pos = "",
+                                             ax_tx_s = 13) +
+                                coord_sf(ylim = c(30,48)) +
+                                scale_y_continuous(breaks = c(30,35,40,45))+
+                                labs(x = "", y = "", title = "State waters approach") +
+                                theme(plot.title = element_text(size = 20)),
+                            # Showing each state separately
+                            ggplot(grid_eez_sw_sf) +
+                                geom_sf(data = subset(us_map,ID %in% c("maine", "new hampshire", "massachusetts", "connecticut",
+                                                                       "rhode island", "new york", "new jersey", "delaware", "maryland",
+                                                                       "virginia", "north carolina"))
+                                ) +
+                                geom_sf(aes(color = group),size = 0.1, alpha = 0.3) +
+                                facet_wrap(~ group) +
+                                theme(legend.position = "top") +
+                                scale_color_manual(values = state_pallet,
+                                                   labels = grid_eez_sw_sf %>% arrange(order) %>%  pull(state) %>% unique()) +
+                                ggtitle("") +
+                                my_ggtheme_m(map_type = "global", leg_pos = ""),
+                            nrow = 1)
+
+                        fp_map <- gridExtra::grid.arrange(
+                            # Overall (overlapping) position
+                            ggplot(grid_eez_fp_sf) +
+                                geom_sf(aes(color =group , fill = group), alpha = 0.3) +
+                                geom_sf(data = subset(us_map,ID %in% c("maine", "new hampshire", "massachusetts", "connecticut",
+                                                                       "rhode island", "new york", "new jersey", "delaware", "maryland",
+                                                                       "virginia", "north carolina"))
+                                ) +
+                                scale_color_manual(values = state_pallet) +
+                                scale_fill_manual(values = state_pallet) +
+                                my_ggtheme_p(leg_pos = "",
+                                             ax_tx_s = 13) +
+                                coord_sf(ylim = c(30,48)) +
+                                scale_y_continuous(breaks = c(30,35,40,45))+
+                                labs(x = "", y = "", title = "Fishing ports approach") +
+                                theme(plot.title = element_text(size = 20)),
+                            # Showing each state separately
+                            ggplot(grid_eez_fp_sf) +
+                                geom_sf(data = subset(us_map,ID %in% c("maine", "new hampshire", "massachusetts", "connecticut",
+                                                                       "rhode island", "new york", "new jersey", "delaware", "maryland",
+                                                                       "virginia", "north carolina"))
+                                ) +
+                                geom_sf(aes(color = group),size = 0.1, alpha = 0.3) +
+                                facet_wrap(~ group) +
+                                theme(legend.position = "top") +
+                                scale_color_manual(values = state_pallet,
+                                                   labels = grid_eez_fp_sf %>% arrange(order) %>%  pull(state) %>% unique()) +
+                                ggtitle("") +
+                                my_ggtheme_m(map_type = "global", leg_pos = ""),
+                            nrow = 1)
+
+                        # Show plots
+                        gridExtra::grid.arrange(sw_map,fp_map,
+                                                bottom = "Longitude",
+                                                left = "Latitude")
+                    }
+
+```
+
+# Acknowkedgments
+
+Some type of acknowledgmentes... Data was generated from... Paper link... etc...

### 2021-11-17 Allocation_tool/summary_report.Rmd
some text for the report

@@
   pdf_document:
-    toc: yes
+    toc: true
 ---
@@
 
+The following table shows the number of grid cells that each state has according to the **Regulatory unit approach** selected (`r input$SpatSelection`).
+Note that these are equivalent to the size of the regulatory unit of each state and directly influence the proportion of the distribution allocated to each state.
+
 ```{r}
@@
 
-## Graph
+## Map of grids per regulatory area
+
+The following map shows the regulatory area that each state has according to the **Regulatory unit approach** selected (`r input$SpatSelection`).
+Note that when overlapping, the distribution would be divided equally among states.
 

### 2021-11-19 Scripts/nefsc_index_script.Rmd
Included Chris' script for merging sfs

---
title: "Merge our grid with NEFSC"
output: html_document
---

# Instructions

Would it be possible for you to add a column that gives the NOAA-NMFS Statistical Area number for each row in the data file?

# Data

## NEFSC Shapefile

Shapefile provided by Chris on the NEFSC website:  ftp://ftp.nefsc.noaa.gov/pub/gis/

- Statistical_Areas_2010_withNames.shp
- Statistical_Areas_2010.shp

- The description and metadata for the shape file are here: https://www.fisheries.noaa.gov/inport/item/26262

This is the NEFSC-recommended citation for the shapefile:

Northeast Fisheries Science Center, 2021: NEFSC Statistical Areas from 2010-06-15 to 2010-08-15. NOAA National Centers for Environmental Information, https://www.fisheries.noaa.gov/inport/item/26262.

## Load Data

```{r load_data}

# oad our grid SF
grid_sf <- st_read(my_path("D","Partial/grid_sw", name = "grid_eez_sw_sf.shp")) %>% 
  st_transform(4326) %>% # to match shape
  st_set_crs(4326) %>% 
  select(index,geometry)

#Load NEFSC shapefile
nefsc_sf <- st_read(my_path("D","Spatial/nefsc", name = "Statistical_Areas_2010.shp")) %>% 
  st_transform(4326) %>% # to match shape
  st_set_crs(4326) %>% 
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1)

# Visualize map (ok)
# nefsc_sf %>% 
#   st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
#   ggplot() +
  # geom_sf()

```

## Merge shapefiles

```{r merge_shapefiles}

# Merge both sf
nefsc_index <- nefsc_sf %>% 
   st_join(grid_sf,
           join = st_intersects) %>% 
   filter(!is.na(index)) %>% 
  as.data.frame() %>% 
  select(Id,index) %>% 
  distinct(.keep_all = T) %>% 
  mutate(plop = "yes") %>% 
  left_join(my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T)) %>% 
  select(Id,index,state)

# Make sure it works
nefsc_sf %>%
  left_join(nefsc_index) %>%
  filter(!is.na(index)) %>%
  ggplot() +
  geom_sf(aes(fill = index))

```

## Save shapefile

```{r}

# File name
file_name <- my_path("D","Spatial", name = "nefsc_index.csv")

write_csv(nefsc_index %>% select(-state), file_name)
```

### 2021-11-22 Allocation_tool/server.R
Running Demo, but still takes some time

@@ -116,9 +116,9 @@ shinyServer(function(input, output,session) {
             output$Allocation_tbl <- renderFormattable(NULL)
         })
         
-# ---------------------------- #
-# Data ####
-# ---------------------------- #
+        # ---------------------------- #
+        # Data ####
+        # ---------------------------- #
         
         raw_data <- reactive({
             
@@ -186,9 +186,9 @@ shinyServer(function(input, output,session) {
         })
         
         
-# ---------------------------- #
-# Regulatory Units Table ####
-# ---------------------------- #
+        # ---------------------------- #
+        # Regulatory Units Table ####
+        # ---------------------------- #
         output$gridN <- renderFormattable({
             
             customGreen = "#71CA97"
@@ -207,9 +207,9 @@ shinyServer(function(input, output,session) {
                 
                 
                 x <- formattable(n_grids,
-                            list(
-                                Grids = color_bar(customGreen)
-                            )
+                                 list(
+                                     Grids = color_bar(customGreen)
+                                 )
                 )
                 
             } 
@@ -228,10 +228,10 @@ shinyServer(function(input, output,session) {
                     arrange(Ports) 
                 
                 x <- formattable(n_grids,
-                            align =c("l",rep("c",9),"r"),
-                            list(
-                                Ports = color_bar(customGreen)
-                            )
+                                 align =c("l",rep("c",9),"r"),
+                                 list(
+                                     Ports = color_bar(customGreen)
+                                 )
                 )
                 
             }
@@ -258,19 +258,19 @@ shinyServer(function(input, output,session) {
                            "State waters" = sw,
                            Difference) %>% 
                     arrange(desc(Difference))
-                    
-
+                
+                
                 
                 x <- formattable(n_grids,
-                            align =c("l",rep("c",9),"r"),
-                            list(
-                                Difference = color_bar(customGreen)
-                            )
+                                 align =c("l",rep("c",9),"r"),
+                                 list(
+                                     Difference = color_bar(customGreen)
+                                 )
                 )
-                   
+                
             }
             x
-
+            
         })
         
         
@@ -445,6 +445,7 @@ shinyServer(function(input, output,session) {
         output$distPlot <- renderPlot({
             
             # Set the filters
+            
             years <- seq(input$YearSelection[1],input$YearSelection[2],1) #seq(1971,2019,1)
             
[…]

### 2021-11-22 Allocation_tool/ui.R

@@ -29,6 +29,7 @@ dashboardPage(
       menuItem("Information", tabName = "info", icon = icon("info")),
       br(),
       menuItem("Tool", tabName = "dashboard", icon = icon("dashboard")),
+      menuItem("Demo", tabName = "demo", icon = icon("test")),
       br(),
       menuItem("Instructions", tabName = "instructions", icon = icon("gear")),
       br(),
@@ -37,27 +38,27 @@ dashboardPage(
         tabName = "download",
         icon = icon("download"),
         div(
-        textInput(
-          inputId = "filename",
-          placeholder = "Name download file",
-          label = "File name",
-          value = "Report"
-        )
-        ),
           textInput(
-            inputId = "UserName",
-            placeholder = "Name of user",
-            label = "User name",
-            value = "Annon"
-            
-          ),
+            inputId = "filename",
+            placeholder = "Name download file",
+            label = "File name",
+            value = "Report"
+          )
+        ),
+        textInput(
+          inputId = "UserName",
+          placeholder = "Name of user",
+          label = "User name",
+          value = "Annon"
+          
+        ),
         checkboxGroupInput('results', 'Choose results', c("All",'Grid table', 'Grid plot',"Distribution map"),
                            selected = "All",
-                     inline = FALSE
+                           inline = FALSE
         ),
-          radioButtons('format', 'Document format', c('PDF', 'Word',"HTML"),
-                       inline = TRUE
-                       ),
+        radioButtons('format', 'Document format', c('PDF', 'Word',"HTML"),
+                     inline = TRUE
+        ),
         div(
           downloadButton(
             outputId = "downloadReport",
@@ -345,16 +346,16 @@ dashboardPage(
               column(12,
                      align = "center",
                      h4(strong("Read me:"), "Before running the query, select the outputs you want to show by clicking in the + sign of each box. Note that this step might take a couple of seconds"),
-              actionButton("do",
-                           "Run Query",
-                           icon = icon("gear"),
-                           class = "btn-warning"
-                           ),
-              actionButton("reset",
-                           "Clear all",
-                           icon = icon("clean"),
-                           class = "btn-warning"
-              ),
+                     actionButton("do",
+                                  "Run Query",
+                                  icon = icon("gear"),
+                                  class = "btn-warning"
+                     ),
+                     actionButton("reset",
+                                  "Clear all",
+                                  icon = icon("clean"),
+                                  class = "btn-warning"
+                     ),
               ),
[…]

### 2021-11-22 Allocation_tool/server.R
faster demo grid plot

@@ -38,41 +38,44 @@ state_order <- my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read
 # Grid data ####
 # ---------------------------- #
 # Load grid of state waters
-grid_eez_sw_sf <- st_read(my_path("D","Partial/grid_sw", name = "grid_eez_sw_sf.shp")) %>%
-    select(index,state,geometry) %>%
-    mutate(method = "state_waters",
-           state = str_to_sentence(state)) %>%
-    left_join(state_order)
+# grid_eez_sw_sf <- st_read(my_path("D","Partial/grid_sw", name = "grid_eez_sw_sf.shp")) %>%
+#     select(index,state,geometry) %>%
+#     mutate(method = "state_waters",
+#            state = str_to_sentence(state)) %>%
+#     left_join(state_order)
+# 
+# grid_eez_sw_sf$group <- factor(grid_eez_sw_sf$abrev,      # Reordering group factor levels
+#                                levels = state_order$abrev)
+# 
+# # Load grid of fishing ports
+# grid_eez_fp_sf <-  st_read(my_path("D","Partial/grid_fp", name = "grid_eez_fp.shp")) %>%
+#     select(index,abrev=stt_pst,geometry) %>%
+#     mutate(method = "fishing_port"#,
+#            # state = str_to_sentence(landing_port)
+#     )%>%
+#     left_join(state_order)
+# 
+# grid_eez_fp_sf$group <- factor(grid_eez_fp_sf$abrev,      # Reordering group factor levels
+#                                levels = state_order$abrev)
+# 
+# grid_eez_fp_sf <- arrange(grid_eez_fp_sf,group)
 
-grid_eez_sw_sf$group <- factor(grid_eez_sw_sf$abrev,      # Reordering group factor levels
-                               levels = state_order$abrev)
-
-# Load grid of fishing ports
-grid_eez_fp_sf <-  st_read(my_path("D","Partial/grid_fp", name = "grid_eez_fp.shp")) %>%
-    select(index,abrev=stt_pst,geometry) %>%
-    mutate(method = "fishing_port"#,
-           # state = str_to_sentence(landing_port)
-    )%>%
-    left_join(state_order)
-
-grid_eez_fp_sf$group <- factor(grid_eez_fp_sf$abrev,      # Reordering group factor levels
-                               levels = state_order$abrev)
-
[…]

### 2021-11-22 Allocation_tool/ui.R
UI of demo

@@ -21,6 +21,7 @@ dashboardPage(
   dashboardHeader(title = "Across Boundaries Project"),
   #______________________________________________________________________#
   # Sidebar  ####
+  # Incons https://rstudio.github.io/shinydashboard/appearance.html
   #______________________________________________________________________#
   dashboardSidebar(
     sidebarMenu(
@@ -28,8 +29,8 @@ dashboardPage(
       br(),
       menuItem("Information", tabName = "info", icon = icon("info")),
       br(),
+      menuItem("Demo", tabName = "demo", icon = icon("dashboard", lib = "glyphicon")),
       menuItem("Tool", tabName = "dashboard", icon = icon("dashboard")),
-      menuItem("Demo", tabName = "demo", icon = icon("test")),
       br(),
       menuItem("Instructions", tabName = "instructions", icon = icon("gear")),
       br(),
@@ -427,8 +428,8 @@ dashboardPage(
       ## Demo ####
       #______________________________________________________________________#
       tabItem(tabName = "demo",
-              h1("Control panel"),
-              h4(strong("Read me:"),"Please select from the following options in the blue boxes.", em("Note that all options need to be selected in order for results to appear")),
+              h1("Demo Control panel"),
+              h4(strong("Read me:"),"This is a demonstration control pannel. It is exactlly the same as the original control panel but it has fewer options. It is inteded for familiarization and exploration of the tool. Please select from the following options in the blue boxes.", em("Note that all options need to be selected in order for results to appear")),
               #______________________________________________________________________#
               ### Control panel ####
               #______________________________________________________________________#
@@ -440,7 +441,6 @@ dashboardPage(
                   collapsible = TRUE,
                   title = "Select species",
                   status = "primary", # blue color
-                  # p("Inst. Select here the species you want to explore"),
                   selectizeInput(
                     "SppSelection","",
                     choices = c("Centropristis striata"),
@@ -486,7 +486,7 @@ dashboardPage(
               ),
               column(12,
                      align = "center",
-                     h4(strong("Read me:"), "Before running the query, select the outputs you want to show by clicking in the + sign of each box. Note that this step might take a couple of seconds"),
+                     h4(strong("Read me:"), "Ii the original tool you will have to select the outputs you want to show by clicking in the + sign of each box, before running the query. This is not needed in for the Demo version"),
                      actionButton("do_demo",
                                   "Run Demo",
                                   icon = icon("gear"),
[…]

### 2021-11-22 Allocation_tool/server.R
Faster grid plotting for FP and SW on main tool

@@ -283,164 +283,74 @@ shinyServer(function(input, output,session) {
         # ---------------------------- #
         output$RegUnit <- renderPlot({
             
+            
             # ---------------------------- #
             ## State Waters ######
             # ---------------------------- #
             if(input$SpatSelection == "State waters"){
-                
-                gridExtra::grid.arrange(
-                    # Overall (overlapping) position
-                    ggplot(grid_eez_sw_sf) +
-                        geom_sf(aes(color =group , fill = group), alpha = 0.3) +
-                        geom_sf(data = subset(us_map,ID %in% c("maine", "new hampshire", "massachusetts", "connecticut",
-                                                               "rhode island", "new york", "new jersey", "delaware", "maryland",
-                                                               "virginia", "north carolina"))
-                        ) +
-                        scale_color_manual(values = state_pallet) +
-                        scale_fill_manual(values = state_pallet) +
-                        my_ggtheme_p(leg_pos = "",
-                                     ax_tx_s = 13) +
-                        coord_sf(ylim = c(30,48)) +
-                        scale_y_continuous(breaks = c(30,35,40,45))+
-                        labs(x = "", y = "", title = "") +
-                        theme(plot.title = element_text(size = 20)),
-                    # Showing each state separately
-                    ggplot(grid_eez_sw_sf) +
-                        geom_sf(data = subset(us_map,ID %in% c("maine", "new hampshire", "massachusetts", "connecticut",
-                                                               "rhode island", "new york", "new jersey", "delaware", "maryland",
-                                                               "virginia", "north carolina"))
-                        ) +
-                        geom_sf(aes(color = group),size = 0.1, alpha = 0.3) +
-                        facet_wrap(~ group) +
-                        theme(legend.position = "top") +
-                        scale_color_manual(values = state_pallet,
-                                           labels = grid_eez_sw_sf %>% arrange(order) %>%  pull(state) %>% unique()) +
-                        ggtitle("") +
-                        my_ggtheme_p(leg_pos = "",
-                                     ax_tx_s = 11,
-                                     axx_tx_ang = 45,
-                                     hjust = 1
-                        ),
-                    nrow = 1)
-                
-            }else{
-                # ---------------------------- #
-                # Fishing Ports ######
-                # ---------------------------- #
-                if(input$SpatSelection == "Fishing ports"){
-                    
-                    gridExtra::grid.arrange(
-                        # Overall (overlapping) position
[…]

### 2021-11-22 Allocation_tool/server.R
Added loading spinners tot he figues

@@ -283,74 +283,187 @@ shinyServer(function(input, output,session) {
         # ---------------------------- #
         output$RegUnit <- renderPlot({
             
-            
-            # ---------------------------- #
-            ## State Waters ######
-            # ---------------------------- #
-            if(input$SpatSelection == "State waters"){
-            grids_data <- grids %>% 
-                filter(spatial == "sw")
-            
+            if(input$SpatSelection == "Both apporaches"){
+                
+                # State waters data
+                grids_sw_data <- grids %>% 
+                    filter(spatial == "sw")
+                
+                grids_sw_data$group <- factor(grids_sw_data$abrev,      # Reordering group factor levels
+                                              levels = state_order$abrev)
+                
+                # Fishing port data
+                grids_fp_data <- grids %>% 
+                    filter(spatial == "fp")
+                
+                grids_fp_data$group <- factor(grids_fp_data$abrev,      # Reordering group factor levels
+                                              levels = state_order$abrev)
+                
+                
+                
+                # Maps
+                
+                sw_map <- gridExtra::grid.arrange(
+                    # Overall (overlapping) position
+                    ggplot(grids_sw_data) +
+                        geom_tile(aes(x = lon,
+                                      y = lat,
+                                      color = group , 
+                                      fill = group), 
+                                  alpha = 0.3) +
+                        geom_sf(data = subset(us_map,ID %in% c("maine", "new hampshire", "massachusetts", "connecticut",
+                                                               "rhode island", "new york", "new jersey", "delaware", "maryland",
+                                                               "virginia", "north carolina"))
+                        ) +
+                        scale_color_manual(values = state_pallet) +
+                        scale_fill_manual(values = state_pallet) +
+                        my_ggtheme_p(leg_pos = "",
+                                     ax_tx_s = 10) +
+                        coord_sf(ylim = c(30,48)) +
+                        scale_y_continuous(breaks = c(30,35,40,45))+
+                        labs(x = "", y = "", title = "") +
+                        theme(plot.title = element_text(size = 20)),
+                    # Showing each state separately
+                    ggplot(grids_sw_data) +
+                        geom_sf(data = subset(us_map,ID %in% c("maine", "new hampshire", "massachusetts", "connecticut",
+                                                               "rhode island", "new york", "new jersey", "delaware", "maryland",
+                                                               "virginia", "north carolina"))
+                        ) +
+                        geom_tile(aes(x = lon,
+                                      y = lat,
+                                      color =group , 
[…]

### 2021-11-22 Allocation_tool/ui.R

@@ -8,7 +8,7 @@
 #
 
 
-MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","plotly","formattable","shinydashboard","shinyjs"))
+MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","plotly","formattable","shinydashboard","shinyjs","shinycssloaders"))
 
 spp_survey <- read.csv("./data/spp_region.csv") %>% 
   filter(
@@ -372,7 +372,7 @@ dashboardPage(
                     collapsed = TRUE,
                     title = "Stock's distribution",
                     status = "success", # green color
-                    plotOutput("distPlot")
+                    plotOutput("distPlot") %>% withSpinner(color="#0dc5c1",type = 6)
                 )
               ),
               fluidRow(
@@ -383,7 +383,7 @@ dashboardPage(
                     collapsed = TRUE,
                     title = "Regulatory Units",
                     status = "success", # green color
-                    plotOutput("RegUnit")
+                    plotOutput("RegUnit") %>% withSpinner(color="#0dc5c1",type = 6)
                 ),
                 box(width = 6, 
                     solidHeader = TRUE,
@@ -391,7 +391,7 @@ dashboardPage(
                     collapsed = TRUE,
                     title = "Number of grids per regulatory area",
                     status = "success", # green color
-                    formattableOutput("gridN")
+                    formattableOutput("gridN") %>% withSpinner(color="#0dc5c1",type = 6)
                 )
               ), # close firs fluid row
               fluidRow(
@@ -402,7 +402,8 @@ dashboardPage(
                     collapsed = TRUE,
                     title = "State's proportion",
                     status = "success", # green color
-                    plotOutput("propPlot")),
+                    plotOutput("propPlot") %>% withSpinner(color="#0dc5c1",type = 6)
+                    ),
                 #### Area plot -----------------
                 box(width = 6, 
                     solidHeader = TRUE,
@@ -410,7 +411,7 @@ dashboardPage(
                     collapsed = TRUE,
                     title = "Difference between historic and current distribution",
                     status = "success", # green color
-                    plotOutput("propDiffPlot")
+                    plotOutput("propDiffPlot") %>% withSpinner(color="#0dc5c1",type = 6)
                 )
               ),# # close second fluid row
               fluidRow(
@@ -420,7 +421,7 @@ dashboardPage(
                     collapsed = TRUE,
[…]

### 2021-11-29 Scripts/spatial_analisis.Rmd
Re ran analysis to include Wanchese, NC

@@
     total_live_pounds = as.numeric(total_live_pounds),
-    total_value = as.numeric(total_value)
+    total_value = as.numeric(total_value),
+    # Allocate all bsb NC data to Wanchese
+    port_name = ifelse(species_name == "black sea bass" & state_postal == "nc" & port_name == "unknown","wanchese",port_name)
   ) %>% 
@@
   )
+
+# quantiles_df <- overall_port_data %>% 
+#   group_by(species_name) %>% 
+#   summarise(
+#     "95th" = quantile(year_ton, 0.95),
+#     "75th" = quantile(year_ton, 0.75),
+#     "50th" = quantile(year_ton, 0.50)) %>% 
+#   gather("tresh","quant",`95th`:`50th`)
+# 
+# 
+# top_portsb <- overall_port_data %>% 
+#   left_join(quantiles_df,
+#             by = "species_name") %>% 
+#   mutate(
+#     treshold = ifelse(year_ton >= quant,tresh,NA) 
+#   )
 
@@
     group_by(species_name) %>% 
-    top_frac(0.5,year_ton) %>%  
-    mutate(tresh = "95th"),
+    top_frac(0.05,year_ton) %>%  
+    mutate(tresh = "95th"), # top 95
   # 85%
@@
     top_frac(0.15,year_ton) %>% 
-    mutate(tresh = "85th"),
+    mutate(tresh = "85th"), # top 85
   # 65%
@@
     group_by(species_name) %>% 
-    top_frac(0.5,year_ton) %>%  # top 75
+    top_frac(0.5,year_ton) %>%  # top 50
     mutate(tresh = "50th")
@@
 # Save data for future analysis
-# write_csv(noaa_ports_complete,
-#           my_path("D","Partial", name = "top_ports.csv")
-#           )
+write_csv(noaa_ports_complete,
+          my_path("D","Partial", name = "top_ports.csv")
+          )
 
@@
 bbox <- c(st_bbox(state_bf))
+
+# xmin      ymin      xmax      ymax 
+# -82.57346  29.77459 -62.88543  49.19141
 
@@
 # Get the overlapping segments 
-# NOTE: Takes some gooooood time (~20 min)
+# NOTE: Takes some gooooood time (~ min)
 Sys.time()
@@
 
-write_sf(grid_eez_sf_fp, my_path("D", "Partial/grid_fp",name="grid_eez_fp.shp"))
+grid_eez_sf_fp_save <- grid_eez_sf_fp %>% 
+  select(spp = species_name,
+         index,
+         port_name,
+         abrev = state_postal,
+         geometry) %>% 
+  left_join(as.data.frame(land_sf),
+            by = "abrev") %>% 
+  select(-geom,-ID)
+
+write_sf(grid_eez_sf_fp_save, my_path("D", "Partial/grid_fp",name="grid_eez_fp.shp"))
 
 # Get final df with index
-grid_eez_fp_df <- as.data.frame(grid_eez_sf_fp) %>%
-  select(index,port_name,abrev=state_postal,spp=species_name) %>% 
-  left_join(ne_grid,
-            by = "index")
+grid_eez_fp_df <- as.data.frame(st_coordinates(grid_eez_sf_fp_save)) %>% 
+  rename(lon = X, lat = Y) %>% 
+  bind_cols(grid_eez_sf_fp_save) %>% 
+  select(-geometry)
 
@@
 ) %>% 
+  left_join(land_sf) %>% 
+  select(index,state,abrev,lat,lon,spp) %>% 
   mutate(spatial = "sw",
-         port_name = NA,
-         abrev = NA
+         port_name = NA
          )

### 2021-11-29 Scripts/spatial_analisis.Rmd
F1 updated with ports

@@
 
-# Get state order from North to south
-state_order <- my_path("D","Spatial/grid_eez_sw", name = "grid_eez_sw_df.csv",read = T) %>%
-  group_by(state) %>% 
-  summarise(
-    order = mean(lat)
-  ) %>% 
-  mutate(abrev = c("CT","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VA")
-  ) %>% 
-  arrange(desc(order)) %>% 
-  mutate(order= c("b","a",letters[3:11])) %>% # weirdly maine goes below
-  arrange(order)
-
 # Load grid of state waters
-grid_eez_sw_sf <-  st_read(my_path("D","Spatial/grid_eez_sw", name = "grid_eez_sw_sf.shp")) %>%
+grid_eez_sw_sf <-  st_read(my_path("D","Partial/grid_sw", name = "grid_eez_sw_sf.shp")) %>%
   select(index,state,geometry) %>% 
@@
          state = str_to_sentence(state)) %>% 
-  left_join(state_order)
+  left_join(state_lat)
 
 grid_eez_sw_sf$group <- factor(grid_eez_sw_sf$abrev,      # Reordering group factor levels
-                               levels = state_order$abrev)
+                               levels = state_lat$abrev)
 
 # Load grid of fishing ports
-grid_eez_fp_sf <-  st_read(my_path("D","Spatial/grid_eez_fp", name = "grid_eez_fp.shp")) %>%
-  select(index,abrev=lndng_s,geometry) %>% 
+grid_eez_fp_sf <-  st_read(my_path("D","Partial/grid_fp", name = "grid_eez_fp.shp")) %>%
+  select(index,abrev,geometry) %>% 
   mutate(method = "fishing_port"#,
@@
          )%>% 
-  left_join(state_order)
+  left_join(state_lat)
 
 grid_eez_fp_sf$group <- factor(grid_eez_fp_sf$abrev,      # Reordering group factor levels
-                               levels = state_order$abrev)
+                               levels = state_lat$abrev)
 
@@
     # scale_fill_manual(values = state_pallet) +
-    scale_color_manual(values = c(state_pallet[3:4],state_pallet[6:13])) +
-    scale_fill_manual(values = c(state_pallet[3:4],state_pallet[6:13])) +
+    scale_color_manual(values = c(state_pallet[3:7],state_pallet[9:11])) +
+    scale_fill_manual(values = c(state_pallet[3:7],state_pallet[9:11])) +
     my_ggtheme_p(leg_pos = "",
@@
     # scale_color_manual(values = state_pallet,
-    scale_color_manual(values = c(state_pallet[3:4],state_pallet[6:13]),
+    scale_color_manual(values = c(state_pallet[3:7],state_pallet[9:11]),
                        # labels = unique(grid_eez_fp_sf$group)) +

### 2021-11-29 Scripts/spatial_analisis.Rmd
Fixed ME NH lat issue

@@
   filter(!is.na(state)) %>% 
-  mutate(abrev = c("CT","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VA")
-  ) %>% 
-  arrange(desc(order)) %>% 
-  mutate(lat = order,
-    # order = letters[1:11],
-    order = c("b","a",letters[3:11]),)
+  mutate(abrev = c("CT","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VA"),
+         order = ifelse(abrev == "ME", order+1,order)
+  ) %>% 
+  arrange(desc(order))
 

### 2021-11-29 Scripts/spatial_analisis.Rmd
Changed F3 to positive/negative scale

@@
 ) %>%
-  mutate(spatial = "fp")
+  mutate(spatial = "fp",
+  spp = ifelse(spp == "summer flounder","Paralichthys dentatus", 
+                 ifelse(spp == "scup", "Stenotomus chrysops", 
+                        "Centropristis striata"
+                 )
+    )
+  )
 
@@
 
-unique(historic_spp$spp)
-unique(historic_spp$region)
-unique(historic_spp$season)
+# Data summary
+c(unique(historic_spp$spp),
+  unique(historic_spp$region),
+  unique(historic_spp$season),
+  unique(historic_spp$spatial)
+)
 
@@
   mutate(
-    difference = abs(fp-sw),
+    difference = fp-sw,
     difference = ifelse(difference > 100,100,
@@
   geom_sf(aes(fill = mean_per)) +
-  viridis::scale_fill_viridis("Difference (%)", alpha = 0.8,option = "C",
-                              breaks = seq(0,25,5),
-                              limits=(c(0,25)),
+  # viridis::scale_fill_viridis("Difference (%)", alpha = 0.8,option = "C",
+  #                             breaks = seq(0,25,5),
+  #                             limits=(c(0,25)),
+  #                             # labels = c("<-10",seq(-75,75,25),">100")
+  #                             ) +
+  scale_fill_gradient2("% Difference\n(fp-sw)", 
+                       breaks = seq(-14,35,7),
+                       limits=(c(-14,35)),
                               # labels = c("<-10",seq(-75,75,25),">100")
@@
   mutate(
-    Difference = abs(Fall-Spring),
+    Difference = Fall-Spring,
     Difference = ifelse(Difference > 100,100,

### 2021-11-29 Scripts/spatial_analisis.Rmd
Updated F3 with plys/minus scake

@@
   geom_sf(aes(fill = mean_per)) +
-  viridis::scale_fill_viridis("Difference (%)", alpha = 0.8,option = "C",
-                              breaks = seq(0,5,1),
-                              limits=(c(0,5)),
+  # viridis::scale_fill_viridis("Difference (%)", alpha = 0.8,option = "C",
+  #                             breaks = seq(0,5,1),
+  #                             limits=(c(0,5)),
+  #                             # labels = c("<-10",seq(-75,75,25),">100")
+  #                             ) +
+  scale_fill_gradient2("% Difference\n(Fall-Spring)", 
+                       breaks = seq(-4,4,2),
+                       limits=(c(-4,4)),
                               # labels = c("<-10",seq(-75,75,25),">100")

### 2021-11-29 Scripts/spatial_analisis.Rmd
Fixed color issue for F5

@@
                                wes_palette(n = 5, name = "Darjeeling2"),
-                               # wes_palette(n = 2, name = "GrandBudapest1")
                   "#FD6467"
                   )
+
+length(state_pallet)
+
+barplot(c(1,2,3,4,5,6,7,8,9,10,11), col=state_pallet)
 
@@
 
-## Regulatory units result
+## F1 Regulatory units result
 
@@
       y = round(RMean),
-      fill = order
-      # fill = state
+      # fill = abrev
+      fill = state
     )
@@
              ) +
-
   ylab("Propotion (10 yrs running average)") +
@@
     "State\n(Latitudinal order)",
-    values = state_pallet,
-    labels = state_fit %>% arrange(order) %>%  pull(state) %>% unique()
+    values = c(state_pallet[1:10],state_pallet[10]),
+                      labels = state_fit %>% arrange(desc(order)) %>%  pull(state) %>% unique()
   ) +

### 2021-11-29 Scripts/spatial_analisis.Rmd
misc

@@
       y = round(RMean),
-      # fill = abrev
-      fill = state
+      fill = abrev
+      # fill = state
     )
@@
   # viridis::scale_fill_viridis(discrete = T, alpha = 0.8) +
-  scale_fill_manual(
-    "State\n(Latitudinal order)",
-    values = c(state_pallet[1:10],state_pallet[10]),
+  scale_fill_manual("State\n(Latitudinal order)",
+                    values = state_pallet,
                                labels = state_fit %>% arrange(desc(order)) %>%  pull(state) %>% unique()
                     ) +
-    scale_color_manual("",values = "grey90"
-  ) +
+    scale_color_manual("",values = "grey90") +
   facet_grid(spp~spatial) +

### 2021-11-29 Scripts/manuscript_acrossboundaries.Rmd
Further changes to manuscript

@@
 title: "Quantifying fish range shifts across poorly defined management boundaries"
-subtitle: "DRAFT. Target journal *PlosOne*"
-author: "Palacios-Abrantes Juliano, Crosson Scott, Dumas Chris, Fujita Rod, Levine Arielle, Longo Catherine, Jensen Olaf"
+author: "DRAFT. Target journal *PlosOne*"
+subtitle: "Juliano Palacios-Abrantes*^1^, Scott Crosson^2^, Chris Dumas^3^, Rod Fujita^4^, Arielle Levine^5^, Catherine Longo^6^, Olaf Jensen^1^"
+date: "Affiliations: ^1^Center for Limnology, University of Wisconsin-Madison, US.
+^2^National Oceanic and Atmospheric Administration, US.
+^3^University of North Carolina Wilmington, US.
+^4^Rod Fujita, Environmental Defense Fund, US.
+^5^San Diego State University, US.
+^6^Marine Stewardship Council, UK."
 output: 
@@
     toc: no
+    latex_engine: xelatex
+bibliography: ../References/Across_Bound_Ref.bib
+csl: ../References/plos-one.csl
+header-includes:
+  - \usepackage{setspace}
+  - \usepackage{caption}
+  - \usepackage[left]{lineno} # for numbers in lines
+  - \usepackage{float} # Use the 'float' package
+  - \captionsetup[figure]{name = Fig}
+  - \floatplacement{figure}{H}
 ---
@@
 The extrapolation was done separately for both Fall and Spring seasons covering the time period of 1971 to 2019.
+
+**WANCHEESE NORTH CAROLINA FOR BLACK SEA BASS**
 

### 2021-12-07 Scripts/spatial_analisis.Rmd
Included grid numbers area

@@
 
+expand.grid(
+    lon = seq(from = 40, to = 44, by = 0.1),
+    lat = seq(from = 40, to = 45, by = 0.1)
+)
+
 ```
@@
                           ifelse( spp == "Centropristis striata" & year >= 1980 & year <= 2001,"Reference",
-                                 ifelse(year > 2001,"Today",NA)
+                                 ifelse(year > 2009,"2010-2019",NA)
                           )
@@
 ## F1 Regulatory units result
+
+```{r numbers_for_paper}
+
+# Estimate Area
+# Degree ressolution for area estimation
+# https://rdrr.io/github/stineb/rbeni/src/R/area.R
+# https://www.pmel.noaa.gov/maillists/tmap/ferret_users/fu_2004/msg00023.html
+# https://www.engr.scu.edu/~emaurer/tools/calc_cell_area_cgi.pl
+
+r_earth <- 6371000 # NASA's volumetric mean radious https://nssdc.gsfc.nasa.gov/planetary/factsheet/earthfact.html
+res_lon <- 0.3 # data degree ressolution
+
+grids %>% 
+  group_by(state,spatial,spp,index,lat,lon) %>%
+  tally() %>% 
+  # View()
+  mutate(
+    area = (4 * r_earth^2 * 0.5 * 0.3 * pi/180 * cos(abs(lat) * pi/180 ) * sin(0.5 * 0.3 * pi/180))/1000000
+  ) %>% 
+  # View()
+  group_by(state,spatial,spp) %>%
+  summarise(tot_area = sum(area)) %>% 
+  select(-spp) %>%
+  group_by(state,spatial) %>%
+  top_n(1,tot_area) %>%
+  group_by(state,spatial) %>%
+  summarise(tot_area = mean(tot_area)) %>%
+  spread(spatial,tot_area) %>%
+  mutate(
+    # fp = replace_na(fp,0),
+    diff = round((abs(fp-sw))/((fp+sw)/2)*100)
+  ) %>% 
+  View()
+
+# Estimate distance between points
+
+my_path("D","Partial","top_ports.csv", read = T) %>% 
+  filter(tresh == "75th",
+         state_postal == "NY") %>% 
+  ggplot() +
+  geom_point(
+    aes(
+      x = lon,
+      y = lat,
+      color = port_name
+    )
+  )
+
+# Most distant ports Mntauk and point lookout
+
+ny_dist <- grids %>% 
+  filter(port_name %in% c("montauk","point lookout")) %>% 
+  group_by(port_name) %>% 
+  summarise_at(vars(lat,lon),
+               mean)
+
+# Distance between furthest ports in NY
+geosphere::distm(c(ny_dist$lon[1], ny_dist$lat[1]), c(ny_dist$lon[2], ny_dist$lat[2]), fun = geosphere::distHaversine)/1000
+
+```
 
@@
 
-## Interpolation result
+## F2 Interpolation result
 
@@
 
+# For face order
+interpol_result$labelx = factor(interpol_result$label, levels=c("Reference","2010-2019"))
+centroid_db$labelx = factor(centroid_db$label, levels=c("Reference","2010-2019"))
+
 inter_map <- ggplot() +
@@
              shape = 3,
-             color = "white"
+             color = "black"
   ) + 
@@
 # wes anderson option
-scale_fill_gradientn("CPUE",
+scale_fill_gradientn("CPUE\n(log 10)",
                      colours = pal,
@@
 ) +
-  scale_color_gradientn("CPUE",
+  scale_color_gradientn("CPUE\n(log 10)",
                         colours = pal,
@@
   ) +
-  facet_grid(spp~season+label) +
-  my_ggtheme_m(map_type = "na", leg_pos = "right",ax_tx_s = 7,ax_tl_s = 10,leg_tx_s = 12) #+
-# theme(legend.key.width = unit(3,"line"))
+  facet_grid(spp~season+labelx) +
+  my_ggtheme_m(map_type = "na", leg_pos = "right",ax_tx_s = 7,ax_tl_s = 10,leg_tx_s = 12)
 
@@
 
+# For face order
+reg_unit$labelx = factor(reg_unit$label, levels=c("Reference","2010-2019"))
+
 # The plot
@@
                               )+
-  facet_grid(spatial~ spp+label) +
+  facet_grid(spatial~ spp+labelx) +
   labs(x = "", 
@@
                               ) +
-  facet_grid(spatial~ spp+label) +
+  facet_grid(spatial~ spp+labelx) +
   labs(x = "", 
@@
 
+library(cowplot)
+
 # Cowplot option
@@
   draw_plot(diff_plot, x = 0, y = 0, width = 1, height = 0.4) +
+  # Logos/images
+  # draw_image("https://media.fisheries.noaa.gov/styles/original/s3/dam-migration/640x427-black-sea-bass.png?itok=7Ax8suz_", 
+  #            x = -0.31,
+  #            y = 0.345, 
+  #            scale = 0.15) +
+  # draw_image("https://media.fisheries.noaa.gov/styles/original/s3/dam-migration/scup.png?itok=noMUoDe0", 
+  #            x = 0.05,
+  #            y = 0.345, 
+  #            scale = 0.15) +
+  # draw_image("https://media.fisheries.noaa.gov/styles/original/s3/2021-03/640x427-summer-flounder.png?itok=B6G4jkW7", 
+  #            x = 0.35,
+  #            y = 0.345, 
+  #            scale = 0.15) +
   draw_plot_label(label = c("Latitude", "Longitude"), 
@@
   mutate(spp = gsub(" ","\n",spp))
+
+# For face order
+season_fit$labelx = factor(season_fit$label, levels=c("Reference","2010-2019"))
 
@@
                               )+
-  facet_grid(season~ spp+label) +
+  facet_grid(season~ spp+labelx) +
   labs(x = "", 
@@
   scale_fill_gradient2("% Difference\n(Fall-Spring)", 
-                       breaks = seq(-4,4,2),
-                       limits=(c(-4,4)),
+                       breaks = seq(-5,5,1),
+                       limits=(c(-5,5)),
                               # labels = c("<-10",seq(-75,75,25),">100")
                               ) +
-  facet_grid(season~ spp+label) +
+  facet_grid(season~ spp+labelx) +
   labs(x = "", 

### 2021-12-07 Scripts/manuscript_acrossboundaries.Rmd
misc

@@
   mutate_if(is.numeric,~.*100) %>%
-  # readr::write_csv("quota_table.csv")
-  # group_by() %>% #just checking they add up
-  # summarise_if(is.numeric,sum)
+  readr::write_csv("../Results/quota_table.csv")
+  group_by() %>% #just checking they add up
+  summarise_if(is.numeric,sum)
   kable("latex",

### 2021-12-08 Allocation_tool/server.R
Made double stock's distribution plots

@@ -128,8 +128,9 @@ shinyServer(function(input, output,session) {
             name <- paste0("obs_",str_replace(input$SppSelection," ","_"),".csv")
             
             data <- my_path("D","Spp/Observation",name = name, read = T)
-            
-            # data <- readRDS("/Volumes/Enterprise/Data/AcrossBoundaries/Data/pinskylab-OceanAdapt-966adf0/data_clean/dat_exploded.rds") %>%
+
+              # Test Data
+            # raw_data <- readRDS("/Volumes/Enterprise/Data/AcrossBoundaries/Data/pinskylab-OceanAdapt-966adf0/data_clean/dat_exploded.rds") %>%
             #     filter(
             #         spp %in% c("Centropristis striata","Paralichthys dentatus","Stenotomus chrysops"),
             #         region %in% c("Northeast US Fall" , "Northeast US Spring")
@@ -149,8 +150,8 @@ shinyServer(function(input, output,session) {
             
             # Set the filters
             species <- input$SppSelection #"Centropristis striata"
-            survey <-input$SurveySelection # "Northeast US Fall"
-            reg_area <- input$SpatSelection # "State waters"
+            # survey <-input$SurveySelection # "Northeast US Fall"
+            # reg_area <- input$SpatSelection # "State waters"
             
             
             data <- my_path("R","Partial/Interpolation/",name = name, read = T) %>% 
@@ -163,9 +164,7 @@ shinyServer(function(input, output,session) {
                                      ifelse(spatial == "sw","State waters","Difference")
                     )
                 ) %>% 
-                filter(spp %in% species,
-                       region %in% survey,
-                       spatial %in% reg_area)
+                filter(spp %in% species)
             
             # For testing
             # data <- my_path("R","Partial/Interpolation/",name = "tif_Centropristis_striata.csv", read = T)
@@ -471,26 +470,45 @@ shinyServer(function(input, output,session) {
         output$distPlot <- renderPlot({
             
             # Set the filters
+            # years <- seq(1971,2019,1) # for testing
+            years <- seq(input$YearSelection[1],input$YearSelection[2],1) 
             
-            years <- seq(input$YearSelection[1],input$YearSelection[2],1) #seq(1971,2019,1)
+            if(input$SurveySelection == "Both surveys"){
+                tif_data <- tif_data()
+                raw_data <- raw_data()
+            }else{
+                
+                tif_data <- tif_data() %>%
+                    filter(region %in% input$SurveySelection)
+                
+                raw_data <- raw_data() %>%
[…]

### 2021-12-08 Allocation_tool/ui.R

@@ -286,7 +286,7 @@ dashboardPage(
                   selectizeInput(
                     'SurveySelection', 
                     "", 
-                    choices = unique(spp_survey$region),
+                    choices = c(unique(spp_survey$region),"Both surveys"),
                     options = list(
                       placeholder = 'Type or click to select a season',
                       onInitialize = I('function() { this.setValue(""); }')

### 2021-12-08 Allocation_tool/server.R
Included output option for tif plot

@@ -495,20 +495,20 @@ shinyServer(function(input, output,session) {
                 filter(spp %in% input$SppSelection,
                        year %in% years) %>%
                 group_by(region,spp,lon,lat) %>% 
-                summarise(mean_wtcpue = mean(wtcpue,na.rm = T), .groups = T)
+                summarise(mean_wtcpue = mean(wtcpue,na.rm = T), .groups = "drop")
             
             
             # Set the plot data
             tif_plot_data <- tif_data %>%
                 group_by(index,region,spp,lon,lat) %>% 
-                summarise(mean_cpue = mean(value,na.rm = T)) %>% 
+                summarise(mean_cpue = mean(value,na.rm = T), .groups = "drop") %>% 
                 mutate(cpue_log10 = log10(mean_cpue)) %>% 
                 gather("type","cpue",mean_cpue,cpue_log10)
             
             
             plot <- ggplot(us_map) +
                 geom_sf()+
-                geom_tile( data = subset(tif_plot_data, type == "mean_cpue"),
+                geom_tile( data = subset(tif_plot_data, type == input$output),
                            aes(
                                x = lon,
                                y = lat,
@@ -534,13 +534,15 @@ shinyServer(function(input, output,session) {
                 ggtitle("Distribution estimated by using Triangular Irregular Surface method")
             
             
-            if(input$SurveySelection != "Both surveys"){
-                plot + facet_wrap(~type, ncol = 2)
-            }else{
+            # if(input$SurveySelection != "Both surveys"){
+            #     plot + facet_wrap(~type, ncol = 2)
+            # }else{
                 if(input$SurveySelection == "Both surveys"){
-                    plot + facet_wrap(~type+region, ncol = 2)
+                    plot + facet_wrap(~region, ncol = 2)
+                }else{
+                    plot
                 }
-            }
+            # }
         })
         
         # ---------------------------- #

### 2021-12-08 Allocation_tool/ui.R

@@ -372,6 +372,14 @@ dashboardPage(
                     collapsed = TRUE,
                     title = "Stock's distribution",
                     status = "success", # green color
+                    # Include output option
+                    radioButtons('output', "Output unit", 
+                                 c('Mean CPUE' = "mean_cpue",
+                                   "Log 10 CPUE" = "cpue_log10"
+                                   ),
+                                 selected = "mean_cpue",
+                                 inline = TRUE
+                    ),
                     plotOutput("distPlot") %>% withSpinner(color="#0dc5c1",type = 6)
                 )
               ),

### 2021-12-08 Allocation_tool/server.R
Included different maps for regulatory units sw and fp

@@ -15,8 +15,6 @@
 library(MyFunctions)
 MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","DT","plotly","wesanderson","zoo","formattable","viridis","shinydashboard","rmarkdown"))
 
-us_map <- st_as_sf(map("state", plot = FALSE, fill = TRUE))
-
 state_pallet <- c(wes_palette(n = 5, name = "Darjeeling1"),
                   wes_palette(n = 5, name = "Darjeeling2"),
                   wes_palette(n = 3, name = "Royal1")
@@ -34,48 +32,44 @@ state_order <- my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read
     mutate(order= c("b","a",letters[3:11])) %>% # weirdly maine goes below
     arrange(order)
 
+us_map <- st_as_sf(map("state", plot = FALSE, fill = TRUE)) %>% 
+    mutate(
+        state = str_to_sentence(ID)
+    ) %>% 
+    left_join(state_order,
+              by = "state")
+
 # ---------------------------- #
 # Grid data ####
 # ---------------------------- #
-# Load grid of state waters
-# grid_eez_sw_sf <- st_read(my_path("D","Partial/grid_sw", name = "grid_eez_sw_sf.shp")) %>%
-#     select(index,state,geometry) %>%
-#     mutate(method = "state_waters",
-#            state = str_to_sentence(state)) %>%
-#     left_join(state_order)
-# 
-# grid_eez_sw_sf$group <- factor(grid_eez_sw_sf$abrev,      # Reordering group factor levels
-#                                levels = state_order$abrev)
-# 
-# # Load grid of fishing ports
-# grid_eez_fp_sf <-  st_read(my_path("D","Partial/grid_fp", name = "grid_eez_fp.shp")) %>%
-#     select(index,abrev=stt_pst,geometry) %>%
-#     mutate(method = "fishing_port"#,
-#            # state = str_to_sentence(landing_port)
-#     )%>%
-#     left_join(state_order)
-# 
-# grid_eez_fp_sf$group <- factor(grid_eez_fp_sf$abrev,      # Reordering group factor levels
-#                                levels = state_order$abrev)
-# 
-# grid_eez_fp_sf <- arrange(grid_eez_fp_sf,group)
 
[…]

### 2021-12-08 Allocation_tool/ui.R

@@ -391,6 +391,12 @@ dashboardPage(
                     collapsed = TRUE,
                     title = "Regulatory Units",
                     status = "success", # green color
+                    # Include number of maps 
+                    radioButtons('map_type', "Map type", 
+                                 c("Both",'Overlapping',"By State"),
+                                 selected = "Both",
+                                 inline = TRUE
+                    ),
                     plotOutput("RegUnit") %>% withSpinner(color="#0dc5c1",type = 6)
                 ),
                 box(width = 6, 

### 2021-12-08 Allocation_tool/server.R
grid maps are working fro all

@@ -15,9 +15,16 @@
 library(MyFunctions)
 MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","DT","plotly","wesanderson","zoo","formattable","viridis","shinydashboard","rmarkdown"))
 
+# state_pallet <- c(wes_palette(n = 5, name = "Darjeeling1"),
+#                   wes_palette(n = 5, name = "Darjeeling2"),
+#                   wes_palette(n = 3, name = "Royal1")
+# )
+
+
+# Create specific state pallet from our friend Wes Andersson
 state_pallet <- c(wes_palette(n = 5, name = "Darjeeling1"),
                   wes_palette(n = 5, name = "Darjeeling2"),
-                  wes_palette(n = 3, name = "Royal1")
+                  "#FD6467"
 )
 
 # Set the filters
@@ -43,49 +50,52 @@ us_map <- st_as_sf(map("state", plot = FALSE, fill = TRUE)) %>%
 # Grid data ####
 # ---------------------------- #
 
-grids_sw <- bind_rows(
-    my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
-        mutate(spp = "Paralichthys dentatus"),
-    my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
-        mutate(spp = "Stenotomus chrysops"),
-    my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
-        mutate(spp = "Centropristis striata")
-) %>% 
+# grids_sw <- bind_rows(
+#     my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
+#         mutate(spp = "Paralichthys dentatus"),
+#     my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
+#         mutate(spp = "Stenotomus chrysops"),
+#     my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
+#         mutate(spp = "Centropristis striata")
+# ) %>% 
+#     left_join(state_order) %>% 
+#     select(index,state,abrev,lat,lon,spp) %>% 
+#     mutate(spatial = "sw",
+#            port_name = NA
+#     )
+# 
[…]

### 2021-12-08 Scripts/spatial_analisis.Rmd
misc

@@
 # Create specific state pallet from our friend Wes Andersson
+
 state_pallet <- c(wes_palette(n = 5, name = "Darjeeling1"),
                                wes_palette(n = 5, name = "Darjeeling2"),
-                               wes_palette(n = 3, name = "Royal1")
+                  "#FD6467"
                   )
@@
 
-# State pallet
-
-state_pallet <- c(wes_palette(n = 5, name = "Darjeeling1"),
-                               wes_palette(n = 5, name = "Darjeeling2"),
-                  "#FD6467"
-                  )
-
 length(state_pallet)
@@
 ## F1 Regulatory units result
+
+### NUmbers for papaer
 
@@
 
+### Figure plotting
+
 ```{r cropped_plot_paper, eval = F, echo = T}
@@
          # state = str_to_sentence(landing_port)
-         )%>% 
+         ) %>% 
   left_join(state_lat)

### 2021-12-08 Allocation_tool/server.R
Done with reguñaltory units options

@@ -15,17 +15,17 @@
 library(MyFunctions)
 MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","DT","plotly","wesanderson","zoo","formattable","viridis","shinydashboard","rmarkdown"))
 
-# state_pallet <- c(wes_palette(n = 5, name = "Darjeeling1"),
-#                   wes_palette(n = 5, name = "Darjeeling2"),
-#                   wes_palette(n = 3, name = "Royal1")
-# )
+state_pallet <- c(wes_palette(n = 5, name = "Darjeeling1"),
+                  wes_palette(n = 5, name = "Darjeeling2"),
+                  wes_palette(n = 3, name = "Royal1")
+)
 
 
 # Create specific state pallet from our friend Wes Andersson
-state_pallet <- c(wes_palette(n = 5, name = "Darjeeling1"),
-                  wes_palette(n = 5, name = "Darjeeling2"),
-                  "#FD6467"
-)
+# state_pallet <- c(wes_palette(n = 5, name = "Darjeeling1"),
+#                   wes_palette(n = 5, name = "Darjeeling2"),
+#                   "#FD6467"
+# )
 
 # Set the filters
 state_order <- my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>%
@@ -341,8 +341,7 @@ shinyServer(function(input, output,session) {
                         geom_tile(aes(x = lon,
                                       y = lat,
                                       color =group , 
-                                      fill = group), 
-                                  alpha = 0.3) +
+                                      fill = group)) +
                         labs(x = "", y = "", title = "") +
                         facet_wrap(~ group) +
                         scale_color_manual(values = state_pallet,
@@ -383,32 +382,31 @@ shinyServer(function(input, output,session) {
                         geom_tile(aes(x = lon,
                                       y = lat,
                                       color =group , 
-                                      fill = group), 
-                                  alpha = 0.3) +
+                                      fill = group)
+                                  ) +
                         labs(x = "", y = "", title = "") +
                         facet_wrap(~ group) +
                         theme(legend.position = "top") +
                 scale_color_manual(values = c(state_pallet[3:7],state_pallet[9:11])) +
                 scale_fill_manual(values = c(state_pallet[3:7],state_pallet[9:11])) +
                         scale_y_continuous(breaks = c(30,35,40,45))+
-                        ggtitle("") +
                         my_ggtheme_m(leg_pos = "")
             
             
[…]

### 2021-12-08 Allocation_tool/server.R
misc

@@ -132,8 +132,8 @@ shinyServer(function(input, output,session) {
             name <- paste0("obs_",str_replace(input$SppSelection," ","_"),".csv")
             
             data <- my_path("D","Spp/Observation",name = name, read = T)
-
-              # Test Data
+            
+            # Test Data
             # raw_data <- readRDS("/Volumes/Enterprise/Data/AcrossBoundaries/Data/pinskylab-OceanAdapt-966adf0/data_clean/dat_exploded.rds") %>%
             #     filter(
             #         spp %in% c("Centropristis striata","Paralichthys dentatus","Stenotomus chrysops"),
@@ -170,37 +170,23 @@ shinyServer(function(input, output,session) {
                 ) %>% 
                 filter(spp %in% species)
             
-            # For testing
-            # data <- my_path("R","Partial/Interpolation/",name = "tif_Centropristis_striata.csv", read = T)
-            
-            
-            # tif_data <- data %>%
-            #     left_join(grids,
-            #               by = c("index","lat","lon")
-            #     ) %>%
-            #     filter(!is.na(spatial)) %>%
-            #     mutate(
-            #         spatial = ifelse(spatial == "fp","Fishing ports",
-            #                          ifelse(spatial == "sw","State waters","Difference")
-            #         )
-            #     ) %>%
-            #     filter(#spp %in% species,
-            #            region %in% survey,
-            #            # spatial %in% reg_area
-            #            )
             
         })
         
         
         # ---------------------------- #
-        # Regulatory Units Table ####
+        # Regulatory Units ####
         # ---------------------------- #
+        
+        ## ---------------------------- ##
+        #### Table #####
+        ## ---------------------------- ##
         output$gridN <- renderFormattable({
             
             customGreen = "#71CA97"
             
             # ---------------------------- #
-            # State waters ######
+            ##### State waters ######
             # ---------------------------- #
             
             if(input$SpatSelection == "State waters"){
@@ -220,7 +206,7 @@ shinyServer(function(input, output,session) {
                 
             } 
             # ---------------------------- #
-            # Fishing Ports ######
+            #### Fishing Ports ######
             # ---------------------------- #
             if(input$SpatSelection == "Fishing ports"){
                 
@@ -241,12 +227,13 @@ shinyServer(function(input, output,session) {
                 )
                 
             }
-            
+            # ---------------------------- #
+            #### Both approaches ######
+            # ---------------------------- #
             if(input$SpatSelection == "Both apporaches"){
[…]

### 2021-12-08 Allocation_tool/server.R
Showing all sttes filtering by stock

@@ -50,52 +50,52 @@ us_map <- st_as_sf(map("state", plot = FALSE, fill = TRUE)) %>%
 # Grid data ####
 # ---------------------------- #
 
-# grids_sw <- bind_rows(
-#     my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
-#         mutate(spp = "Paralichthys dentatus"),
-#     my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
-#         mutate(spp = "Stenotomus chrysops"),
-#     my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
-#         mutate(spp = "Centropristis striata")
-# ) %>% 
+grids_sw <- bind_rows(
+    my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>%
+        mutate(spp = "Paralichthys dentatus"),
+    my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>%
+        mutate(spp = "Stenotomus chrysops"),
+    my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>%
+        mutate(spp = "Centropristis striata")
+) %>%
+    left_join(state_order) %>%
+    select(index,state,abrev,lat,lon,spp) %>%
+    mutate(spatial = "sw",
+           port_name = NA
+    )
+
+grids_fp <- my_path("D", "Partial/grid_fp", name = "grid_eez_fp_df.csv", read = T
+) %>%
+    mutate(spatial = "fp",
+           spp = ifelse(spp == "summer flounder","Paralichthys dentatus",
+                        ifelse(spp == "scup", "Stenotomus chrysops",
+                               "Centropristis striata"
+                        )
+           )
+    )
+
+# Join both approaches
+grids <- bind_rows(grids_sw,grids_fp)
+
+unique(grids_fp$state)
+unique(grids_sw$state)
+
+# grids <- my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
+#     mutate(
+#         spatial = "sw"
+#     ) %>% 
 #     left_join(state_order) %>% 
-#     select(index,state,abrev,lat,lon,spp) %>% 
-#     mutate(spatial = "sw",
-#            port_name = NA
-#     )
-# 
[…]

### 2021-12-08 Allocation_tool/server.R
Cleaned rthe regulatory units part, but it is slow beacuse it runs the whole thing every time

@@ -271,136 +271,139 @@ shinyServer(function(input, output,session) {
         # ---------------------------- #        
         
         # ---------------------------- #
-        ###### Both approaches ######
+        ###### Create maps ######
         # ---------------------------- #        
         output$RegUnit <- renderPlot({
             
+            # if(input$SpatSelection == "Both apporaches"){
+            
+            # State waters data
+            grids_sw_data <- grids %>% 
+                filter(spatial == "sw")
+            
+            
+            # Fishing port data
+            grids_fp_data <- grids %>% 
+                filter(spatial == "fp",
+                       spp == input$SppSelection) #%>% 
+            # group_by(index,state,abrev,lat,lon,spatial,port_name) %>% 
+            # summarise(n())
+            
+            empty_data <- grids_sw_data %>% 
+                filter(!state %in% unique(grids_fp_data$state)) %>% 
+                group_by(state,abrev,spp,spatial) %>% 
+                tally()
+            
+            grids_fp_data <- grids_fp_data %>% bind_rows(empty_data)
+            
+            
+            
+            grids_sw_data$group <- factor(grids_sw_data$abrev,      # Reordering group factor levels
+                                          levels = state_order$abrev)
+            
+            
+            grids_fp_data$group <- factor(grids_fp_data$abrev,      # Reordering group factor levels
+                                          levels = state_order$abrev)
+            
+            
+            # Maps
+            # Overall (overlapping) position
+            sw_overlapping_map <- ggplot(grids_sw_data) +
+                geom_tile(aes(x = lon,
+                              y = lat,
+                              color = group , 
+                              fill = group), 
+                          alpha = 0.3) +
+                geom_sf(data = subset(us_map,ID %in% c("maine", "new hampshire", "massachusetts", "connecticut",
+                                                       "rhode island", "new york", "new jersey", "delaware", "maryland",
+                                                       "virginia", "north carolina"))
+                ) +
+                scale_color_manual(values = state_pallet,
+                                   labels = grids_sw_data %>% arrange(group) %>%  pull(group) %>% unique()) +
+                scale_fill_manual(values = state_pallet,
+                                  labels = grids_sw_data %>% arrange(group) %>%  pull(group) %>% unique()) +
+                my_ggtheme_p(leg_pos = "",
+                             ax_tx_s = 10) +
+                coord_sf(ylim = c(30,48)) +
+                scale_y_continuous(breaks = c(30,35,40,45))+
[…]

### 2021-12-08 Allocation_tool/server.R
Moved groid loading to reactive. A bit faster

@@ -178,6 +178,42 @@ shinyServer(function(input, output,session) {
         # Regulatory Units ####
         # ---------------------------- #
         
+        grids_sw_data <- reactive({
+        
+            # State waters data
+            sw_data <- grids %>% 
+            filter(spatial == "sw")
+
+        sw_data$group <- factor(sw_data$abrev,      # Reordering group factor levels
+                                      levels = state_order$abrev)
+        sw_data
+        })
+        
+        
+        grids_fp_data <- reactive({
+            
+            
+            # Fishing port data
+            grids_fp_data <- grids %>% 
+                filter(spatial == "fp",
+                       spp == input$SppSelection) 
+            
+            empty_data <- grids %>% 
+                filter(spatial == "sw")%>% 
+                filter(!state %in% unique(grids_fp_data$state)) %>% 
+                group_by(state,abrev,spp,spatial) %>% 
+                tally()
+            
+            fp_data <- grids_fp_data %>% bind_rows(empty_data)
+            
+        
+            
+            fp_data$group <- factor(fp_data$abrev,      # Reordering group factor levels
+                                          levels = state_order$abrev)
+            
+            fp_data
+        })
+        
         ## ---------------------------- ##
         #### Table #####
         ## ---------------------------- ##
@@ -275,36 +311,10 @@ shinyServer(function(input, output,session) {
         # ---------------------------- #        
         output$RegUnit <- renderPlot({
             
-            # if(input$SpatSelection == "Both apporaches"){
             
-            # State waters data
-            grids_sw_data <- grids %>% 
-                filter(spatial == "sw")
+            grids_sw_data <- grids_sw_data() 
             
-            
-            # Fishing port data
-            grids_fp_data <- grids %>% 
-                filter(spatial == "fp",
-                       spp == input$SppSelection) #%>% 
-            # group_by(index,state,abrev,lat,lon,spatial,port_name) %>% 
-            # summarise(n())
-            
-            empty_data <- grids_sw_data %>% 
-                filter(!state %in% unique(grids_fp_data$state)) %>% 
-                group_by(state,abrev,spp,spatial) %>% 
-                tally()
-            
-            grids_fp_data <- grids_fp_data %>% bind_rows(empty_data)
-            
-            
-            
-            grids_sw_data$group <- factor(grids_sw_data$abrev,      # Reordering group factor levels
-                                          levels = state_order$abrev)
-            
-            
[…]

### 2021-12-08 Allocation_tool/server.R
Speed up regulatory areas maps. Code is longer, but faster.

@@ -179,14 +179,14 @@ shinyServer(function(input, output,session) {
         # ---------------------------- #
         
         grids_sw_data <- reactive({
-        
+            
             # State waters data
             sw_data <- grids %>% 
-            filter(spatial == "sw")
-
-        sw_data$group <- factor(sw_data$abrev,      # Reordering group factor levels
-                                      levels = state_order$abrev)
-        sw_data
+                filter(spatial == "sw")
+            
+            sw_data$group <- factor(sw_data$abrev,      # Reordering group factor levels
+                                    levels = state_order$abrev)
+            sw_data
         })
         
         
@@ -206,10 +206,10 @@ shinyServer(function(input, output,session) {
             
             fp_data <- grids_fp_data %>% bind_rows(empty_data)
             
-        
+            
             
             fp_data$group <- factor(fp_data$abrev,      # Reordering group factor levels
-                                          levels = state_order$abrev)
+                                    levels = state_order$abrev)
             
             fp_data
         })
@@ -312,135 +312,124 @@ shinyServer(function(input, output,session) {
         output$RegUnit <- renderPlot({
             
             
-            grids_sw_data <- grids_sw_data() 
-            
-            grids_fp_data <- grids_fp_data() 
-            
-            # Maps
-            # Overall (overlapping) position
-            sw_overlapping_map <- ggplot(grids_sw_data) +
-                geom_tile(aes(x = lon,
-                              y = lat,
-                              color = group , 
-                              fill = group), 
-                          alpha = 0.3) +
-                geom_sf(data = subset(us_map,ID %in% c("maine", "new hampshire", "massachusetts", "connecticut",
-                                                       "rhode island", "new york", "new jersey", "delaware", "maryland",
-                                                       "virginia", "north carolina"))
-                ) +
-                scale_color_manual(values = state_pallet,
-                                   labels = grids_sw_data %>% arrange(group) %>%  pull(group) %>% unique()) +
-                scale_fill_manual(values = state_pallet,
-                                  labels = grids_sw_data %>% arrange(group) %>%  pull(group) %>% unique()) +
-                my_ggtheme_p(leg_pos = "",
-                             ax_tx_s = 10) +
-                coord_sf(ylim = c(30,48)) +
-                scale_y_continuous(breaks = c(30,35,40,45))+
-                labs(x = "", y = "", title = "") +
-                theme(plot.title = element_text(size = 20))
-            
-            
-            # Showing each state separately
[…]

### 2021-12-08 Allocation_tool/server.R
Updated table to show also area but estimations are wrong

@@ -215,47 +215,45 @@ shinyServer(function(input, output,session) {
         })
         
         ## ---------------------------- ##
-        #### Table #####
+        ### Table #####
         ## ---------------------------- ##
         output$gridN <- renderFormattable({
             
             customGreen = "#71CA97"
+            r_earth <- 6371000 # NASA's volumetric mean radious https://nssdc.gsfc.nasa.gov/planetary/factsheet/earthfact.html
+            res_lon <- 0.3 # data degree resolution 
             
-            # ---------------------------- #
-            ##### State waters ######
-            # ---------------------------- #
+            n_grids <- grids %>% 
+                group_by(state,spatial,port_name,spp,index,lat,lon) %>%
+                tally() %>% 
+                # View()
+                mutate(
+                    area = (4 * r_earth^2 * 0.5 * 0.3 * pi/180 * cos(abs(lat) * pi/180 ) * sin(0.5 * 0.3 * pi/180))/1000000
+                ) %>% 
+                # View()
+                group_by(state,spp,spatial) %>%
+                summarise(tot_area = sum(area),
+                          n_grids = n(),
+                          n_ports = length(unique(port_name))
+                ) %>% 
+                gather("unit","value",tot_area:n_grids)
             
-            if(input$SpatSelection == "State waters"){
-                
-                n_grids <- grids %>%
-                    filter(spatial == "sw") %>% 
-                    group_by(state) %>% 
-                    summarise(Grids = length(unique(index))) %>% 
-                    arrange(Grids)
-                
-                
-                x <- formattable(n_grids,
-                                 list(
-                                     Grids = color_bar(customGreen)
-                                 )
-                )
-                
-            } 
             # ---------------------------- #
             #### Fishing Ports ######
             # ---------------------------- #
             if(input$SpatSelection == "Fishing ports"){
                 
                 
-                n_grids <- grids %>%
-                    filter(spatial == "fp") %>% 
-                    group_by(state) %>% 
-                    summarise(Grids = length(unique(index)),
-                              Ports = length(unique(landing_port))
-                    ) %>% 
-                    arrange(Ports) 
+                grid_table <- n_grids %>% 
+                    filter(spatial == "fp",
+                           spp == input$SppSelection,
+                           unit == input$table_output
+                           ) %>%  
+                    ungroup() %>% 
+                    select(state,n_ports,value) %>% 
+                    arrange(desc(n_ports))
                 
-                x <- formattable(n_grids,
+                x <- formattable(grid_table,
[…]

### 2021-12-08 Allocation_tool/ui.R

@@ -399,12 +399,20 @@ dashboardPage(
                     ),
                     plotOutput("RegUnit") %>% withSpinner(color="#0dc5c1",type = 6)
                 ),
+                #### Regulatory units table --------------
                 box(width = 6, 
                     solidHeader = TRUE,
                     collapsible = TRUE,
                     collapsed = TRUE,
                     title = "Number of grids per regulatory area",
                     status = "success", # green color
+                    radioButtons('table_output', "Output unit", 
+                                 c('n grid-cells' = "n_grids",
+                                   "Area (thousand km2)" = "tot_area"
+                                 ),
+                                 selected = "n_grids",
+                                 inline = TRUE
+                    ),
                     formattableOutput("gridN") %>% withSpinner(color="#0dc5c1",type = 6)
                 )
               ), # close firs fluid row

### 2021-12-09 Allocation_tool/server.R
Moved the allocation tool to its own repository for ease sharing

@@ -1,1007 +1,0 @@
-#
-# This is the server logic of a Shiny web application. You can run the
-# application by clicking 'Run App' above.
-#
-# Find out more about building applications with Shiny here:
-#
-#    http://shiny.rstudio.com/
-# https://shiny.rstudio.com/gallery/nutrition-calculator.html
-
-# ---------------------------- #
-# Setup
-# ---------------------------- #
-
-# Get functions and shapefiles
-library(MyFunctions)
-MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","DT","plotly","wesanderson","zoo","formattable","viridis","shinydashboard","rmarkdown"))
-
-state_pallet <- c(wes_palette(n = 5, name = "Darjeeling1"),
-                  wes_palette(n = 5, name = "Darjeeling2"),
-                  wes_palette(n = 3, name = "Royal1")
-)
-
-
-# Create specific state pallet from our friend Wes Andersson
-# state_pallet <- c(wes_palette(n = 5, name = "Darjeeling1"),
-#                   wes_palette(n = 5, name = "Darjeeling2"),
-#                   "#FD6467"
-# )
-
-# Set the filters
-state_order <- my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>%
-    group_by(state) %>%
-    summarise(
-        order = mean(lat)
-    ) %>%
-    mutate(abrev = c("CT","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VA")
-    ) %>%
-    arrange(desc(order)) %>%
-    mutate(order= c("b","a",letters[3:11])) %>% # weirdly maine goes below
-    arrange(order)
-
-us_map <- st_as_sf(map("state", plot = FALSE, fill = TRUE)) %>% 
-    mutate(
-        state = str_to_sentence(ID)
-    ) %>% 
-    left_join(state_order,
-              by = "state")
-
-# ---------------------------- #
-# Grid data ####
-# ---------------------------- #
-
-grids_sw <- bind_rows(
-    my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>%
-        mutate(spp = "Paralichthys dentatus"),
-    my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>%
-        mutate(spp = "Stenotomus chrysops"),
[…]

### 2021-12-09 Allocation_tool/ui.R

@@ -1,556 +1,0 @@
-#
-# This is the user-interface definition of a Shiny web application. You can
-# run the application by clicking 'Run App' above.
-#
-# Find out more about building applications with Shiny here:
-#
-#    http://shiny.rstudio.com/
-#
-
-
-MyFunctions::my_lib(c("ggmap","sf","tidyverse","tools","readr","data.table","maps","shiny","plotly","formattable","shinydashboard","shinyjs","shinycssloaders"))
-
-spp_survey <- read.csv("./data/spp_region.csv") %>% 
-  filter(
-    # spp %in% c ("Centropristis striata","Gadus morhua"),
-    region %in% c("Northeast US Fall" , "Northeast US Spring")) #No more seasons
-
-
-
-dashboardPage(
-  dashboardHeader(title = "Across Boundaries Project"),
-  #______________________________________________________________________#
-  # Sidebar  ####
-  # Incons https://rstudio.github.io/shinydashboard/appearance.html
-  #______________________________________________________________________#
-  dashboardSidebar(
-    sidebarMenu(
-      menuItem("Home", tabName = "home", icon = icon("home")),
-      br(),
-      menuItem("Information", tabName = "info", icon = icon("info")),
-      br(),
-      menuItem("Demo", tabName = "demo", icon = icon("dashboard", lib = "glyphicon")),
-      menuItem("Tool", tabName = "dashboard", icon = icon("dashboard")),
-      br(),
-      menuItem("Instructions", tabName = "instructions", icon = icon("gear")),
-      br(),
-      menuItem(
-        "Download report",
-        tabName = "download",
-        icon = icon("download"),
-        div(
-          textInput(
-            inputId = "filename",
-            placeholder = "Name download file",
-            label = "File name",
-            value = "Report"
-          )
-        ),
-        textInput(
-          inputId = "UserName",
-          placeholder = "Name of user",
-          label = "User name",
-          value = "Annon"
-          
-        ),
-        checkboxGroupInput('results', 'Choose results', c("All",'Grid table', 'Grid plot',"Distribution map"),
-                           selected = "All",
-                           inline = FALSE
-        ),
-        radioButtons('format', 'Document format', c('PDF', 'Word',"HTML"),
-                     inline = TRUE
-        ),
-        div(
-          downloadButton(
-            outputId = "downloadReport",
-            label = "Download report",
-            icon = icon("download"),
[…]

### 2022-01-12 Scripts/spatial_analisis.Rmd
Fixed paths after splitting projects

@@
 grids_sw <- bind_rows(
-  my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
+  my_path("G", "AcrossBoundaries/Data/Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
     mutate(spp = "Paralichthys dentatus"),
-  my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
+  my_path("G", "AcrossBoundaries/Data/Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
     mutate(spp = "Stenotomus chrysops"),
-  my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
+  my_path("G", "AcrossBoundaries/Data/Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
     mutate(spp = "Centropristis striata")
@@
 
-grids_fp <- my_path("D", "Partial/grid_fp", name = "grid_eez_fp_df.csv", read = T
+grids_fp <- my_path("G", "AcrossBoundaries/Data/Partial/grid_fp", name = "grid_eez_fp_df.csv", read = T
 ) %>%
@@
 # Ports data
-ports_df <- my_path("D","Partial", "top_ports.csv", read = T) %>% 
+ports_df <- my_path("G","AcrossBoundaries/Data/Partial", "top_ports.csv", read = T) %>% 
   filter(tresh == "75th") %>%
@@
 
-spp_paths <- list.files(my_path("R",extra_path = "Partial/Interpolation/"))
+spp_paths <- list.files(my_path("G",extra_path = "AcrossBoundaries/Results/Partial/Interpolation/"))
 
@@
 
-taxon_sw <- my_path("R",extra_path = "Partial/Interpolation/", name = taxon_read)
+taxon_sw <- my_path("G",extra_path = "AcrossBoundaries/Results/Partial/Interpolation/", name = taxon_read)
 

### 2022-01-12 Scripts/spatial_analisis.Rmd
Created partial figures and an alternative Fig 1b

@@
 
+# Save image for manuscript
+
+eez_plot <- ggplot(eez_sf) +
+  geom_sf()
+
+name <- my_path("G", "AcrossBoundaries/Results/Figures", name = "eez_map.png")
+ggsave(name,
+       eez_plot)
+
 ```
@@
 
+# Visual exploration (o.k! )
+state_mpa <- st_read("~/OneDrive - UW-Madison/FederalAndStateWaters/FederalAndStateWaters.gdb") %>%
+  janitor::clean_names() %>% 
+  mutate(jurisdicti = str_to_lower(jurisdicti)) %>% 
+  filter(jurisdicti %in% States) %>% 
+  mutate(state = str_to_sentence(jurisdicti)) %>% 
+  st_transform(crs = 4326) %>%   # for matching projections
+  st_simplify(preserveTopology = TRUE, dTolerance = 0.01) %>% 
+  left_join(state_lat)
+
+state_mpa$group <- factor(state_mpa$abrev,      # Reordering group factor levels
+                               levels = state_lat$abrev)
+
+state_mpa <- ggplot() +
+  geom_sf(data = eez_sf,aes(), fill = "grey90") +
+  geom_sf(data = land_sf,aes(), fill = "grey50") +
+  geom_sf(data = state_mpa, aes(fill = group, color = group)) +
+  scale_fill_manual(values = state_pallet) +
+  scale_color_manual(values = state_pallet) +
+  my_ggtheme_p(leg_pos = "right")
+
+name <- my_path("G", "AcrossBoundaries/Results/Figures", name = "state_sw_map.png")
+ggsave(name,
+       state_mpa)
+
 ```
@@
 
-ports_path <- my_path("D","NOAA", name = "PalaciosJ - BSB, SFlounder, Scup by Port 1970-2020 - 2021.10.25.xlsx")
+ports_path <- my_path("G","AcrossBoundaries/Data/NOAA", name = "PalaciosJ - BSB, SFlounder, Scup by Port 1970-2020 - 2021.10.25.xlsx")
 
@@
 
-# Check for missing ports
+# Check for missing ports (Should be empty!)
 noaa_ports_complete %>% 
@@
 # Save data for future analysis
-write_csv(noaa_ports_complete,
-          my_path("D","Partial", name = "top_ports.csv")
-          )
+# write_csv(noaa_ports_complete,
+#           my_path("D","Partial", name = "top_ports.csv")
+#           )
 
@@
 
-noaa_ports_complete %>% 
-  filter(tresh == "75th") %>% 
-  ggplot() +
-  geom_point(
+port_map <- noaa_ports_complete %>%  
+  filter(tresh == "75th")
+
+port_map <- ggplot() +
+  geom_sf(data = eez_sf,aes(), fill = "grey90") +
+  geom_sf(data = land_sf,aes(), fill = "grey50") +
+  geom_point( data = port_map,
     aes(
@@
     ),
-    size = 5,
+    size = 3,
     alpha = 0.5
-  )
+  ) +
+  my_ggtheme_p(leg_pos = "right")
+
+name <- my_path("G", "AcrossBoundaries/Results/Figures", name = "state_fp_map.png")
+
+ggsave(name,
+       port_map)
 
@@
 
+# ------------------------------ #
+# Saving for plot
+# ------------------------------ #
+
+state_bf_plot <- state_bf %>% 
+  left_join(state_lat)
+
+state_bf_plot$group <- factor(state_bf_plot$abrev, levels = state_lat$abrev)
+
+state_sf_plot <- state_sf %>% 
+  left_join(state_lat)
+
+state_sf_plot$group <- factor(state_sf_plot$abrev, levels = state_lat$abrev)
+
+state_bf_map <- ggplot(state_bf_plot) +
+  geom_sf(data = eez_sf,aes(), fill = "grey90") +
+  geom_sf(data = land_sf,aes(), fill = "grey50") +
+  geom_sf(data = state_bf_plot, aes(color = group), fill = NA) +
+  geom_sf(data = state_sf_plot, aes(color = group), fill = NA) +
+  scale_color_manual(values = state_pallet) +
+  my_ggtheme_p(leg_pos = "right")
+
+name <- my_path("G", "AcrossBoundaries/Results/Figures", name = "state_bf_plot_sw.png")
+
+ggsave(name,
+       state_bf_map)
+
 ```
@@
 #Load top port data 
-ports_df <- my_path("D","Partial", "top_ports.csv", read = T) %>% 
+ports_df <- my_path("G","AcrossBoundaries/Data/Partial", "top_ports.csv", read = T) %>% 
   filter(tresh == "75th")
@@
   theme_dark()
+
+ #------------------------------ #
+# Saving for plot
+# ------------------------------ #
+
+state_bf_plot_fp <- port_bf %>% 
+  rename(abrev = state_postal) %>% 
+  left_join(state_lat)
+
+state_bf_plot_fp$group <- factor(state_bf_plot_fp$abrev, levels = state_lat$abrev)
+
+state_bf_map_fp <- ggplot() +
+  geom_sf(data = eez_sf,aes(), fill = "grey90") +
+  geom_sf(data = land_sf,aes(), fill = "grey50") +
+  geom_sf(data = state_bf_plot_fp, aes(color = group), fill = NA) +
+  geom_sf(data = state_sf_plot, aes(color = group), fill = NA) +
+  scale_color_manual(values = state_pallet) +
+  my_ggtheme_p(leg_pos = "right")
+
+name <- my_path("G", "AcrossBoundaries/Results/Figures", name = "state_bf_plot_fp.png")
+
+ggsave(name,
+       state_bf_map_fp)
 
@@
 
-### NUmbers for papaer
+### Numbers for papaer
 
@@
 # Load grid of state waters
-grid_eez_sw_sf <-  st_read(my_path("D","Partial/grid_sw", name = "grid_eez_sw_sf.shp")) %>%
+grid_eez_sw_sf <-  st_read(my_path("G","AcrossBoundaries/Data/Partial/grid_sw", name = "grid_eez_sw_sf.shp")) %>%
   select(index,state,geometry) %>% 
@@
 # Load grid of fishing ports
-grid_eez_fp_sf <-  st_read(my_path("D","Partial/grid_fp", name = "grid_eez_fp.shp")) %>%
+grid_eez_fp_sf <-  st_read(my_path("G","AcrossBoundaries/Data/Partial/grid_fp", name = "grid_eez_fp.shp")) %>%
   select(index,abrev,geometry) %>% 
@@
   ggplot(grid_eez_sw_sf) +
-    geom_sf(data = eez_sf, aes(), fill = "white") + 
+    geom_sf(data = eez_sf, aes(), fill = "grey90") + 
     geom_sf(aes(color =group , fill = group), alpha = 0.3) +
-    geom_sf(data = land_sf, aes()) +
-    ggsflabel::geom_sf_label_repel(data = land_sf, aes(label= abrev), 
-                                   size = 4,
-                                   box.padding = 0.10,
-                                   hjust = 1) +
+    geom_sf(data = land_sf, aes(), fill = "grey50") +
+    # ggsflabel::geom_sf_label_repel(data = land_sf, aes(label= abrev), 
+    #                                size = 4,
+    #                                box.padding = 0.10,
+    #                                hjust = 1) +
     scale_color_manual(values = state_pallet) +
@@
     scale_y_continuous(breaks = c(30,35,40,45))+
-    labs(x = "", y = "", title = "A) State waters approach") +
-    theme(plot.title = element_text(size = 20)),
+    labs(x = "", y = "", title = ""),
+    # theme(plot.title = element_text(size = 20)),
   # Showing each state separately
   ggplot(grid_eez_sw_sf) +
-    geom_sf(data = land_sf, aes(), fill = "grey80") +
+    geom_sf(data = land_sf, aes(), fill = "grey50") +
     geom_sf(aes(color = group),size = 0.1, alpha = 0.3) +
@@
 
+name <- my_path("G", "AcrossBoundaries/Results/Figures", name = "sw_reg_units.png")
+
+ggsave(name,
+       p_sw,
+       width = 9,
+       height = 9)
+
 ##### ------------- ####
@@
 
+# Include state with no Regulaotry units in plot
 grid_eez_fp_sf <- grid_eez_sw_sf %>% 
@@
   ggplot(data = subset(grid_eez_fp_sf, index != "NA")) +
-    geom_sf(data = eez_sf, aes(), fill = "white") + 
+    geom_sf(data = eez_sf, aes(), fill = "grey90") + 
     geom_sf(aes(color = group, fill = abrev), alpha = 0.3) +
-    geom_sf(data = land_sf, aes()) +
-    ggsflabel::geom_sf_label_repel(data = land_sf, aes(label= abrev), 
-                                   size = 4,
-                                   box.padding = 0.10,
-                                   hjust = 1) +
+    geom_sf(data = land_sf, aes(), fill = "grey50") +
+    # ggsflabel::geom_sf_label_repel(data = land_sf, aes(label= abrev), 
+    #                                size = 4,
+    #                                box.padding = 0.10,
+    #                                hjust = 1) +
     # scale_color_manual(values = state_pallet) +
@@
     scale_y_continuous(breaks = c(30,35,40,45)) +
-    labs(x = "", y = "", title = "B) Fishing ports approach") +
+    # labs(x = "", y = "", title = "B) Fishing ports approach") +
     theme(plot.title = element_text(size = 20)),
@@
     geom_sf(data = subset(grid_eez_fp_sf, index != "NA"), aes(color = group),size = 0.1, alpha = 0.3) +
-    geom_sf(data = land_sf, aes(), fill = "grey80") +
+    geom_sf(data = land_sf, aes(), fill = "grey50") +
     facet_wrap(~ group) +
@@
   nrow = 1)
+
+name <- my_path("G", "AcrossBoundaries/Results/Figures", name = "fp_reg_units.png")
+
+ggsave(name,
+       p_fp,
+       width = 9,
+       height = 9)
 

### 2022-01-16 Scripts/spatial_analisis.Rmd
Included all ports for sensitivity analysis

@@
     "shinnecock indian reservation, ny", #40.865873983968754, -72.4420929172018
-    "westport, ma"
+    "westport, ma",
+    "east haven, ct", # 41.287588297369965, -72.91332498109327
+    "menemsha, ma", #41.35483795676015, -70.76878790249602
+    "sandwich (census name for sandwich center), ma", #41.773295466525006, -70.4834693734216
+    "niantic (east lyme (sta.)), ct", #41.307802578709925, -72.18573251980143
+    "chilmark, ma", # 41.33168444645112, -70.73421932978907
+    "edgartown, ma", # 41.43835263574402, -70.49271845442495
+    "harwich port, ma", # 41.66230920340751, -70.05980519928022
+    "hyannis, ma", # 41.62905544508146, -70.29939641433006
+    "mattapoisett, ma", # 41.65055975280539, -70.81223286674746
+    "menemsha, ma", # 41.373297740713404, -70.77670726558624
+    "center moriches, ny", # 40.782258285123575, -72.7953069671706
+    "east hampton, ny", # 41.11361718020251, -72.06705712645356
+    "greenport, ny", # 41.09916125257237, -72.35456699786954
+    "island park, ny", # 40.94632184498529, -73.72913173589376
+    "mount sinai, ny", # 41.01174251897529, -73.03449296418835
+    "wainscott, ny", # 40.91995090087518, -72.22936945904769
+    "bristol, ri", # 41.65577918701731, -71.28875398475536
+    "jamestown, ri", # 41.470526163808394, -71.37037477616862 
+    "north kingstown (local name wickford), ri", # 41.572678906576364, -71.43055123261533
+    "portsmouth, ri", # 41.59982450656618, -71.22606882143374
+    "south kingstown (town of), ri", # 41.60580919505512, -71.22689676246267
+    "tiverton, ri", # 41.61012807350179, -71.21924759566026
+     "warwick (rr name apponaug), ri", # 41.684523257387276, -71.44148310924662
+    "westerly (rr name apponaug), ri", # 41.35954244353175, -71.83754886478252
+    "westerly (census name westerly center), ri", # 41.35954244353175, -71.83754886478252
+    "accomac, va", # 37.772002695051725, -75.82419557195219
+    "little wicomico river, va", #37.89065111324239, -76.28371085150121
+    "northampton (county), va",  # 37.019536098970725, -76.26084869871761
+    "northumberland (county), va" # 37.82813770009578, -76.30849827818871
   )),
@@
     40.865873983968754,
-    41.49267875746873
+    41.49267875746873,
+    41.287588297369965,
+    41.35483795676015,
+    41.773295466525006,
+    41.307802578709925,
+    41.33168444645112,
+    41.43835263574402,
+    41.66184849328297,
+    41.62905544508146,
+    41.65055975280539,
+    41.373297740713404,
+    40.782258285123575,
+    41.11361718020251,
+    41.09916125257237,
+    40.93886056049701,
+    41.01174251897529,
+    40.91995090087518,
+    41.65577918701731,
+    41.470526163808394,
+    41.572678906576364,
+    41.59982450656618,
+    41.60580919505512,
+    41.61012807350179,
+    41.684523257387276,
+    41.35954244353175,
+    41.35954244353175,
+    37.772002695051725,
+    37.89065111324239,
+    37.019536098970725,
+    37.82813770009578
+
   ),
@@
     -72.4420929172018,
-    -71.05551342392039
+    -71.05551342392039,
+    -72.91332498109327,
+    -70.76878790249602,
+    -70.4834693734216,
+    -72.18573251980143,
+    -70.73421932978907,
+    -70.49271845442495,
+    -70.05918851677775,
+    -70.29939641433006,
+    -70.81223286674746,
+    -70.77670726558624,
+    -72.7953069671706,
+    -72.06705712645356,
+    -72.35456699786954,
+    -73.71669826711323,
+    -73.03449296418835,
+    -72.22936945904769,
+    -71.28875398475536,
+    -71.37037477616862,
+    -71.43055123261533,
+    -71.22606882143374,
+    -71.22689676246267,
+    -71.21924759566026,
+     -71.44148310924662,
+     -71.83754886478252,
+    -71.83754886478252,
+     -75.82419557195219,
+     -76.28371085150121,
+     -76.26084869871761,
+     -76.30849827818871
   )
@@
 noaa_ports_complete %>% 
-  filter(tresh == "75th",
+  filter(
          is.na(lat)) %>%
@@
 # Save data for future analysis
-# write_csv(noaa_ports_complete,
-#           my_path("D","Partial", name = "top_ports.csv")
-#           )
+write_csv(noaa_ports_complete,
+          my_path("G","AcrossBoundaries/Data/Partial", name = "top_ports.csv")
+          )
 
 noaa_ports_complete
+
+my_path("G","AcrossBoundaries/Data/Partial","top_ports.csv", read = T) %>% 
+  filter(is.na(lat)) %>% 
+  group_by(port_name,state_postal,lat,lon) %>% 
+  tally() %>% 
+  View()
 
@@
 
+# Sensitivity analysis
+
+## Top ports sensitivity
+
+```{r sen_data}
+# Estimate distance between points
+
+top_ports_sen <- my_path("G","AcrossBoundaries/Data/Partial","top_ports.csv", read = T)
+
+eez_sf <- st_read(my_path("G", extra_path = "Spatial/SAU/SAU_Shapefile", name = "SAUEEZ_July2015.shp")) %>% 
+  st_transform(crs = 4326) %>% # 4326
+  filter(Name == "USA (East Coast)") %>% 
+  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) #0.1 for paper
+```
+
+### Number of ports per state and sen
+
+```{r number}
+# Number of ports per tresh
+
+top_ports_sen %>% 
+  group_by(species_name, state_postal,tresh) %>% 
+  tally() %>% 
+  # View()
+  ggplot() +
+  geom_bar(
+    aes(
+      x = tresh,
+      y = n,
+      fill = tresh
+    ),
+    stat = "identity"
+  ) +
+  facet_grid(species_name~state_postal) +
+  labs(y = "Number of ports")
+
+```
+
+### Number of ports per state and sen
+
+```{r data_prep}
+
+port_sf <- st_as_sf(top_ports_sen,
+                    coords =c("lon","lat"),
+                    crs = 4326)
+
+# Buffer state waters
+port_bf <- st_buffer(port_sf, 5) %>% # port
+  st_transform(4326) %>% # to match shape
+  st_set_crs(4326)
+
+# Expand grid
+
+# xmin      ymin      xmax      ymax 
+# -82.57346  29.77459 -62.88543  49.19141
+
+# Expand the grid
+ne_grid <- expand.grid(
+  lon = seq(from = -82.57346, to = -62.88543, by = 0.3),
+  lat = seq(from = 29.77459, to = 49.19141 , by = 0.3)
+) %>% 
+  rowid_to_column("index")
+
+# Crop grid to EEz
+grid_fp_sf <- st_as_sf(ne_grid,
+                       coords = c("lon", "lat"),
+                       crs = 4326) %>% 
+  st_join(port_bf) %>% # join to port sf
+  filter(!is.na(port_name)) #%>%
+# distinct(index,port_name, .keep_all = TRUE) #removes like 400K overlapping rows
+
+# Create data frame for future computations
+# Note, will be used in next chunk
+grid_fp_bf_dt <- as.data.frame(grid_fp_sf) %>%
+  select(index,port_name,state_postal,species_name,tresh)
+
+```
+
+#### Numbers
+
+```{r numbers_per_tresh}
+
+sens_plot <- grid_fp_bf_dt %>% 
+  group_by(species_name,state_postal,Threshold = tresh) %>% 
+  summarise(n = n(),
+            nuni = length(unique(as.character(index)))
+  ) %>% 
+  ggplot() +
+  geom_bar(
+    aes(
+      x = Threshold,
+      y = nuni,
+      fill = Threshold
+    ),
+    stat = "identity"
+  ) +
+  facet_grid(species_name~state_postal) +
+  my_ggtheme_p(leg_pos = "right",
+               ax_tx_s = 11
+               ) +
+  theme(axis.text.x = element_blank(),
+        strip.background = element_rect(fill = "grey"))+
+  labs(y = "Number of grid-cells (n)", x = "Threshold") +
+  scale_fill_brewer(palette = "Set3")
+
+ggsave(filename = "tresh_sens_plot.png",
+       sens_plot)
+
+```
 # Old code

### 2022-01-25 Scripts/poster.Rmd
started poster for Olaf

---
title: "Quantifying fish range shifts across poorly defined management boundaries"
output: 
  posterdown::posterdown_html
author: "DRAFT. Target journal *PlosOne*"
subtitle: "Juliano Palacios-Abrantes*^1^, Scott Crosson^2^, Chris Dumas^3^, Rod Fujita^4^, Arielle Levine^5^, Catherine Longo^6^, Olaf Jensen^1^"
date: "Affiliations: ^1^Center for Limnology, University of Wisconsin-Madison, US. ^2^National Oceanic and Atmospheric Administration, US. ^3^University of North Carolina Wilmington, US. ^4^Rod Fujita, Environmental Defense Fund, US. ^5^San Diego State University, US. ^6^Marine Stewardship Council, UK."
---

```{r setup, include=FALSE}

library(MyFunctions)
MyFunctions::my_lib(c("dplyr","tibble","knitr","kableExtra","png","grid"))

```

# Introduction

Management regimes that rely on spatial boundaries for the management of marine resources might be poorly adapted to changes in the distribution of these resources caused by climate change, resulting in mismatches between species distributions and the spatial boundaries. This is of specific concern for the management of fish stocks that cross management jurisdictions, known as shared stocks. Transitioning to dynamic ocean management has been suggested as a solution to this issue, however, in many cases spatial boundaries are not clearly drawn, hampering such transition. This is the case along the East coast of the United States (U.S.), where the need for individual states to coordinate the management of shifting shared stocks is challenged by a lack of clear spatially-explicit state regulatory subunits within federal waters (i.e., Exclusive Economic Zone -EEZ). This can result in a number of problems, such as misalignment between allocations based on historical stock distribution and actual stock distribution, which can in turn change catch rates, discard rates, and fishing costs.

# Objectives

Explore different approaches to designing spatial regulatory units to facilitate the adaptation of fisheries management to species shifting distributions.

# Methods

1. - Determine the yearly distribution of each stock within the U.S. Mid-Atlantic EEZ from 1951 to 2019 during two sampling seasons (Fall and Spring).

2.- Explore two approaches for drawing regulatory units: one based on state waters and another on historical landings from North Carolina to Maine.

3-. Estimate each state’s proportion of the stock’s distribution and compare historical and recent values.

```{r bufferFig, eval = T, echo = T, fig.width = 20, echo=FALSE, fig.cap="Spatial regions within the United States' North East Exclusive Economic Zone. A) Spatial buffers from each state's waters. B) Spatial buffers from the main fishing ports. States are aligned by average latitude from north to south. ME, Maine; NH, New Hampshire; MA, Massachusetts; RI, Rhode Island; CT, Connecticut; NY, New York; NY, New Jersey; DE, Delaware; MD, Maryland; VA Virginia; North Carolina."}

# Call the image
img <- readPNG("../Figures/Fig1alt.png")
# Print the image
grid.raster(img)
```

# Results

The choice of boundary expansion method (e.g., fishing port radius or extension of state boundaries) is highly consequential for determining the spatial extent of each state’s regulatory unit.

Seasonality plays an important role in determining the distributional range of black sea bass, scup, and summer flounder.

```{r interpolation, eval = T, echo = T,  fig.width = 20, echo=FALSE, fig.cap="Interpolation results for all species and seasons within the US Northeast Exclusive Economic Zone. Scale showing Catch per Unit of Effort (CPUE) at a log 10 scale. Black cross represents the species’ centroid defined as the region with the largest CPUE with grey regions representing no CPUE."}

# Call the image
img <- readPNG("../Figures/Fig2.png")
# Print the image
grid.raster(img)
```

We overlaid the putative regulatory units with the interpolated CPUE of black sea bass, summer flounder and scup to estimate each state’s proportion of the total CPUE (Fig. 3). Under the state waters approach, each state has a regulatory unit and thus captures a part of the CPUE of each species. However, under the fishing ports approach some states end up without regulatory units resulting in no CPUE.

```{r reg_unit_spatial, eval = T, echo = T, fig.width = 20, echo=FALSE, fig.cap="Proportion of the Catch per Unit of Effort (CPUE) for each state and species by spatial approach. Top and middle rows represent the fishing port and state waters approach, respectively. Bottom row is the difference between both approaches (Δα_reg; see methods). All values in percentage units."}

# Call the image
img <- readPNG("../Figures/Fig3.png")
# Print the image
grid.raster(img)
```

Seasonal differences in state’s CPUE proportion are also evident, although smaller than the regulatory units differences.

```{r reg_unit_season, eval = T, echo = T, fig.width = 20, echo=FALSE, fig.cap="Proportion of the Catch Per Unit of Effort (CPUE) proportion for each state and species by survey season. Top and middle rows represent fall and spring surveys, respectively. "}

# Call the image
img <- readPNG("../Figures/Fig4.png")
# Print the image
grid.raster(img)
```

Over the last 40 years, the proportion of CPUE in each state has increased for northern states and decreased for southern states for all three species (Fig. 5).

```{r area_plot, eval = T, echo = T, fig.width = 20, echo=FALSE, fig.cap="Historical Catch Per Unit of Effort (CPUE) proportion for each state and species by spatial approach. Proportion presented in 10 years running mean percentage. States presented latitudinally from north to south."}

# Call the image
img <- readPNG("../Figures/Fig5.png")
# Print the image
grid.raster(img)
```

### 2022-01-25 Scripts/spatial_analisis.Rmd
misc.

@@
 # https://www.pmel.noaa.gov/maillists/tmap/ferret_users/fu_2004/msg00023.html
+# DOUBLE CHECK RESULTS BELOW
 # https://www.engr.scu.edu/~emaurer/tools/calc_cell_area_cgi.pl
@@
   mutate(
-    area = (4 * r_earth^2 * 0.5 * 0.3 * pi/180 * cos(abs(lat) * pi/180 ) * sin(0.5 * 0.3 * pi/180))/1000000
+    area = (4 * r_earth^2 * 0.5 * res_lon * pi/180 * cos(abs(lat) * pi/180 ) * sin(0.5 * res_lon * pi/180))/1000000
   ) %>% 

### 2022-01-25 Scripts/poster.Rmd
FIrst full poster draft ignoring rendered versions

@@
 title: "Quantifying fish range shifts across poorly defined management boundaries"
+author:
+  - name: Juliano Palacios-Abrantes
+    affil: 1
+    orcid: '0000-0001-8969-5416'
+    main: TRUE 
+    email: "jpalacios2@wisc.edu"
+  - name: Scott Crosson
+  - name: Chris Dumas
+  - name: Rod Fujita
+  - name: Arielle Levine
+  - name: Catherine Longo
+  - name: Olaf Jensen
+    affil: 1
+affiliation:
+  - num: 1
+    address: Center for Limnology, University of Wisconsin - Madison | jpalacios2@wisc.edu
+logoright_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
 output: 
-  posterdown::posterdown_html
-author: "DRAFT. Target journal *PlosOne*"
-subtitle: "Juliano Palacios-Abrantes*^1^, Scott Crosson^2^, Chris Dumas^3^, Rod Fujita^4^, Arielle Levine^5^, Catherine Longo^6^, Olaf Jensen^1^"
-date: "Affiliations: ^1^Center for Limnology, University of Wisconsin-Madison, US.
-^2^National Oceanic and Atmospheric Administration, US.
-^3^University of North Carolina Wilmington, US.
-^4^Rod Fujita, Environmental Defense Fund, US.
-^5^San Diego State University, US.
-^6^Marine Stewardship Council, UK."
+  posterdown::posterdown_html:
+    self_contained: TRUE
+    fig_width: 12
+    fig_height: 7 
+knit: pagedown::chrome_print
+# output: 
+  # posterdown::posterdown_html
 ---
@@
 ```
+
+<!-- Some Usefull links  -->
+<!-- https://stackoverflow.com/questions/67723469/rendering-html-file-from-posterdown-package-r-as-a-pdf -->
+<!-- https://github.com/brentthorne/posterdown/wiki/posterdown_html -->
 
@@
 
-1. - Determine the yearly distribution of each stock within the U.S. Mid-Atlantic EEZ from 1951 to 2019 during two sampling seasons (Fall and Spring).
+1.- Determine the yearly distribution of each stock within the U.S. Mid-Atlantic EEZ from 1951 to 2019 during two sampling seasons (Fall and Spring).
 
@@
 
-```{r bufferFig, eval = T, echo = T, fig.width = 20, echo=FALSE, fig.cap="Spatial regions within the United States' North East Exclusive Economic Zone.
+```{r bufferFig, eval = T, echo = T, echo=FALSE, fig.align='center', fig.cap="Spatial regions within the United States' North East Exclusive Economic Zone.
 A) Spatial buffers from each state's waters.
-B) Spatial buffers from the main fishing ports.
-States are aligned by average latitude from north to south.
-ME, Maine; NH, New Hampshire; MA, Massachusetts; RI, Rhode Island; CT, Connecticut; NY, New York; NY, New Jersey; DE, Delaware; MD, Maryland; VA Virginia; North Carolina."}
+B) Spatial buffers from the main fishing ports."}
 
@@
 
-# Results
-
-The choice of boundary expansion method (e.g., fishing port radius or extension of state boundaries) is highly consequential for determining the spatial extent of each state’s regulatory unit.
+# Results (Preeliminary)
 
@@
 
-```{r interpolation, eval = T, echo = T,  fig.width = 20, echo=FALSE, fig.cap="Interpolation results for all species and seasons within the US Northeast Exclusive Economic Zone.
+```{r interpolation, eval = T, echo = T, echo=FALSE,  fig.align='center',fig.cap="Interpolation results for all species and seasons within the US Northeast Exclusive Economic Zone.
 Scale showing Catch per Unit of Effort (CPUE) at a log 10 scale.
@@
 
-We overlaid the putative regulatory units with the interpolated CPUE of black sea bass, summer flounder and scup to estimate each state’s proportion of the total CPUE (Fig.
-3).
+We overlaid the putative regulatory units with the interpolated CPUE of black sea bass, summer flounder and scup to estimate each state’s proportion of the total CPUE.
 Under the state waters approach, each state has a regulatory unit and thus captures a part of the CPUE of each species.
@@
 
-```{r reg_unit_spatial, eval = T, echo = T, fig.width = 20, echo=FALSE, fig.cap="Proportion of the Catch per Unit of Effort (CPUE) for each state and species by spatial approach.
+```{r regulatoryunit, eval = T, echo = T, echo=FALSE, fig.align='center', fig.cap="Proportion of the Catch per Unit of Effort (CPUE) for each state and species by spatial approach.
 Top and middle rows represent the fishing port and state waters approach, respectively.
-Bottom row is the difference between both approaches (Δα_reg; see methods).
+Bottom row is the difference between both approaches).
 All values in percentage units."}
@@
 
-Seasonal differences in state’s CPUE proportion are also evident, although smaller than the regulatory units differences.
+Seasonal differences in state’s CPUE proportion are also evident, although smaller than the regulatory units differences with half of the cases representing 1% or no seasonality difference.
+The largest seasonal differences are in the latitudinal extremes!
 
-```{r reg_unit_season, eval = T, echo = T, fig.width = 20, echo=FALSE, fig.cap="Proportion of the Catch Per Unit of Effort (CPUE) proportion for each state and species by survey season.
-Top and middle rows represent fall and spring surveys, respectively.
-"}
+```{r regunitseason, eval = T, echo = T, echo=FALSE, fig.align='center', fig.cap="Proportion of the Catch Per Unit of Effort (CPUE) proportion for each state and species by survey season.
+Top and middle rows represent fall and spring surveys, respectively."}
 
@@
 
-Over the last 40 years, the proportion of CPUE in each state has increased for northern states and decreased for southern states for all three species (Fig. 5).
+Over the last 40 years, the proportion of CPUE in each state has increased for northern states and decreased for southern states for all three species.
 
-```{r area_plot, eval = T, echo = T, fig.width = 20, echo=FALSE, fig.cap="Historical Catch Per Unit of Effort (CPUE) proportion for each state and species by spatial approach.
+```{r areaplot, eval = T, echo = T, echo=FALSE, fig.align='center', fig.cap="Historical Catch Per Unit of Effort (CPUE) proportion for each state and species by spatial approach.
 Proportion presented in 10 years running mean percentage.
@@
 ```
+
+# Conclusions
+
+The present work asks how the choice of survey timing and regulatory unit design influences our perception of fish biomass distribution changes relative to management boundaries.
+We use black sea bass, scup and summer flounder in the Northeast United States as case studies of transboundary stocks shifting distributions.
+We show that the distribution of all three stocks has changed relative to the years used to determine the current quota allocation across states, with an overall gain for center-northern states at the expense of the southernmost states.
+In terms of the distribution of allocation, we find that while seasonal differences exist, the biggest differences in state-quota come from the method for designing regulatory areas.
+Our analysis highlights some of the challenges that managers will face in adapting to climate change-driven shifting stocks.

### 2022-02-04 Scripts/spatial_analisis.Rmd
Fixed Figure 5 bug on names swap

@@
                                10,
+                               align = "left",
                                fill = NA,
@@
   )
+
+        data_new <- state_fit
+
+        data_new$group <- factor(data_new$state,                 # Relevel group factor
+                                 levels = state_lat$state)
 
@@
 ssp_area <-
-  ggplot(state_fit) +
+  ggplot(data_new) +
   geom_area(
@@
       y = round(RMean),
-      fill = abrev
+      fill = group
       # fill = state
@@
   scale_fill_manual("State\n(Latitudinal order)",
-                    values = state_pallet,
-                    labels = state_fit %>% arrange(desc(order)) %>%  pull(state) %>% unique()
+                    values = state_pallet#,
+                    # labels = state_fit %>% arrange(desc(order)) %>%  pull(state) %>% unique()
   ) +
@@
        plot = ssp_area,
-       path = my_path("R","Figures"),
+       # path = my_path("R","Figures"),
        width = 14,

### 2022-08-09 Scripts/nefsc_index_script.Rmd
Estimated grid area for Chris D.

@@
 ```
+
+# Estimate area of gridcell
+
+Would it be possible for you to send me a file with the area in hectares for each of the “index” grid areas in your fish distribution analysis?
+You sent me kg/ha as one field in the dataset, so I’m hoping that you also have hectares for each index area, and that it’s easy to send.
+
+```{r area_estimation}
+
+library("tidyverse")
+
+# Load coordinate grid
+coords <- MyFunctions::my_path("D", extra_path = "Spatial", name = "inter_grid_df.csv", read = T, header = T)
+
+# 1.2 Estimate gridcell area based on global variables (m^2)
+# Degree ressolution for area estimation
+# https://rdrr.io/github/stineb/rbeni/src/R/area.R
+# https://www.pmel.noaa.gov/maillists/tmap/ferret_users/fu_2004/msg00023.html
+# https://www.engr.scu.edu/~emaurer/tools/calc_cell_area_cgi.pl
+
+r_earth <- 6371000 # NASA's volumetric mean radious https://nssdc.gsfc.nasa.gov/planetary/factsheet/earthfact.html
+res_lon <- 0.3 # lon degree resolution
+res_lat <- 0.3 # lat degree resolution
+
+coords <- coords %>% 
+  mutate(
+    area = (4 * r_earth^2 * 0.5 * res_lon * pi/180 * cos(abs(lat) * pi/180 ) * sin(0.5 * res_lat * pi/180))/10000
+  )
+
+write_csv(coords, "corrds_area.csv")
+
+```
+
+```{r plot_test}
+
+ggplot(coords) +
+  geom_tile(
+    aes(
+      x = lon,
+      y = lat,
+      fill = area
+    )
+  ) +
+  scale_fill_gradient(low = "yellow", high = "red", na.value = NA)
+
+```

### 2022-09-19 Scripts/spatial_analisis.Rmd
Fixed threshold mess 75trh to 25

@@
 # Visual exploration (o.k! )
-ggplot(land_sf) +
-  geom_sf(aes(fill = state)) +
+# Visual exploration (o.k! )
+ggplot() +
+  geom_sf(data = st_as_sf(map("state", plot = FALSE, fill = TRUE))) +
+  geom_sf(data = land_sf, aes(fill = state)) +
   scale_fill_manual(values = state_pallet) +
-  theme_dark()
+  my_ggtheme_m(leg_pos = "right")
 
@@
 #     "95th" = quantile(year_ton, 0.95),
-#     "75th" = quantile(year_ton, 0.75),
+#     "12th" = quantile(year_ton, 0.75),
 #     "50th" = quantile(year_ton, 0.50)) %>% 
@@
 top_ports <- bind_rows(
-  # 75th percentile used in project
+  # Top 25 % used in this project
   overall_port_data %>% 
     group_by(species_name) %>% 
-    top_frac(0.25,year_ton) %>%  # top 75
-    mutate(tresh = "75th"),
+    top_frac(0.25,year_ton) %>%  # top 25 %
+    mutate(tresh = "25th"),
   # -------------------- #
@@
   # -------------------- #
-  # 95%
+  # 5%
   overall_port_data %>% 
@@
     top_frac(0.05,year_ton) %>%  
-    mutate(tresh = "95th"), # top 95
-  # 85%
+    mutate(tresh = "5th"), # top 5%
+  # 15%
   overall_port_data %>% 
@@
     top_frac(0.15,year_ton) %>% 
-    mutate(tresh = "85th"), # top 85
-  # 65%
+    mutate(tresh = "15th"), # top 15%
+  # 35%
   overall_port_data %>% 
     group_by(species_name) %>% 
-    top_frac(0.35,year_ton) %>%  # top 75
-    mutate(tresh = "65th"),
+    top_frac(0.35,year_ton) %>%  # top 35%
+    mutate(tresh = "35th"),
   # 50%
@@
     group_by(species_name) %>% 
-    top_frac(0.5,year_ton) %>%  # top 50
+    top_frac(0.5,year_ton) %>%  # top 50 %
     mutate(tresh = "50th")
@@
 port_map <- noaa_ports_complete %>%  
-  filter(tresh == "75th")
+  filter(tresh == "25th")
 
@@
   geom_sf(data = state_sf, aes(color = state), fill = NA) +
-  geom_point(data = subset(noaa_ports_complete, tresh == "75th"), aes(x = lon, y = lat,
+  geom_point(data = subset(noaa_ports_complete, tresh == "12th"), aes(x = lon, y = lat,
                                                                       shape = species_name), size = 3, alpha = 0.7) +
@@
 ports_df <- my_path("G","AcrossBoundaries/Data/Partial", "top_ports.csv", read = T) %>% 
-  filter(tresh == "75th")
+  filter(tresh == "12th")
 
@@
 ports_df <- my_path("G","AcrossBoundaries/Data/Partial", "top_ports.csv", read = T) %>% 
-  filter(tresh == "75th") %>%
+  filter(tresh == "12th") %>%
   group_by(species_name,state_postal) %>% 
@@
 my_path("D","Partial","top_ports.csv", read = T) %>% 
-  filter(tresh == "75th",
+  filter(tresh == "12th",
          state_postal == "NY") %>% 

### 2022-09-19 Scripts/spatial_analisis.Rmd
included new figure showing where each state is within the US

@@
 
-# Visual exploration (o.k! )
-# Visual exploration (o.k! )
+# Include figure for paper
+
+land_sf$group <- factor(state_mpa$abrev,      # Reordering group factor levels
+                          levels = state_lat$abrev)
+
 ggplot() +
@@
 
-state_sf <-  st_read("~/OneDrive - UW-Madison/FederalAndStateWaters/FederalAndStateWaters.gdb") %>%
+state_sf <-  st_read("/Volumes/Enterprise/Data/Spatial/FederalAndStateWaters") %>%
   janitor::clean_names() %>% 
@@
 #     "95th" = quantile(year_ton, 0.95),
-#     "12th" = quantile(year_ton, 0.75),
+#     "25th" = quantile(year_ton, 0.75),
 #     "50th" = quantile(year_ton, 0.50)) %>% 
@@
   geom_sf(data = state_sf, aes(color = state), fill = NA) +
-  geom_point(data = subset(noaa_ports_complete, tresh == "12th"), aes(x = lon, y = lat,
+  geom_point(data = subset(noaa_ports_complete, tresh == "25th"), aes(x = lon, y = lat,
                                                                       shape = species_name), size = 3, alpha = 0.7) +
@@
 ports_df <- my_path("G","AcrossBoundaries/Data/Partial", "top_ports.csv", read = T) %>% 
-  filter(tresh == "12th")
+  filter(tresh == "25th")
 
@@
 ports_df <- my_path("G","AcrossBoundaries/Data/Partial", "top_ports.csv", read = T) %>% 
-  filter(tresh == "12th") %>%
+  filter(tresh == "25th") %>%
   group_by(species_name,state_postal) %>% 
@@
 
-length(state_pallet)
+# length(state_pallet)
 
@@
 head(historic_spp)
+```
+
+## F0 Map of the US and study site
+
+```{r}
+
+# re order states by latitude
+land_sf_t <- land_sf
+
+land_sf_t$group <- factor(land_sf_t$abrev,      # Reordering group factor levels
+                               levels = state_lat$abrev)
+
+ land_sf_t <- land_sf_t %>% 
+  left_join(state_lat) %>% 
+   mutate(
+     name = paste0(str_to_title(state)," (",abrev,")")
+   )
+
+ # Load us MAP
+ us_map <- st_as_sf(map("state", plot = FALSE, fill = TRUE))
+
+ # Plot figure
+study_plot <-
+  ggplot() +
+  geom_sf(data = us_map, aes(),fill = "grey", color = "lightgrey") +
+  geom_sf(data = land_sf_t, aes(fill = reorder(name,-order))) +
+  scale_fill_manual("State",
+                    values = state_pallet) +
+  my_ggtheme_m(leg_pos = "right",map_type = "R")
+
+name_f0 <- my_path("G", "AcrossBoundaries/Results/Figures", name = "study_region.png")
+
+ggsave(name_f0,
+       study_plot,
+       width = 9,
+       height = 4)
+
 ```
@@
 my_path("D","Partial","top_ports.csv", read = T) %>% 
-  filter(tresh == "12th",
+  filter(tresh == "25th",
          state_postal == "NY") %>% 

### 2022-09-20 Scripts/spatial_analisis.Rmd
Updated script obe reporductible

@@
 library(MyFunctions)
-MyFunctions::my_lib(c("ggmap","sf","st","tidyverse","tools","readr","data.table","maps","viridis","wesanderson","knitr","kableExtra","plotly","ggrepel","ggsflabel","janitor","interp","rnaturalearth","readxl","cowplot"))
+MyFunctions::my_lib(c("ggmap","sf","st","tidyverse","tools","readr","data.table","maps","viridis","wesanderson","knitr","kableExtra","plotly","ggrepel","ggsflabel","janitor","interp","rnaturalearth","readxl","cowplot","here"))
 
@@
   )
-
-# Include figure for paper
-
-land_sf$group <- factor(state_mpa$abrev,      # Reordering group factor levels
-                          levels = state_lat$abrev)
-
-ggplot() +
-  geom_sf(data = st_as_sf(map("state", plot = FALSE, fill = TRUE))) +
-  geom_sf(data = land_sf, aes(fill = state)) +
-  scale_fill_manual(values = state_pallet) +
-  my_ggtheme_m(leg_pos = "right")
 
@@
 
-x <- as.data.frame(st_read(my_path("D", "Partial/grid_fp",name="grid_eez_fp.shp"))) %>% 
-  select(index,spp = spcs_nm,port_name = port_nm, abrev = stt_pst) %>% 
+x <- as.data.frame(st_read(here("Data/Processed/grid_fp/grid_eez_fp.shp"))) %>% 
+  select(index, spp, port_name, abrev) %>% 
   bind_cols(
-    as.data.frame(st_coordinates(st_read(my_path("D", "Partial/grid_fp",name="grid_eez_fp.shp"))))
+    as.data.frame(st_coordinates(st_read(here("Data/Processed/grid_fp/grid_eez_fp.shp"))))
   ) %>% 
@@
 
-write_csv(x,my_path("D", "Partial/grid_fp",name="grid_eez_fp_df.csv"))
+# write_csv(x,my_path("D", "Partial/grid_fp",name="grid_eez_fp_df.csv"))
 
@@
 grids_sw <- bind_rows(
-  my_path("G", "AcrossBoundaries/Data/Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
+  read_csv(here("Data/Processed/grid_sw/grid_eez_sw_df.csv")) %>% 
     mutate(spp = "Paralichthys dentatus"),
-  my_path("G", "AcrossBoundaries/Data/Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
+  read_csv(here("Data/Processed/grid_sw/grid_eez_sw_df.csv")) %>% 
     mutate(spp = "Stenotomus chrysops"),
-  my_path("G", "AcrossBoundaries/Data/Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
+  read_csv(here("Data/Processed/grid_sw/grid_eez_sw_df.csv")) %>% 
     mutate(spp = "Centropristis striata")
@@
 
-grids_fp <- my_path("G", "AcrossBoundaries/Data/Partial/grid_fp", name = "grid_eez_fp_df.csv", read = T
-) %>%
+grids_fp <- read_csv(here("Data/Processed/grid_fp/grid_eez_fp_df.csv")) %>%
   mutate(spatial = "fp",
@@
 # Ports data
-ports_df <- my_path("G","AcrossBoundaries/Data/Partial", "top_ports.csv", read = T) %>% 
-  filter(tresh == "25th") %>%
+ports_df <- read_csv(here("Data/Processed/top_ports.csv")) %>% 
+  filter(tresh == "75th") %>% # this selects the top 25%
   group_by(species_name,state_postal) %>% 
@@
 
-spp_paths <- list.files(my_path("G",extra_path = "AcrossBoundaries/Results/Partial/Interpolation/"))
-
-# Some gibiris for names
-taxon_list <- gsub("_"," ",spp_paths)
-taxon_list <- gsub("tif ","",taxon_list)
-taxon_list <- gsub(".csv","",taxon_list)
-
-taxon_list <- taxon_list[taxon_list %in% Species]
-
-# Now set a list of files to read
-taxon_read <- paste0("tif_",taxon_list,".csv")
-taxon_read <- gsub(" ","_",taxon_read)
-
-taxon_read <- spp_paths[spp_paths %in% taxon_read]
+# Get files
+spp_paths <- list.files(here("Data/Processed/Interpolation"),
+                        full.names = T)
 
@@
 
-taxon_sw <- my_path("G",extra_path = "AcrossBoundaries/Results/Partial/Interpolation/", name = taxon_read)
-
 # Load all sp in one table
-historic_spp <- bind_rows(lapply(taxon_sw, fread)) %>% 
+historic_spp <- bind_rows(lapply(spp_paths, fread)) %>% 
   left_join(grids,
@@
 # re order states by latitude
-land_sf_t <- land_sf
-
-land_sf_t$group <- factor(land_sf_t$abrev,      # Reordering group factor levels
+land_sf$group <- factor(land_sf$abrev,      # Reordering group factor levels
                                levels = state_lat$abrev)
 
- land_sf_t <- land_sf_t %>% 
+ land_sf_to_plot <- land_sf %>% 
   left_join(state_lat) %>% 
@@
 
- # Plot figure
-study_plot <-
-  ggplot() +
+ # Plot figure 0 ( NewFig 1)
+study_plot <- ggplot() +
   geom_sf(data = us_map, aes(),fill = "grey", color = "lightgrey") +
-  geom_sf(data = land_sf_t, aes(fill = reorder(name,-order))) +
+  geom_sf(data = land_sf_to_plot, aes(fill = reorder(name,-order))) +
   scale_fill_manual("State",
@@
 
-my_path("D","Partial","top_ports.csv", read = T) %>% 
-  filter(tresh == "25th",
+read_csv(here("Data/Processed/top_ports.csv")) %>% 
+  filter(tresh == "75th",
          state_postal == "NY") %>% 
@@
 # Load grid of state waters
-grid_eez_sw_sf <-  st_read(my_path("G","AcrossBoundaries/Data/Partial/grid_sw", name = "grid_eez_sw_sf.shp")) %>%
+grid_eez_sw_sf <-  st_read(here("Data/Processed/grid_sw/grid_eez_sw_sf.shp")) %>%
   select(index,state,geometry) %>% 
@@
 # Load grid of fishing ports
-grid_eez_fp_sf <-  st_read(my_path("G","AcrossBoundaries/Data/Partial/grid_fp", name = "grid_eez_fp.shp")) %>%
+grid_eez_fp_sf <-  st_read(here("Data/Processed/grid_fp/grid_eez_fp_sf.shp")) %>%
   select(index,abrev,geometry) %>% 
@@
 
-top_ports_sen <- my_path("G","AcrossBoundaries/Data/Partial","top_ports.csv", read = T)
+top_ports_sen <- read_csv(here("Data/Processed/top_ports.csv"))
 
@@
         strip.background = element_rect(fill = "grey"))+
-  labs(y = "Number of grid-cells (n)", x = "Threshold") +
+  labs(y = "Number of grid-cells (n)", x = "Top Ports") +
   scale_fill_brewer(palette = "Set3")
@@
 ```
+
 # Old code

### 2023-01-03 Scripts/spatial_analisis.Rmd
Get percentage of data included for each port

@@
 
-*License???.*
-
 ```{r}
@@
 
-ports_path <- my_path("G","AcrossBoundaries/Data/NOAA", name = "PalaciosJ - BSB, SFlounder, Scup by Port 1970-2020 - 2021.10.25.xlsx")
+ports_path <- here("Data/Raw/ACCSP/PalaciosJ - BSB, SFlounder, Scup by Port 1970-2020 - 2021.10.25.xlsx")
 
@@
 )
+
+# get percentage for revisions
+
+overall_port_data %>% 
+  group_by(species_name) %>% 
+  summarise(total = sum(year_ton),
+            n_tot = n()) %>% 
+  left_join(top_ports) %>% 
+  filter(tresh == "25th") %>% 
+  group_by(species_name,total,n_tot) %>% 
+  summarise(top_sum = sum(year_ton),
+            n_top =n()
+            ) %>% 
+  mutate(round(top_sum/total,2),
+         round(n_top/n_tot,2))
 
